### 2020-09-24 reanalysis.Rmd
first commit

---
title: "Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the fallacy of the null hypothesis"
shorttitle: "The fallacy of the null"

author: 
  - name: Ladislas Nalborczyk
    affiliation: 1
    corresponding: yes
    address: GIPSA-lab, CNRS, Univ. Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France
    email: ladislas.nalborczyk@gipsa-lab.fr

affiliation:
  - id: 1
    institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France

abstract: "Blah blah... Complete source code, reproducible analyses, and figures are available at https://osf.io/ntmgv/."

keywords: NHST, Bayesian, fallacy, reanalysis

csl: csl/apa7.csl
classoption: man
linenumbers: yes
floatsintext: yes
link-citations: true
numbersections: false

bibliography: [bib/brms_tutorial.bib, bib/r-references.bib]

nocite: | 
  @R-base, @R-knitr, @R-rmarkdown, @R-tidyverse, @R-papaja, @R-wordcountaddin,
  @R-here

output:
  papaja::apa6_pdf:
    keep_tex: true
    highlight: tango
    latex_engine: xelatex
---

```{r setup, message = FALSE, warning = FALSE, results = "hide"}
library(wordcountaddin)
library(rethinking)
library(extrafont)
library(rmarkdown)
library(tidyverse)
library(patchwork)
library(bayesplot)
library(ggExtra)
library(papaja)
library(knitr)
library(here)
library(brms)

# setting seed for reproducibility
set.seed(666)

# setting up knitr options
knitr::opts_chunk$set(
  cache = TRUE, eval = TRUE, echo = FALSE,
  warning = FALSE, message = FALSE,
  fig.align = "center", dev = "pdf",
  out.width = "75%", fig.pos = "!htb"
  )

# counting words in the current .Rmd file
wordcount <- word_count(knitr::current_input() )
```

Wordcount (excluding abstract, references, tables, and figures): `r wordcount`

\newpage

<!-- NB: You can add comments using these tags -->

# Introduction

...

# Conclusions

...

# Supplementary materials {#supp}

Supplementary materials, data, reproducible code and figures are available at https://osf.io/ntmgv/.

# Acknowledgements {-}

...

# References {-}

```{r create_r_references, cache = FALSE}
r_refs(file = "bib/r-references.bib")
```

### 2020-09-24 reanalysis.tex
first commit

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Re-analysing the data from Moffatt et al.~(2020): A textbook illustration of the fallacy of the null hypothesis},
  pdflang={en-EN},
  pdfkeywords={NHST, Bayesian, fallacy, reanalysis},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

% Table formatting
\usepackage{longtable}
\usepackage{lscape}
% \usepackage[counterclockwise]{rotating}   % Landscape page setup for large tables
\usepackage{multirow}		% Table styling
\usepackage{tabularx}		% Control Column width
\usepackage[flushleft]{threeparttable}	% Allows for three part tables with a specified notes section
\usepackage{threeparttablex}            % Lets threeparttable work with longtable

% Create new environments so endfloat can handle them
% \newenvironment{ltable}
%   {\begin{landscape}\begin{center}\begin{threeparttable}}
%   {\end{threeparttable}\end{center}\end{landscape}}
\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}

% Enables adjusting longtable caption width to table width
% Solution found at http://golatex.de/longtable-mit-caption-so-breit-wie-die-tabelle-t15767.html
\makeatletter
\newcommand\LastLTentrywidth{1em}
\newlength\longtablewidth
\setlength{\longtablewidth}{1in}
\newcommand{\getlongtablewidth}{\begingroup \ifcsname LT@\roman{LT@tables}\endcsname \global\longtablewidth=0pt \renewcommand{\LT@entry}[2]{\global\advance\longtablewidth by ##2\relax\gdef\LastLTentrywidth{##2}}\@nameuse{LT@\roman{LT@tables}} \fi \endgroup}

% \setlength{\parindent}{0.5in}
% \setlength{\parskip}{0pt plus 0pt minus 0pt}

% \usepackage{etoolbox}
\makeatletter
\patchcmd{\HyOrg@maketitle}
  {\section{\normalfont\normalsize\abstractname}}
  {\section*{\normalfont\normalsize\abstractname}}
  {}{\typeout{Failed to patch abstract.}}
\makeatother
\shorttitle{The fallacy of the null}
\author{Ladislas Nalborczyk\textsuperscript{1}}
\affiliation{
\vspace{0.5cm}
\textsuperscript{1} Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France}
\authornote{

Correspondence concerning this article should be addressed to Ladislas Nalborczyk, GIPSA-lab, CNRS, Univ. Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France. E-mail: ladislas.nalborczyk@gipsa-lab.fr}
\keywords{NHST, Bayesian, fallacy, reanalysis}
\usepackage{lineno}

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newenvironment{cslreferences}%
  {\setlength{\parindent}{0pt}%
  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
  {\par}

\title{Re-analysing the data from Moffatt et al.~(2020): A textbook illustration of the fallacy of the null hypothesis}

\date{}

\abstract{
Blah blah\ldots{} Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ntmgv/}.
}

\begin{document}
\maketitle

Wordcount (excluding abstract, references, tables, and figures): 29

\newpage

\hypertarget{introduction}{%
\section{Introduction}\label{introduction}}

\ldots{}

\hypertarget{conclusions}{%
\section{Conclusions}\label{conclusions}}

\ldots{}

\hypertarget{supp}{%
\section{Supplementary materials}\label{supp}}

Supplementary materials, data, reproducible code and figures are available at \url{https://osf.io/ntmgv/}.

\hypertarget{acknowledgements}{%
\section*{Acknowledgements}\label{acknowledgements}}
\addcontentsline{toc}{section}{Acknowledgements}

\ldots{}

\hypertarget{references}{%
\section*{References}\label{references}}
\addcontentsline{toc}{section}{References}

\hypertarget{refs}{}
\begin{cslreferences}
\leavevmode\hypertarget{ref-R-papaja}{}%
Aust, F., \& Barth, M. (2017). \emph{papaja: Create APA manuscripts with R Markdown}. \url{https://github.com/crsh/papaja}

\leavevmode\hypertarget{ref-R-wordcountaddin}{}%
Marwick, B. (2019). \emph{Wordcountaddin: Word counts and readability statistics in r markdown documents}.

\leavevmode\hypertarget{ref-R-here}{}%
Müller, K. (2017). \emph{Here: A simpler way to find your files}. \url{https://CRAN.R-project.org/package=here}

\leavevmode\hypertarget{ref-R-base}{}%
R Core Team. (2017). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}

\leavevmode\hypertarget{ref-R-tidyverse}{}%
Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. \url{https://CRAN.R-project.org/package=tidyverse}

\leavevmode\hypertarget{ref-R-knitr}{}%
Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Chapman; Hall/CRC. \url{https://yihui.org/knitr/}

\leavevmode\hypertarget{ref-R-rmarkdown}{}%
Xie, Y., Allaire, J. J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Chapman; Hall/CRC. \url{https://bookdown.org/yihui/rmarkdown}
\end{cslreferences}

\end{document}

### 2020-09-24 reanalysis.R

@@ -1,0 +1,659 @@
+library(ggbeeswarm)
+library(tidyverse)
+library(patchwork)
+library(magrittr)
+library(parallel)
+library(readxl)
+library(papaja)
+library(dplyr)
+library(knitr)
+library(BEST)
+library(here)
+library(glue)
+library(brms)
+
+# imports data
+df <- read_excel("data/RUM_master_data.xlsx")
+
+# position for groups
+pd <- position_dodge(0.8)
+
+# plotting for order 1 (BAS>DIS>RUM)
+p1 <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    filter(order == 1) %>%
+    mutate(order = as.factor(order) ) %>%
+    # plots the data
+    ggplot(aes(x = condition, y = value) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.2,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        # draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    geom_dotplot(
+        stackdir = "center",
+        binaxis = "y",
+        position = pd,
+        # binwidth = 1,
+        dotsize = 1,
+        alpha = 0.3
+        ) +
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        aes(group = order),
+        position = pd,
+        show.legend = FALSE
+        ) +
+    # plotting means
+    stat_summary(
+        fun.y = "mean", geom = "point", shape = 16, size = 3,
+        position = pd,
+        show.legend = TRUE
+        ) +
+    # plotting confidence intervals
+    stat_summary(
+        fun.data = mean_cl_normal,
+        geom = "errorbar", size = 1, width = 0,
+        fun.args = list(mult = 1.96),
+        show.legend = FALSE,
+        position = pd
+        ) +
[…]

### 2020-09-25 reanalysis.R
minor updates

@@ -1,3 +1,11 @@
+################################################################
+# Reanalysing the data from Moffatt et al. (2020)
+# ----------------------------------------------------------
+# Ladislas Nalborczyk
+# Last updated on 23.09.2020
+# https://github.com/lnalborczyk/inner_experience_EMG
+#########################################################
+
 library(ggbeeswarm)
 library(tidyverse)
 library(patchwork)
@@ -400,7 +408,8 @@ pp_check(varying_effects, resp = "OOI")
 # simulating data from the posterior
 # (for new, that is, non-observed, participants from the same population)
 # https://bookdown.org/content/4857/models-with-memory.html#multilevel-posterior-predictions
-################################################################################################
+# https://bookdown.org/content/4857/models-with-memory.html#posterior-prediction-for-new-clusters
+###################################################################################################
 
 # extracting posterior samples from varying-effects model
 post <- posterior_samples(varying_effects)
@@ -408,8 +417,30 @@ post <- posterior_samples(varying_effects)
 # number of simulated participants
 n_ppts <- 200
 
-# what are the conditions?
-nd <- distinct(df2, condition) %>% arrange(condition)
+# for the 3 initials conditions and 200 new participants
+# nd <- distinct(df2, condition) %>% arrange(condition)
+nd <- crossing(distinct(df2, condition), data.frame(ID = 101:(101 + n_ppts - 1) ) )
+
+# simulating data
+# simulated_data <- fitted(
+#     varying_effects,
+#     newdata = nd,
+#     # probs = c(.1, .9),
+#     allow_new_levels = TRUE,
+#     sample_new_levels = "gaussian",
+#     summary = FALSE,
+#     # nsamples = n_ppts
+#     nsamples = 1
+#     ) %>% 
+#     data.frame() %>%
+#     # set_names(1:4) %>%
+#     # mutate(iter = 1:n_ppts) %>% 
+#     # pivot_longer(-iter) %>%
+#     pivot_longer(cols = 1:ncol(.) ) %>%
+#     # mutate(ID = rep(101:200, 3) ) %>% head
+#     separate(col = name, into = c("condition", "muscle"), sep = "\\.") %>%
+#     mutate(condition = factor(condition, labels = nd$condition) ) %>%
[…]

### 2020-09-28 reanalysis.Rmd
minor updates in manuscript and reanalysis script

@@
 shorttitle: "The fallacy of the null"
-
 author: 
@@
     email: ladislas.nalborczyk@gipsa-lab.fr
-
 affiliation:
@@
     institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France
-
-abstract: "Blah blah... Complete source code, reproducible analyses, and figures are available at https://osf.io/ntmgv/."
-
-keywords: NHST, Bayesian, fallacy, reanalysis
-
+abstract: "Moffatt et al.
+(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressful event.
+Based on the observation...
+We show ou this conclusion seems at best hasty...
+Indeed, concluding on the null, relation between self-reports and physiological measures...
+Although the question Moffatt et al.
+(2020) pursued if of interest, and mehods...
+it is unclear whether this contribution really adds to the current knowledge...
+Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
+keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
 csl: csl/apa7.csl
@@
 numbersections: false
-
 bibliography: [bib/brms_tutorial.bib, bib/r-references.bib]
-
 nocite: | 
@@
   @R-here
-
 output:
@@
     latex_engine: xelatex
+editor_options: 
+  chunk_output_type: console
 ---
 
-```{r setup, message = FALSE, warning = FALSE, results = "hide"}
+```{r setup, include = FALSE, message = FALSE, warning = FALSE}
 library(wordcountaddin)
-library(rethinking)
-library(extrafont)
+library(ggbeeswarm)
 library(rmarkdown)
@@
 library(papaja)
+library(readxl)
 library(knitr)
+library(BEST)
 library(here)
-library(brms)
+library(glue)
 
@@
   fig.align = "center", dev = "pdf",
-  out.width = "75%", fig.pos = "!htb"
+  out.width = "100%", fig.pos = "!htb"
   )
@@
 
-# Conclusions
+# Some thoughts on the data
+
+```{r importing_data}
+# importing data
+df <- read_excel("data/RUM_master_data.xlsx")
+
+# data reshaping (from wide to long)
+# NB: 26 participants in the final dataset...
+
+df2 <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    # extracts muscle name
+    mutate(muscle = substr(muscle, 1, 3) ) %>%
+    # from long to wide
+    pivot_wider(names_from = muscle, values_from = value)
+```
+
+```{r babar, fig.cap = "General plot (N = 26)..."}
+# position for groups
+pd <- position_dodge(0.8)
+
+# plotting the dtaa
+df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    # mutate(order = factor(order) ) %>%
+    # plots the data
+    ggplot(aes(x = condition, y = value) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.2,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        # draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    geom_dotplot(
+        stackdir = "center",
+        binaxis = "y",
+        position = pd,
+        # binwidth = 1,
+        dotsize = 0.5,
+        alpha = 0.3
+        ) +
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        # aes(group = interaction(muscle, order) ),
+        aes(group = muscle),
+        position = pd,
+        show.legend = FALSE
+        ) +
+    # plotting means
+    stat_summary(
+        fun.y = "mean",
+        geom = "point", shape = 16, size = 3,
+        position = pd,
+        show.legend = TRUE
+        ) +
+    # plotting confidence intervals
+    stat_summary(
+        fun.data = mean_cl_normal,
+        geom = "errorbar", size = 1, width = 0,
+        fun.args = list(mult = 1.96),
+        show.legend = FALSE,
+        position = pd
+        ) +
+    # geom_point(alpha = 0.25, size = 0.5) + 
+    # alxtheme +
+    facet_grid(~muscle, scales = "free") +
+    # scale_color_manual (values = colors2) +
+    # scale_fill_manual (values = colors2) +
+    labs(x = "Condition", y = "EMG log-amplitude") +
+    # theme(legend.title = element_blank() ) +
+    # forces lower xlim to 0
+    # coord_cartesian(xlim = c(0, 1) ) +
+    theme_bw(base_size = 12) +
+    scale_colour_brewer(palette = "Dark2", direction = 1) +
+    scale_fill_brewer(palette = "Dark2", direction = 1)
+```
+
+...
+
+## Concluding on the null from low-powered studies
+
+https://theethicalskeptic.com/2015/08/17/the-four-types-of-null-hypothesis-fallacy/...
+
+```{r}
+# importing data
+# df <- read_excel("data/RUM_master_data.xlsx")
+```
+
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
+
+> "In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
+This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (B10 = 18.79), and moderate evidence in favour of the null hypothesis for the OOS (B10 = 0.232) and OOI (B10 = 0.278) muscles, according to current guidelines for interpreting Bayes factors [43]."
+
+...
+
+## Does everyone?
+
+...
+
+```{r everyone, fig.cap = "General plot (mean and 95\\% CI)... showing the inter-individual variability..."}
+# does everyone plot
+df2 %>%
+    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
+    pivot_wider(names_from = condition, values_from = value) %>%
+    mutate(ruminator = ifelse(RUM > DIS, 1, 0) ) %>%
+    mutate(ruminator = as.factor(ruminator) ) %>%
+    pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
+    ggplot(aes(x = condition, y = value, colour = ruminator, fill = ruminator) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.2,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        # draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    # geom_quasirandom(alpha = 0.3) +
+    geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
+    geom_line(aes(group = ID), size = 1, alpha = 0.8, show.legend = FALSE) +
+    # plitting the by-group mean
+    # stat_summary(
+    #     fun.y = mean,
+    #     geom = "line", size = 2,
+    #     aes(group = interaction(muscle, ruminator) ),
+    #     position = pd,
+    #     show.legend = FALSE
+    #     ) +
+    # plotting means
+    # stat_summary(
+    #     fun.y = "mean",
+    #     geom = "point", shape = 16, size = 4,
+    #     position = pd,
+    #     show.legend = TRUE
+    #     ) +
+    # plotting confidence intervals
+    # stat_summary(
+    #     fun.data = mean_cl_normal,
+    #     geom = "errorbar", size = 2, width = 0,
+    #     fun.args = list(mult = 1.96),
+    #     show.legend = FALSE,
+    #     position = pd
+    #     ) +
+    # facetting by muscle
+    facet_wrap(~muscle) +
+    # axis labels
+    labs(x = "Condition", y = "EMG log-amplitude") +
+    # forces lower xlim to 0
+    # coord_cartesian(xlim = c(0, 1) ) +
+    theme_bw(base_size = 12) +
+    scale_colour_brewer(palette = "Dark2", direction = -1) +
+    scale_fill_brewer(palette = "Dark2", direction = -1)
+```
+
+Huge inter-individual variability... which leads to the next point, what is the relation between self-reports and EMG?
+
+## Relation between self-report and EMG correlates
+
+...
+
+# Discussion and conclusions
 
@@
 
-Supplementary materials, data, reproducible code and figures are available at https://osf.io/ntmgv/.
+Reproducible code and figures are available at https://github.com/lnalborczyk/inner_experience_EMG.
 

### 2020-09-28 reanalysis.tex
minor updates in manuscript and reanalysis script

@@
   pdflang={en-EN},
-  pdfkeywords={NHST, Bayesian, fallacy, reanalysis},
+  pdfkeywords={NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography},
   hidelinks,
@@
 E-mail: ladislas.nalborczyk@gipsa-lab.fr}
-\keywords{NHST, Bayesian, fallacy, reanalysis}
+\keywords{NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography}
 \usepackage{lineno}
@@
 \abstract{
-Blah blah\ldots{} Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ntmgv/}.
+Moffatt et al.~(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of induced rumination and distraction, following a stressful event.
+Based on the observation\ldots{} We show ou this conclusion seems at best hasty\ldots{} Indeed, concluding on the null, relation between self-reports and physiological measures\ldots{} Although the question Moffatt et al.~(2020) pursued if of interest, and mehods\ldots{} it is unclear whether this contribution really adds to the current knowledge\ldots{} Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
 }
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 29
+Wordcount (excluding abstract, references, tables, and figures): 107
 
@@
 
-\hypertarget{conclusions}{%
-\section{Conclusions}\label{conclusions}}
+\hypertarget{some-thoughts-on-the-data}{%
+\section{Some thoughts on the data}\label{some-thoughts-on-the-data}}
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/babar-1}
+
+}
+
+\caption{General plot (N = 26)...}\label{fig:babar}
+\end{figure}
+
+\ldots{}
+
+\hypertarget{concluding-on-the-null-from-low-powered-studies}{%
+\subsection{Concluding on the null from low-powered studies}\label{concluding-on-the-null-from-low-powered-studies}}
+
+\url{https://theethicalskeptic.com/2015/08/17/the-four-types-of-null-hypothesis-fallacy/}\ldots{}
+
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+
+\hypertarget{does-everyone}{%
+\subsection{Does everyone?}\label{does-everyone}}
+
+\ldots{}
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/everyone-1}
+
+}
+
+\caption{General plot (mean and 95\% CI)... showing the inter-individual variability...}\label{fig:everyone}
+\end{figure}
+
+Huge inter-individual variability\ldots{} which leads to the next point, what is the relation between self-reports and EMG?
+
+\hypertarget{relation-between-self-report-and-emg-correlates}{%
+\subsection{Relation between self-report and EMG correlates}\label{relation-between-self-report-and-emg-correlates}}
+
+\ldots{}
+
+\hypertarget{discussion-and-conclusions}{%
+\section{Discussion and conclusions}\label{discussion-and-conclusions}}
 
@@
 
-Supplementary materials, data, reproducible code and figures are available at \url{https://osf.io/ntmgv/}.
+Reproducible code and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
 

### 2020-09-28 reanalysis.R

@@ -295,6 +295,63 @@ df2 <- df %>%
     # from long to wide
     pivot_wider(names_from = muscle, values_from = value)
 
+# plotting the baseline-normalised EMG-aplitude
+df2 %>%
+    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
+    pivot_wider(names_from = condition, values_from = value) %>%
+    mutate(DIS_bas = DIS - BAS, RUM_bas = RUM - BAS) %>%
+    select(ID, order, muscle, DIS_bas, RUM_bas) %>%
+    pivot_longer(cols = DIS_bas:RUM_bas, names_to = "condition") %>%
+    ggplot(aes(x = condition, y = value) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.2,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        # draw_quantiles = 0.5,
+        show.legend = FALSE
+    ) +
+    # plotting individual data points
+    geom_quasirandom(alpha = 0.3) +
+    # plitting the by-group mean
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        aes(group = muscle),
+        position = pd,
+        show.legend = FALSE
+    ) +
+    # plotting means
+    stat_summary(
+        fun.y = "mean",
+        geom = "point", shape = 16, size = 3,
+        position = pd,
+        show.legend = TRUE
+    ) +
+    # plotting confidence intervals
+    stat_summary(
+        fun.data = mean_cl_normal,
+        geom = "errorbar", size = 1, width = 0,
+        fun.args = list(mult = 1.96),
+        show.legend = FALSE,
+        position = pd
+    ) +
+    # facetting by muscle
+    facet_wrap(~muscle) +
+    # axis labels
+    labs(
+        x = "Condition", y = "EMG log-amplitude",
+        title = paste0("General plot for (mean and 95% CI)")
+    ) +
+    # forces lower xlim to 0
+    # coord_cartesian(xlim = c(0, 1) ) +
+    theme_bw(base_size = 12) +
+    scale_colour_brewer(palette = "Dark2", direction = 1) +
+    scale_fill_brewer(palette = "Dark2", direction = 1)
+
 #############################################
 # Bayesian multilevel models
 ########################################
@@ -360,7 +417,7 @@ plotPost(
[…]

### 2020-09-29 reanalysis.Rmd
bf simulation

@@
 title: "Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the fallacy of the null hypothesis"
+
 shorttitle: "The fallacy of the null"
+
 author: 
@@
     institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France
+
 abstract: "Moffatt et al.
-(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressful event.
-Based on the observation...
-We show ou this conclusion seems at best hasty...
-Indeed, concluding on the null, relation between self-reports and physiological measures...
+(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on an absence of significant difference in the perioral EMG-amplitude between the rumination and distraction conditions, Moffatt et al.
+(2020) concluded that (the *self-reported*) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+We suggest this conclusion is hasty and based on waggly evidence.
+Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
+Moreover, there relation between self-reports and physiological measures...
 Although the question Moffatt et al.
-(2020) pursued if of interest, and mehods...
-it is unclear whether this contribution really adds to the current knowledge...
+(2020) pursued is of interest, and mehods...
+Given these limitations, it is unclear whether the target article really adds to the current knowledge.
 Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
+
 keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
+
 csl: csl/apa7.csl
@@
 bibliography: [bib/brms_tutorial.bib, bib/r-references.bib]
+
 nocite: | 
@@
   @R-here
+
 output:
@@
     latex_engine: xelatex
-editor_options: 
-  chunk_output_type: console
 ---

### 2020-09-29 reanalysis.tex
bf simulation

@@
 \abstract{
-Moffatt et al.~(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of induced rumination and distraction, following a stressful event.
-Based on the observation\ldots{} We show ou this conclusion seems at best hasty\ldots{} Indeed, concluding on the null, relation between self-reports and physiological measures\ldots{} Although the question Moffatt et al.~(2020) pursued if of interest, and mehods\ldots{} it is unclear whether this contribution really adds to the current knowledge\ldots{} Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
+Moffatt et al.~(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on an absence of significant difference in the perioral EMG-amplitude between the rumination and distraction conditions, Moffatt et al.~(2020) concluded that (the \emph{self-reported}) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+We suggest this conclusion is hasty and based on waggly evidence.
+Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
+Moreover, there relation between self-reports and physiological measures\ldots{} Although the question Moffatt et al.~(2020) pursued is of interest, and mehods\ldots{} Given these limitations, it is unclear whether the target article really adds to the current knowledge.
+Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
 }
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 107
+Wordcount (excluding abstract, references, tables, and figures): 184
 
@@
 Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+
+\begin{quote}
+``In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
+This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (B10 = 18.79), and moderate evidence in favour of the null hypothesis for the OOS (B10 = 0.232) and OOI (B10 = 0.278) muscles, according to current guidelines for interpreting Bayes factors {[}43{]}.''
+\end{quote}
+
+\ldots{}
 

### 2020-09-29 reanalysis.R

@@ -1,10 +1,10 @@
-################################################################
-# Reanalysing the data from Moffatt et al. (2020)
-# ----------------------------------------------------------
-# Ladislas Nalborczyk
-# Last updated on 23.09.2020
-# https://github.com/lnalborczyk/inner_experience_EMG
-#########################################################
+#######################################################
+# Reanalysing the data from Moffatt et al. (2020)     #
+# --------------------------------------------------- #
+# Ladislas Nalborczyk                                 #
+# Last updated on 28.09.2020                          #
+# https://github.com/lnalborczyk/inner_experience_EMG #
+#######################################################
 
 library(ggbeeswarm)
 library(tidyverse)
@@ -352,9 +352,9 @@ df2 %>%
     scale_colour_brewer(palette = "Dark2", direction = 1) +
     scale_fill_brewer(palette = "Dark2", direction = 1)
 
-#############################################
-# Bayesian multilevel models
-########################################
+##############################
+# Bayesian multilevel models #
+##############################
 
 # priors for the constant-effects model
 priors_constant <- c(
@@ -695,14 +695,14 @@ simulated_data_varying_effects <- update(
     # family = gaussian(),
     # prior = priors_varying,
     # prior = priors_simulated_data,
-    data = simulated_data_wide,
+    newdata = simulated_data_wide,
     chains = 4,
     cores = parallel::detectCores(),
     warmup = 2000, iter = 5000,
     control = list(adapt_delta = 0.99),
     sample_prior = TRUE,
     file = here("models/simulated_data_varying_effects")
-)
+    )
 
 # model summary
 summary(simulated_data_varying_effects)
@@ -741,23 +741,23 @@ plot(hyp_ooi, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
 post <- posterior_samples(simulated_data_varying_effects)
 
 plotPost(
-    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS
-    # compVal = 0, ROPE = c(-0.1, 0.1)
+    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS,
+    compVal = 0, ROPE = c(-0.1, 0.1)
     )
 
 plotPost(
[…]

### 2020-09-29 reanalysis.Rmd
updating abstract and introduction

--- 2020-09-24 reanalysis.Rmd
@@
 ---
-title: "Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the fallacy of the null hypothesis"
+title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the fallacy of the null hypothesis"
+
 shorttitle: "The fallacy of the null"
@@
 
-abstract: "Blah blah... Complete source code, reproducible analyses, and figures are available at https://osf.io/ntmgv/."
+abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that (the *self-reported*) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+We suggest this conclusion is hasty and based on waggly evidence.
+Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
+Moreover, the relation between self-reports and physiological measures was not *directly* assessed, but only indirectly inferred from differences (or absence thereof) in group means.
+Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiolgogical measures from group means is inappropriate.
+Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways foward, both from a theoretical and from a methodological perspective.
+Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
 
-keywords: NHST, Bayesian, fallacy, reanalysis
+keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
 
@@
 numbersections: false
-
-bibliography: [bib/brms_tutorial.bib, bib/r-references.bib]
+bibliography: [bib/library.bib, bib/r-references.bib]
 
@@
 
-```{r setup, message = FALSE, warning = FALSE, results = "hide"}
+```{r setup, include = FALSE, message = FALSE, warning = FALSE}
 library(wordcountaddin)
-library(rethinking)
-library(extrafont)
+library(ggbeeswarm)
 library(rmarkdown)
@@
 
+The activity of silently talking to oneself or "inner speech" is a foundational ability...
+despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative...
+These inner speech "dysfunctions"...
+
+@moffatt_inner_2020, @loevenbruck_cognitive_2018, @grandchamp_condialint_2019, @alderson-day_inner_2015, @wilkinson_auditory_2017, and @perrone-bertolotti_what_2014, @nalborczyk_can_2020, @nalborczyk_introduction_2019, @nalborczyk_orofacial_2017, @nalborczyk_understanding_2019...
+
+The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech".
+In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on...
+Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
+That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
+This suggests unexplored variation in the determinants of this effects (e.g., the content of the inner experience).
+Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
+However, given the previous point, this appears highly problematic.
+We explore each of these limitations and suggests ways forward in the following section.
+
+# Exploring the data
+
+```{r importing_data}
+# importing data
+df <- read_excel(path = "data/RUM_master_data.xlsx", sheet = 1)
+
+# importing codebook
+codebook <- read_excel(path = "data/RUM_master_data.xlsx", sheet = 2)
+
+# data reshaping (from wide to long)
+# NB: 26 participants in the final dataset...
+
+# Order in which rumination and distraction inductions were completed
+# 1 = rumination induction completed first
+# 2 = distraction induction completed first
+
+df2 <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    # extracts muscle name
+    mutate(muscle = substr(muscle, 1, 3) ) %>%
+    # from long to wide
+    pivot_wider(names_from = muscle, values_from = value)
+```
+
+```{r general, fig.cap = "Average log-EMG amplitude by muscle and condition.
+The black dots and intervals represent the by-group average and 95\\% confidence interval (N = 26).
+The horizontal white line in the violin plot represents the median.
+The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition."}
+# position for groups
+pd <- position_dodge(0.8)
+
+# plotting the data
+df2 %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = FRO:OOI,
+        names_to = "muscle",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    mutate(order = factor(order) ) %>%
+    # plots the data
+    ggplot(aes(x = condition, y = value) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.15,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    # geom_dotplot(
+    #     stackdir = "center",
+    #     binaxis = "y",
+    #     position = pd,
+    #     # binwidth = 1,
+    #     dotsize = 0.5,
+    #     alpha = 0.3
+    #     ) +
+    geom_quasirandom(alpha = 0.3) +
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        # aes(group = interaction(muscle, order) ),
+        aes(group = muscle),
+        position = pd,
+        show.legend = FALSE
+        ) +
+    # plotting means
+    stat_summary(
+        fun.y = "mean",
+        geom = "point", shape = 16, size = 3,
+        position = pd,
+        show.legend = TRUE
+        ) +
+    # plotting confidence intervals
+    stat_summary(
+        fun.data = mean_cl_normal,
+        geom = "errorbar", size = 1, width = 0,
+        fun.args = list(mult = 1.96),
+        show.legend = FALSE,
+        position = pd
+        ) +
+    # facet_wrap(~order*muscle, ncol = 3) +
+    facet_wrap(~muscle, ncol = 3) +
+    labs(x = "Condition", y = "EMG log-amplitude") +
+    theme_bw(base_size = 10) +
+    scale_colour_brewer(palette = "Dark2", direction = 1) +
+    scale_fill_brewer(palette = "Dark2", direction = 1)
+```
+
 ...
 
-# Conclusions
+## Concluding on the null from low-powered studies
+
+https://theethicalskeptic.com/2015/08/17/the-four-types-of-null-hypothesis-fallacy/...
+
+```{r}
+# importing data
+# df <- read_excel("data/RUM_master_data.xlsx")
+```
+
+...
+
+> "In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
+This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (B10 = 18.79), and moderate evidence in favour of the null hypothesis for the OOS (B10 = 0.232) and OOI (B10 = 0.278) muscles, according to current guidelines for interpreting Bayes factors [43]."
+
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
+
+```{r order, fig.cap = "Average log-EMG amplitude by muscle and condition.
+The black dots and intervals represent the by-group average and 95\\% confidence interval (N = 26).
+The horizontal white line in the violin plot represents the median.
+The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition."}
+# position for groups
+pd <- position_dodge(0.8)
+
+# plotting the data
+df2 %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = FRO:OOI,
+        names_to = "muscle",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    mutate(order = factor(order, labels = c("RUM -> DIS", "DIS -> RUM")) ) %>%
+    # plots the data
+    ggplot(aes(x = condition, y = value, colour = order, fill = order) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.15,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    # geom_dotplot(
+    #     stackdir = "center",
+    #     binaxis = "y",
+    #     position = pd,
+    #     # binwidth = 1,
+    #     dotsize = 0.5,
+    #     alpha = 0.3
+    #     ) +
+    geom_quasirandom(alpha = 0.3) +
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        aes(group = interaction(muscle, order) ),
+        # aes(group = muscle),
+        position = pd,
+        show.legend = FALSE
+        ) +
+    # plotting means
+    stat_summary(
+        fun.y = "mean",
+        geom = "point", shape = 16, size = 3,
+        position = pd,
+        show.legend = TRUE
+        ) +
+    # plotting confidence intervals
+    stat_summary(
+        fun.data = mean_cl_normal,
+        geom = "errorbar", size = 1, width = 0,
+        fun.args = list(mult = 1.96),
+        show.legend = FALSE,
+        position = pd
+        ) +
+    # facet_wrap(~order*muscle, ncol = 3) +
+    facet_wrap(~muscle, ncol = 3) +
+    labs(x = "Condition", y = "EMG log-amplitude") +
+    theme_bw(base_size = 10) +
+    scale_colour_brewer(palette = "Dark2", direction = 1) +
+    scale_fill_brewer(palette = "Dark2", direction = 1)
+```
+
+...
+
+## Does everyone?
+
+@haaf_developing_2017...
+
+```{r everyone, fig.cap = "Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
+Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
+# does everyone plot
+df2 %>%
+    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
+    pivot_wider(names_from = condition, values_from = value) %>%
+    mutate(ruminator = ifelse(RUM > DIS, 1, 0) ) %>%
+    mutate(ruminator = as.factor(ruminator) ) %>%
+    pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
+    ggplot(aes(x = condition, y = value, colour = ruminator, fill = ruminator) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.15,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    # geom_quasirandom(alpha = 0.3) +
+    geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
+    geom_line(aes(group = ID), size = 0.5, alpha = 0.8, show.legend = FALSE) +
+    # plitting the by-group mean
+    # stat_summary(
+    #     fun.y = mean,
+    #     geom = "line", size = 2,
+    #     aes(group = interaction(muscle, ruminator) ),
+    #     position = pd,
+    #     show.legend = FALSE
+    #     ) +
+    # plotting means
+    # stat_summary(
+    #     fun.y = "mean",
+    #     geom = "point", shape = 16, size = 4,
+    #     position = pd,
+    #     show.legend = TRUE
+    #     ) +
+    # plotting confidence intervals
+    # stat_summary(
+    #     fun.data = mean_cl_normal,
+    #     geom = "errorbar", size = 2, width = 0,
+    #     fun.args = list(mult = 1.96),
+    #     show.legend = FALSE,
+    #     position = pd
+    #     ) +
+    # facetting by muscle
+    facet_wrap(~muscle) +
+    # axis labels
+    labs(x = "Condition", y = "EMG log-amplitude") +
+    theme_bw(base_size = 12) +
+    scale_colour_brewer(palette = "Dark2", direction = -1) +
+    scale_fill_brewer(palette = "Dark2", direction = -1)
+```
+
+Huge inter-individual variability... which leads to the next point, what is the relation between self-reports and EMG?
+
+## Relation between self-report and EMG correlates
+
+...
+
+# Discussion and conclusions
 

### 2020-09-29 reanalysis.tex
updating abstract and introduction

@@
 \hypersetup{
-  pdftitle={Re-analysing the data from Moffatt et al.~(2020): A textbook illustration of the fallacy of the null hypothesis},
+  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the fallacy of the null hypothesis},
   pdflang={en-EN},
@@
 
-\title{Re-analysing the data from Moffatt et al.~(2020): A textbook illustration of the fallacy of the null hypothesis}
+\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the fallacy of the null hypothesis}
 
@@
 \abstract{
-Moffatt et al.~(2020) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
-Based on an absence of significant difference in the perioral EMG-amplitude between the rumination and distraction conditions, Moffatt et al.~(2020) concluded that (the \emph{self-reported}) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that (the \emph{self-reported}) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
 We suggest this conclusion is hasty and based on waggly evidence.
 Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
-Moreover, there relation between self-reports and physiological measures\ldots{} Although the question Moffatt et al.~(2020) pursued is of interest, and mehods\ldots{} Given these limitations, it is unclear whether the target article really adds to the current knowledge.
+Moreover, the relation between self-reports and physiological measures was not \emph{directly} assessed, but only indirectly inferred from differences (or absence thereof) in group means.
+Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiolgogical measures from group means is inappropriate.
+Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways foward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 184
+Wordcount (excluding abstract, references, tables, and figures): 465
 
@@
 
-\ldots{}
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability\ldots{} despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions''\ldots{}
 
-\hypertarget{some-thoughts-on-the-data}{%
-\section{Some thoughts on the data}\label{some-thoughts-on-the-data}}
+Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), Lœvenbruck et al.
+(\protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}), Grandchamp et al.
+(\protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), Alderson-Day and Fernyhough (\protect\hyperlink{ref-alderson-day_inner_2015}{2015}), Wilkinson and Fernyhough (\protect\hyperlink{ref-wilkinson_auditory_2017}{2017}), and Perrone-Bertolotti et al.
+(\protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}), Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_can_2020}{2020}), Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_introduction_2019}{2019}), Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019})\ldots{}
+
+The main conclusion from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech''.
+In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on\ldots{} Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
+That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
+This suggests unexplored variation in the determinants of this effects (e.g., the content of the inner experience).
+Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
+However, given the previous point, this appears highly problematic.
+We explore each of these limitations and suggests ways forward in the following section.
+
+\hypertarget{exploring-the-data}{%
+\section{Exploring the data}\label{exploring-the-data}}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/babar-1}
+{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/general-1}
 
@@
 
-\caption{General plot (N = 26)...}\label{fig:babar}
+\caption{Average log-EMG amplitude by muscle and condition.
+The black dots and intervals represent the by-group average and 95\% confidence interval (N = 26).
+The horizontal white line in the violin plot represents the median.
+The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition.}\label{fig:general}
 \end{figure}
@@
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+\ldots{}
 
@@
 
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/order-1}
+
+}
+
+\caption{Average log-EMG amplitude by muscle and condition.
+The black dots and intervals represent the by-group average and 95\% confidence interval (N = 26).
+The horizontal white line in the violin plot represents the median.
+The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition.}\label{fig:order}
+\end{figure}
+
 \ldots{}
@@
 
-\ldots{}
+Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017})\ldots{}
 
@@
 
-\caption{General plot (mean and 95\% CI)... showing the inter-individual variability...}\label{fig:everyone}
+\caption{Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
+Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
 \end{figure}
@@
 \begin{cslreferences}
+\leavevmode\hypertarget{ref-alderson-day_inner_2015}{}%
+Alderson-Day, B., \& Fernyhough, C.
+(2015).
+Inner speech: Development, cognitive functions, phenomenology, and neurobiology.
+\emph{Psychological Bulletin}, \emph{141}(5), 931--965.
+\url{https://doi.org/10.1037/bul0000021}
+
 \leavevmode\hypertarget{ref-R-papaja}{}%
 Aust, F., \& Barth, M. (2017). \emph{papaja: Create APA manuscripts with R Markdown}. \url{https://github.com/crsh/papaja}
+
+\leavevmode\hypertarget{ref-grandchamp_condialint_2019}{}%
+Grandchamp, R., Rapin, L., Perrone-Bertolotti, M., Pichat, C., Haldin, C., Cousin, E., Lachaux, J.-P., Dohen, M., Perrier, P., Garnier, M., Baciu, M., \& Lœvenbruck, H.
+(2019).
+The ConDialInt Model: Condensation, Dialogality, and Intentionality Dimensions of Inner Speech Within a Hierarchical Predictive Control Framework.
+\emph{Frontiers in Psychology}, \emph{10}.
+\url{https://doi.org/10.3389/fpsyg.2019.02019}
+
+\leavevmode\hypertarget{ref-haaf_developing_2017}{}%
+Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in Bayesian mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
+
+\leavevmode\hypertarget{ref-loevenbruck_cognitive_2018}{}%
+Lœvenbruck, H., Grandchamp, R., Rapin, L., Nalborczyk, L., Dohen, M., Perrier, P., Baciu, M., \& Perrone-Bertolotti, M.
+(2018).
+A cognitive neuroscience view of inner language: To predict and to hear, see, feel.
+In P.
+Langland-Hassan \& A.
+Vicente (Eds.), \emph{Inner speech: New voices} (p.
+37).
+Oxford University Press.
 
@@
 
+\leavevmode\hypertarget{ref-moffatt_inner_2020}{}%
+Moffatt, J., Mitrenga, K.
+J., Alderson-Day, B., Moseley, P., \& Fernyhough, C.
+(2020).
+Inner experience differs in rumination and distraction without a change in electromyographical correlates of inner speech.
+\emph{PLOS ONE}, \emph{15}(9), e0238920.
+\url{https://doi.org/10.1371/journal.pone.0238920}
+
 \leavevmode\hypertarget{ref-R-here}{}%
 Müller, K. (2017). \emph{Here: A simpler way to find your files}. \url{https://CRAN.R-project.org/package=here}
+
+\leavevmode\hypertarget{ref-nalborczyk_understanding_2019}{}%
+Nalborczyk, L. (2019). \emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}PhD Thesis{]}. Univ. Grenoble Alpes \& Ghent University.
+
+\leavevmode\hypertarget{ref-nalborczyk_introduction_2019}{}%
+Nalborczyk, L., Batailler, C., Lœvenbruck, H., Vilain, A., \& Bürkner, P.-C.
+(2019).
+An introduction to Bayesian multilevel models using brms: A case study of gender effects on vowel variability in standard indonesian.
+\emph{Journal of Speech Language and Hearing Research}, \emph{62}(5), 1225--1242.
+\url{https://doi.org/10.1044/2018_JSLHR-S-18-0006}
+
+\leavevmode\hypertarget{ref-nalborczyk_can_2020}{}%
+Nalborczyk, L., Grandchamp, R., Koster, E.
+H.
+W., Perrone-Bertolotti, M., \& Lœvenbruck, H.
+(2020).
+Can we decode phonetic features in inner speech using surface electromyography?
+\emph{PLOS ONE}, \emph{15}(5), e0233282.
+\url{https://doi.org/10.1371/journal.pone.0233282}
+
+\leavevmode\hypertarget{ref-nalborczyk_orofacial_2017}{}%
+Nalborczyk, L., Perrone-Bertolotti, M., Baeyens, C., Grandchamp, R., Polosan, M., Spinelli, E., Koster, E.
+H.
+W., \& Lœvenbruck, H.
+(2017).
+Orofacial electromyographic correlates of induced verbal rumination.
+\emph{Biological Psychology}, \emph{127}, 53--63.
+\url{https://doi.org/10.1016/j.biopsycho.2017.04.013}
+
+\leavevmode\hypertarget{ref-perrone-bertolotti_what_2014}{}%
+Perrone-Bertolotti, M., Rapin, L., Lachaux, J.
+P., Baciu, M., \& Lœvenbruck, H.
+(2014).
+What is that little voice inside my head?
+Inner speech phenomenology, its role in cognitive performance, and its relation to self-monitoring.
+\emph{Behavioural Brain Research}, \emph{261}, 220--239.
+\url{https://doi.org/10.1016/j.bbr.2013.12.034}
 
@@
 Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. \url{https://CRAN.R-project.org/package=tidyverse}
+
+\leavevmode\hypertarget{ref-wilkinson_auditory_2017}{}%
+Wilkinson, S., \& Fernyhough, C.
+(2017).
+Auditory verbal hallucinations and inner speech: A predictive processing perspective.
+In Z.
+Radman (Ed.), \emph{Before Consciousness: In Search of the Fundamentals of Mind}.
+Imprint Academic, Ltd.
 

### 2020-09-29 reanalysis.R

@@ -2,7 +2,7 @@
 # Reanalysing the data from Moffatt et al. (2020)     #
 # --------------------------------------------------- #
 # Ladislas Nalborczyk                                 #
-# Last updated on 28.09.2020                          #
+# Last updated on 29.09.2020                          #
 # https://github.com/lnalborczyk/inner_experience_EMG #
 #######################################################
 
@@ -812,61 +812,85 @@ simulating_bfs <- function (n_obs) {
         "FRO_conditionRUM - FRO_conditionDIS = 0"
         )
     
-    bf_fro <- 1 / bf_hyp_fro$hypothesis$Evid.Ratio # %>% as.numeric
+    bf_fro <- 1 / bf_hyp_fro$hypothesis$Evid.Ratio
     
     bf_hyp_ooi <- hypothesis(
         bf_simulated_data_varying_effects,
         "OOI_conditionRUM - OOI_conditionDIS = 0"
         )
     
-    bf_ooi <- 1 / bf_hyp_ooi$hypothesis$Evid.Ratio # %>% as.numeric
+    bf_ooi <- 1 / bf_hyp_ooi$hypothesis$Evid.Ratio
     
     bf_hyp_oos <- hypothesis(
         bf_simulated_data_varying_effects,
         "OOS_conditionRUM - OOS_conditionDIS = 0"
         )
     
-    bf_oos <- 1 / bf_hyp_oos$hypothesis$Evid.Ratio # %>% as.numeric
+    bf_oos <- 1 / bf_hyp_oos$hypothesis$Evid.Ratio
     
-    results <- data.frame(
-        n_obs = n_obs,
-        bf_fro = bf_fro,
-        bf_ooi = bf_ooi,
-        bf_oos = bf_oos
-        )
+    # results <- data.frame(
+    #     n_obs = n_obs,
+    #     bf_fro = bf_fro,
+    #     bf_ooi = bf_ooi,
+    #     bf_oos = bf_oos
+    #     )
     
-    return(results)
+    return(c(bf_fro, bf_ooi, bf_oos) )
     
     }
 
 # simulating for some range of sample sizes
-sample_size <- seq.int(from = 20, to = 200, by = 10)
+nsims <- 10
+sample_size <- seq.int(from = 20, to = 200, by = 20)
+sample_size <- rep(sample_size, each = nsims)
+
+# initialising results
+overall_results <- data.frame(
+    nobs = sample_size,
[…]

### 2020-09-29 reanalysis.Rmd
minor updates in abstract

@@
 Moreover, the relation between self-reports and physiological measures was not *directly* assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiolgogical measures from group means is inappropriate.
-Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways foward, both from a theoretical and from a methodological perspective.
+Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."

### 2020-09-29 reanalysis.tex
minor updates in abstract

@@
 Moreover, the relation between self-reports and physiological measures was not \emph{directly} assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiolgogical measures from group means is inappropriate.
-Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways foward, both from a theoretical and from a methodological perspective.
+Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.

### 2020-09-29 reanalysis.R

@@ -853,12 +853,8 @@ overall_results <- data.frame(
     bf_oos = numeric(length = length(sample_size) )
     )
 
-# initialises the progress bar
-# pb <- txtProgressBar(min = 0, max = nrow(overall_results), initial = 0) 
-
 # looping over these sample sizes
-# for (i in 1:nrow(empty_results) ) {
-for (i in 1:2) {
+for (i in 1:nrow(empty_results) ) {
     
     if (i == 1) {
         
@@ -873,7 +869,7 @@ for (i in 1:2) {
     # gets BFs for this sample size and stores it in "overall_results"
     overall_results[i, 3:5] <- simulating_bfs(n_obs = overall_results[i, ]$nobs)
     
-    if (i == 2) {
+    if (i == nrow(empty_results) ) {
         
         # time of simulation end
         stop_time <- Sys.time()

### 2020-09-29 reanalysis.Rmd
updates in manuscript

@@
 ---
-title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the fallacy of the null hypothesis"
+title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy"
 
@@
 library(glue)
+library(pwr)
 
@@
 despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative...
-These inner speech "dysfunctions"...
+These inner speech "dysfunctions" [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018]...
 
-@moffatt_inner_2020, @loevenbruck_cognitive_2018, @grandchamp_condialint_2019, @alderson-day_inner_2015, @wilkinson_auditory_2017, and @perrone-bertolotti_what_2014, @nalborczyk_can_2020, @nalborczyk_introduction_2019, @nalborczyk_orofacial_2017, @nalborczyk_understanding_2019...
+Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020;  @nalborczyk_articulatory_2020]...
+
+@moffatt_inner_2020, @grandchamp_condialint_2019,  @wilkinson_auditory_2017, @nalborczyk_introduction_2019...
 
@@
 In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on...
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) and on reliable measures...
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
@@
 
-https://theethicalskeptic.com/2015/08/17/the-four-types-of-null-hypothesis-fallacy/...
+There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology [e.g., @harlow_problem_1997; @meehl_appraising_1990-1; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
+By "uninformative", we mean that some null-hypothesis significance tests are often *not* diagnostic with regards to the substantive question of interest...
 
-```{r}
-# importing data
-# df <- read_excel("data/RUM_master_data.xlsx")
+As highlighted by many authors [e.g.,@kline], concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the...
+The argument from ignorance, such as "Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space."...
+the absence of evidence fallacy or fallacy of acceptance...
+
+This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the test has good *severity* [e.g., @mayo_severe_2006; @mayo_statistical_2018].
+In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is if it survives *severe tests*.
+In other words, some claim (e.g., $\theta = 0$) is said to be *severely tested*) if it had great chances of being falsified, was the claim false.
+More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ [@mayo_severe_2006; @mayo_statistical_2018]...To put it simply...
+https://www.analytics-toolkit.com/glossary/severity/...
+
+Anticipating the critics on the power of their study (a critic that was probably raised during peer review), @moffatt_inner_2020 report the results of a (possibly ran a posteriori) power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$, which is highly optimistic estimate of the substantive effect of interest in the target article (i.e., the difference in EMG amplitude between the rumination and distraction conditions) as this effects represents the standardised mean difference *between a rest period and a rumination one* [@nalborczyk_orofacial_2017]...
+
+```{r power, echo = TRUE}
+# How many participants do we need for a target statistical power of 0.8?
+library(pwr)
+pwr.t.test(
+  d = 0.72, sig.level = 0.05, power = 0.8,
+  type = "one.sample", alternative = "two.sided"
+  )
 ```
 
-...
+We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was was much lower than suggested by the authors.
+Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction condition may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+If we assume that the former is half the size of the latter [which seems reasonable given the distribution of effects sizes in Experimental Psychology, e.g., @szucs_empirical_2017], therefore the a priori power of the main statistical test from @moffatt_inner_2020 is around $0.44$, meaning that they had less than 1 chance over two to find a significant effect, given the effect in the population is actually $0.36$.
+Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
 
-> "In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
-This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (B10 = 18.79), and moderate evidence in favour of the null hypothesis for the OOS (B10 = 0.232) and OOI (B10 = 0.278) muscles, according to current guidelines for interpreting Bayes factors [43]."
+```{r actual_power, echo = TRUE}
+# A priori power for n = 26 (per condition) and d = 0.36
+pwr.t.test(
+  n = 26, d = 0.72 / 2, sig.level = 0.05,
+  type = "one.sample", alternative = "two.sided"
+  )
+```
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
+Anticipating again the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence of the absence of the effect, @moffatt_inner_2020 report the following Bayes factor analysis:
+
+> "[...] therefore it is possible that the sample size of the present study lacked sufficient power to detect the effect of rumination on muscle activity.
+In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
+This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle ($B_{10} = 18.79$), and moderate evidence in favour of the null hypothesis for the OOS ($B_{10} = 0.232$) and OOI ($B_{10} = 0.278$) muscles, according to current guidelines for interpreting Bayes factors [43]."
+
+While we appreciate the effort, the current approach poses new problems.
+First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+Second, no details are given with regards to the exact models that were compared.
+Second...
+Third, and most importantly, the BFs indicate moderate evidence in favour of the null for the OOI and OOS muscles.
+More precisely, these BFs indicated that the (observed) data are $1 / 0.232 \approx 4.31$ times more likely under the null than under the alternative hypothesis for the OOS and $1 / 0.278 \approx 3.6$ times more likely under the null than under the alternative hypothesis for the OOI.
+In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with different prior scales) may unsurprisingly results in various BFs...
+For instance...
+Finally and most importantly, the power...
+
+```{r sensitivity, echo = TRUE}
+library(BayesFactor)
+ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "medium")
+ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "wide")
+ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "ultrawide")
+# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2)/2)
+# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = 1)
+# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2) )
+```
+
+We fitted a multivariate Bayesian regression model on these data...
+then we generated new datasets from the posterior predictive distribution...
+and computed the Bayes factor in favour of the alternative hypothesis ($BF_{10}$) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $10$ simulations (i.e., 1000 simulated datasets) for each sample size...
+
+```{r simulated-power, fig.width = 10, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
+# loading the results
+load(file = "results/overall_results.Rda")
+
+# simulations parameters
+nsims <- 1e3
+sample_size <- seq.int(from = 20, to = 200, by = 20)
+
+# plotting the results
+overall_results %>%
+    na.omit() %>%
+    filter_all(any_vars(. != 0) ) %>%
+    pivot_longer(cols = bf_fro:bf_oos, names_to = "bf_type") %>%
+    mutate(value = log(value) ) %>%
+    mutate(bf_type = factor(bf_type, labels = c("FRO", "OOI", "OOS") ) ) %>%
+    group_by(nobs, bf_type) %>%
+    summarise(
+        across(
+            .cols = value,
+            .fns = list(mean = mean, median = median, se = ~sd(.x) / sqrt(nsims), mad = mad)
+            )
+        ) %>%
+    ungroup() %>%
+    ggplot(aes(x = nobs, y = value_mean, colour = bf_type, fill = bf_type) ) +
+    geom_hline(yintercept = 0, lty = 3) +
+    geom_ribbon(
+        aes(x = nobs, ymin = value_mean - 1.96 * value_se, ymax = value_mean + 1.96 * value_se, colour = NULL),
+        # aes(x = nobs, ymin = value_median - value_mad, ymax = value_median + value_mad, colour = NULL),
+        alpha = 0.5, show.legend = FALSE
+        ) + 
+    geom_line(show.legend = FALSE) +
+    # geom_line(aes(y = value_median), show.legend = FALSE) +
+    geom_point(show.legend = FALSE) +
+    facet_wrap(~bf_type, scales = "free") +
+    scale_x_continuous(breaks = unique(sample_size) ) +
+    theme_bw(base_size = 12) +
+    labs(x = "Number of participants", y = "Natural logarithm of the Bayes factor") +
+    scale_colour_brewer(palette = "Dark2", direction = 1) +
+    scale_fill_brewer(palette = "Dark2", direction = 1)
+```
+
+As shown in Figure \@ref(fig:simulated-power), the BF in favour of the alternative hypothesis is growing proportionally with the sample size...
+
+We should keep in mind the limitations of this analysis, which uses simulated datasets form the posterior distribution estimated from...
+which corresponds more or less to the Bayesian analogue of the post-hoc frequentist power analysis, which has been much criticised [e.g., @lakens_20_2014].
+However, the present analysis differs from this kind of analysis by relying on the posterior distribution...
+and because we do not aim to reach a dichotomic (e.g., accept/reject) goal but rather to see how the BF amplitude evolves with varying sample sizes.
+
+## Manipulating rumination within-subject
+
+In @nalborczyk_dissociating_2020, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects...
+In contrast to this approach, @moffatt_inner_2020 asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure)...
 
@@
 
-...
+...@moffatt_inner_2020 say:
+
+> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interac- tions involving order."
+
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
+@sassenhagen_common_2016...
 

### 2020-09-29 reanalysis.tex
updates in manuscript

@@
 \hypersetup{
-  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the fallacy of the null hypothesis},
+  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the absence of evidence fallacy},
   pdflang={en-EN},
@@
 \urlstyle{same} % disable monospaced font for URLs
+\usepackage{color}
+\usepackage{fancyvrb}
+\newcommand{\VerbBar}{|}
+\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
+\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
+% Add ',fontsize=\small' for more characters per line
+\usepackage{framed}
+\definecolor{shadecolor}{RGB}{248,248,248}
+\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
+\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
+\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
+\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\BuiltInTok}[1]{#1}
+\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
+\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
+\newcommand{\ExtensionTok}[1]{#1}
+\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
+\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\ImportTok}[1]{#1}
+\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
+\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
+\newcommand{\NormalTok}[1]{#1}
+\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
+\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
+\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
+\newcommand{\RegionMarkerTok}[1]{#1}
+\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
+\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
+\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
 
-\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the fallacy of the null hypothesis}
+\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
 
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 465
+Wordcount (excluding abstract, references, tables, and figures): 1526
 
@@
 
-The activity of silently talking to oneself or ``inner speech'' is a foundational ability\ldots{} despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions''\ldots{}
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability\ldots{} despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions'' (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014})\ldots{}
+
+Given the predominantly verbal nature of rumination {[}{]}, we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020})\ldots{}
 
 Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), Lœvenbruck et al.
-(\protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}), Grandchamp et al.
-(\protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), Alderson-Day and Fernyhough (\protect\hyperlink{ref-alderson-day_inner_2015}{2015}), Wilkinson and Fernyhough (\protect\hyperlink{ref-wilkinson_auditory_2017}{2017}), and Perrone-Bertolotti et al.
-(\protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}), Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_can_2020}{2020}), Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_introduction_2019}{2019}), Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019})\ldots{}
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), Grandchamp et al.
+(\protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), Wilkinson and Fernyhough (\protect\hyperlink{ref-wilkinson_auditory_2017}{2017}), Nalborczyk, Batailler, et al.
+(\protect\hyperlink{ref-nalborczyk_introduction_2019}{2019})\ldots{}
 
@@
 In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on\ldots{} Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) and on reliable measures\ldots{} Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
 That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
@@
 
-\url{https://theethicalskeptic.com/2015/08/17/the-four-types-of-null-hypothesis-fallacy/}\ldots{}
+There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology (e.g., Meehl, \protect\hyperlink{ref-harlow_problem_1997}{1997}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990}\protect\hyperlink{ref-meehl_why_1990}{a}, \protect\hyperlink{ref-meehl_appraising_1990-1}{1990}\protect\hyperlink{ref-meehl_appraising_1990-1}{b}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}).
+By ``uninformative'', we mean that some null-hypothesis significance tests are often \emph{not} diagnostic with regards to the substantive question of interest\ldots{}
 
-\ldots{}
+As highlighted by many authors (e.g., {\textbf{???}}), concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the\ldots{} The argument from ignorance, such as ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.''\ldots{} the absence of evidence fallacy or fallacy of acceptance\ldots{}
+
+This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the test has good \emph{severity} (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
+In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is if it survives \emph{severe tests}.
+In other words, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested}) if it had great chances of being falsified, was the claim false.
+More formally, we can define \(\text{SEV}(T, x0, H)\), the severity with which claim \(H\) passes test \(T\) with outcome \(x0\), and \(\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})\) (Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}; Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006})\ldots To put it simply\ldots{} \url{https://www.analytics-toolkit.com/glossary/severity/}\ldots{}
+
+Anticipating the critics on the power of their study (a critic that was probably raised during peer review), Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a (possibly ran a posteriori) power analysis using the effect size reported in Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\), which is highly optimistic estimate of the substantive effect of interest in the target article (i.e., the difference in EMG amplitude between the rumination and distraction conditions) as this effects represents the standardised mean difference \emph{between a rest period and a rumination one} (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017})\ldots{}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# How many participants do we need for a target statistical power of 0.8?}
+\KeywordTok{library}\NormalTok{(pwr)}
+\KeywordTok{pwr.t.test}\NormalTok{(}
+  \DataTypeTok{d =} \FloatTok{0.72}\NormalTok{, }\DataTypeTok{sig.level =} \FloatTok{0.05}\NormalTok{, }\DataTypeTok{power =} \FloatTok{0.8}\NormalTok{,}
+  \DataTypeTok{type =} \StringTok{"one.sample"}\NormalTok{, }\DataTypeTok{alternative =} \StringTok{"two.sided"}
+\NormalTok{  )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+##      One-sample t test power calculation 
+## 
+##               n = 17.16004
+##               d = 0.72
+##       sig.level = 0.05
+##           power = 0.8
+##     alternative = two.sided
+\end{verbatim}
+
+We suggest the (a priori) power of the study ran by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was was much lower than suggested by the authors.
+Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction condition may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+If we assume that the former is half the size of the latter (which seems reasonable given the distribution of effects sizes in Experimental Psychology, e.g., Szucs \& Ioannidis, \protect\hyperlink{ref-szucs_empirical_2017}{2017}), therefore the a priori power of the main statistical test from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is around \(0.44\), meaning that they had less than 1 chance over two to find a significant effect, given the effect in the population is actually \(0.36\).
+Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# A priori power for n = 26 (per condition) and d = 0.36}
+\KeywordTok{pwr.t.test}\NormalTok{(}
+  \DataTypeTok{n =} \DecValTok{26}\NormalTok{, }\DataTypeTok{d =} \FloatTok{0.72} \OperatorTok{/}\StringTok{ }\DecValTok{2}\NormalTok{, }\DataTypeTok{sig.level =} \FloatTok{0.05}\NormalTok{,}
+  \DataTypeTok{type =} \StringTok{"one.sample"}\NormalTok{, }\DataTypeTok{alternative =} \StringTok{"two.sided"}
+\NormalTok{  )}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## 
+##      One-sample t test power calculation 
+## 
+##               n = 26
+##               d = 0.36
+##       sig.level = 0.05
+##           power = 0.4228455
+##     alternative = two.sided
+\end{verbatim}
+
+Anticipating again the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence of the absence of the effect, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the following Bayes factor analysis:
 
 \begin{quote}
-``In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
-This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (B10 = 18.79), and moderate evidence in favour of the null hypothesis for the OOS (B10 = 0.232) and OOI (B10 = 0.278) muscles, according to current guidelines for interpreting Bayes factors {[}43{]}.''
+``{[}\ldots{]} therefore it is possible that the sample size of the present study lacked sufficient power to detect the effect of rumination on muscle activity.
+In order to test this, a Bayesian paired samples t-test was conducted for the peak log values of muscle activity between the rumination and distraction conditions.
+This revealed strong evidence in favour of the alternative hypothesis for the FRO muscle (\(B_{10} = 18.79\)), and moderate evidence in favour of the null hypothesis for the OOS (\(B_{10} = 0.232\)) and OOI (\(B_{10} = 0.278\)) muscles, according to current guidelines for interpreting Bayes factors {[}43{]}.''
 \end{quote}
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+While we appreciate the effort, the current approach poses new problems.
+First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+Second, no details are given with regards to the exact models that were compared.
+Second\ldots{} Third, and most importantly, the BFs indicate moderate evidence in favour of the null for the OOI and OOS muscles.
+More precisely, these BFs indicated that the (observed) data are \(1 / 0.232 \approx 4.31\) times more likely under the null than under the alternative hypothesis for the OOS and \(1 / 0.278 \approx 3.6\) times more likely under the null than under the alternative hypothesis for the OOI.
+In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with different prior scales) may unsurprisingly results in various BFs\ldots{} For instance\ldots{} Finally and most importantly, the power\ldots{}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{library}\NormalTok{(BayesFactor)}
+\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"medium"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Bayes factor analysis
+## --------------
+## [1] Alt., r=0.707 : 0.2796158 ±0.03%
+## 
+## Against denominator:
+##   Null, mu = 0 
+## ---
+## Bayes factor type: BFoneSample, JZS
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"wide"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Bayes factor analysis
+## --------------
+## [1] Alt., r=1 : 0.2072665 ±0.06%
+## 
+## Against denominator:
+##   Null, mu = 0 
+## ---
+## Bayes factor type: BFoneSample, JZS
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"ultrawide"}\NormalTok{)}
+\end{Highlighting}
+\end{Shaded}
+
+\begin{verbatim}
+## Bayes factor analysis
+## --------------
+## [1] Alt., r=1.414 : 0.1505836 ±0%
+## 
+## Against denominator:
+##   Null, mu = 0 
+## ---
+## Bayes factor type: BFoneSample, JZS
+\end{verbatim}
+
+\begin{Shaded}
+\begin{Highlighting}[]
+\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2)/2)}
+\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = 1)}
+\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2) )}
+\end{Highlighting}
+\end{Shaded}
+
+We fitted a multivariate Bayesian regression model on these data\ldots{} then we generated new datasets from the posterior predictive distribution\ldots{} and computed the Bayes factor in favour of the alternative hypothesis (\(BF_{10}\)) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(10\) simulations (i.e., 1000 simulated datasets) for each sample size\ldots{}
+
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/simulated-power-1}
+
+}
+
+\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.}\label{fig:simulated-power}
+\end{figure}
+
+As shown in Figure \ref{fig:simulated-power}, the BF in favour of the alternative hypothesis is growing proportionally with the sample size\ldots{}
+
+We should keep in mind the limitations of this analysis, which uses simulated datasets form the posterior distribution estimated from\ldots{} which corresponds more or less to the Bayesian analogue of the post-hoc frequentist power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
+However, the present analysis differs from this kind of analysis by relying on the posterior distribution\ldots{} and because we do not aim to reach a dichotomic (e.g., accept/reject) goal but rather to see how the BF amplitude evolves with varying sample sizes.
+
+\hypertarget{manipulating-rumination-within-subject}{%
+\subsection{Manipulating rumination within-subject}\label{manipulating-rumination-within-subject}}
+
+In Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects\ldots{} In contrast to this approach, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure)\ldots{}
 
@@
 
-\ldots{}
+\ldots{}Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
+
+\begin{quote}
+``Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interac- tions involving order.''
+\end{quote}
+
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{} Sassenhagen and Alday (\protect\hyperlink{ref-sassenhagen_common_2016}{2016})\ldots{}
 
@@
 
+\leavevmode\hypertarget{ref-lakens_20_2014}{}%
+Lakens, D. (2014). The 20\% Statistician: Observed power, and what to do if your editor asks for post-hoc power analyses. In \emph{The 20\% Statistician}.
+
 \leavevmode\hypertarget{ref-loevenbruck_cognitive_2018}{}%
@@
 Marwick, B. (2019). \emph{Wordcountaddin: Word counts and readability statistics in r markdown documents}.
+
+\leavevmode\hypertarget{ref-mayo_statistical_2018}{}%
+Mayo, D. G. (2018). \emph{Statistical Inference as Severe Testing: How to Get Beyond the Statistics Wars}. Cambridge University Press. \url{https://doi.org/10.1017/9781107286184}
+
+\leavevmode\hypertarget{ref-mayo_severe_2006}{}%
+Mayo, D.
+G., \& Spanos, A.
+(2006).
+Severe Testing as a Basic Concept in a NeymanPearson Philosophy of Induction.
+\emph{The British Journal for the Philosophy of Science}, \emph{57}(2), 323--357.
+\url{https://doi.org/10.1093/bjps/axl003}
+
+\leavevmode\hypertarget{ref-meehl_theoretical_1978}{}%
+Meehl, P.
+E.
+(1978).
+Theoretical risks and tabular asterisks: Sir Karl, Sir Ronald, and the slow progress of soft psychology.
+\emph{Journal of Consulting and Clinical Psychology}, \emph{46}(4), 806--834.
+\url{https://doi.org/10.1037/0022-006X.46.4.806}
+
+\leavevmode\hypertarget{ref-meehl_why_1990}{}%
+Meehl, P. E. (1990a). Why Summaries of Research on Psychological Theories are Often Uninterpretable. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
+
+\leavevmode\hypertarget{ref-harlow_problem_1997}{}%
+Meehl, P.
+E.
+(1997).
+The problem is epistemology, not statistics: Replace significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
+\emph{What If There Were No Significance Tests?}, 393--425.
+
+\leavevmode\hypertarget{ref-meehl_appraising_1990-1}{}%
+Meehl, P.
+E.
+(1990b).
+Appraising and Amending Theories: The Strategy of Lakatosian Defense and Two Principles that Warrant It.
+\emph{Psychological Inquiry}, \emph{1}(2), 108--141.
+\url{https://doi.org/10.1207/s15327965pli0102_1}
+
+\leavevmode\hypertarget{ref-meehl_theory-testing_1967}{}%
+Meehl, P. E. (1967). Theory-testing in Psychology and Physics: A methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
 
@@
 Nalborczyk, L. (2019). \emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}PhD Thesis{]}. Univ. Grenoble Alpes \& Ghent University.
+
+\leavevmode\hypertarget{ref-nalborczyk_dissociating_2020}{}%
+Nalborczyk, L., Banjac, S., Celine, B., Grandchamp, R., Koster, E.
+H.
+W., Marcela, P.-B., \& Loevenbruck, H.
+(2020).
+\emph{Dissociating facial electromyographic correlates of visual and verbal induced rumination}.
+\url{https://doi.org/10.31234/osf.io/vfjn2}
 
@@
 
+\leavevmode\hypertarget{ref-nalborczyk_articulatory_2020}{}%
+Nalborczyk, L., Perrone-Bertolotti, M., Baeyens, C., Grandchamp, R., Spinelli, E., Koster, E.
+H.
+W., \& Lœvenbruck, H.
+(2020).
+\emph{Articulatory suppression effects on induced rumination} {[}Under Review{]}.
+
 \leavevmode\hypertarget{ref-perrone-bertolotti_what_2014}{}%
@@
 R Core Team. (2017). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-sassenhagen_common_2016}{}%
+Sassenhagen, J., \& Alday, P.
+M.
+(2016).
+A common misapplication of statistical inference: Nuisance control with null-hypothesis significance tests.
+\emph{Brain and Language}, \emph{162}, 42--45.
+\url{https://doi.org/10.1016/j.bandl.2016.08.001}
+
+\leavevmode\hypertarget{ref-szucs_empirical_2017}{}%
+Szucs, D., \& Ioannidis, J.
+P.
+A.
+(2017).
+Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
+\emph{PLOS Biology}, \emph{15}(3), e2000797.
+\url{https://doi.org/10.1371/journal.pbio.2000797}
 

### 2020-09-29 reanalysis.R

@@ -794,39 +794,57 @@ simulating_bfs <- function (n_obs) {
         mutate(ID = as.numeric(ID), condition = as.character(condition) )
     
     # fitting the model
-    bf_simulated_data_varying_effects <- update(
-        varying_effects,
-        newdata = bf_simulated_data_wide,
-        # mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
-        # family = gaussian(),
-        # prior = priors_varying,
-        # data = simulated_data_wide,
-        chains = 4, cores = detectCores(),
-        warmup = 2000, iter = 5000,
-        control = list(adapt_delta = 0.95),
-        sample_prior = TRUE
-        )
+    # bf_simulated_data_varying_effects <- update(
+    #     varying_effects,
+    #     newdata = bf_simulated_data_wide,
+    #     # mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
+    #     # family = gaussian(),
+    #     # prior = priors_varying,
+    #     # data = simulated_data_wide,
+    #     chains = 4, cores = detectCores(),
+    #     warmup = 2000, iter = 5000,
+    #     control = list(adapt_delta = 0.95),
+    #     sample_prior = TRUE
+    #     )
     
-    bf_hyp_fro <- hypothesis(
-        bf_simulated_data_varying_effects,
-        "FRO_conditionRUM - FRO_conditionDIS = 0"
-        )
+    # bf_hyp_fro <- hypothesis(
+    #     bf_simulated_data_varying_effects,
+    #     "FRO_conditionRUM - FRO_conditionDIS = 0"
+    #     )
+    # 
+    # bf_fro <- 1 / bf_hyp_fro$hypothesis$Evid.Ratio
+    # 
+    # bf_hyp_ooi <- hypothesis(
+    #     bf_simulated_data_varying_effects,
+    #     "OOI_conditionRUM - OOI_conditionDIS = 0"
+    #     )
+    # 
+    # bf_ooi <- 1 / bf_hyp_ooi$hypothesis$Evid.Ratio
+    # 
+    # bf_hyp_oos <- hypothesis(
+    #     bf_simulated_data_varying_effects,
+    #     "OOS_conditionRUM - OOS_conditionDIS = 0"
+    #     )
+    # 
+    # bf_oos <- 1 / bf_hyp_oos$hypothesis$Evid.Ratio
     
-    bf_fro <- 1 / bf_hyp_fro$hypothesis$Evid.Ratio
[…]

### 2020-09-29 reanalysis.Rmd
updates in manuscript

@@
 title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy"
-
-shorttitle: "The fallacy of the null"
+shorttitle: "The absence of evidence fallacy"
 
@@
 ```{r simulated-power, fig.width = 10, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
+# running the simulations
+# source("code/bf_simulation.R")
+
 # loading the results
@@
     # violin plots
-    geom_violin(
-        scale = "count",
-        fill = "black",
-        alpha = 0.15,
-        colour = "white",
-        position = pd,
-        # adjust = 0.8,
-        draw_quantiles = 0.5,
-        show.legend = FALSE
-        ) +
+    # geom_violin(
+    #     scale = "count",
+    #     fill = "black",
+    #     alpha = 0.15,
+    #     colour = "white",
+    #     position = pd,
+    #     # adjust = 0.8,
+    #     draw_quantiles = 0.5,
+    #     show.legend = FALSE
+    #     ) +
     # plotting individual data points
@@
         ) +
-    # facet_wrap(~order*muscle, ncol = 3) +
+    # facetting by muscle
     facet_wrap(~muscle, ncol = 3) +
@@
 
-...@moffatt_inner_2020 say:
+About the order effects, @moffatt_inner_2020 say:
 
-> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interac- tions involving order."
+> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order."
 
 Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
-@sassenhagen_common_2016...
 
@@
 
-...
+Baseline-standardisation...
 

### 2020-09-29 reanalysis.tex
updates in manuscript

@@
 \makeatother
-\shorttitle{The fallacy of the null}
+\shorttitle{The absence of evidence fallacy}
 \author{Ladislas Nalborczyk\textsuperscript{1}}
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 1526
+Wordcount (excluding abstract, references, tables, and figures): 1527
 
@@
 
-\ldots{}Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
+About the order effects, Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
 
 \begin{quote}
-``Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interac- tions involving order.''
+``Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order.''
 \end{quote}
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{} Sassenhagen and Alday (\protect\hyperlink{ref-sassenhagen_common_2016}{2016})\ldots{}
+Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
 
@@
 
-\ldots{}
+Baseline-standardisation\ldots{}
 
@@
 
-\leavevmode\hypertarget{ref-sassenhagen_common_2016}{}%
-Sassenhagen, J., \& Alday, P.
-M.
-(2016).
-A common misapplication of statistical inference: Nuisance control with null-hypothesis significance tests.
-\emph{Brain and Language}, \emph{162}, 42--45.
-\url{https://doi.org/10.1016/j.bandl.2016.08.001}
-
 \leavevmode\hypertarget{ref-szucs_empirical_2017}{}%

### 2020-09-29 code/bf_simulation.R

@@ -1,0 +1,191 @@
+########################################################
+# Re-analysing the data from Moffatt et al. (2020)     #
+# Simulating the effect of sample size on BFs          #
+# ---------------------------------------------------- #
+# Ladislas Nalborczyk                                  #
+# Last updated on 30.09.2020                           #
+# https://github.com/lnalborczyk/inner_experience_EMG  #
+########################################################
+
+library(BayesFactor)
+library(tidyverse)
+library(brms)
+
+# imports data
+df <- read_excel("data/RUM_master_data.xlsx")
+
+# reshapes data
+df2 <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        values_to = "value",
+        values_drop_na = TRUE
+    ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+    ) %>%
+    # extracts muscle name
+    mutate(muscle = substr(muscle, 1, 3) ) %>%
+    # from long to wide
+    pivot_wider(names_from = muscle, values_from = value)
+
+# imports model
+varying_effects <- readRDS("models/varying_effects.rds")
+
+# function for simulating BFs
+simulating_bfs <- function (n_obs) {
+    
+    # extracting posterior samples from varying-effects model
+    post <- posterior_samples(varying_effects)
+    
+    # number of simulated participants
+    n_ppts <- n_obs
+    
+    # what are the conditions?
+    nd <- crossing(
+        distinct(df2, condition),
+        data.frame(ID = as.numeric(201:(201 + n_ppts - 1) ) )
+        )
+    
+    # simulating data
+    bf_simulated_data <- posterior_predict(
+        varying_effects,
+        newdata = nd,
+        allow_new_levels = TRUE,
+        sample_new_levels = "uncertainty", # "gaussian"
+        summary = FALSE,
+        nsamples = 1
+        )[1, , ] %>%
+        data.frame() %>%
+        bind_cols(nd) %>%
[…]

### 2020-09-29 reanalysis.R

@@ -316,7 +316,7 @@ df2 %>%
     ) +
     # plotting individual data points
     geom_quasirandom(alpha = 0.3) +
-    # plitting the by-group mean
+    # splitting the by-group mean
     stat_summary(
         fun.y = mean,
         geom = "line", size = 1,

### 2020-09-29 code/bf_simulation.R
minor updates in readme

@@ -18,18 +18,18 @@ df <- read_excel("data/RUM_master_data.xlsx")
 df2 <- df %>%
     select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
     na.omit %>%
-    # reshapes data from wide to long format
+    # reshapes wide to long format
     pivot_longer(
         cols = starts_with(c("RUM", "DIS", "BAS") ),
         names_to = "condition",
         values_to = "value",
         values_drop_na = TRUE
-    ) %>%
+        ) %>%
     separate(
         col = condition,
         into = c("condition", "muscle"),
         sep = "_", extra = "merge"
-    ) %>%
+        ) %>%
     # extracts muscle name
     mutate(muscle = substr(muscle, 1, 3) ) %>%
     # from long to wide
@@ -77,29 +77,23 @@ simulating_bfs <- function (n_obs) {
         x = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "RUM"],
         y = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "DIS"],
         paired = TRUE, rscale = "medium"
-    ) %>% data.frame %>% pull(bf)
+        ) %>% data.frame %>% pull(bf)
     
     bf_ooi <- ttestBF(
         x = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "RUM"],
         y = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "DIS"],
         paired = TRUE, rscale = "medium"
-    ) %>% data.frame %>% pull(bf)
+        ) %>% data.frame %>% pull(bf)
     
     bf_oos <- ttestBF(
         x = bf_simulated_data_wide$OOS[bf_simulated_data_wide$condition == "RUM"],
         y = bf_simulated_data_wide$OOS[bf_simulated_data_wide$condition == "DIS"],
         paired = TRUE, rscale = "medium"
-    ) %>% data.frame %>% pull(bf)
+        ) %>% data.frame %>% pull(bf)
     
     return(c(bf_fro, bf_ooi, bf_oos) )
     
 }
-
-# plotting the cauchy prior
-# x <- seq(-5, 5, by = 0.01)
-# plot(x = x, dcauchy(x, location = 0, scale = sqrt(2) / 2), col = "red", type = "l")
[…]

### 2020-09-29 reanalysis.R

@@ -950,6 +950,12 @@ overall_results %>%
         title = "Mean +/- SE (computed over 100 simulations)"
         )
 
+# plotting the cauchy prior
+x <- seq(-5, 5, by = 0.01)
+plot(x = x, dcauchy(x, location = 0, scale = sqrt(2) / 2), col = "red", type = "l")
+lines(x = x, dcauchy(x, location = 0, scale = 1), col = "steelblue", type = "l")
+lines(x = x, dcauchy(x, location = 0, scale = sqrt(2)), col = "darkgreen", type = "l")
+
 ##################
 # Does everyone? #
 ##################

### 2020-09-29 reanalysis.Rmd
minor updates in figures

@@
     facet_wrap(~muscle, ncol = 3) +
-    labs(x = "Condition", y = "EMG log-amplitude") +
-    theme_bw(base_size = 10) +
+    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
+    theme_bw(base_size = 12) +
     scale_colour_brewer(palette = "Dark2", direction = 1) +
@@
     ggplot(aes(x = condition, y = value, colour = order, fill = order) ) +
-    # violin plots
-    # geom_violin(
-    #     scale = "count",
-    #     fill = "black",
-    #     alpha = 0.15,
-    #     colour = "white",
-    #     position = pd,
-    #     # adjust = 0.8,
-    #     draw_quantiles = 0.5,
-    #     show.legend = FALSE
-    #     ) +
     # plotting individual data points
-    # geom_dotplot(
-    #     stackdir = "center",
-    #     binaxis = "y",
-    #     position = pd,
-    #     # binwidth = 1,
-    #     dotsize = 0.5,
-    #     alpha = 0.3
-    #     ) +
     geom_quasirandom(alpha = 0.3) +
+    # plotting means
     stat_summary(
@@
     facet_wrap(~muscle, ncol = 3) +
-    labs(x = "Condition", y = "EMG log-amplitude") +
-    theme_bw(base_size = 10) +
+    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
+    theme_bw(base_size = 12) +
     scale_colour_brewer(palette = "Dark2", direction = 1) +
-    scale_fill_brewer(palette = "Dark2", direction = 1)
+    scale_fill_brewer(palette = "Dark2", direction = 1) +
+    theme(
+      legend.title = element_blank(),
+      # legend.position = c(0.85, 0.85),
+      legend.position = "top",
+      legend.background = element_rect(size = 0.5, linetype = "solid", colour = "black")
+    )
 ```
@@
     # axis labels
-    labs(x = "Condition", y = "EMG log-amplitude") +
+    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
     theme_bw(base_size = 12) +

### 2020-09-29 reanalysis.Rmd
minor updates in readme

@@
 # setting seed for reproducibility
-set.seed(666)
+# set.seed(666)
 
@@
   fig.align = "center", dev = "pdf",
-  out.width = "100%", fig.pos = "!htb"
+  out.width = "100%", fig.width = 8,
+  fig.pos = "!htb"
   )
@@
     labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
-    theme_bw(base_size = 12) +
+    theme_bw(base_size = 10) +
     scale_colour_brewer(palette = "Dark2", direction = 1) +
@@
 ...
+
+```{r model, eval = FALSE, results = "hide"}
+# priors for the varying-effects model
+priors_varying <- c(
+    prior(normal(0, 10), class = Intercept, resp = "FRO"),
+    prior(normal(0, 1), class = b, resp = "FRO"),
+    prior(exponential(1), class = sigma, resp = "FRO"),
+    prior(exponential(1), class = sd, resp = "FRO"),
+    prior(normal(0, 10), class = Intercept, resp = "OOS"),
+    prior(normal(0, 1), class = b, resp = "OOS"),
+    prior(exponential(1), class = sigma, resp = "OOS"),
+    prior(exponential(1), class = sd, resp = "OOS"),
+    prior(normal(0, 10), class = Intercept, resp = "OOI"),
+    prior(normal(0, 1), class = b, resp = "OOI"),
+    prior(exponential(1), class = sigma, resp = "OOI"),
+    prior(exponential(1), class = sd, resp = "OOI")
+    )
+
+# fitting the model
+varying_effects <- brm(
+    mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
+    family = gaussian(),
+    prior = priors_varying,
+    data = df2,
+    chains = 4, cores = detectCores(),
+    warmup = 2000, iter = 10000,
+    control = list(adapt_delta = 0.95),
+    sample_prior = TRUE,
+    file = here("models/varying_effects")
+    )
+```
+
+Posterior distribution of the difference between the distraction and rumination conditions...
 
@@
 
-```{r simulated-power, fig.width = 10, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
+```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
 # running the simulations
@@
     scale_x_continuous(breaks = unique(sample_size) ) +
-    theme_bw(base_size = 12) +
+    theme_bw(base_size = 10) +
     labs(x = "Number of participants", y = "Natural logarithm of the Bayes factor") +
@@
 ```{r everyone, fig.cap = "Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
-Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
+Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
 # does everyone plot
@@
     # plotting individual data points
-    # geom_quasirandom(alpha = 0.3) +
     geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
+    # plotting individual trajectories
     geom_line(aes(group = ID), size = 0.5, alpha = 0.8, show.legend = FALSE) +
-    # plitting the by-group mean
-    # stat_summary(
-    #     fun.y = mean,
-    #     geom = "line", size = 2,
-    #     aes(group = interaction(muscle, ruminator) ),
-    #     position = pd,
-    #     show.legend = FALSE
-    #     ) +
-    # plotting means
-    # stat_summary(
-    #     fun.y = "mean",
-    #     geom = "point", shape = 16, size = 4,
-    #     position = pd,
-    #     show.legend = TRUE
-    #     ) +
-    # plotting confidence intervals
-    # stat_summary(
-    #     fun.data = mean_cl_normal,
-    #     geom = "errorbar", size = 2, width = 0,
-    #     fun.args = list(mult = 1.96),
-    #     show.legend = FALSE,
-    #     position = pd
-    #     ) +
     # facetting by muscle
@@
     labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
-    theme_bw(base_size = 12) +
+    theme_bw(base_size = 10) +
     scale_colour_brewer(palette = "Dark2", direction = -1) +

### 2020-09-29 reanalysis.tex
minor updates in readme

@@
 \caption{Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
-Green dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
+Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
 \end{figure}

### 2020-09-30 reanalysis.Rmd
updating simulation results

@@
 abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
-Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that (the *self-reported*) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that *self-reported* inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
 We suggest this conclusion is hasty and based on waggly evidence.
-Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on a low-powered non-significant p-value is strongly problematic/uninformative.
 Moreover, the relation between self-reports and physiological measures was not *directly* assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
 Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
@@
 library(wordcountaddin)
+library(BayesFactor)
 library(ggbeeswarm)
@@
 
-Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020;  @nalborczyk_articulatory_2020]...
+Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020;@nalborczyk_articulatory_2020]...
 
-@moffatt_inner_2020, @grandchamp_condialint_2019,  @wilkinson_auditory_2017, @nalborczyk_introduction_2019...
+We have previously shown that...
+However, it was unclear...
+therefore, the extension of our study by @moffatt_inner_2020, which consisted by including a distraction control group, is more than welcome...
+However...
 
@@
 In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) and on reliable measures...
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
@@
     # plotting individual data points
-    # geom_dotplot(
-    #     stackdir = "center",
-    #     binaxis = "y",
-    #     position = pd,
-    #     # binwidth = 1,
-    #     dotsize = 0.5,
-    #     alpha = 0.3
-    #     ) +
     geom_quasirandom(alpha = 0.3) +
+    # plotting means
     stat_summary(
@@
 
-As highlighted by many authors [e.g.,@kline], concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the...
+As highlighted by many authors [e.g., @pollard_probability_1987; @rouder_is_2016], concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the...
 The argument from ignorance, such as "Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space."...
@@
 library(BayesFactor)
+# rscale = sqrt(2) / 2
 ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "medium")
+# rscale = 1
 ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "wide")
+# rscale = sqrt(2)
 ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "ultrawide")
-# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2)/2)
-# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = 1)
-# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2) )
 ```
 
-We fitted a multivariate Bayesian regression model on these data...
+We fitted a multivariate Bayesian regression model on these data using the `brms` package [@R-brms]...
 then we generated new datasets from the posterior predictive distribution...
 and computed the Bayes factor in favour of the alternative hypothesis ($BF_{10}$) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $10$ simulations (i.e., 1000 simulated datasets) for each sample size...
+We then computed the BF using the `BayesFactor` package [@R-BayesFactor], using a "medium" prior on the scale of the Cauchy prior for the alternative hypothesis (i.e., a scale of 1).
 
-```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model."}
+```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
+A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null)."}
 # running the simulations
@@
 nsims <- 1e3
-sample_size <- seq.int(from = 20, to = 200, by = 20)
+sample_size <- seq.int(from = 20, to = 200, by = 10)
 
@@
             .cols = value,
-            .fns = list(mean = mean, median = median, se = ~sd(.x) / sqrt(nsims), mad = mad)
+            .fns = list(mean = mean, se = ~sd(.x) / sqrt(nsims) )
             )
@@
     geom_hline(yintercept = 0, lty = 3) +
+    # geom_raster(fill = value_mean) +
     geom_ribbon(
-        aes(x = nobs, ymin = value_mean - 1.96 * value_se, ymax = value_mean + 1.96 * value_se, colour = NULL),
-        # aes(x = nobs, ymin = value_median - value_mad, ymax = value_median + value_mad, colour = NULL),
+        aes(
+          x = nobs, ymin = value_mean - 1.96 * value_se,
+          ymax = value_mean + 1.96 * value_se, colour = NULL
+          ),
         alpha = 0.5, show.legend = FALSE
@@
     geom_line(show.legend = FALSE) +
-    # geom_line(aes(y = value_median), show.legend = FALSE) +
     geom_point(show.legend = FALSE) +
     facet_wrap(~bf_type, scales = "free") +
-    scale_x_continuous(breaks = unique(sample_size) ) +
+    scale_x_continuous(breaks = unique(sample_size)[c(TRUE, FALSE)]) +
     theme_bw(base_size = 10) +
@@
 
-As shown in Figure \@ref(fig:simulated-power), the BF in favour of the alternative hypothesis is growing proportionally with the sample size...
+As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
+More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles.
+For instance, the average $BF_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
+Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.
 
@@
     mutate(ruminator = as.factor(ruminator) ) %>%
+    mutate(rum_dis = RUM - DIS) %>%
     pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
-    ggplot(aes(x = condition, y = value, colour = ruminator, fill = ruminator) ) +
+    ggplot(aes(x = condition, y = value, colour = ruminator) ) +
     # violin plots
@@
     theme_bw(base_size = 10) +
+    # scale_color_gradient2(midpoint = 0, low = "red", mid = "green", high = "blue", space = "Lab")
     scale_colour_brewer(palette = "Dark2", direction = -1) +
@@
 
+Many packages have been used for the writing of this paper, among which the `ggplot2` package for plotting [@R-ggplot2] as well as the `glue` and `tidyverse` packages for code writing and formatting [@R-glue;@R-tidyverse]...
+
 # Acknowledgements {-}

### 2020-09-30 reanalysis.tex
updating simulation results

@@
 Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that (the \emph{self-reported}) inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
 We suggest this conclusion is hasty and based on waggly evidence.
-Indeed, concluding on the absence of an effect based on a low-powered statistical test is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on a low-powered non-significant p-value is strongly problematic/uninformative.
 Moreover, the relation between self-reports and physiological measures was not \emph{directly} assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested through our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
 Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 1527
+Wordcount (excluding abstract, references, tables, and figures): 1731
 
@@
 
-Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), Grandchamp et al.
-(\protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), Wilkinson and Fernyhough (\protect\hyperlink{ref-wilkinson_auditory_2017}{2017}), Nalborczyk, Batailler, et al.
-(\protect\hyperlink{ref-nalborczyk_introduction_2019}{2019})\ldots{}
+We have previously shown that\ldots{} However, it was unclear\ldots{} therefore, the extension of our study by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), which consisted by including a distraction control group, is more than welcome\ldots{} However\ldots{}
 
@@
 In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to brings information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) and on reliable measures\ldots{} Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
 That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
@@
 
+Posterior distribution of the difference between the distraction and rumination conditions\ldots{}
+
 \hypertarget{concluding-on-the-null-from-low-powered-studies}{%
@@
 
-As highlighted by many authors (e.g., {\textbf{???}}), concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the\ldots{} The argument from ignorance, such as ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.''\ldots{} the absence of evidence fallacy or fallacy of acceptance\ldots{}
+As highlighted by many authors (e.g., Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the\ldots{} The argument from ignorance, such as ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.''\ldots{} the absence of evidence fallacy or fallacy of acceptance\ldots{}
 
@@
 \KeywordTok{library}\NormalTok{(BayesFactor)}
+\CommentTok{\# rscale = sqrt(2) / 2}
 \KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"medium"}\NormalTok{)}
@@
 \begin{Highlighting}[]
+\CommentTok{\# rscale = 1}
 \KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"wide"}\NormalTok{)}
@@
 \begin{Highlighting}[]
+\CommentTok{\# rscale = sqrt(2)}
 \KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"ultrawide"}\NormalTok{)}
@@
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2)/2)}
-\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = 1)}
-\CommentTok{\# ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = sqrt(2) )}
-\end{Highlighting}
-\end{Shaded}
-
-We fitted a multivariate Bayesian regression model on these data\ldots{} then we generated new datasets from the posterior predictive distribution\ldots{} and computed the Bayes factor in favour of the alternative hypothesis (\(BF_{10}\)) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(10\) simulations (i.e., 1000 simulated datasets) for each sample size\ldots{}
+We fitted a multivariate Bayesian regression model on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017})\ldots{} then we generated new datasets from the posterior predictive distribution\ldots{} and computed the Bayes factor in favour of the alternative hypothesis (\(BF_{10}\)) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(10\) simulations (i.e., 1000 simulated datasets) for each sample size\ldots{} We then computed the BF using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}), using a ``medium'' prior on the scale of the Cauchy prior for the alternative hypothesis (i.e., a scale of 1).
 
@@
 
-\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.}\label{fig:simulated-power}
+\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
+A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null).}\label{fig:simulated-power}
 \end{figure}
 
-As shown in Figure \ref{fig:simulated-power}, the BF in favour of the alternative hypothesis is growing proportionally with the sample size\ldots{}
+As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
+More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles.
+For instance, the average \(BF_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
+Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.
 
@@
 
+Many packages have been used for the writing of this paper, among which the \texttt{ggplot2} package for plotting (Wickham, \protect\hyperlink{ref-R-ggplot2}{2016}) as well as the \texttt{glue} and \texttt{tidyverse} packages for code writing and formatting (Hester, \protect\hyperlink{ref-R-glue}{2020}; Wickham, \protect\hyperlink{ref-R-tidyverse}{2017})\ldots{}
+
 \hypertarget{acknowledgements}{%
@@
 
-\leavevmode\hypertarget{ref-grandchamp_condialint_2019}{}%
-Grandchamp, R., Rapin, L., Perrone-Bertolotti, M., Pichat, C., Haldin, C., Cousin, E., Lachaux, J.-P., Dohen, M., Perrier, P., Garnier, M., Baciu, M., \& Lœvenbruck, H.
-(2019).
-The ConDialInt Model: Condensation, Dialogality, and Intentionality Dimensions of Inner Speech Within a Hierarchical Predictive Control Framework.
-\emph{Frontiers in Psychology}, \emph{10}.
-\url{https://doi.org/10.3389/fpsyg.2019.02019}
+\leavevmode\hypertarget{ref-R-brms}{}%
+Bürkner, P.-C. (2017). brms: An R package for bayesian multilevel models using Stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in Bayesian mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
+
+\leavevmode\hypertarget{ref-R-glue}{}%
+Hester, J. (2020). \emph{Glue: Interpreted string literals}. \url{https://CRAN.R-project.org/package=glue}
 
@@
 
+\leavevmode\hypertarget{ref-R-BayesFactor}{}%
+Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. \url{https://CRAN.R-project.org/package=BayesFactor}
+
 \leavevmode\hypertarget{ref-R-here}{}%
@@
 \url{https://doi.org/10.31234/osf.io/vfjn2}
-
-\leavevmode\hypertarget{ref-nalborczyk_introduction_2019}{}%
-Nalborczyk, L., Batailler, C., Lœvenbruck, H., Vilain, A., \& Bürkner, P.-C.
-(2019).
-An introduction to Bayesian multilevel models using brms: A case study of gender effects on vowel variability in standard indonesian.
-\emph{Journal of Speech Language and Hearing Research}, \emph{62}(5), 1225--1242.
-\url{https://doi.org/10.1044/2018_JSLHR-S-18-0006}
 
@@
 
+\leavevmode\hypertarget{ref-pollard_probability_1987}{}%
+Pollard, P., \& Richardson, J. T. (1987). On the probability of making Type I errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
+
 \leavevmode\hypertarget{ref-R-base}{}%
 R Core Team. (2017). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\hypertarget{ref-rouder_is_2016}{}%
+Rouder, J.
+N., Morey, R.
+D., Verhagen, J., Province, J.
+M., \& Wagenmakers, E.-J.
+(2016).
+Is There a Free Lunch in Inference?
+\emph{Topics in Cognitive Science}, \emph{8}(3), 520--547.
+\url{https://doi.org/10.1111/tops.12214}
 
@@
 
+\leavevmode\hypertarget{ref-R-ggplot2}{}%
+Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{http://ggplot2.org}
+
 \leavevmode\hypertarget{ref-R-tidyverse}{}%
 Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. \url{https://CRAN.R-project.org/package=tidyverse}
-
-\leavevmode\hypertarget{ref-wilkinson_auditory_2017}{}%
-Wilkinson, S., \& Fernyhough, C.
-(2017).
-Auditory verbal hallucinations and inner speech: A predictive processing perspective.
-In Z.
-Radman (Ed.), \emph{Before Consciousness: In Search of the Fundamentals of Mind}.
-Imprint Academic, Ltd.
 

### 2020-09-30 code/bf_simulation.R

@@ -7,36 +7,32 @@
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 
-library(BayesFactor)
-library(tidyverse)
-library(brms)
-
 # imports data
-df <- read_excel("data/RUM_master_data.xlsx")
+# df <- read_excel("data/RUM_master_data.xlsx")
 
 # reshapes data
-df2 <- df %>%
-    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
-    na.omit %>%
-    # reshapes wide to long format
-    pivot_longer(
-        cols = starts_with(c("RUM", "DIS", "BAS") ),
-        names_to = "condition",
-        values_to = "value",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = condition,
-        into = c("condition", "muscle"),
-        sep = "_", extra = "merge"
-        ) %>%
-    # extracts muscle name
-    mutate(muscle = substr(muscle, 1, 3) ) %>%
-    # from long to wide
-    pivot_wider(names_from = muscle, values_from = value)
+# df2 <- df %>%
+#     select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+#     na.omit %>%
+#     # reshapes wide to long format
+#     pivot_longer(
+#         cols = starts_with(c("RUM", "DIS", "BAS") ),
+#         names_to = "condition",
+#         values_to = "value",
+#         values_drop_na = TRUE
+#         ) %>%
+#     separate(
+#         col = condition,
+#         into = c("condition", "muscle"),
+#         sep = "_", extra = "merge"
+#         ) %>%
+#     # extracts muscle name
+#     mutate(muscle = substr(muscle, 1, 3) ) %>%
+#     # from long to wide
+#     pivot_wider(names_from = muscle, values_from = value)
 
 # imports model
-varying_effects <- readRDS("models/varying_effects.rds")
+# varying_effects <- readRDS("models/varying_effects.rds")
 
 # function for simulating BFs
 simulating_bfs <- function (n_obs) {
@@ -58,7 +54,7 @@ simulating_bfs <- function (n_obs) {
         varying_effects,
         newdata = nd,
         allow_new_levels = TRUE,
-        sample_new_levels = "uncertainty", # "gaussian"
[…]

### 2020-09-30 manuscript.Rmd
reorganising the repo

--- 2020-09-30 reanalysis.Rmd
@@
 shorttitle: "The absence of evidence fallacy"
-
 author: 
@@
     institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France
-
 abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
@@
 Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
-
 keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
-
 csl: csl/apa7.csl
@@
 bibliography: [bib/library.bib, bib/r-references.bib]
-
 nocite: | 
@@
     latex_engine: xelatex
+editor_options: 
+  chunk_output_type: console
 ---
@@
 library(tidyverse)
-library(patchwork)
-library(bayesplot)
-library(ggExtra)
 library(papaja)
@@
 library(knitr)
-library(BEST)
+library(brms)
 library(here)
-library(glue)
 library(pwr)
@@
     stat_summary(
-        fun.y = mean,
+        fun = mean,
         geom = "line", size = 1,
@@
     stat_summary(
-        fun.y = "mean",
+        fun = "mean",
         geom = "point", shape = 16, size = 3,
@@
     facet_wrap(~muscle, ncol = 3) +
+    # axis labels
     labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
@@
 
-```{r model, eval = FALSE, results = "hide"}
+```{r model, results = "hide"}
 # priors for the varying-effects model
@@
 
-## Concluding on the null from low-powered studies
+## Concluding on the null from low-powered studies is uninformative
 

### 2020-09-30 manuscript.tex
reorganising the repo

--- 2020-09-30 reanalysis.tex
@@
 
-{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/general-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/general-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/simulated-power-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/simulated-power-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/order-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/order-1}
 
@@
 
-{\centering \includegraphics[width=1\linewidth]{reanalysis_files/figure-latex/everyone-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/everyone-1}
 

### 2020-09-30 code/bf_simulation.R

@@ -7,34 +7,7 @@
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 
-# imports data
-# df <- read_excel("data/RUM_master_data.xlsx")
-
-# reshapes data
-# df2 <- df %>%
-#     select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
-#     na.omit %>%
-#     # reshapes wide to long format
-#     pivot_longer(
-#         cols = starts_with(c("RUM", "DIS", "BAS") ),
-#         names_to = "condition",
-#         values_to = "value",
-#         values_drop_na = TRUE
-#         ) %>%
-#     separate(
-#         col = condition,
-#         into = c("condition", "muscle"),
-#         sep = "_", extra = "merge"
-#         ) %>%
-#     # extracts muscle name
-#     mutate(muscle = substr(muscle, 1, 3) ) %>%
-#     # from long to wide
-#     pivot_wider(names_from = muscle, values_from = value)
-
-# imports model
-# varying_effects <- readRDS("models/varying_effects.rds")
-
-# function for simulating BFs
+# function for simulating BFs with varying sample size
 simulating_bfs <- function (n_obs) {
     
     # extracting posterior samples from varying-effects model
@@ -69,24 +42,28 @@ simulating_bfs <- function (n_obs) {
         pivot_wider(names_from = muscle, values_from = value) %>%
         mutate(ID = as.numeric(ID), condition = as.character(condition) )
     
+    # computing the BF10 for the FRO muscle
     bf_fro <- ttestBF(
         x = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "RUM"],
         y = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "DIS"],
         paired = TRUE, rscale = "medium"
         ) %>% data.frame %>% pull(bf)
     
+    # computing the BF10 for the OOI muscle
     bf_ooi <- ttestBF(
         x = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "RUM"],
         y = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "DIS"],
         paired = TRUE, rscale = "medium"
         ) %>% data.frame %>% pull(bf)
     
+    # computing the BF10 for the OOS muscle
     bf_oos <- ttestBF(
[…]

### 2020-09-30 code/reanalysis.R

@@ -1,0 +1,1104 @@
+#######################################################
+# Reanalysing the data from Moffatt et al. (2020)     #
+# --------------------------------------------------- #
+# Ladislas Nalborczyk                                 #
+# Last updated on 29.09.2020                          #
+# https://github.com/lnalborczyk/inner_experience_EMG #
+#######################################################
+
+library(ggbeeswarm)
+library(tidyverse)
+library(patchwork)
+library(magrittr)
+library(parallel)
+library(readxl)
+library(papaja)
+library(dplyr)
+library(knitr)
+library(BEST)
+library(here)
+library(glue)
+library(brms)
+
+# imports data
+df <- read_excel("data/RUM_master_data.xlsx")
+
+# position for groups
+pd <- position_dodge(0.8)
+
+# plotting for order 1 (BAS>DIS>RUM)
+p1 <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    filter(order == 1) %>%
+    mutate(order = as.factor(order) ) %>%
+    # plots the data
+    ggplot(aes(x = condition, y = value) ) +
+    # violin plots
+    geom_violin(
+        scale = "count",
+        fill = "black",
+        alpha = 0.2,
+        colour = "white",
+        position = pd,
+        # adjust = 0.8,
+        # draw_quantiles = 0.5,
+        show.legend = FALSE
+        ) +
+    # plotting individual data points
+    geom_dotplot(
+        stackdir = "center",
+        binaxis = "y",
+        position = pd,
+        # binwidth = 1,
+        dotsize = 1,
+        alpha = 0.3
+        ) +
+    stat_summary(
+        fun.y = mean,
+        geom = "line", size = 1,
+        aes(group = order),
+        position = pd,
+        show.legend = FALSE
+        ) +
+    # plotting means
+    stat_summary(
[…]

### 2020-09-30 reanalysis.R

@@ -1,1104 +1,0 @@
-#######################################################
-# Reanalysing the data from Moffatt et al. (2020)     #
-# --------------------------------------------------- #
-# Ladislas Nalborczyk                                 #
-# Last updated on 29.09.2020                          #
-# https://github.com/lnalborczyk/inner_experience_EMG #
-#######################################################
-
-library(ggbeeswarm)
-library(tidyverse)
-library(patchwork)
-library(magrittr)
-library(parallel)
-library(readxl)
-library(papaja)
-library(dplyr)
-library(knitr)
-library(BEST)
-library(here)
-library(glue)
-library(brms)
-
-# imports data
-df <- read_excel("data/RUM_master_data.xlsx")
-
-# position for groups
-pd <- position_dodge(0.8)
-
-# plotting for order 1 (BAS>DIS>RUM)
-p1 <- df %>%
-    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
-    na.omit %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = starts_with(c("RUM", "DIS", "BAS") ),
-        names_to = "condition",
-        # names_prefix = "wk",
-        values_to = "value",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = condition,
-        into = c("condition", "muscle"),
-        sep = "_", extra = "merge"
-        ) %>%
-    filter(order == 1) %>%
-    mutate(order = as.factor(order) ) %>%
-    # plots the data
-    ggplot(aes(x = condition, y = value) ) +
-    # violin plots
-    geom_violin(
-        scale = "count",
-        fill = "black",
-        alpha = 0.2,
-        colour = "white",
-        position = pd,
-        # adjust = 0.8,
-        # draw_quantiles = 0.5,
-        show.legend = FALSE
-        ) +
-    # plotting individual data points
-    geom_dotplot(
-        stackdir = "center",
-        binaxis = "y",
-        position = pd,
-        # binwidth = 1,
-        dotsize = 1,
-        alpha = 0.3
-        ) +
-    stat_summary(
-        fun.y = mean,
-        geom = "line", size = 1,
-        aes(group = order),
-        position = pd,
-        show.legend = FALSE
-        ) +
-    # plotting means
-    stat_summary(
[…]

### 2020-09-30 manuscript.Rmd
minor updates in manusript

@@
 
-Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020;@nalborczyk_articulatory_2020]...
+Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020; @nalborczyk_articulatory_2020]...
 
@@
 
-We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was was much lower than suggested by the authors.
-Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction condition may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
-If we assume that the former is half the size of the latter [which seems reasonable given the distribution of effects sizes in Experimental Psychology, e.g., @szucs_empirical_2017], therefore the a priori power of the main statistical test from @moffatt_inner_2020 is around $0.44$, meaning that they had less than 1 chance over two to find a significant effect, given the effect in the population is actually $0.36$.
+We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was much lower than suggested by the authors.
+Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction conditions may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+If we assume that the former is half the size of the latter [which seems reasonable given the high inter-individual variability in such effects, cf.
+the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect, given that the effect in the population was actually $0.36$.
 Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
@@
 
-Anticipating again the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence of the absence of the effect, @moffatt_inner_2020 report the following Bayes factor analysis:
+Anticipating the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
 
@@
 
+<!--
+
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
-Second, no details are given with regards to the exact models that were compared.
-Second...
+First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power (we discuss this issue in more depth below).
+Second, few details are given with regards to the exact models that were compared.
 Third, and most importantly, the BFs indicate moderate evidence in favour of the null for the OOI and OOS muscles.
 More precisely, these BFs indicated that the (observed) data are $1 / 0.232 \approx 4.31$ times more likely under the null than under the alternative hypothesis for the OOS and $1 / 0.278 \approx 3.6$ times more likely under the null than under the alternative hypothesis for the OOI.
-In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with different prior scales) may unsurprisingly results in various BFs...
+In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with varying prior scales for the alternative hypothesis) may unsurprisingly results in various BFs.
 For instance...
-Finally and most importantly, the power...
 
-```{r sensitivity, echo = TRUE}
+-->
+
+While we appreciate the effort, the current approach poses new problems.
+First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power...
+
+```{r sensitivity, echo = FALSE, eval = FALSE}
 library(BayesFactor)
@@
 
-We fitted a multivariate Bayesian regression model on these data using the `brms` package [@R-brms]...
-then we generated new datasets from the posterior predictive distribution...
-and computed the Bayes factor in favour of the alternative hypothesis ($BF_{10}$) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $10$ simulations (i.e., 1000 simulated datasets) for each sample size...
-We then computed the BF using the `BayesFactor` package [@R-BayesFactor], using a "medium" prior on the scale of the Cauchy prior for the alternative hypothesis (i.e., a scale of 1).
+We first fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the `brms` package [@R-brms].
+From there, we i) generated new datasets from the posterior predictive distribution and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
+We used a "medium" prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
+We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $1000$ simulations (i.e., 1000 simulated datasets) for each sample size.
 
-```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
+```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
 A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null)."}
@@
 As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
-More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles.
-For instance, the average $BF_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
-Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.
+More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles for sample sizes larger than 80 participants.
+For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.^[Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.]
 
-We should keep in mind the limitations of this analysis, which uses simulated datasets form the posterior distribution estimated from...
-which corresponds more or less to the Bayesian analogue of the post-hoc frequentist power analysis, which has been much criticised [e.g., @lakens_20_2014].
-However, the present analysis differs from this kind of analysis by relying on the posterior distribution...
-and because we do not aim to reach a dichotomic (e.g., accept/reject) goal but rather to see how the BF amplitude evolves with varying sample sizes.
+We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
+This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
+Most importantly, an assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest (in addition to the prior we specified earlier).
+However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
+First, with the present analysis, we do not aim to assess the ability of our statistical test to pass some dichotomic threshold (e.g., accept/reject).
+Instead, we aim to assess how the $\text{BF}_{10}$ (i.e., the evidence for the alternative hypothesis, relative to the null hypothesis) behaves with varying sample sizes.
+Second, the present analysis relies on the posterior predictive distribution of the model fitted on the data from @moffatt_inner_2020, which naturally incorporates uncertainty about the effect of interest.
+By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the simulation.
 
@@
 
-Baseline-standardisation...
+...
 
@@
 Reproducible code and figures are available at https://github.com/lnalborczyk/inner_experience_EMG.
-
-Many packages have been used for the writing of this paper, among which the `ggplot2` package for plotting [@R-ggplot2] as well as the `glue` and `tidyverse` packages for code writing and formatting [@R-glue;@R-tidyverse]...
 

### 2020-09-30 manuscript.tex
minor updates in manusript

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 1731
+Wordcount (excluding abstract, references, tables, and figures): 1727
 
@@
 
-\hypertarget{concluding-on-the-null-from-low-powered-studies}{%
-\subsection{Concluding on the null from low-powered studies}\label{concluding-on-the-null-from-low-powered-studies}}
+\hypertarget{concluding-on-the-null-from-low-powered-studies-is-uninformative}{%
+\subsection{Concluding on the null from low-powered studies is uninformative}\label{concluding-on-the-null-from-low-powered-studies-is-uninformative}}
 
@@
 We suggest the (a priori) power of the study ran by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was was much lower than suggested by the authors.
-Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction condition may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
-If we assume that the former is half the size of the latter (which seems reasonable given the distribution of effects sizes in Experimental Psychology, e.g., Szucs \& Ioannidis, \protect\hyperlink{ref-szucs_empirical_2017}{2017}), therefore the a priori power of the main statistical test from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is around \(0.44\), meaning that they had less than 1 chance over two to find a significant effect, given the effect in the population is actually \(0.36\).
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
+Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction conditions may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), therefore the a priori power of the main statistical test from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect, given that the effect in the population was actually \(0.36\).
 Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
@@
 
-Anticipating again the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence of the absence of the effect, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the following Bayes factor analysis:
+Anticipating the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence for the absence of an effect, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis:
 
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
-Second, no details are given with regards to the exact models that were compared.
-Second\ldots{} Third, and most importantly, the BFs indicate moderate evidence in favour of the null for the OOI and OOS muscles.
-More precisely, these BFs indicated that the (observed) data are \(1 / 0.232 \approx 4.31\) times more likely under the null than under the alternative hypothesis for the OOS and \(1 / 0.278 \approx 3.6\) times more likely under the null than under the alternative hypothesis for the OOI.
-In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with different prior scales) may unsurprisingly results in various BFs\ldots{} For instance\ldots{} Finally and most importantly, the power\ldots{}
+First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve \emph{at all} the problem of low power\ldots{}
 
-\begin{Shaded}
-\begin{Highlighting}[]
-\KeywordTok{library}\NormalTok{(BayesFactor)}
-\CommentTok{\# rscale = sqrt(2) / 2}
-\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"medium"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Bayes factor analysis
-## --------------
-## [1] Alt., r=0.707 : 0.2796158 ±0.03%
-## 
-## Against denominator:
-##   Null, mu = 0 
-## ---
-## Bayes factor type: BFoneSample, JZS
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# rscale = 1}
-\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"wide"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Bayes factor analysis
-## --------------
-## [1] Alt., r=1 : 0.2072665 ±0.06%
-## 
-## Against denominator:
-##   Null, mu = 0 
-## ---
-## Bayes factor type: BFoneSample, JZS
-\end{verbatim}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# rscale = sqrt(2)}
-\KeywordTok{ttestBF}\NormalTok{(}\DataTypeTok{x =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "RUM"}\NormalTok{], }\DataTypeTok{y =}\NormalTok{ df2}\OperatorTok{$}\NormalTok{OOI[df2}\OperatorTok{$}\NormalTok{condition }\OperatorTok{==}\StringTok{ "DIS"}\NormalTok{], }\DataTypeTok{paired =} \OtherTok{TRUE}\NormalTok{, }\DataTypeTok{rscale =} \StringTok{"ultrawide"}\NormalTok{)}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## Bayes factor analysis
-## --------------
-## [1] Alt., r=1.414 : 0.1505836 ±0%
-## 
-## Against denominator:
-##   Null, mu = 0 
-## ---
-## Bayes factor type: BFoneSample, JZS
-\end{verbatim}
-
-We fitted a multivariate Bayesian regression model on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017})\ldots{} then we generated new datasets from the posterior predictive distribution\ldots{} and computed the Bayes factor in favour of the alternative hypothesis (\(BF_{10}\)) for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(10\) simulations (i.e., 1000 simulated datasets) for each sample size\ldots{} We then computed the BF using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}), using a ``medium'' prior on the scale of the Cauchy prior for the alternative hypothesis (i.e., a scale of 1).
+We first fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}).
+From there, we i) generated new datasets from the posterior predictive distribution and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
+We used a ``medium'' prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
+We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(1000\) simulations (i.e., 1000 simulated datasets) for each sample size.
 
@@
 
-\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis (BF10), along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
+\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
 A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null).}\label{fig:simulated-power}
@@
 As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
-More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles.
-For instance, the average \(BF_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
-Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.
+More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles for sample sizes larger than 80 participants.
+For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.\footnote{Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.}
 
-We should keep in mind the limitations of this analysis, which uses simulated datasets form the posterior distribution estimated from\ldots{} which corresponds more or less to the Bayesian analogue of the post-hoc frequentist power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
-However, the present analysis differs from this kind of analysis by relying on the posterior distribution\ldots{} and because we do not aim to reach a dichotomic (e.g., accept/reject) goal but rather to see how the BF amplitude evolves with varying sample sizes.
+We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
+Most importantly, an assumption of the present analysis is that the data from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is our best source of information regarding the main effect of interest (in addition to the prior we specified earlier).
+However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
+First, with the present analysis, we do not aim to assess the ability of our statistical test to pass some dichotomic threshold (e.g., accept/reject).
+Instead, we aim to assess how the \(\text{BF}_{10}\) (i.e., the evidence for the alternative hypothesis, relative to the null hypothesis) behaves with varying sample sizes.
+Second, the present analysis relies on the posterior predictive distribution of the model fitted on the data from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), which naturally incorporates uncertainty about the effect of interest.
+By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the simulation.
 
@@
 
-Baseline-standardisation\ldots{}
+\ldots{}
 
@@
 Reproducible code and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
-
-Many packages have been used for the writing of this paper, among which the \texttt{ggplot2} package for plotting (Wickham, \protect\hyperlink{ref-R-ggplot2}{2016}) as well as the \texttt{glue} and \texttt{tidyverse} packages for code writing and formatting (Hester, \protect\hyperlink{ref-R-glue}{2020}; Wickham, \protect\hyperlink{ref-R-tidyverse}{2017})\ldots{}
 
@@
 Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in Bayesian mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
-
-\leavevmode\hypertarget{ref-R-glue}{}%
-Hester, J. (2020). \emph{Glue: Interpreted string literals}. \url{https://CRAN.R-project.org/package=glue}
 
@@
 
-\leavevmode\hypertarget{ref-szucs_empirical_2017}{}%
-Szucs, D., \& Ioannidis, J.
-P.
-A.
-(2017).
-Empirical assessment of published effect sizes and power in the recent cognitive neuroscience and psychology literature.
-\emph{PLOS Biology}, \emph{15}(3), e2000797.
-\url{https://doi.org/10.1371/journal.pbio.2000797}
-
-\leavevmode\hypertarget{ref-R-ggplot2}{}%
-Wickham, H. (2016). \emph{Ggplot2: Elegant graphics for data analysis}. Springer-Verlag New York. \url{http://ggplot2.org}
-
 \leavevmode\hypertarget{ref-R-tidyverse}{}%

### 2020-09-30 manuscript.Rmd
minor updates in manuscript

@@
 ---
-title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy"
+title: |
+  | Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy
+  | 
+  | Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.
+
 shorttitle: "The absence of evidence fallacy"
+
 author: 
@@
     email: ladislas.nalborczyk@gipsa-lab.fr
+
 affiliation:
@@
     institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France
+
 abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
@@
 Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
+
 keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
 csl: csl/apa7.csl
-classoption: man
+classoption: man, donotrepeattitle
 linenumbers: yes
@@
 numbersections: false
+
 bibliography: [bib/library.bib, bib/r-references.bib]
+
 nocite: | 
@@
     latex_engine: xelatex
+
 editor_options: 
@@
 library(tidyverse)
+library(patchwork)
+library(parallel)
 library(papaja)
@@
 library(brms)
+library(glue)
 library(here)
@@
 
+<!--
+
+NB: You can add comments using these tags
+
 Wordcount (excluding abstract, references, tables, and figures): `r wordcount`
+
+-->
 
@@
 
-<!-- NB: You can add comments using these tags -->
-
 # Introduction
 
-The activity of silently talking to oneself or "inner speech" is a foundational ability...
-despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative...
+The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan self-motivate or self-regulate.
+Despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative...
 These inner speech "dysfunctions" [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018]...
 
-Given the predominantly verbal nature of rumination [], we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_can_2020; @nalborczyk_articulatory_2020]...
-
-We have previously shown that...
-However, it was unclear...
-therefore, the extension of our study by @moffatt_inner_2020, which consisted by including a distraction control group, is more than welcome...
-However...
+Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used historically to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
+We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period [@nalborczyk_orofacial_2017].
+However, because the rumination condition did not have a proper control condition in this first study, it was unclear whether this perioral activity were specifically related to (inner) speech processes.
+Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of @nalborczyk_dissociating_2020 and more extensively in @nalborczyk_understanding_2019.
+Although these discussions were blatantly ignored by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
 
 The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech".
-In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+This is unlikely to be the case here, for reasons that we will present and discuss in the following.
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
 That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
-This suggests unexplored variation in the determinants of this effects (e.g., the content of the inner experience).
+This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
 Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
@@
 
-```{r general, fig.cap = "Average log-EMG amplitude by muscle and condition.
+@moffatt_inner_2020 recorded...
+in 26 participants (data available at https://osf.io/hj7tz/)...
+The EMG data is depicted in Figure \@ref(fig:general) by condition (where `BAS`, `DIS`, and `RUM` refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (`FRO`, `OOI`, `OOS`).
+
+```{r general, fig.cap = "Average natural logarithm of the EMG peak amplitude per muscle and condition.
 The black dots and intervals represent the by-group average and 95\\% confidence interval (N = 26).
@@
 
-...
+We fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the `brms` package [@R-brms]...
 
-```{r model, results = "hide"}
+```{r models, results = "hide"}
+##############################
+# Bayesian multilevel models #
+##############################
+
+# priors for the constant-effects model
+priors_constant <- c(
+    prior(normal(0, 10), class = Intercept, resp = "FRO"),
+    prior(normal(0, 1), class = b, resp = "FRO"),
+    prior(exponential(1), class = sigma, resp = "FRO"),
+    prior(normal(0, 10), class = Intercept, resp = "OOS"),
+    prior(normal(0, 1), class = b, resp = "OOS"),
+    prior(exponential(1), class = sigma, resp = "OOS"),
+    prior(normal(0, 10), class = Intercept, resp = "OOI"),
+    prior(normal(0, 1), class = b, resp = "OOI"),
+    prior(exponential(1), class = sigma, resp = "OOI")
+    )
+
+# fitting the model
+constant_effects <- brm(
+    mvbind(FRO, OOS, OOI) ~ 1 + condition,
+    family = gaussian(),
+    prior = priors_constant,
+    data = df2,
+    chains = 4, cores = detectCores(),
+    warmup = 2000, iter = 10000,
+    control = list(adapt_delta = 0.95),
+    sample_prior = TRUE,
+    file = here("models/constant_effects")
+    )
+
 # priors for the varying-effects model
@@
 
-## Concluding on the null from low-powered studies is uninformative
+```{r posterior, eval = FALSE, fig.cap = "..."}
+# extracts posterior samples
+post <- posterior_samples(varying_effects)
+
+plotPost(
+    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS,
+    compVal = 0#, ROPE = c(-0.1, 0.1)
+    )
+
+plotPost(
+    post$b_OOI_conditionRUM - post$b_OOI_conditionDIS,
+    compVal = 0#, ROPE = c(-0.1, 0.1)
+    )
+
+plotPost(
+    post$b_OOS_conditionRUM - post$b_OOS_conditionDIS,
+    compVal = 0#, ROPE = c(-0.1, 0.1)
+    )
+```
+
+```{r bf, fig.width = 10, fig.cap = "Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
+The BF is computed as the ratio of the posterior density to the prior density at $\\theta = 0$."}
+# BF testing
+hyp_fro <- hypothesis(
+    varying_effects,
+    "FRO_conditionDIS = FRO_conditionRUM"
+    )
+
+p1 <- plot(hyp_fro, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
+    geom_vline(xintercept = 0, linetype = 2) +
+    coord_cartesian(xlim = c(-5, 5) ) +
+    theme_bw(base_size = 10) +
+    theme(legend.title = element_blank() ) +
+    labs(
+      x = "Log EMG peak amplitude",
+      title = paste0(
+        "BF10 = ", round(1 / hyp_fro$hypothesis$Evid.Ratio, 3),
+        " (BF01 = ", round(hyp_fro$hypothesis$Evid.Ratio, 3), ")"
+        )
+      )
+
+hyp_ooi <- hypothesis(
+    varying_effects,
+    "OOI_conditionDIS = OOI_conditionRUM"
+    )
+
+p2 <- plot(hyp_ooi, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
+    geom_vline(xintercept = 0, linetype = 2) +
+    coord_cartesian(xlim = c(-5, 5) ) +
+    theme_bw(base_size = 10) +
+    theme(legend.title = element_blank() ) +
+    labs(
+      x = "Log EMG peak amplitude",
+      title = paste0(
+        "BF10 = ", round(1 / hyp_ooi$hypothesis$Evid.Ratio, 3),
+        " (BF01 = ", round(hyp_ooi$hypothesis$Evid.Ratio, 3), ")"
+        )
+      )
+
+hyp_oos <- hypothesis(
+    varying_effects,
+    "OOS_conditionDIS = OOS_conditionRUM"
+    )
+
+p3 <- plot(hyp_oos, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
+    geom_vline(xintercept = 0, linetype = 2) +
+    coord_cartesian(xlim = c(-5, 5) ) +
+    theme_bw(base_size = 10) +
+    theme(legend.title = element_blank() ) +
+    labs(
+      x = "Log EMG peak amplitude",
+      title = paste0(
+        "BF10 = ", round(1 / hyp_oos$hypothesis$Evid.Ratio, 3),
+        " (BF01 = ", round(hyp_oos$hypothesis$Evid.Ratio, 3), ")"
+        )
+      )
+
+p1 + p2 + p3 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
+```
+
+A summary of the estimations from this model is presented in Table \@ref(tab:summary).
+For each muscle, the intercept gives the estimated of the natural logarithm of the EMG peak amplitude in the baseline condition, whereas the `conditionDIS` and `conditionRUM` parameters indicate deviations from the baseline in the distraction and rumination conditions (respectively).
+
+```{r summary, result = "asis"}
+summary_varying_effects <- 
+    # retrieve estimations from bmod5
+    summary(varying_effects, prob = 0.95)$fixed %>%
+    # convert to dataframe
+    data.frame %>%
+    # sets rownames as the first column
+    rownames_to_column(var = "response") %>%
+    # removing ESS information
+    dplyr::select(-Bulk_ESS, -Tail_ESS) %>%
+    # split response name as two columns
+    # separate(col = response, into = c("response", "term"), sep = "_", extra = "merge") %>%
+    # rename columns
+    magrittr::set_colnames(
+        c("Term", "Estimate", "SE", "Lower", "Upper", "Rhat")
+        ) %>%
+    # compute BF for each effect
+    mutate(
+        BF10 = 1 / hypothesis(varying_effects, glue("{Term} = 0") )$hypothesis$Evid.Ratio
+        ) %>%
+    # round BFs
+    # mutate(BF01 = ifelse(BF01 < .001, "<0.001", BF01) ) %>%
+    mutate(BF10 = ifelse(BF10 < .001, changeSciNot(BF10), round(BF10, 3) ) ) %>%
+    # if numeric, round to 3 decimals
+    mutate_if(is.numeric, round, 3)
+
+apa_table(
+    summary_varying_effects,
+    placement = "H",
+    align = c("l", rep("c", 6) ),
+    caption = "Estimated value of the natural logarithm of the EMG peak amplitude in each condition and for each muscle.",
+    note = "For each effect, the 'Estimate' reports the estimated average value of the natural logarithm of the EMG peak amplitude, followed by its standard error (SE).
+The 'Lower' and 'Upper' columns contain the lower and upper bounds of the 95% CrI, whereas the 'Rhat' column reports the Gelman-Rubin statistic.
+The last column reports the BF in favour of the alternative hypothesis (relative to the null hypothesis).",
+    small = TRUE,
+    escape = TRUE
+    )
+```
+
+...
+
+## Concluding on the null from low-powered studies: what could go wrong?
 
@@
 
-## Manipulating rumination within-subject
+## Within-subject manipulation of rumination and distraction
 
@@
 
-## Does everyone?
+## Does everyone show the effect?
 
@@
 
-## Relation between self-report and EMG correlates
+## Relating the subjective inner experience to the psychophysiological correlates
 
@@
 
-...
+Acknowledgements will be included in the final version of this manuscript.
 

### 2020-09-30 manuscript.tex
minor updates in manuscript

@@
   english,
-  man,floatsintext]{apa6}
+  man, donotrepeattitle,floatsintext]{apa6}
 \usepackage{lmodern}
@@
 \hypersetup{
-  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the absence of evidence fallacy},
   pdflang={en-EN},
@@
 
-\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
+\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy\\
+~\\
+Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.}
 
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 1727
-
 \newpage
@@
 
-The activity of silently talking to oneself or ``inner speech'' is a foundational ability\ldots{} despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions'' (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014})\ldots{}
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan self-motivate or self-regulate.
+Despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions'' (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014})\ldots{}
 
-Given the predominantly verbal nature of rumination {[}{]}, we previously proposed to study rumination as other forms of inner speech have been studied in the past, namely using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020})\ldots{}
-
-We have previously shown that\ldots{} However, it was unclear\ldots{} therefore, the extension of our study by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), which consisted by including a distraction control group, is more than welcome\ldots{} However\ldots{}
+Given the predominantly verbal nature of rumination (e.g., Ehring \& Watkins, \protect\hyperlink{ref-ehring_repetitive_2008}{2008}; Goldwin et al., \protect\hyperlink{ref-goldwin_concreteness_2013}{2013}; Goldwin \& Behar, \protect\hyperlink{ref-goldwin_concreteness_2012}{2012}; McLaughlin et al., \protect\hyperlink{ref-mclaughlin_effects_2007}{2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used historically to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+However, because the rumination condition did not have a proper control condition in this first study, it was unclear whether this perioral activity were specifically related to (inner) speech processes.
+Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+Although these discussions were blatantly ignored by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech''.
-In other words, their conclusion is that inner experience is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+This is unlikely to be the case here, for reasons that we will present and discuss in the following.
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
 That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
-This suggests unexplored variation in the determinants of this effects (e.g., the content of the inner experience).
+This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
 Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
@@
 
+Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) recorded\ldots{} in 26 participants (data available at \url{https://osf.io/hj7tz/})\ldots{} The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (\texttt{FRO}, \texttt{OOI}, \texttt{OOS}).
+
 \begin{figure}[!htb]
@@
 
-\caption{Average log-EMG amplitude by muscle and condition.
+\caption{Average natural logarithm of the EMG peak amplitude per muscle and condition.
 The black dots and intervals represent the by-group average and 95\% confidence interval (N = 26).
@@
 
-\ldots{}
+We fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017})\ldots{}
 
@@
 
-\hypertarget{concluding-on-the-null-from-low-powered-studies-is-uninformative}{%
-\subsection{Concluding on the null from low-powered studies is uninformative}\label{concluding-on-the-null-from-low-powered-studies-is-uninformative}}
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/bf-1}
+
+}
+
+\caption{Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
+The BF is computed as the ratio of the posterior density to the prior density at $\theta = 0$.}\label{fig:bf}
+\end{figure}
+
+A summary of the estimations from this model is presented in Table \ref{tab:summary}.
+For each muscle, the intercept gives the estimated of the natural logarithm of the EMG peak amplitude in the baseline condition, whereas the \texttt{conditionDIS} and \texttt{conditionRUM} parameters indicate deviations from the baseline in the distraction and rumination conditions (respectively).
+
+\begin{table}[H]
+
+\begin{center}
+\begin{threeparttable}
+
+\caption{\label{tab:summary}Estimated value of the natural logarithm of the EMG peak amplitude in each condition and for each muscle.}
+
+\small{
+
+\begin{tabular}{lcccccc}
+\toprule
+Term & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{Lower} & \multicolumn{1}{c}{Upper} & \multicolumn{1}{c}{Rhat} & \multicolumn{1}{c}{BF10}\\
+\midrule
+FRO\_Intercept & -2.08 & 0.10 & -2.27 & -1.89 & 1.00 & NA\\
+OOS\_Intercept & -2.36 & 0.14 & -2.64 & -2.09 & 1.00 & NA\\
+OOI\_Intercept & -2.29 & 0.12 & -2.52 & -2.05 & 1.00 & NA\\
+FRO\_conditionDIS & 0.00 & 0.07 & -0.14 & 0.13 & 1.00 & 0.06\\
+FRO\_conditionRUM & 0.22 & 0.07 & 0.09 & 0.36 & 1.00 & 10.51\\
+OOS\_conditionDIS & 0.16 & 0.11 & -0.06 & 0.38 & 1.00 & 0.35\\
+OOS\_conditionRUM & 0.21 & 0.11 & -0.01 & 0.43 & 1.00 & 0.71\\
+OOI\_conditionDIS & 0.29 & 0.12 & 0.06 & 0.53 & 1.00 & 2.31\\
+OOI\_conditionRUM & 0.37 & 0.12 & 0.14 & 0.61 & 1.00 & 15.22\\
+\bottomrule
+\addlinespace
+\end{tabular}
+
+}
+
+\begin{tablenotes}[para]
+\normalsize{\textit{Note.} For each effect, the 'Estimate' reports the estimated average value of the natural logarithm of the EMG peak amplitude, followed by its standard error (SE).
+The 'Lower' and 'Upper' columns contain the lower and upper bounds of the 95\% CrI, whereas the 'Rhat' column reports the Gelman-Rubin statistic.
+The last column reports the BF in favour of the alternative hypothesis (relative to the null hypothesis).}
+\end{tablenotes}
+
+\end{threeparttable}
+\end{center}
+
+\end{table}
+
+\ldots{}
+
+\hypertarget{concluding-on-the-null-from-low-powered-studies-what-could-go-wrong}{%
+\subsection{Concluding on the null from low-powered studies: what could go wrong?}\label{concluding-on-the-null-from-low-powered-studies-what-could-go-wrong}}
 
@@
 
-\hypertarget{manipulating-rumination-within-subject}{%
-\subsection{Manipulating rumination within-subject}\label{manipulating-rumination-within-subject}}
+\hypertarget{within-subject-manipulation-of-rumination-and-distraction}{%
+\subsection{Within-subject manipulation of rumination and distraction}\label{within-subject-manipulation-of-rumination-and-distraction}}
 
@@
 
-\hypertarget{does-everyone}{%
-\subsection{Does everyone?}\label{does-everyone}}
+\hypertarget{does-everyone-show-the-effect}{%
+\subsection{Does everyone show the effect?}\label{does-everyone-show-the-effect}}
 
@@
 
-\hypertarget{relation-between-self-report-and-emg-correlates}{%
-\subsection{Relation between self-report and EMG correlates}\label{relation-between-self-report-and-emg-correlates}}
+\hypertarget{relating-the-subjective-inner-experience-to-the-psychophysiological-correlates}{%
+\subsection{Relating the subjective inner experience to the psychophysiological correlates}\label{relating-the-subjective-inner-experience-to-the-psychophysiological-correlates}}
 
@@
 
-\ldots{}
+Acknowledgements will be included in the final version of this manuscript.
 
@@
 Bürkner, P.-C. (2017). brms: An R package for bayesian multilevel models using Stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\hypertarget{ref-ehring_repetitive_2008}{}%
+Ehring, T., \& Watkins, E.
+R.
+(2008).
+Repetitive negative thinking as a transdiagnostic process.
+\emph{International Journal of Cognitive Therapy}, \emph{1}(3), 192--205.
+\url{https://doi.org/10.1680/ijct.2008.1.3.192}
+
+\leavevmode\hypertarget{ref-goldwin_concreteness_2012}{}%
+Goldwin, M., \& Behar, E.
+(2012).
+Concreteness of idiographic periods of worry and depressive rumination.
+\emph{Cognitive Therapy and Research}, \emph{36}(6), 840--846.
+\url{https://doi.org/10.1007/s10608-011-9428-1}
+
+\leavevmode\hypertarget{ref-goldwin_concreteness_2013}{}%
+Goldwin, M., Behar, E., \& Sibrava, N.
+J.
+(2013).
+Concreteness of depressive rumination and trauma recall in individuals with elevated trait rumination and/or posttraumatic stress symptoms.
+\emph{Cognitive Therapy and Research}, \emph{37}(4), 680--689.
+\url{https://doi.org/10.1007/s10608-012-9507-y}
 
@@
 \url{https://doi.org/10.1093/bjps/axl003}
+
+\leavevmode\hypertarget{ref-mclaughlin_effects_2007}{}%
+McLaughlin, K.
+A., Borkovec, T.
+D., \& Sibrava, N.
+J.
+(2007).
+The effects of worry and rumination on affect states and cognitive activity.
+\emph{Behavior Therapy}, \emph{38}(1), 23--38.
+\url{https://doi.org/10.1016/j.beth.2006.03.003}
 

### 2020-09-30 manuscript.Rmd
minor updates in cover page

@@
 title: |
+  | **Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.**
+  | 
+  | 
   | Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy
-  | 
-  | Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.
 

### 2020-09-30 manuscript.tex
minor updates in cover page

@@
 
-\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy\\
+\title{\textbf{Submitted to Meta-Psychology.
+Click here to follow the fully transparent editorial process of this submission.
+Participate in open peer review by commenting through hypothes.is directly on this preprint.}\\
 ~\\
-Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.}
+~\\
+Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
 

### 2020-10-01 manuscript.Rmd
updating the manuscript

@@
 library(knitr)
+library(BEST)
 library(brms)
@@
 
-The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan self-motivate or self-regulate.
-Despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative...
-These inner speech "dysfunctions" [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018]...
+The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018].
+Although there are debates about the exact nature of inner speech and whether it is better described as the...
+of abstract linguistic representations or as the...
 
-Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used historically to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
+<!--
+
+However, whereas the use inner speech is associated with plenty of adaptive functions in everyday life, inner speech dysfunctions are suspected to play a role in multiple psychological disorders...
+
+-->
+
+Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period [@nalborczyk_orofacial_2017].
-However, because the rumination condition did not have a proper control condition in this first study, it was unclear whether this perioral activity were specifically related to (inner) speech processes.
+However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
 Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
@@
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
-This is unlikely to be the case here, for reasons that we will present and discuss in the following.
+This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
@@
 Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
-However, given the previous point, this appears highly problematic.
-We explore each of these limitations and suggests ways forward in the following section.
+However, given the important inter-individual variability, this reasoning appears highly problematic.
+In the following, we explore each of these limitations and suggests ways forward, both from a methodological and from a theoretical perspective.
 
 # Exploring the data
+
+As typical in studies manipulating induced rumination, @moffatt_inner_2020 designed a two-step protocol.
+First, they aimed to induce a negative mood by asking participants unsolvable and excessively difficult anagram and subtraction tasks, respectively.
+Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to "think about the causes, consequences, and meaning of their current feelings") or to distract themselves (by asking them to "think about a village, city or town that you are particularly familiar with").
+Rumination and distraction was manipulated within-subject, will all subjects alternating between rumination and distraction, in a counter-balanced order.
 
@@
 
-@moffatt_inner_2020 recorded...
-in 26 participants (data available at https://osf.io/hj7tz/)...
+Their final sample of participants, after data exclusion, included 26 participants (data available at https://osf.io/hj7tz/).
 The EMG data is depicted in Figure \@ref(fig:general) by condition (where `BAS`, `DIS`, and `RUM` refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (`FRO`, `OOI`, `OOS`).
+This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
+However, the average natural logarithm of the EMG peak amplitude recorded over the OOI and OOS muscles was higher than baseline in both the rumination and distraction conditions, with a slight increase from distraction to rumination (both on the mean and median).
 
@@
 
-We fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the `brms` package [@R-brms]...
+To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and *Condition* (baseline, rumination, distraction) as a categorical predictor.
+Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the `baseline` condition, and the slopes for the `rumination` and `distraction` conditions represent deviations from the baseline.
+These analyses were conducted using the `brms` package [@R-brms], an `R` implementation of Bayesian multilevel models that employs the probabilistic programming language `Stan` [@carpenter_stan_2017].
+We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations.
+Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
+Constant effects estimates were summarised via their posterior mean and 95% credible interval.
+We also report Bayes factors (BFs) computed using the Savage-Dickey method.^[This method simply consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point [@wagenmakers_bayesian_2010].] These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
+A summary of the estimations from this model is presented in Table \@ref(tab:summary).
+This analysis revealed that...
 
@@
 priors_constant <- c(
-    prior(normal(0, 10), class = Intercept, resp = "FRO"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "FRO"),
     prior(normal(0, 1), class = b, resp = "FRO"),
     prior(exponential(1), class = sigma, resp = "FRO"),
-    prior(normal(0, 10), class = Intercept, resp = "OOS"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOS"),
     prior(normal(0, 1), class = b, resp = "OOS"),
     prior(exponential(1), class = sigma, resp = "OOS"),
-    prior(normal(0, 10), class = Intercept, resp = "OOI"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOI"),
     prior(normal(0, 1), class = b, resp = "OOI"),
@@
 constant_effects <- brm(
-    mvbind(FRO, OOS, OOI) ~ 1 + condition,
+    mvbind(FRO, OOS, OOI) ~ 0 + Intercept + condition,
     family = gaussian(),
@@
 # priors for the varying-effects model
+# priors_varying <- c(
+#     prior(normal(0, 10), class = Intercept, resp = "FRO"),
+#     prior(normal(0, 1), class = b, resp = "FRO"),
+#     prior(exponential(1), class = sigma, resp = "FRO"),
+#     prior(exponential(1), class = sd, resp = "FRO"),
+#     prior(normal(0, 10), class = Intercept, resp = "OOS"),
+#     prior(normal(0, 1), class = b, resp = "OOS"),
+#     prior(exponential(1), class = sigma, resp = "OOS"),
+#     prior(exponential(1), class = sd, resp = "OOS"),
+#     prior(normal(0, 10), class = Intercept, resp = "OOI"),
+#     prior(normal(0, 1), class = b, resp = "OOI"),
+#     prior(exponential(1), class = sigma, resp = "OOI"),
+#     prior(exponential(1), class = sd, resp = "OOI")
+#     )
+
+# fitting the model
+# varying_effects <- brm(
+#     mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
+#     family = gaussian(),
+#     prior = priors_varying,
+#     data = df2,
+#     chains = 4, cores = detectCores(),
+#     warmup = 2000, iter = 10000,
+#     control = list(adapt_delta = 0.95),
+#     sample_prior = TRUE,
+#     file = here("models/varying_effects")
+#     )
+
+# priors for the varying-effects model
 priors_varying <- c(
-    prior(normal(0, 10), class = Intercept, resp = "FRO"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "FRO"),
     prior(normal(0, 1), class = b, resp = "FRO"),
@@
     prior(exponential(1), class = sd, resp = "FRO"),
-    prior(normal(0, 10), class = Intercept, resp = "OOS"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOS"),
     prior(normal(0, 1), class = b, resp = "OOS"),
@@
     prior(exponential(1), class = sd, resp = "OOS"),
-    prior(normal(0, 10), class = Intercept, resp = "OOI"),
+    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOI"),
     prior(normal(0, 1), class = b, resp = "OOI"),
@@
 
-# fitting the model
+# fitting the model (for computing the bf on the intercept)
 varying_effects <- brm(
-    mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
+    mvbind(FRO, OOS, OOI) ~ 0 + Intercept + condition + (0 + Intercept | ID),
     family = gaussian(),
@@
 
-Posterior distribution of the difference between the distraction and rumination conditions...
-
-```{r posterior, eval = FALSE, fig.cap = "..."}
-# extracts posterior samples
-post <- posterior_samples(varying_effects)
-
-plotPost(
-    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS,
-    compVal = 0#, ROPE = c(-0.1, 0.1)
-    )
-
-plotPost(
-    post$b_OOI_conditionRUM - post$b_OOI_conditionDIS,
-    compVal = 0#, ROPE = c(-0.1, 0.1)
-    )
-
-plotPost(
-    post$b_OOS_conditionRUM - post$b_OOS_conditionDIS,
-    compVal = 0#, ROPE = c(-0.1, 0.1)
-    )
-```
-
-```{r bf, fig.width = 10, fig.cap = "Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
+```{r bf, eval = FALSE, fig.width = 10, fig.cap = "Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
 The BF is computed as the ratio of the posterior density to the prior density at $\\theta = 0$."}
@@
 
-A summary of the estimations from this model is presented in Table \@ref(tab:summary).
-For each muscle, the intercept gives the estimated of the natural logarithm of the EMG peak amplitude in the baseline condition, whereas the `conditionDIS` and `conditionRUM` parameters indicate deviations from the baseline in the distraction and rumination conditions (respectively).
+```{r summary, result = "asis"}
+changeSciNot <- function(n) {
 
-```{r summary, result = "asis"}
+  output <- format(n, digits = 4, scientific = TRUE)
+  output <- sub("e", "*10^", output)
+  output <- sub("\\+0?", "", output)
+  output <- sub("-0?", "-", output)
+  output
+
+}
+
 summary_varying_effects <-
@@
     mutate(
-        BF10 = 1 / hypothesis(varying_effects, glue("{Term} = 0") )$hypothesis$Evid.Ratio
+        BF10 = 1 / hypothesis(
+          varying_effects, glue("{Term} = 0")
+          )$hypothesis$Evid.Ratio
         ) %>%
@@
     # mutate(BF01 = ifelse(BF01 < .001, "<0.001", BF01) ) %>%
-    mutate(BF10 = ifelse(BF10 < .001, changeSciNot(BF10), round(BF10, 3) ) ) %>%
+    mutate(
+      BF10 = ifelse(
+        BF10 < 0.001 | BF10 > 1e3,
+        changeSciNot(abs(BF10) ),
+        round(BF10, 3)
+        )
+      ) %>%
     # if numeric, round to 3 decimals
@@
     placement = "H",
+    digits = 3,
     align = c("l", rep("c", 6) ),
@@
 
-...
+Because the results of such an analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between the conditions of interest (i.e., the difference between the rumination and the distraction conditions).
+Thus, in Figure \@ref(fig:posterior) we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle...
 
-## Concluding on the null from low-powered studies: what could go wrong?
+```{r posterior, fig.width = 10, fig.height = 5, eval = TRUE, fig.cap = "Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\\% credible interval."}
+# extracts posterior samples
+post <- posterior_samples(varying_effects)
+
+# grid of plots
+par(mfrow = c(1, 3) )
+
+plotPost(
+    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS,
+    compVal = 0, xlab = "Rumination - Distraction", main = "FRO"
+    )
+
+plotPost(
+    post$b_OOI_conditionRUM - post$b_OOI_conditionDIS,
+    compVal = 0, xlab = "Rumination - Distraction", main = "OOI"
+    )
+
+plotPost(
+    post$b_OOS_conditionRUM - post$b_OOS_conditionDIS,
+    compVal = 0, xlab = "Rumination - Distraction", main = "OOS"
+    )
+```
+
+We now turn to a discussion of the problems related to conclusions that can be made from a low-powered non-significant result...
+
+## Concluding on the null from under-powered studies: what could go wrong?
 
 There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology [e.g., @harlow_problem_1997; @meehl_appraising_1990-1; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
-By "uninformative", we mean that some null-hypothesis significance tests are often *not* diagnostic with regards to the substantive question of interest...
+By "uninformative", we mean that some null-hypothesis significance tests are *not* diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
-As highlighted by many authors [e.g., @pollard_probability_1987; @rouder_is_2016], concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the...
-The argument from ignorance, such as "Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space."...
-the absence of evidence fallacy or fallacy of acceptance...
+As highlighted by many authors [e.g., @pollard_probability_1987; @rouder_is_2016], concluding that an effect is probably based on a non-significant *p*-value is the continuous (i.e., probabilistic) extension of the logical fallacy of the ...
+This fallacious argument is also known as the *fallacy of acceptance*, the *absence of evidence fallacy* or *the argument from ignorance*, which proceeds as follows: "Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space." This argument is fallacious in that it considers that not finding evidence for a claim is evidence for the contrapositive.
 
-This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the test has good *severity* [e.g., @mayo_severe_2006; @mayo_statistical_2018].
-In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is if it survives *severe tests*.
-In other words, some claim (e.g., $\theta = 0$) is said to be *severely tested*) if it had great chances of being falsified, was the claim false.
-More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ [@mayo_severe_2006; @mayo_statistical_2018]...To put it simply...
+This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the claim under scrutiny is submitted to *severe* tests [e.g., @mayo_severe_2006; @mayo_statistical_2018].
+In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
+More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, was the claim false.
+More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ the...
+[@mayo_severe_2006; @mayo_statistical_2018].
+To put it simply...
 https://www.analytics-toolkit.com/glossary/severity/...
 
-Anticipating the critics on the power of their study (a critic that was probably raised during peer review), @moffatt_inner_2020 report the results of a (possibly ran a posteriori) power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$, which is highly optimistic estimate of the substantive effect of interest in the target article (i.e., the difference in EMG amplitude between the rumination and distraction conditions) as this effects represents the standardised mean difference *between a rest period and a rumination one* [@nalborczyk_orofacial_2017]...
+When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong evidence (bad test, no evidence)...
 
-```{r power, echo = TRUE}
+Anticipating the legitimate critiques on the power of their study, @moffatt_inner_2020 report the results of a (possibly ran a posteriori) power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$.
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude *between a rest and a rumination periods* [@nalborczyk_orofacial_2017].
+
+```{r power, echo = FALSE}
 # How many participants do we need for a target statistical power of 0.8?
@@
 We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was much lower than suggested by the authors.
-Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction conditions may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+Indeed, we may speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
 If we assume that the former is half the size of the latter [which seems reasonable given the high inter-individual variability in such effects, cf.
-the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect, given that the effect in the population was actually $0.36$.
+the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually $0.36$).
 Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
@@
 ```{r actual_power, echo = TRUE}
-# A priori power for n = 26 (per condition) and d = 0.36
+# A priori power for n = 26 and d = 0.36
+library(pwr)
 pwr.t.test(
@@
 
-Anticipating the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
+Once again, anticipating the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
 
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power...
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power.
+More precisely, the sensitivity of an experiment design to detect a given effect is an issue that...
 
-```{r sensitivity, echo = FALSE, eval = FALSE}
-library(BayesFactor)
-# rscale = sqrt(2) / 2
-ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "medium")
-# rscale = 1
-ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "wide")
-# rscale = sqrt(2)
-ttestBF(x = df2$OOI[df2$condition == "RUM"], y = df2$OOI[df2$condition == "DIS"], paired = TRUE, rscale = "ultrawide")
-```
-
-We first fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the `brms` package [@R-brms].
-From there, we i) generated new datasets from the posterior predictive distribution and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
+In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by @moffatt_inner_2020.
+Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
 We used a "medium" prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
@@
 
-```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
-A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null)."}
+```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
+(2020).
+A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative hypothesis) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null hypothesis)."}
 # running the simulations
@@
     geom_hline(yintercept = 0, lty = 3) +
-    # geom_raster(fill = value_mean) +
     geom_ribbon(
@@
 
-As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
-More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles for sample sizes larger than 80 participants.
-For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.^[Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.]
+As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
+More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on adequately-powered samples support the alternative hypothesis for all three facial muscles.
+For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
+To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis) this pattern may very well reverse for higher sample sizes.
 
@@
 This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
-Most importantly, an assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest (in addition to the prior we specified earlier).
+A crucial assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest.
 However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
@@
 
-@haaf_developing_2017...
+...
 
@@
 
-Huge inter-individual variability... which leads to the next point, what is the relation between self-reports and EMG?
+Huge inter-individual variability...
+It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may be assessed formally via the model comparison approach developped by @haaf_developing_2017.
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [such as in @nalborczyk_can_2020], so that multilevel models with both varying intercepts and varying slopes could be estimated.
+
+<!--
+
+Which leads to the next point, what is the relation between self-reports and EMG?
 
@@
 
-...
+From page 10: "Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163).
+The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumina- tion second (t(29) = 2.513, p = 0.018, d = 0.903).
+In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first"...
+
+```{r reports, eval = FALSE}
+# reshaping from wide to long
+EMG <- df %>%
+    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS", "BAS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "EMG",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "muscle"),
+        sep = "_", extra = "merge"
+        ) %>%
+    # extracts muscle name
+    mutate(muscle = substr(muscle, 1, 3) )
+
+ESM <- df %>%
+    select(ID, order = Order, DIS_Future:RUM_Thoughts) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with(c("RUM", "DIS") ),
+        names_to = "condition",
+        # names_prefix = "wk",
+        values_to = "ESM",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = condition,
+        into = c("condition", "esm_scale"),
+        sep = "_", extra = "merge"
+        )
+
+VISQ <- df %>%
+    select(ID, order = Order, starts_with("VISQ") ) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with("VISQ"),
+        names_to = "visq_item",
+        # names_prefix = "wk",
+        values_to = "visq_value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = visq_item,
+        into = c("visq_item", "condition"),
+        sep = "_(?=[^_]+$)"
+        # sep = "_", extra = "merge"
+        )
+
+# MOOD <- df %>%
+#     select(ID, order = Order, PANAS_T1:VAS_Sad_T2) %>%
+#     na.omit
+
+VAS <- df %>%
+    select(ID, order = Order, VAS_Feelings_RUM:VAS_Problems_DIS) %>%
+    na.omit %>%
+    # reshapes data from wide to long format
+    pivot_longer(
+        cols = starts_with("VAS"),
+        names_to = "vas_item",
+        # names_prefix = "wk",
+        values_to = "vas_value",
+        values_drop_na = TRUE
+        ) %>%
+    separate(
+        col = vas_item,
+        into = c("vas_item", "condition"),
+        sep = "_(?=[^_]+$)"
+        # sep = "_", extra = "merge"
+        )
+
+df3 <- bind_cols(c(EMG, ESM, VAS, VISQ) )
+```
+
+-->
 
@@
 
-...
+Summary of the methodological arguments + theoretical discussion from @nalborczyk_understanding_2019...
+
+"Given that lip muscle activity has previously been related to inner speech production [23], this suggests that rumination has no specific boost of inner speech production relative to distraction.
+The increase in lip-muscle activity during states where thoughts were guided (rumination, distraction), compared to rest may therefore reflect the extra effort required to guide one’s thoughts and to engage in inner speech production"...
+
+"In conclusion, induced rumination appeared to involve similar levels of inner speech- related muscle activity to a period of distraction"...
 

### 2020-10-01 manuscript.tex
updating the manuscript

@@
 
-The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan self-motivate or self-regulate.
-Despite its multiple adaptive functions in everyday life, inner speech can go awry and leads to sustained negative\ldots{} These inner speech ``dysfunctions'' (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014})\ldots{}
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}).
+Although there are debates about the exact nature of inner speech and whether it is better described as the\ldots{} of abstract linguistic representations or as the\ldots{}
 
-Given the predominantly verbal nature of rumination (e.g., Ehring \& Watkins, \protect\hyperlink{ref-ehring_repetitive_2008}{2008}; Goldwin et al., \protect\hyperlink{ref-goldwin_concreteness_2013}{2013}; Goldwin \& Behar, \protect\hyperlink{ref-goldwin_concreteness_2012}{2012}; McLaughlin et al., \protect\hyperlink{ref-mclaughlin_effects_2007}{2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used historically to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+Given the predominantly verbal nature of rumination (e.g., Ehring \& Watkins, \protect\hyperlink{ref-ehring_repetitive_2008}{2008}; Goldwin et al., \protect\hyperlink{ref-goldwin_concreteness_2013}{2013}; Goldwin \& Behar, \protect\hyperlink{ref-goldwin_concreteness_2012}{2012}; McLaughlin et al., \protect\hyperlink{ref-mclaughlin_effects_2007}{2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
-However, because the rumination condition did not have a proper control condition in this first study, it was unclear whether this perioral activity were specifically related to (inner) speech processes.
+However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
 Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
@@
 Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
-However, given the previous point, this appears highly problematic.
-We explore each of these limitations and suggests ways forward in the following section.
+However, given the important inter-individual variability, this reasoning appears highly problematic.
+In the following, we explore each of these limitations and suggests ways forward, both from a methodological and from a theoretical perspective.
 
@@
 
-Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) recorded\ldots{} in 26 participants (data available at \url{https://osf.io/hj7tz/})\ldots{} The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (\texttt{FRO}, \texttt{OOI}, \texttt{OOS}).
+As typical in studies manipulating induced rumination, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
+First, they aimed to induce a negative mood by asking participants unsolvable and excessively difficult anagram and subtraction tasks, respectively.
+Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to ``think about the causes, consequences, and meaning of their current feelings'') or to distract themselves (by asking them to ``think about a village, city or town that you are particularly familiar with'').
+Rumination and distraction was manipulated within-subject, will all subjects alternating between rumination and distraction, in a counter-balanced order.
+
+Their final sample of participants, after data exclusion, included 26 participants (data available at \url{https://osf.io/hj7tz/}).
+The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (\texttt{FRO}, \texttt{OOI}, \texttt{OOS}).
+This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
+However, the average natural logarithm of the EMG peak amplitude recorded over the OOI and OOS muscles was higher than baseline in both the rumination and distraction conditions, with a slight increase from distraction to rumination (both on the mean and median).
 
@@
 
-We fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017})\ldots{}
-
-Posterior distribution of the difference between the distraction and rumination conditions\ldots{}
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/bf-1}
-
-}
-
-\caption{Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
-The BF is computed as the ratio of the posterior density to the prior density at $\theta = 0$.}\label{fig:bf}
-\end{figure}
-
+To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and \emph{Condition} (baseline, rumination, distraction) as a categorical predictor.
+Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the \texttt{baseline} condition, and the slopes for the \texttt{rumination} and \texttt{distraction} conditions represent deviations from the baseline.
+These analyses were conducted using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (Carpenter et al., \protect\hyperlink{ref-carpenter_stan_2017}{2017}).
+We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations.
+Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
+Constant effects estimates were summarised via their posterior mean and 95\% credible interval.
+We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method simply consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (Wagenmakers et al., \protect\hyperlink{ref-wagenmakers_bayesian_2010}{2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
 A summary of the estimations from this model is presented in Table \ref{tab:summary}.
-For each muscle, the intercept gives the estimated of the natural logarithm of the EMG peak amplitude in the baseline condition, whereas the \texttt{conditionDIS} and \texttt{conditionRUM} parameters indicate deviations from the baseline in the distraction and rumination conditions (respectively).
 
@@
 \midrule
-FRO\_Intercept & -2.08 & 0.10 & -2.27 & -1.89 & 1.00 & NA\\
-OOS\_Intercept & -2.36 & 0.14 & -2.64 & -2.09 & 1.00 & NA\\
-OOI\_Intercept & -2.29 & 0.12 & -2.52 & -2.05 & 1.00 & NA\\
-FRO\_conditionDIS & 0.00 & 0.07 & -0.14 & 0.13 & 1.00 & 0.06\\
-FRO\_conditionRUM & 0.22 & 0.07 & 0.09 & 0.36 & 1.00 & 10.51\\
-OOS\_conditionDIS & 0.16 & 0.11 & -0.06 & 0.38 & 1.00 & 0.35\\
-OOS\_conditionRUM & 0.21 & 0.11 & -0.01 & 0.43 & 1.00 & 0.71\\
-OOI\_conditionDIS & 0.29 & 0.12 & 0.06 & 0.53 & 1.00 & 2.31\\
-OOI\_conditionRUM & 0.37 & 0.12 & 0.14 & 0.61 & 1.00 & 15.22\\
+FRO\_Intercept & -2.076 & 0.096 & -2.266 & -1.888 & 1.000 & 1.785*10\textasciicircum{}16\\
+FRO\_conditionDIS & -0.006 & 0.066 & -0.136 & 0.124 & 1.000 & 0.068\\
+FRO\_conditionRUM & 0.223 & 0.067 & 0.091 & 0.354 & 1.000 & 19.703\\
+OOS\_Intercept & -2.362 & 0.142 & -2.641 & -2.085 & 1.000 & 4.254*10\textasciicircum{}14\\
+OOS\_conditionDIS & 0.165 & 0.111 & -0.053 & 0.384 & 1.000 & 0.336\\
+OOS\_conditionRUM & 0.212 & 0.111 & -0.005 & 0.432 & 1.000 & 0.689\\
+OOI\_Intercept & -2.284 & 0.117 & -2.514 & -2.053 & 1.001 & 7.411*10\textasciicircum{}15\\
+OOI\_conditionDIS & 0.290 & 0.120 & 0.054 & 0.526 & 1.000 & 2.006\\
+OOI\_conditionRUM & 0.371 & 0.119 & 0.137 & 0.603 & 1.000 & 12.876\\
 \bottomrule
@@
 
-\ldots{}
+Because the results of such an analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between the conditions of interest (i.e., the difference between the rumination and the distraction conditions).
+Thus, in Figure \ref{fig:posterior} we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle\ldots{}
 
-\hypertarget{concluding-on-the-null-from-low-powered-studies-what-could-go-wrong}{%
-\subsection{Concluding on the null from low-powered studies: what could go wrong?}\label{concluding-on-the-null-from-low-powered-studies-what-could-go-wrong}}
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/posterior-1}
+
+}
+
+\caption{Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\% credible interval.}\label{fig:posterior}
+\end{figure}
+
+We now turn to a discussion of the problems related to conclusions that can be made from a low-powered non-significant result\ldots{}
+
+\hypertarget{concluding-on-the-null-from-under-powered-studies-what-could-go-wrong}{%
+\subsection{Concluding on the null from under-powered studies: what could go wrong?}\label{concluding-on-the-null-from-under-powered-studies-what-could-go-wrong}}
 
 There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology (e.g., Meehl, \protect\hyperlink{ref-harlow_problem_1997}{1997}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990}\protect\hyperlink{ref-meehl_why_1990}{a}, \protect\hyperlink{ref-meehl_appraising_1990-1}{1990}\protect\hyperlink{ref-meehl_appraising_1990-1}{b}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}).
-By ``uninformative'', we mean that some null-hypothesis significance tests are often \emph{not} diagnostic with regards to the substantive question of interest\ldots{}
+By ``uninformative'', we mean that some null-hypothesis significance tests are \emph{not} diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
-As highlighted by many authors (e.g., Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding on an absence of difference based on not obtaining evidence for the difference is the continuous extension of the logical fallacy of the\ldots{} The argument from ignorance, such as ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.''\ldots{} the absence of evidence fallacy or fallacy of acceptance\ldots{}
+As highlighted by many authors (e.g., Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding that an effect is probably based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the logical fallacy of the \ldots{} This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, which proceeds as follows: ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.'' This argument is fallacious in that it considers that not finding evidence for a claim is evidence for the contrapositive.
 
-This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the test has good \emph{severity} (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
-In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is if it survives \emph{severe tests}.
-In other words, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested}) if it had great chances of being falsified, was the claim false.
-More formally, we can define \(\text{SEV}(T, x0, H)\), the severity with which claim \(H\) passes test \(T\) with outcome \(x0\), and \(\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})\) (Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}; Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006})\ldots To put it simply\ldots{} \url{https://www.analytics-toolkit.com/glossary/severity/}\ldots{}
+This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the claim under scrutiny is submitted to \emph{severe} tests (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
+In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
+More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, was the claim false.
+More formally, we can define \(\text{SEV}(T, x0, H)\), the severity with which claim \(H\) passes test \(T\) with outcome \(x0\), and \(\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})\) the\ldots{} (Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}; Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}).
+To put it simply\ldots{} \url{https://www.analytics-toolkit.com/glossary/severity/}\ldots{}
 
-Anticipating the critics on the power of their study (a critic that was probably raised during peer review), Moffatt et al.
+When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong evidence (bad test, no evidence)\ldots{}
+
+Anticipating the legitimate critiques on the power of their study, Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a (possibly ran a posteriori) power analysis using the effect size reported in Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\), which is highly optimistic estimate of the substantive effect of interest in the target article (i.e., the difference in EMG amplitude between the rumination and distraction conditions) as this effects represents the standardised mean difference \emph{between a rest period and a rumination one} (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017})\ldots{}
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# How many participants do we need for a target statistical power of 0.8?}
-\KeywordTok{library}\NormalTok{(pwr)}
-\KeywordTok{pwr.t.test}\NormalTok{(}
-  \DataTypeTok{d =} \FloatTok{0.72}\NormalTok{, }\DataTypeTok{sig.level =} \FloatTok{0.05}\NormalTok{, }\DataTypeTok{power =} \FloatTok{0.8}\NormalTok{,}
-  \DataTypeTok{type =} \StringTok{"one.sample"}\NormalTok{, }\DataTypeTok{alternative =} \StringTok{"two.sided"}
-\NormalTok{  )}
-\end{Highlighting}
-\end{Shaded}
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
-Indeed, we may speculate that the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and distraction conditions may be much weaker than the effect (i.e., the standardised mean difference in EMG amplitude) between the rumination and the rest conditions.
+Indeed, we may speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
 If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), therefore the a priori power of the main statistical test from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect, given that the effect in the population was actually \(0.36\).
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually \(0.36\)).
 Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
@@
 \begin{Highlighting}[]
-\CommentTok{\# A priori power for n = 26 (per condition) and d = 0.36}
+\CommentTok{\# A priori power for n = 26 and d = 0.36}
+\KeywordTok{library}\NormalTok{(pwr)}
 \KeywordTok{pwr.t.test}\NormalTok{(}
@@
 
-Anticipating the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence for the absence of an effect, Moffatt et al.
+Once again, anticipating the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence for the absence of an effect, Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis:
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve \emph{at all} the problem of low power\ldots{}
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve \emph{at all} the problem of low power.
+More precisely, the sensitivity of an experiment design to detect a given effect is an issue that\ldots{}
 
-We first fitted a multivariate Bayesian regression model with varying-intercepts (by participant) and weakly informative priors on these data using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}).
-From there, we i) generated new datasets from the posterior predictive distribution and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
+In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
 We used a ``medium'' prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
@@
 
-\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model.
-A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null).}\label{fig:simulated-power}
+\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
+(2020).
+A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative hypothesis) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null hypothesis).}\label{fig:simulated-power}
 \end{figure}
 
-As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with the sample size.
-More precisely, whereas low sample sizes (i.e., below 80) support the null hypothesis, adequately-powered sample sizes support the alternative hypothesis for all three facial muscles for sample sizes larger than 80 participants.
-For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.\footnote{Alternatively, the BF can be interpreted as an updating factor, from prior odds to posterior odds.}
+As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
+More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on adequately-powered samples support the alternative hypothesis for all three facial muscles.
+For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
+To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis) this pattern may very well reverse for higher sample sizes.
 
@@
 This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
-Most importantly, an assumption of the present analysis is that the data from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is our best source of information regarding the main effect of interest (in addition to the prior we specified earlier).
+A crucial assumption of the present analysis is that the data from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is our best source of information regarding the main effect of interest.
 However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
@@
 
-Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017})\ldots{}
+\ldots{}
 
@@
 
-Huge inter-individual variability\ldots{} which leads to the next point, what is the relation between self-reports and EMG?
-
-\hypertarget{relating-the-subjective-inner-experience-to-the-psychophysiological-correlates}{%
-\subsection{Relating the subjective inner experience to the psychophysiological correlates}\label{relating-the-subjective-inner-experience-to-the-psychophysiological-correlates}}
-
-\ldots{}
+Huge inter-individual variability\ldots{} It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may be assessed formally via the model comparison approach developped by Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (such as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), so that multilevel models with both varying intercepts and varying slopes could be estimated.
 
@@
 
-\ldots{}
+Summary of the methodological arguments + theoretical discussion from Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019})\ldots{}
+
+``Given that lip muscle activity has previously been related to inner speech production {[}23{]}, this suggests that rumination has no specific boost of inner speech production relative to distraction.
+The increase in lip-muscle activity during states where thoughts were guided (rumination, distraction), compared to rest may therefore reflect the extra effort required to guide one's thoughts and to engage in inner speech production''\ldots{}
+
+``In conclusion, induced rumination appeared to involve similar levels of inner speech- related muscle activity to a period of distraction''\ldots{}
 
@@
 Bürkner, P.-C. (2017). brms: An R package for bayesian multilevel models using Stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+
+\leavevmode\hypertarget{ref-carpenter_stan_2017}{}%
+Carpenter, B., Gelman, A., Hoffman, M., Lee, D., Goodrich, B., Betancourt, M., Brubaker, M., Guo, J., Li, P., \& Riddell, A.
+(2017).
+Stan: A probabilistic programming language.
+\emph{Journal of Statistical Software, Articles}, \emph{76}(1), 1--32.
+\url{https://doi.org/10.18637/jss.v076.i01}
 
@@
 
+\leavevmode\hypertarget{ref-wagenmakers_bayesian_2010}{}%
+Wagenmakers, E.-J., Lodewyckx, T., Kuriyal, H., \& Grasman, R.
+(2010).
+Bayesian hypothesis testing for psychologists: A tutorial on the SavageDickey method.
+\emph{Cognitive Psychology}, \emph{60}(3), 158--189.
+\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+
 \leavevmode\hypertarget{ref-R-tidyverse}{}%

### 2020-10-02 manuscript.Rmd
updating the manuscript

@@
 We suggest this conclusion is hasty and based on waggly evidence.
-Indeed, concluding on the absence of an effect based on a low-powered non-significant p-value is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly problematic/uninformative.
 Moreover, the relation between self-reports and physiological measures was not *directly* assessed, but only indirectly inferred from differences (or absence thereof) in group means.
 Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
-Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
+Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020 and we suggest ways forward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
 
-keywords: NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography
+keywords: NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography
 csl: csl/apa7.csl
@@
 
+-->
+
 Wordcount (excluding abstract, references, tables, and figures): `r wordcount`
-
--->
 
@@
 The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018].
-Although there are debates about the exact nature of inner speech and whether it is better described as the...
-of abstract linguistic representations or as the...
+However, whereas the use inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse [for a review, see @Nolen-Hoeksema2008].
 
@@
 
-However, whereas the use inner speech is associated with plenty of adaptive functions in everyday life, inner speech dysfunctions are suspected to play a role in multiple psychological disorders...
+Although there are debates about the exact nature of inner speech and whether it is better described as the mere evocation of abstract linguistic representations or as the simulation of executed (overt) speech, there is a considerable amount of evidence that (expanded) inner speech production is accompanied by peripheral muscular activity in the speech effectors [for an overview, see @nalborczyk_understanding_2019]...
 
@@
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative of other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
 This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
@@
 However, given the important inter-individual variability, this reasoning appears highly problematic.
-In the following, we explore each of these limitations and suggests ways forward, both from a methodological and from a theoretical perspective.
+In the following, we explore each of these limitations and suggests ways forward, both from a theoretical and from a methodological perspective.
 
@@
 Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to "think about the causes, consequences, and meaning of their current feelings") or to distract themselves (by asking them to "think about a village, city or town that you are particularly familiar with").
-Rumination and distraction was manipulated within-subject, will all subjects alternating between rumination and distraction, in a counter-balanced order.
+Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
 
@@
 To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and *Condition* (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the `baseline` condition, and the slopes for the `rumination` and `distraction` conditions represent deviations from the baseline.
+Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
 These analyses were conducted using the `brms` package [@R-brms], an `R` implementation of Bayesian multilevel models that employs the probabilistic programming language `Stan` [@carpenter_stan_2017].
@@
 A summary of the estimations from this model is presented in Table \@ref(tab:summary).
-This analysis revealed that...
+This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles.
+However, the BFs supported the null hypothesis (i.e., no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
 
@@
 
-Because the results of such an analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between the conditions of interest (i.e., the difference between the rumination and the distraction conditions).
-Thus, in Figure \@ref(fig:posterior) we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle...
+Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
+In Figure \@ref(fig:posterior) we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle.
+This figure reveals that the most probable value for this difference was $\beta = 0.228$ (95% CrI [0.098, 0.357]) for the FRO muscle, $\beta = 0.081$ (95% CrI [-0.155, 0.324]) for the FRO muscle, and $\beta = 0.047$ (95% CrI [-0.167, 0.27]) for the OOS muscle.
+Moreover, comparing the posterior distribution to $\theta = 0$ reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition [given the model, the priors, and the data from @moffatt_inner_2020].
 
-```{r posterior, fig.width = 10, fig.height = 5, eval = TRUE, fig.cap = "Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\\% credible interval."}
+```{r posterior, fig.width = 10, fig.height = 4, eval = TRUE, fig.cap = "Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\\% credible interval."}
 # extracts posterior samples
@@
 
-We now turn to a discussion of the problems related to conclusions that can be made from a low-powered non-significant result...
+Having nuanced some of the conclusions from @moffatt_inner_2020, we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
 
@@
 
-There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology [e.g., @harlow_problem_1997; @meehl_appraising_1990-1; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
-By "uninformative", we mean that some null-hypothesis significance tests are *not* diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
+There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology [e.g., @harlow_problem_1997; @meehl_appraising_1990-1; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
+By "uninformative", we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
-As highlighted by many authors [e.g., @pollard_probability_1987; @rouder_is_2016], concluding that an effect is probably based on a non-significant *p*-value is the continuous (i.e., probabilistic) extension of the logical fallacy of the ...
-This fallacious argument is also known as the *fallacy of acceptance*, the *absence of evidence fallacy* or *the argument from ignorance*, which proceeds as follows: "Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space." This argument is fallacious in that it considers that not finding evidence for a claim is evidence for the contrapositive.
+As highlighted by several authors [e.g., @cohen_earth_1994; @pollard_probability_1987; @rouder_is_2016], concluding that an effect is probably absent solely based on a non-significant *p*-value is the continuous (i.e., probabilistic) extension of the modus tollens and is not a valid argument (i.e., the conclusion does not follow from the premises).
+This fallacious argument is also known as the *fallacy of acceptance*, the *absence of evidence fallacy* or *the argument from ignorance*, and proceeds as follows: "If the null hypothesis is true, then this observation should *rarely* occur.
+This observation occurred.
+Therefore, the null hypothesis is false (or has low probability).
+In short, this argument is fallacious because it fails to consider the alternative hypothesis.
 
-This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the claim under scrutiny is submitted to *severe* tests [e.g., @mayo_severe_2006; @mayo_statistical_2018].
-In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
+<!--
+
+" Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space."
+
+-->
+
+This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to *severe* tests [e.g., @mayo_severe_2006; @mayo_statistical_2018].
+In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
 More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, was the claim false.
-More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ the...
-[@mayo_severe_2006; @mayo_statistical_2018].
-To put it simply...
-https://www.analytics-toolkit.com/glossary/severity/...
+When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
 
-When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong evidence (bad test, no evidence)...
+<!--
+
+More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ the severity of the test the claim $\mu > \mu_{1}$ was submitted to [@mayo_severe_2006; @mayo_statistical_2018]...
+
+-->
 
@@
 
-```{r power, echo = FALSE}
+```{r power, echo = FALSE, eval = FALSE}
 # How many participants do we need for a target statistical power of 0.8?
@@
 We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was much lower than suggested by the authors.
-Indeed, we may speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
+Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
 If we assume that the former is half the size of the latter [which seems reasonable given the high inter-individual variability in such effects, cf.
 the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually $0.36$).
-Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
 
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power.
-More precisely, the sensitivity of an experiment design to detect a given effect is an issue that...
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue both for frequentist and Bayesian statistical tests.
+To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
 
@@
 We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
-This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
+This analysis resembles to a loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
 A crucial assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest.
@@
 
-In @nalborczyk_dissociating_2020, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects...
-In contrast to this approach, @moffatt_inner_2020 asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure)...
+In @nalborczyk_dissociating_2020, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
+In contrast to this approach, @moffatt_inner_2020 asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
+In Figure \@ref(fig:order), we depict again the EMG data, this time grouped by the order in which the participants went through the rumination and distraction conditions.
+This figure reveals some potentially interesting differences between the two groups of participants.
+For instance, the participants that first went through the rumination condition (in green) seem to show a higher increase in the average EMG peak amplitude  recorded over the FRO muscle from baseline than the participants that first went through the distraction condition (in orange).
 
@@
       legend.title = element_blank(),
-      # legend.position = c(0.85, 0.85),
       legend.position = "top",
@@
 
-About the order effects, @moffatt_inner_2020 say:
+Anticipating again that the order of the within-subject conditions may be an issue, @moffatt_inner_2020 say:
 
@@
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative...
+Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
+Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the (possibly) very low power of the tests that were performed.
+This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \@ref(fig:order), which suggests possibly crucial differences between the two groups of participants.
+However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
 
@@
 
-...
+We previously noted [e.g., @nalborczyk_orofacial_2017; @nalborczyk_dissociating_2020; @nalborczyk_understanding_2019; @nalborczyk_can_2020] that surface EMG measures of inner speech production were highly variable between individuals.
+This can be explained by the imagery ability of each individual, the reliability of the measurement, and the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
+The data collected by @moffatt_inner_2020 is no exception and present an important degree of inter-individual variability.
+In Figure \@ref(fig:everyone), we represent again the EMG data for each participant (each line is a participant).
+We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
+As it can be seen from this figure, whereas some participants show "intermediate" or "ambiguous" patterns across the conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) or in the distraction condition (in orange).
 
@@
     theme_bw(base_size = 10) +
-    # scale_color_gradient2(midpoint = 0, low = "red", mid = "green", high = "blue", space = "Lab")
     scale_colour_brewer(palette = "Dark2", direction = -1) +
@@
 
-Huge inter-individual variability...
-It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may be assessed formally via the model comparison approach developped by @haaf_developing_2017.
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [such as in @nalborczyk_can_2020], so that multilevel models with both varying intercepts and varying slopes could be estimated.
+This important inter-individual variability calls into question the use of group averages to describe the nature of inner speech at an individual level.
+Moreover, this variability suggests that some important confounding factors were not taken into account (i.e., either not manipulated in the experiment or statistically controlled for).
+In line with @moffatt_inner_2020, we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
+We agree that a lot could be learnt by relating this (self-reported) subjective experience to the peripheral muscular correlates of inner speech production.
+However, this can not be done at the group level, at the risk of missing individual-level patterns.
+Therefore, we encourage @moffatt_inner_2020 to re-analyse their data to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
+
+It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by @haaf_developing_2017.
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [e.g., as in @nalborczyk_can_2020], so that multilevel models with both varying intercepts and varying slopes could be estimated.
 
@@
 
-Summary of the methodological arguments + theoretical discussion from @nalborczyk_understanding_2019...
+With this paper we aim to nuance the strong conclusion made by @moffatt_inner_2020, who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we reanalysed the data from @moffatt_inner_2020 and provided some nuance to the conclusion that can be made from these data.
+Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of @moffatt_inner_2020.
+Because the tests conducted by @moffatt_inner_2020 were heavily under-powered, they provide only weak evidence for the absence of difference.
+Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
+Finally, we showed that the group analyses masked important inter-individual variability that should be more carefully examined.
 
-"Given that lip muscle activity has previously been related to inner speech production [23], this suggests that rumination has no specific boost of inner speech production relative to distraction.
+In addition to these methodological limitations, we now wish the theoretical interpretations and implications of these results.
+As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
+Following our initial study [@nalborczyk_orofacial_2017], we ran an extension of this study in which we compared verbal to non-verbal rumination.
+The results of this study suggested that the facial EMG correlates of verbal and non-verbal rumination were similar [@nalborczyk_dissociating_2020].
+Given the ample evidence on the EMG correlates of inner speech production [for an overview, see Chapter 1 in @nalborczyk_understanding_2019], we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
+
+In @nalborczyk_dissociating_2020, we suggested that this observation was coherent with the mental-habit view of depressive rumination [@watkins_habit-goal_2014], which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+Indeed, habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the [e.g., @cohen_motor_1986; @sokolov_inner_1972]...
+
+In the discussion of @nalborczyk_understanding_2019, we discussed these findings in length and proposed several theoretical interpretations that can account for these results...
+
+<!--
+
+@nalborczyk_understanding_2019...
+
+@moffatt_inner_2020 stated that:
+
+> "Given that lip muscle activity has previously been related to inner speech production [23], this suggests that rumination has no specific boost of inner speech production relative to distraction.
 The increase in lip-muscle activity during states where thoughts were guided (rumination, distraction), compared to rest may therefore reflect the extra effort required to guide one’s thoughts and to engage in inner speech production"...
 
-"In conclusion, induced rumination appeared to involve similar levels of inner speech- related muscle activity to a period of distraction"...
+However...
+
+-->
+
+To conclude, we wish to bring some nuance to the conclusion of @moffatt_inner_2020, who stated that "In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction".
+In consideration of the limitations discussed in the present article, this conclusion seems hasty.
+Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence for the null hypothesis in this study.
+Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.
+Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
+We urge the authors to nuance their conclusions, to reanalyse their data, and to plan adequately powered future studies in order to settle these issues.
 

### 2020-10-02 manuscript.tex
updating the manuscript

@@
   pdflang={en-EN},
-  pdfkeywords={NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography},
+  pdfkeywords={NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography},
   hidelinks,
@@
 E-mail: ladislas.nalborczyk@gipsa-lab.fr}
-\keywords{NHST, Bayesian, fallacy, reanalysis, inner speech, rumination, electromyography}
+\keywords{NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography}
 \usepackage{lineno}
@@
 We suggest this conclusion is hasty and based on waggly evidence.
-Indeed, concluding on the absence of an effect based on a low-powered non-significant p-value is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly problematic/uninformative.
 Moreover, the relation between self-reports and physiological measures was not \emph{directly} assessed, but only indirectly inferred from differences (or absence thereof) in group means.
 Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
-Given these limitations, we conclude that it is unclear whether the target article adds to the current/extent knowledge and we suggest ways forward, both from a theoretical and from a methodological perspective.
+Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and we suggest ways forward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
@@
 \maketitle
+
+Wordcount (excluding abstract, references, tables, and figures): 3934
 
@@
 The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}).
-Although there are debates about the exact nature of inner speech and whether it is better described as the\ldots{} of abstract linguistic representations or as the\ldots{}
+However, whereas the use inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (Martin \& Tesser, \protect\hyperlink{ref-Martin}{1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse (for a review, see Nolen-Hoeksema et al., \protect\hyperlink{ref-Nolen-Hoeksema2008}{2008}).
 
@@
 Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to ``think about the causes, consequences, and meaning of their current feelings'') or to distract themselves (by asking them to ``think about a village, city or town that you are particularly familiar with'').
-Rumination and distraction was manipulated within-subject, will all subjects alternating between rumination and distraction, in a counter-balanced order.
+Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
 
@@
 To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and \emph{Condition} (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the \texttt{baseline} condition, and the slopes for the \texttt{rumination} and \texttt{distraction} conditions represent deviations from the baseline.
+Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
 These analyses were conducted using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (Carpenter et al., \protect\hyperlink{ref-carpenter_stan_2017}{2017}).
@@
 A summary of the estimations from this model is presented in Table \ref{tab:summary}.
+This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles.
+However, the BFs supported the null hypothesis (i.e., no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
 
@@
 
-Because the results of such an analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between the conditions of interest (i.e., the difference between the rumination and the distraction conditions).
-Thus, in Figure \ref{fig:posterior} we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle\ldots{}
+Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
+In Figure \ref{fig:posterior} we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle.
+This figure reveals that the most probable value for this difference was \(\beta = 0.228\) (95\% CrI {[}0.098, 0.357{]}) for the FRO muscle, \(\beta = 0.081\) (95\% CrI {[}-0.155, 0.324{]}) for the FRO muscle, and \(\beta = 0.047\) (95\% CrI {[}-0.167, 0.27{]}) for the OOS muscle.
+Moreover, comparing the posterior distribution to \(\theta = 0\) reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition (given the model, the priors, and the data from Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}).
 
@@
 
-We now turn to a discussion of the problems related to conclusions that can be made from a low-powered non-significant result\ldots{}
+Having nuanced some of the conclusions from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
 
@@
 
-There is an infamous tradition of running uninformative null-hypothesis significance tests in Psychology (e.g., Meehl, \protect\hyperlink{ref-harlow_problem_1997}{1997}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990}\protect\hyperlink{ref-meehl_why_1990}{a}, \protect\hyperlink{ref-meehl_appraising_1990-1}{1990}\protect\hyperlink{ref-meehl_appraising_1990-1}{b}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}).
-By ``uninformative'', we mean that some null-hypothesis significance tests are \emph{not} diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
+There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (e.g., Meehl, \protect\hyperlink{ref-harlow_problem_1997}{1997}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990}\protect\hyperlink{ref-meehl_why_1990}{a}, \protect\hyperlink{ref-meehl_appraising_1990-1}{1990}\protect\hyperlink{ref-meehl_appraising_1990-1}{b}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}).
+By ``uninformative'', we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
-As highlighted by many authors (e.g., Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding that an effect is probably based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the logical fallacy of the \ldots{} This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, which proceeds as follows: ``Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space.'' This argument is fallacious in that it considers that not finding evidence for a claim is evidence for the contrapositive.
+As highlighted by several authors (e.g., Cohen, \protect\hyperlink{ref-cohen_earth_1994}{1994}; Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding that an effect is probably absent solely based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the modus tollens and is not a valid argument (i.e., the conclusion does not follow from the premises).
+This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, and proceeds as follows: "If the null hypothesis is true, then this observation should \emph{rarely} occur.
+This observation occurred.
+Therefore, the null hypothesis is false (or has low probability).
+In short, this argument is fallacious because it fails to consider the alternative hypothesis.
 
-This problem is tackled in modern usages of null-hypothesis significance test by ensuring that the claim under scrutiny is submitted to \emph{severe} tests (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
-In general terms, we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
+This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to \emph{severe} tests (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
+In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
 More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, was the claim false.
-More formally, we can define \(\text{SEV}(T, x0, H)\), the severity with which claim \(H\) passes test \(T\) with outcome \(x0\), and \(\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})\) the\ldots{} (Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}; Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}).
-To put it simply\ldots{} \url{https://www.analytics-toolkit.com/glossary/severity/}\ldots{}
-
-When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong evidence (bad test, no evidence)\ldots{}
+When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
 
@@
 
-\begin{verbatim}
-## 
-##      One-sample t test power calculation 
-## 
-##               n = 17.16004
-##               d = 0.72
-##       sig.level = 0.05
-##           power = 0.8
-##     alternative = two.sided
-\end{verbatim}
-
 We suggest the (a priori) power of the study ran by Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
-Indeed, we may speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
+Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
 If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), therefore the a priori power of the main statistical test from Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually \(0.36\)).
-Because this is less than the chance of obtaining a head in a coin flip, we feel these resources may have been better invested.
 
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve \emph{at all} the problem of low power.
-More precisely, the sensitivity of an experiment design to detect a given effect is an issue that\ldots{}
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue both for frequentist and Bayesian statistical tests.
+To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-This analysis is the loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
+This analysis resembles to a loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
 A crucial assumption of the present analysis is that the data from Moffatt et al.
@@
 In Nalborczyk, Banjac, et al.
-(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects\ldots{} In contrast to this approach, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure)\ldots{}
+(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
+In contrast to this approach, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
+In Figure \ref{fig:order}, we depict again the EMG data, this time grouped by the order in which the participants went through the rumination and distraction conditions.
+This figure reveals some potentially interesting differences between the two groups of participants.
+For instance, the participants that first went through the rumination condition (in green) seem to show a higher increase in the average EMG peak amplitude recorded over the FRO muscle from baseline than the participants that first went through the distraction condition (in orange).
 
@@
 
-About the order effects, Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
+Anticipating again that the order of the within-subject conditions may be an issue, Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
 
@@
 
-Unfortunately, the same line of reasoning applies for testing the effect of the order, which is even less powered than the test of the main effect of interest, rendering it practically uninformative\ldots{}
+Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
+Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the (possibly) very low power of the tests that were performed.
+This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \ref{fig:order}, which suggests possibly crucial differences between the two groups of participants.
+However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
 
@@
 
-\ldots{}
+We previously noted (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}; Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}) that surface EMG measures of inner speech production were highly variable between individuals.
+This can be explained by the imagery ability of each individual, the reliability of the measurement, and the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
+The data collected by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and present an important degree of inter-individual variability.
+In Figure \ref{fig:everyone}, we represent again the EMG data for each participant (each line is a participant).
+We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
+As it can be seen from this figure, whereas some participants show ``intermediate'' or ``ambiguous'' patterns across the conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) or in the distraction condition (in orange).
 
@@
 
-Huge inter-individual variability\ldots{} It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may be assessed formally via the model comparison approach developped by Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (such as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), so that multilevel models with both varying intercepts and varying slopes could be estimated.
+This important inter-individual variability calls into question the use of group averages to describe the nature of inner speech at an individual level.
+Moreover, this variability suggests that some important confounding factors were not taken into account (i.e., either not manipulated in the experiment or statistically controlled for).
+In line with Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
+We agree that a lot could be learnt by relating this (self-reported) subjective experience to the peripheral muscular correlates of inner speech production.
+However, this can not be done at the group level, at the risk of missing individual-level patterns.
+Therefore, we encourage Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to re-analyse their data to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
+
+It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), so that multilevel models with both varying intercepts and varying slopes could be estimated.
 
@@
 
-Summary of the methodological arguments + theoretical discussion from Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019})\ldots{}
+With this paper we aim to nuance the strong conclusion made by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we reanalysed the data from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and provided some nuance to the conclusion that can be made from these data.
+Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+Because the tests conducted by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for the absence of difference.
+Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
+Finally, we showed that the group analyses masked important inter-individual variability that should be more carefully examined.
 
-``Given that lip muscle activity has previously been related to inner speech production {[}23{]}, this suggests that rumination has no specific boost of inner speech production relative to distraction.
-The increase in lip-muscle activity during states where thoughts were guided (rumination, distraction), compared to rest may therefore reflect the extra effort required to guide one's thoughts and to engage in inner speech production''\ldots{}
+In addition to these methodological limitations, we now wish the theoretical interpretations and implications of these results.
+As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
+Following our initial study (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), we ran an extension of this study in which we compared verbal to non-verbal rumination.
+The results of this study suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+Given the ample evidence on the EMG correlates of inner speech production (for an overview, see Chapter 1 in Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}), we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
 
-``In conclusion, induced rumination appeared to involve similar levels of inner speech- related muscle activity to a period of distraction''\ldots{}
+In Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (Watkins \& Nolen-Hoeksema, \protect\hyperlink{ref-watkins_habit-goal_2014}{2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+Indeed, habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972})\ldots{}
+
+In the discussion of Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}), we discussed these findings in length and proposed several theoretical interpretations that can account for these results\ldots{}
+
+To conclude, we wish to bring some nuance to the conclusion of Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction''.
+In consideration of the limitations discussed in the present article, this conclusion seems hasty.
+Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence for the null hypothesis in this study.
+Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.
+Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
+We urge the authors to nuance their conclusions, to reanalyse their data, and to plan adequately powered future studies in order to settle these issues.
 
@@
 \url{https://doi.org/10.18637/jss.v076.i01}
+
+\leavevmode\hypertarget{ref-cohen_motor_1986}{}%
+Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. Springer, Boston, MA.
+
+\leavevmode\hypertarget{ref-cohen_earth_1994}{}%
+Cohen, J. (1994). The earth is round (p \(<\) .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
 
@@
 Oxford University Press.
+
+\leavevmode\hypertarget{ref-Martin}{}%
+Martin, L.
+L., \& Tesser, A.
+(1996).
+Some ruminative thoughts.
+In R.
+S.
+Wyer (Ed.), \emph{Advances in social cognition, vol.
+9} (Vol.
+9, pp.
+1--47).
+Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc.
 
@@
 
+\leavevmode\hypertarget{ref-Nolen-Hoeksema2008}{}%
+Nolen-Hoeksema, S., Wisco, B.
+E., \& Lyubomirsky, S.
+(2008).
+Rethinking rumination.
+\emph{Perspectives on Psychological Science}, \emph{3}(5), 400--424.
+\url{https://doi.org/10.1111/j.1745-6924.2008.00088.x}
+
 \leavevmode\hypertarget{ref-perrone-bertolotti_what_2014}{}%
@@
 
+\leavevmode\hypertarget{ref-sokolov_inner_1972}{}%
+Sokolov, A. (1972). \emph{Inner speech and thought}. Springer-Verlag.
+
 \leavevmode\hypertarget{ref-wagenmakers_bayesian_2010}{}%
@@
 \url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+
+\leavevmode\hypertarget{ref-watkins_habit-goal_2014}{}%
+Watkins, E. R., \& Nolen-Hoeksema, S. (2014). A habit-goal framework of depressive rumination. \emph{Journal of Abnormal Psychology}, \emph{123}(1), 24--34. \url{https://doi.org/10.1037/a0035540}
 

### 2020-10-02 code/bf_simulation.R

@@ -3,7 +3,7 @@
 # Simulating the effect of sample size on BFs          #
 # ---------------------------------------------------- #
 # Ladislas Nalborczyk                                  #
-# Last updated on 30.09.2020                           #
+# Last updated on 01.10.2020                           #
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 

### 2020-10-04 manuscript.Rmd
minor updates in manuscript

@@
 Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that *self-reported* inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
-We suggest this conclusion is hasty and based on waggly evidence.
+We suggest this conclusion is at best hasty.
 Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly problematic/uninformative.
-Moreover, the relation between self-reports and physiological measures was not *directly* assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
+Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group averages is inappropriate.
 Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020 and we suggest ways forward, both from a theoretical and from a methodological perspective.
@@
 This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
-Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group means.
+Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group averages.
 However, given the important inter-individual variability, this reasoning appears highly problematic.
@@
 As typical in studies manipulating induced rumination, @moffatt_inner_2020 designed a two-step protocol.
-First, they aimed to induce a negative mood by asking participants unsolvable and excessively difficult anagram and subtraction tasks, respectively.
-Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to "think about the causes, consequences, and meaning of their current feelings") or to distract themselves (by asking them to "think about a village, city or town that you are particularly familiar with").
+First, they aimed to induce a negative mood by asking participants to solve unsolvable or excessively difficult anagram and subtraction tasks.
+Second, they prompted participants to either ruminate on these (purportedly induced) negative feelings (by asking them to "think about the causes, consequences, and meaning of their current feelings") or to distract themselves (by asking them to "think about a village, city or town that you are particularly familiar with").
 Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
@@
 This observation occurred.
-Therefore, the null hypothesis is false (or has low probability).
+Therefore, the null hypothesis is false (or has low probability)".
 In short, this argument is fallacious because it fails to consider the alternative hypothesis.
@@
 More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, was the claim false.
-When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
+When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
 
@@
 For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
-To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis) this pattern may very well reverse for higher sample sizes.
+To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis), this pattern may very well reverse for higher sample sizes.
 
 We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
-This analysis resembles to a loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
+This analysis resembles to the Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
 A crucial assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest.
@@
 Second, the present analysis relies on the posterior predictive distribution of the model fitted on the data from @moffatt_inner_2020, which naturally incorporates uncertainty about the effect of interest.
-By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the simulation.
+By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the results of the simulation.
 
@@
 We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
-As it can be seen from this figure, whereas some participants show "intermediate" or "ambiguous" patterns across the conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) or in the distraction condition (in orange).
+As it can be seen from this figure, whereas some participants show "intermediate" or "ambiguous" (i.e., equivalent) patterns of muscular activity across conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) and some others in the distraction condition (in orange).
 
@@
 However, this can not be done at the group level, at the risk of missing individual-level patterns.
-Therefore, we encourage @moffatt_inner_2020 to re-analyse their data to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
+Therefore, we encourage @moffatt_inner_2020 to analyse further their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
 
 It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by @haaf_developing_2017.
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [e.g., as in @nalborczyk_can_2020], so that multilevel models with both varying intercepts and varying slopes could be estimated.
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [e.g., as in @nalborczyk_can_2020].
 
@@
 
-In addition to these methodological limitations, we now wish the theoretical interpretations and implications of these results.
+In addition to these methodological limitations, we now wish to discuss the theoretical interpretations and implications of these results.
 As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
@@
 In @nalborczyk_dissociating_2020, we suggested that this observation was coherent with the mental-habit view of depressive rumination [@watkins_habit-goal_2014], which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
-Indeed, habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
 It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the [e.g., @cohen_motor_1986; @sokolov_inner_1972]...
@@
 Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
-We urge the authors to nuance their conclusions, to reanalyse their data, and to plan adequately powered future studies in order to settle these issues.
+We urge the authors to nuance their conclusions, to analyse further their data, and to plan adequately-powered studies in order to settle these issues.
 

### 2020-10-04 manuscript.tex
minor updates in manuscript

@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
-We suggest this conclusion is hasty and based on waggly evidence.
+We suggest this conclusion is at best hasty.
 Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly problematic/uninformative.
-Moreover, the relation between self-reports and physiological measures was not \emph{directly} assessed, but only indirectly inferred from differences (or absence thereof) in group means.
-Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group means is inappropriate.
+Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
+Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group averages is inappropriate.
 Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by Moffatt et al.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 3934
+Wordcount (excluding abstract, references, tables, and figures): 3933
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
-First, they aimed to induce a negative mood by asking participants unsolvable and excessively difficult anagram and subtraction tasks, respectively.
-Second, they prompted the participants to either ruminate on these (purportedly induced) negative feelings (by asking them to ``think about the causes, consequences, and meaning of their current feelings'') or to distract themselves (by asking them to ``think about a village, city or town that you are particularly familiar with'').
+First, they aimed to induce a negative mood by asking participants to solve unsolvable or excessively difficult anagram and subtraction tasks.
+Second, they prompted participants to either ruminate on these (purportedly induced) negative feelings (by asking them to ``think about the causes, consequences, and meaning of their current feelings'') or to distract themselves (by asking them to ``think about a village, city or town that you are particularly familiar with'').
 Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
@@
 As highlighted by several authors (e.g., Cohen, \protect\hyperlink{ref-cohen_earth_1994}{1994}; Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding that an effect is probably absent solely based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the modus tollens and is not a valid argument (i.e., the conclusion does not follow from the premises).
-This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, and proceeds as follows: "If the null hypothesis is true, then this observation should \emph{rarely} occur.
+This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, and proceeds as follows: ``If the null hypothesis is true, then this observation should \emph{rarely} occur.
 This observation occurred.
-Therefore, the null hypothesis is false (or has low probability).
+Therefore, the null hypothesis is false (or has low probability)''.
 In short, this argument is fallacious because it fails to consider the alternative hypothesis.
@@
 More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, was the claim false.
-When a statistical test is under-powered (for detecting a given effect size) the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
+When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
 
@@
 For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
-To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis) this pattern may very well reverse for higher sample sizes.
+To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis), this pattern may very well reverse for higher sample sizes.
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-This analysis resembles to a loose Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
+This analysis resembles to the Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
 A crucial assumption of the present analysis is that the data from Moffatt et al.
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), which naturally incorporates uncertainty about the effect of interest.
-By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the simulation.
+By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the results of the simulation.
 
@@
 We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
-As it can be seen from this figure, whereas some participants show ``intermediate'' or ``ambiguous'' patterns across the conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) or in the distraction condition (in orange).
+As it can be seen from this figure, whereas some participants show ``intermediate'' or ``ambiguous'' (i.e., equivalent) patterns of muscular activity across conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) and some others in the distraction condition (in orange).
 
@@
 Therefore, we encourage Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to re-analyse their data to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to analyse further their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
 
 It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), so that multilevel models with both varying intercepts and varying slopes could be estimated.
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}).
 
@@
 (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (Watkins \& Nolen-Hoeksema, \protect\hyperlink{ref-watkins_habit-goal_2014}{2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
-Indeed, habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
 It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972})\ldots{}

### 2020-10-04 code/bf_simulation.R

@@ -3,7 +3,7 @@
 # Simulating the effect of sample size on BFs          #
 # ---------------------------------------------------- #
 # Ladislas Nalborczyk                                  #
-# Last updated on 01.10.2020                           #
+# Last updated on 02.10.2020                           #
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 

### 2020-10-05 manuscript.Rmd
pushing a first final version

@@
 
-abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
 Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that *self-reported* inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
@@
 To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and *Condition* (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
+Therefore, the intercept represents the estimated natural logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
 These analyses were conducted using the `brms` package [@R-brms], an `R` implementation of Bayesian multilevel models that employs the probabilistic programming language `Stan` [@carpenter_stan_2017].
@@
 Constant effects estimates were summarised via their posterior mean and 95% credible interval.
-We also report Bayes factors (BFs) computed using the Savage-Dickey method.^[This method simply consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point [@wagenmakers_bayesian_2010].] These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
+We also report Bayes factors (BFs) computed using the Savage-Dickey method.^[This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point [@wagenmakers_bayesian_2010].] These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
 A summary of the estimations from this model is presented in Table \@ref(tab:summary).
@@
 
-## Concluding on the null from under-powered studies: what could go wrong?
+## Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could go wrong?
 
@@
 In short, this argument is fallacious because it fails to consider the alternative hypothesis.
-
-<!--
-
-" Science has found no proof of intelligent life nearby us in space, therefore intelligent life does not exist nearby us in space."
-
--->
 
@@
 the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually $0.36$).
+In other words, the chances of detecting the effect (was the effect actually non-null) were less than obtaining a head in a coin flip.
 
@@
 First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
-More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue both for frequentist and Bayesian statistical tests.
+More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
 To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
@@
 As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
-More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on adequately-powered samples support the alternative hypothesis for all three facial muscles.
+More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on larger samples support the alternative hypothesis for all three facial muscles.
 For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
@@
 
-```{r order, fig.cap = "Average log-EMG amplitude by muscle and condition.
-The black dots and intervals represent the by-group average and 95\\% confidence interval (N = 26).
-The horizontal white line in the violin plot represents the median.
-The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition."}
+```{r order, fig.cap = "Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
+The green dots and intervals represent the by-group average and 95\\% confidence interval for the participants that first went through the rumination condition, then through the distraction condition.
+The orange dots and intervals represent the by-group average and 95\\% confidence interval for the participants that first went through the distraction condition, then through the rumination condition.
+The light green and orange dots in the background represent the individual-level average natural logarithm of the EMG amplitude by muscle, condition, and group."}
 # position for groups
@@
 Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
-Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the (possibly) very low power of the tests that were performed.
+Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
 This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \@ref(fig:order), which suggests possibly crucial differences between the two groups of participants.
@@
 
-With this paper we aim to nuance the strong conclusion made by @moffatt_inner_2020, who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+With this paper we aimed to nuance the strong conclusion made by @moffatt_inner_2020, who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
 First, we reanalysed the data from @moffatt_inner_2020 and provided some nuance to the conclusion that can be made from these data.
@@
 We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
-It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the [e.g., @cohen_motor_1986; @sokolov_inner_1972]...
+Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system [e.g., @cohen_motor_1986; @sokolov_inner_1972].
+According to @cohen_motor_1986, the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
+For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
+Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of theses ideas in the broader context of motor imagery, @guillot_imagining_2012].
 
-In the discussion of @nalborczyk_understanding_2019, we discussed these findings in length and proposed several theoretical interpretations that can account for these results...
-
-<!--
-
-@nalborczyk_understanding_2019...
-
-@moffatt_inner_2020 stated that:
-
-> "Given that lip muscle activity has previously been related to inner speech production [23], this suggests that rumination has no specific boost of inner speech production relative to distraction.
-The increase in lip-muscle activity during states where thoughts were guided (rumination, distraction), compared to rest may therefore reflect the extra effort required to guide one’s thoughts and to engage in inner speech production"...
-
-However...
-
--->
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor systems [@nalborczyk_understanding_2019].
+In other words, the production of automatic or non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
+This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulations in speech perception and comprehension [@pickering_integrated_2013].
+The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more simulation of the motor action leading to the speech auditory percept.
+In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating/emulating the corresponding overt action [cf.
+also the motor simulation vs.
+direct simulation (memory retrieval) distinction in @tian_mental_2012].
+Whether the physiological correlates of automatic and non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective [cf.
+the discussion in @nalborczyk_understanding_2019].
 

### 2020-10-05 manuscript.tex
pushing a first final version

@@
 Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial (surface) electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
 Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, Moffatt et al.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 3933
+Wordcount (excluding abstract, references, tables, and figures): 4306
 
@@
 To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and \emph{Condition} (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
+Therefore, the intercept represents the estimated natural logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
 These analyses were conducted using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (Carpenter et al., \protect\hyperlink{ref-carpenter_stan_2017}{2017}).
@@
 Constant effects estimates were summarised via their posterior mean and 95\% credible interval.
-We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method simply consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (Wagenmakers et al., \protect\hyperlink{ref-wagenmakers_bayesian_2010}{2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
+We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (Wagenmakers et al., \protect\hyperlink{ref-wagenmakers_bayesian_2010}{2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
 A summary of the estimations from this model is presented in Table \ref{tab:summary}.
@@
 
-\hypertarget{concluding-on-the-null-from-under-powered-studies-what-could-go-wrong}{%
-\subsection{Concluding on the null from under-powered studies: what could go wrong?}\label{concluding-on-the-null-from-under-powered-studies-what-could-go-wrong}}
+\hypertarget{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-go-wrong}{%
+\subsection{Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could go wrong?}\label{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-go-wrong}}
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually \(0.36\)).
+In other words, the chances of detecting the effect (was the effect actually non-null) were less than obtaining a head in a coin flip.
 
@@
 First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
-More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue both for frequentist and Bayesian statistical tests.
+More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
 To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
@@
 As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
-More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on adequately-powered samples support the alternative hypothesis for all three facial muscles.
+More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on larger samples support the alternative hypothesis for all three facial muscles.
 For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
@@
 
-\caption{Average log-EMG amplitude by muscle and condition.
-The black dots and intervals represent the by-group average and 95\% confidence interval (N = 26).
-The horizontal white line in the violin plot represents the median.
-The grey dots represent the individual-level average natural logarithm of the EMG amplitude by muscle and condition.}\label{fig:order}
+\caption{Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
+The green dots and intervals represent the by-group average and 95\% confidence interval for the participants that first went through the rumination condition, then through the distraction condition.
+The orange dots and intervals represent the by-group average and 95\% confidence interval for the participants that first went through the distraction condition, then through the rumination condition.
+The light green and orange dots in the background represent the individual-level average natural logarithm of the EMG amplitude by muscle, condition, and group.}\label{fig:order}
 \end{figure}
@@
 Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
-Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the (possibly) very low power of the tests that were performed.
+Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
 This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \ref{fig:order}, which suggests possibly crucial differences between the two groups of participants.
@@
 
-With this paper we aim to nuance the strong conclusion made by Moffatt et al.
+With this paper we aimed to nuance the strong conclusion made by Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
@@
 We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
-It has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972})\ldots{}
+Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972}).
+According to Cohen (\protect\hyperlink{ref-cohen_motor_1986}{1986}), the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
+For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
+Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of theses ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
 
-In the discussion of Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}), we discussed these findings in length and proposed several theoretical interpretations that can account for these results\ldots{}
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor systems (Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+In other words, the production of automatic or non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
+This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulations in speech perception and comprehension (Pickering \& Garrod, \protect\hyperlink{ref-pickering_integrated_2013}{2013}).
+The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more simulation of the motor action leading to the speech auditory percept.
+In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating/emulating the corresponding overt action (cf.~also the motor simulation vs.~direct simulation (memory retrieval) distinction in Tian \& Poeppel, \protect\hyperlink{ref-tian_mental_2012}{2012}).
+Whether the physiological correlates of automatic and non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective (cf.~the discussion in Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 
@@
 \url{https://doi.org/10.1007/s10608-012-9507-y}
+
+\leavevmode\hypertarget{ref-grandchamp_condialint_2019}{}%
+Grandchamp, R., Rapin, L., Perrone-Bertolotti, M., Pichat, C., Haldin, C., Cousin, E., Lachaux, J.-P., Dohen, M., Perrier, P., Garnier, M., Baciu, M., \& Lœvenbruck, H.
+(2019).
+The ConDialInt Model: Condensation, Dialogality, and Intentionality Dimensions of Inner Speech Within a Hierarchical Predictive Control Framework.
+\emph{Frontiers in Psychology}, \emph{10}.
+\url{https://doi.org/10.3389/fpsyg.2019.02019}
+
+\leavevmode\hypertarget{ref-guillot_imagining_2012}{}%
+Guillot, A., Di Rienzo, F., MacIntyre, T., Moran, A., \& Collet, C.
+(2012).
+Imagining is not doing but involves specific motor commands: A review of experimental data related to motor inhibition.
+\emph{Frontiers in Human Neuroscience}, \emph{6}.
+\url{https://doi.org/10.3389/fnhum.2012.00247}
 
@@
 
+\leavevmode\hypertarget{ref-pickering_integrated_2013}{}%
+Pickering, M.
+J., \& Garrod, S.
+(2013).
+An integrated theory of language production and comprehension.
+\emph{Behavioral and Brain Sciences}, \emph{36}(04), 329--347.
+\url{https://doi.org/10.1017/S0140525X12001495}
+
 \leavevmode\hypertarget{ref-pollard_probability_1987}{}%
@@
 Sokolov, A. (1972). \emph{Inner speech and thought}. Springer-Verlag.
+
+\leavevmode\hypertarget{ref-tian_mental_2012}{}%
+Tian, X., \& Poeppel, D.
+(2012).
+Mental imagery of speech: Linking motor and perceptual systems through internal simulation and estimation.
+\emph{Frontiers in Human Neuroscience}, \emph{6}.
+\url{https://doi.org/10.3389/fnhum.2012.00314}
 

### 2020-10-06 manuscript.Rmd
adding the dance of the bf

@@
 the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually $0.36$).
+
+<!--
+
 In other words, the chances of detecting the effect (was the effect actually non-null) were less than obtaining a head in a coin flip.
+
+-->
 
@@
 
-<!--
-
-While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, computing a BF (i.e., comparing two models) does not solve *at all* the problem of low power (we discuss this issue in more depth below).
-Second, few details are given with regards to the exact models that were compared.
-Third, and most importantly, the BFs indicate moderate evidence in favour of the null for the OOI and OOS muscles.
-More precisely, these BFs indicated that the (observed) data are $1 / 0.232 \approx 4.31$ times more likely under the null than under the alternative hypothesis for the OOS and $1 / 0.278 \approx 3.6$ times more likely under the null than under the alternative hypothesis for the OOI.
-In other words, the evidence is favour of the null is relatively weak and sensitivity analyses (i.e., reporting the BF with varying prior scales for the alternative hypothesis) may unsurprisingly results in various BFs.
-For instance...
-
--->
-
 While we appreciate the effort, the current approach poses new problems.
@@
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
+To illustrate this point, we present below the results of two simulations.
 
+```{r bf-dance, fig.cap = "Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborcayk et al., 2017)."}
+# https://julianquandt.com/post/power-analysis-by-data-simulation-in-r-part-ii/
+# http://daniellakens.blogspot.com/2016/07/dance-of-bayes-factors.html
+# population effect size
+cohensd <- 0.36
+
+# sample size
+n <- 26
+
+# number of simulated experiments
+nsims <- 1e3
+
+# initialises an empty array to store results
+results <- data.frame(
+  BF10 = numeric(nsims),
+  BF10_null = numeric(nsims),
+  BF10_double = numeric(nsims)
+  )
+
+for (i in 1:nsims) { # for each simulated experiment
+
+  # produce N simulated participants
+  x <- rnorm(n = n, mean = 0, sd = 1)
+
+  # produce N simulated participants
+  y <- rnorm(n = n, mean = 0 + cohensd, sd = 1)
+
+  # produce N simulated participants
+  y_null <- rnorm(n = n, mean = 0, sd = 1)
+
+  # produce N simulated participants
+  y_double <- rnorm(n = n, mean = 0 + cohensd * 2, sd = 1)
+
+  results$BF10[i] <- ttestBF(
+    x = x, y = y, paired = TRUE, rscale = "medium"
+    ) %>%
+    data.frame %>%
+    pull(bf)
+
+  results$BF10_null[i] <- ttestBF(
+    x = x, y = y_null, paired = TRUE, rscale = "medium"
+    ) %>%
+    data.frame %>%
+    pull(bf)
+
+  results$BF10_double[i] <- ttestBF(
+    x = x, y = y_double, paired = TRUE, rscale = "medium"
+    ) %>%
+    data.frame %>%
+    pull(bf)
+
+}
+
+results %>%
+  pivot_longer(cols = BF10:BF10_double, names_to = "type") %>%
+  mutate(
+    type = factor(
+      type,
+      levels = c("BF10_null", "BF10", "BF10_double"),
+      labels = c("Cohen's d = 0", "Cohen's d = 0.36", "Cohen's d = 0.72")
+      )
+    ) %>%
+  ggplot(aes(x = log(value), fill = type) ) +
+  geom_density(alpha = 0.5, show.legend = FALSE) +
+  geom_vline(xintercept = 0, linetype = 2) +
+  theme_bw(base_size = 12) +
+  facet_wrap(~ type, scales = "free_x") +
+  labs(x = "Natural logarithm of the BF10", y = "Density") +
+  scale_colour_brewer(palette = "Dark2", direction = 1) +
+  scale_fill_brewer(palette = "Dark2", direction = 1)
+
+prop_d0 <- mean(results$BF10_null > 1)
+prop_d0.36 <- mean(results$BF10 > 1)
+prop_d0.72 <- mean(results$BF10_double > 1)
+```
+
+First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis), an effect size of d = 0.36 [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of d = 0.72 [i.e., the effect size reported in @nalborczyk_orofacial_2017].
+As shown in Figure \@ref(fig:bf-dance), the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
+For instance, under the null hypothesis (i.e., when the "true" effect size is d = 0), `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis.
+When the "true" effect size is of d = 0.36, `r round(100 - prop_d0.36 * 100, 2)`% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the "true" effect size is of d = 0.72, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
+In other words, for small sample and effect sizes, BFs have high error rates.
+
+Second, we conducted another simulation with the aim of assessing the relation between the sample size and the value of the BF.
 In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by @moffatt_inner_2020.

### 2020-10-06 manuscript.tex
adding the dance of the bf

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4306
+Wordcount (excluding abstract, references, tables, and figures): 4458
 
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually \(0.36\)).
-In other words, the chances of detecting the effect (was the effect actually non-null) were less than obtaining a head in a coin flip.
 
@@
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
+To illustrate this point, we present below the results of two simulations.
 
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/bf-dance-1}
+
+}
+
+\caption{Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborcayk et al., 2017).}\label{fig:bf-dance}
+\end{figure}
+
+First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis), an effect size of d = 0.36 (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of d = 0.72 (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
+For instance, under the null hypothesis (i.e., when the ``true'' effect size is d = 0), 6.20\% of the computed BFs are above 0 and hence support the alternative hypothesis.
+When the ``true'' effect size is of d = 0.36, 71.80\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of d = 0.72, 26.30\% of the BFs are still below 0.
+In other words, for small sample and effect sizes, BFs have high error rates.
+
+Second, we conducted another simulation with the aim of assessing the relation between the sample size and the value of the BF.
 In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by Moffatt et al.

### 2020-10-06 code/bf_simulation.R

@@ -3,7 +3,7 @@
 # Simulating the effect of sample size on BFs          #
 # ---------------------------------------------------- #
 # Ladislas Nalborczyk                                  #
-# Last updated on 02.10.2020                           #
+# Last updated on 05.10.2020                           #
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 
@@ -69,7 +69,7 @@ simulating_bfs <- function (n_obs) {
 }
 
 # number of simulations
-nsims <- 1e3
+nsims <- 1
 
 # defining the range of sample sizes
 sample_size <- seq.int(from = 20, to = 200, by = 10)
@@ -122,4 +122,35 @@ for (i in 1:nrow(overall_results) ) {
 }
 
 # saving the results
-save(overall_results, file = "results/overall_results.Rda")
+# save(overall_results, file = "results/overall_results.Rda")
+
+###############################
+# Speeding up the simulations #
+###############################
+
+# https://datashenanigan.wordpress.com/2016/01/15/speeding-bayesian-power-analysis-t-test-up-with-snowfall/
+# https://www4.stat.ncsu.edu/~post/isaac/parallel_programming_R.pdf
+
+# vectorisation using sapply (slightly faster, ~1.48mn for 1 sim, against 1.69mn for the for loop)
+# set.seed(123)
+# start_time <- proc.time()
+# sapply(sample_size, simulating_bfs)
+# print(proc.time() - start_time)
+
+# parallelisation using the parallel package
+# library(parallel)
+# num_cores <- detectCores() # / 2
+# my_cluster <- makeCluster(num_cores)
+# start_time <- proc.time()
+# results_parallel <- parSapply(my_cluster, sample_size, simulating_bfs)
+# print(proc.time() - start_time)
+# shut down the cluster
+# stopCluster(my_cluster)
+
+# parallelisation using the doParallel package (slightly faster, around 1.75mn for 1 simulation)
+# library(doParallel)
+# cl <- makeCluster(4)
+# registerDoParallel(cl)
+# start_time <- proc.time()
+# results_foreach <- foreach(n = sample_size, .packages = c("brms", "BayesFactor", "tidyverse") ) %dopar% simulating_bfs(n)
+# print(proc.time() - start_time)

### 2020-10-07 manuscript.Rmd
updating the bf dance simulation

@@
 ```{r bf-dance, fig.cap = "Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
-In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborcayk et al., 2017)."}
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017)."}
 # https://julianquandt.com/post/power-analysis-by-data-simulation-in-r-part-ii/
@@
 # number of simulated experiments
-nsims <- 1e3
+nsims <- 1e4
 
@@
 
-First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis), an effect size of d = 0.36 [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of d = 0.72 [i.e., the effect size reported in @nalborczyk_orofacial_2017].
+First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis of d = 0), an effect size of d = 0.36 [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of d = 0.72 [i.e., the effect size reported in @nalborczyk_orofacial_2017].
 As shown in Figure \@ref(fig:bf-dance), the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis (i.e., when the "true" effect size is d = 0), `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis.
+For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is d = 0).
 When the "true" effect size is of d = 0.36, `r round(100 - prop_d0.36 * 100, 2)`% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
 When the "true" effect size is of d = 0.72, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.
+In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the BF10 computed for the OOI by @moffatt_inner_2020 is "surprising" given or "compatible" with the sampling distribution of BFs under the hypothesis of an effect size of d = 0.36, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
 

### 2020-10-07 manuscript.tex
updating the bf dance simulation

--- 2020-10-05 manuscript.tex
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4306
+Wordcount (excluding abstract, references, tables, and figures): 4523
 
@@
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this, we present below the results of a simulation aiming to assess the relation between the sample size and the value of the BF.
+To illustrate this point, we present below the results of two simulations.
 
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/bf-dance-1}
+
+}
+
+\caption{Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017).}\label{fig:bf-dance}
+\end{figure}
+
+First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis of d = 0), an effect size of d = 0.36 (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of d = 0.72 (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
+For instance, under the null hypothesis, 6.96\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is d = 0).
+When the ``true'' effect size is of d = 0.36, 71.83\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of d = 0.72, 25.58\% of the BFs are still below 0.
+In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the BF10 computed for the OOI by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is ``surprising'' given or ``compatible'' with the sampling distribution of BFs under the hypothesis of an effect size of d = 0.36, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
+
+Second, we conducted another simulation with the aim of assessing the relation between the sample size and the value of the BF.
 In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by Moffatt et al.

### 2020-10-07 manuscript.Rmd
including feedback

@@
 We suggest this conclusion is at best hasty.
-Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly uninformative.
 Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
@@
 Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020 and we suggest ways forward, both from a theoretical and from a methodological perspective.
-Complete source code, reproducible analyses, and figures are available at https://github.com/lnalborczyk/inner_experience_EMG."
+Complete source code, reproducible analyses, and figures are available at https://osf.io/ba3gk/."
 
 keywords: NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography
+
 csl: csl/apa7.csl
@@
 
-# setting seed for reproducibility
-# set.seed(666)
-
 # setting up knitr options
@@
 
-<!--
-
-NB: You can add comments using these tags
-
--->
-
 Wordcount (excluding abstract, references, tables, and figures): `r wordcount`
@@
 
-<!--
-
-Although there are debates about the exact nature of inner speech and whether it is better described as the mere evocation of abstract linguistic representations or as the simulation of executed (overt) speech, there is a considerable amount of evidence that (expanded) inner speech production is accompanied by peripheral muscular activity in the speech effectors [for an overview, see @nalborczyk_understanding_2019]...
-
--->
-
 Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
@@
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
 We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of @nalborczyk_dissociating_2020 and more extensively in @nalborczyk_understanding_2019.
-Although these discussions were blatantly ignored by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
+Although these discussions were ignored by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
 
 The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech".
-In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
@@
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
-That is, some participants had higher perioral (OOS and OOI) muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
+That is, some participants had higher perioral muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
 This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
@@
 # data reshaping (from wide to long)
-# NB: 26 participants in the final dataset...
+# NB: 26 participants in the final dataset
 
@@
         names_to = "condition",
-        # names_prefix = "wk",
         values_to = "value",
@@
 Their final sample of participants, after data exclusion, included 26 participants (data available at https://osf.io/hj7tz/).
-The EMG data is depicted in Figure \@ref(fig:general) by condition (where `BAS`, `DIS`, and `RUM` refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (`FRO`, `OOI`, `OOS`).
+The EMG data is depicted in Figure \@ref(fig:general) by condition (where `BAS`, `DIS`, and `RUM` refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, `FRO`; orbicularis oris inferior `OOI`; and oribicularis oris superior, `OOS`).
 This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
@@
         position = pd,
-        # adjust = 0.8,
         draw_quantiles = 0.5,
@@
         geom = "line", size = 1,
-        # aes(group = interaction(muscle, order) ),
         aes(group = muscle),
@@
 A summary of the estimations from this model is presented in Table \@ref(tab:summary).
-This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles.
+This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles (as assessed by the BFs).
 However, the BFs supported the null hypothesis (i.e., no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
@@
 # priors for the varying-effects model
-# priors_varying <- c(
-#     prior(normal(0, 10), class = Intercept, resp = "FRO"),
-#     prior(normal(0, 1), class = b, resp = "FRO"),
-#     prior(exponential(1), class = sigma, resp = "FRO"),
-#     prior(exponential(1), class = sd, resp = "FRO"),
-#     prior(normal(0, 10), class = Intercept, resp = "OOS"),
-#     prior(normal(0, 1), class = b, resp = "OOS"),
-#     prior(exponential(1), class = sigma, resp = "OOS"),
-#     prior(exponential(1), class = sd, resp = "OOS"),
-#     prior(normal(0, 10), class = Intercept, resp = "OOI"),
-#     prior(normal(0, 1), class = b, resp = "OOI"),
-#     prior(exponential(1), class = sigma, resp = "OOI"),
-#     prior(exponential(1), class = sd, resp = "OOI")
-#     )
-
-# fitting the model
-# varying_effects <- brm(
-#     mvbind(FRO, OOS, OOI) ~ 1 + condition + (1 | ID),
-#     family = gaussian(),
-#     prior = priors_varying,
-#     data = df2,
-#     chains = 4, cores = detectCores(),
-#     warmup = 2000, iter = 10000,
-#     control = list(adapt_delta = 0.95),
-#     sample_prior = TRUE,
-#     file = here("models/varying_effects")
-#     )
-
-# priors for the varying-effects model
 priors_varying <- c(
@@
 
-# fitting the model (for computing the bf on the intercept)
+# fitting the model
 varying_effects <- brm(
@@
     dplyr::select(-Bulk_ESS, -Tail_ESS) %>%
-    # split response name as two columns
-    # separate(col = response, into = c("response", "term"), sep = "_", extra = "merge") %>%
     # rename columns
@@
     # round BFs
-    # mutate(BF01 = ifelse(BF01 < .001, "<0.001", BF01) ) %>%
     mutate(
@@
 
-## Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could go wrong?
+## Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could possibly go wrong?
 
@@
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
-More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, was the claim false.
+More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, had the claim been false.
 When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
 
-<!--
-
-More formally, we can define $\text{SEV}(T, x0, H)$, the severity with which claim $H$ passes test $T$ with outcome $x0$, and $\text{SEV}(\mu > \mu_{1}) = \Pr(d(X) \leq d(x0); \mu = \mu_{1})$ the severity of the test the claim $\mu > \mu_{1}$ was submitted to [@mayo_severe_2006; @mayo_statistical_2018]...
-
--->
-
-Anticipating the legitimate critiques on the power of their study, @moffatt_inner_2020 report the results of a (possibly ran a posteriori) power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$.
+Anticipating the legitimate critiques on the power of their study, @moffatt_inner_2020 report the results of a power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$.
 This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude *between a rest and a rumination periods* [@nalborczyk_orofacial_2017].
@@
 
-<!--
-
-In other words, the chances of detecting the effect (was the effect actually non-null) were less than obtaining a head in a coin flip.
-
--->
-
 ```{r actual_power, echo = TRUE}
@@
 
-Once again, anticipating the legitimate critique that the absence of a significant difference is not *necessarily* "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
+Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
 
@@
 
-```{r bf-dance, fig.cap = "Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
+```{r bf-dance, fig.cap = "Illustrating the distribution of Bayes factors in favour of the alternative hypothesis for different population effect sizes (N = 26).
 In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017)."}
-# https://julianquandt.com/post/power-analysis-by-data-simulation-in-r-part-ii/
-# http://daniellakens.blogspot.com/2016/07/dance-of-bayes-factors.html
+# inspired from http://daniellakens.blogspot.com/2016/07/dance-of-bayes-factors.html
 # population effect size
@@
 
-# initialises an empty array to store results
+# initialises an empty array to store the results
 results <- data.frame(
@@
 
-  # produce N simulated participants
+  # produces N simulated participants
   x <- rnorm(n = n, mean = 0, sd = 1)
 
-  # produce N simulated participants
+  # produces N simulated participants when d = 0.36
   y <- rnorm(n = n, mean = 0 + cohensd, sd = 1)
 
-  # produce N simulated participants
+  # produces N simulated participants when d = 0
   y_null <- rnorm(n = n, mean = 0, sd = 1)
 
-  # produce N simulated participants
+  # produces N simulated participants when d = 0.72
   y_double <- rnorm(n = n, mean = 0 + cohensd * 2, sd = 1)
 
+  # computes the BF10 when d = 0.36
   results$BF10[i] <- ttestBF(
@@
 
+  # computes the BF10 when d = 0
   results$BF10_null[i] <- ttestBF(
@@
 
+  # computes the BF10 when d = 0.72
   results$BF10_double[i] <- ttestBF(
@@
 
+# plotting the results
 results %>%
@@
 
+# computing the proportion of simulated BFs above 1
 prop_d0 <- mean(results$BF10_null > 1)
@@
 Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
-We used a "medium" prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
+We used a "medium" prior (i.e., $r = \sqrt{2}/2$) on the scale of the Cauchy prior for the alternative hypothesis.
 We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $1000$ simulations (i.e., 1000 simulated datasets) for each sample size.
@@
         aes(group = interaction(muscle, order) ),
-        # aes(group = muscle),
         position = pd,
@@
 
-Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
+Unfortunately, the problems we discussed in the previous section about the interpretation of under-powered non-significant results also apply to this test.
 Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
-This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \@ref(fig:order), which suggests possibly crucial differences between the two groups of participants.
+This statistical argument is supported by the visual exploration of the data presented in Figure \@ref(fig:order), which suggests possibly crucial differences between the two groups of participants.
 However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
@@
 This can be explained by the imagery ability of each individual, the reliability of the measurement, and the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
-The data collected by @moffatt_inner_2020 is no exception and present an important degree of inter-individual variability.
+The data collected by @moffatt_inner_2020 is no exception and presents an important degree of inter-individual variability.
 In Figure \@ref(fig:everyone), we represent again the EMG data for each participant (each line is a participant).
@@
 As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
-Following our initial study [@nalborczyk_orofacial_2017], we ran an extension of this study in which we compared verbal to non-verbal rumination.
-The results of this study suggested that the facial EMG correlates of verbal and non-verbal rumination were similar [@nalborczyk_dissociating_2020].
+Following our initial study [@nalborczyk_orofacial_2017], we ran an extension in which we compared verbal to non-verbal rumination.
+The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar [@nalborczyk_dissociating_2020].
 Given the ample evidence on the EMG correlates of inner speech production [for an overview, see Chapter 1 in @nalborczyk_understanding_2019], we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
@@
 
-Reproducible code and figures are available at https://github.com/lnalborczyk/inner_experience_EMG.
+Reproducible code and figures are available at https://osf.io/ba3gk/.
 
@@
 
-Acknowledgements will be included in the final version of this manuscript.
+We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for provding helpful comments on a previous version of this manuscript.
 

### 2020-10-07 manuscript.tex
including feedback

@@
 We suggest this conclusion is at best hasty.
-Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly problematic/uninformative.
+Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly uninformative.
 Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and we suggest ways forward, both from a theoretical and from a methodological perspective.
-Complete source code, reproducible analyses, and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
+Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ba3gk/}.
 }
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4523
+Wordcount (excluding abstract, references, tables, and figures): 4536
 
@@
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran an extension of this study, in which we compared verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
 We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of Nalborczyk, Banjac, et al.
 (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
-Although these discussions were blatantly ignored by Moffatt et al.
+Although these discussions were ignored by Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech''.
-In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the OOI and OOS muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
@@
 Their final sample of participants, after data exclusion, included 26 participants (data available at \url{https://osf.io/hj7tz/}).
-The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (\texttt{FRO}, \texttt{OOI}, \texttt{OOS}).
+The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, \texttt{FRO}; orbicularis oris inferior \texttt{OOI}; and oribicularis oris superior, \texttt{OOS}).
 This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
@@
 A summary of the estimations from this model is presented in Table \ref{tab:summary}.
-This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles.
+This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles (as assessed by the BFs).
 However, the BFs supported the null hypothesis (i.e., no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
@@
 
-\hypertarget{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-go-wrong}{%
-\subsection{Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could go wrong?}\label{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-go-wrong}}
+\hypertarget{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-possibly-go-wrong}{%
+\subsection{Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could possibly go wrong?}\label{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-possibly-go-wrong}}
 
@@
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
-More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, was the claim false.
+More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, had the claim been false.
 When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
@@
 Anticipating the legitimate critiques on the power of their study, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a (possibly ran a posteriori) power analysis using the effect size reported in Nalborczyk et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in Nalborczyk et al.
 (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
@@
 
-Once again, anticipating the legitimate critique that the absence of a significant difference is not \emph{necessarily} ``significant'' evidence for the absence of an effect, Moffatt et al.
+Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, Moffatt et al.
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis:
@@
 
-\caption{Illustrating the distribution of Bayes factors (also known as the 'Dance of the Bayes factors') in favour of the alternative hypothesis for different effect sizes (N = 26).
+\caption{Illustrating the distribution of Bayes factors in favour of the alternative hypothesis for different population effect sizes (N = 26).
 In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017).}\label{fig:bf-dance}
@@
 Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
-We used a ``medium'' prior (i.e., a scale of 1) on the scale of the Cauchy prior for the alternative hypothesis.
+We used a ``medium'' prior (i.e., \(r = \sqrt{2}/2\)) on the scale of the Cauchy prior for the alternative hypothesis.
 We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(1000\) simulations (i.e., 1000 simulated datasets) for each sample size.
@@
 
-Unfortunately, the problems we discussed in the next section about the interpretation of under-powered non-significant results also apply to this test.
+Unfortunately, the problems we discussed in the previous section about the interpretation of under-powered non-significant results also apply to this test.
 Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
-This statistical argument is supported by the brief visual exploration fo the data that we presented in Figure \ref{fig:order}, which suggests possibly crucial differences between the two groups of participants.
+This statistical argument is supported by the visual exploration of the data presented in Figure \ref{fig:order}, which suggests possibly crucial differences between the two groups of participants.
 However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
@@
 The data collected by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and present an important degree of inter-individual variability.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and presents an important degree of inter-individual variability.
 In Figure \ref{fig:everyone}, we represent again the EMG data for each participant (each line is a participant).
@@
 As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
-Following our initial study (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), we ran an extension of this study in which we compared verbal to non-verbal rumination.
-The results of this study suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+Following our initial study (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), we ran an extension in which we compared verbal to non-verbal rumination.
+The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
 Given the ample evidence on the EMG correlates of inner speech production (for an overview, see Chapter 1 in Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}), we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
@@
 
-Reproducible code and figures are available at \url{https://github.com/lnalborczyk/inner_experience_EMG}.
+Reproducible code and figures are available at \url{https://osf.io/ba3gk/}.
 
@@
 
-Acknowledgements will be included in the final version of this manuscript.
+We thank Antonio Schettino for suggesting to include the ``Dance of the Bayes factors'' simulation and for provding helpful comments on a previous version of this manuscript.
 

### 2020-10-07 manuscript.Rmd
fixing some typos

@@
 Their final sample of participants, after data exclusion, included 26 participants (data available at https://osf.io/hj7tz/).
-The EMG data is depicted in Figure \@ref(fig:general) by condition (where `BAS`, `DIS`, and `RUM` refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, `FRO`; orbicularis oris inferior `OOI`; and oribicularis oris superior, `OOS`).
+The EMG data is depicted in Figure \@ref(fig:general) by condition (where BAS, DIS, and RUM refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, FRO; orbicularis oris inferior, OOI; and orbicularis oris superior, OOS).
 This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
@@
 If we assume that the former is half the size of the latter [which seems reasonable given the high inter-individual variability in such effects, cf.
-the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.44$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually $0.36$).
+the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.42$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually $0.36$).
 
@@
 
-First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis of d = 0), an effect size of d = 0.36 [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of d = 0.72 [i.e., the effect size reported in @nalborczyk_orofacial_2017].
+First, we simulated 10.000 datasets (for $N = 26$) under the assumption of either no effect (i.e., the null hypothesis of $d = 0$), an effect size of $d = 0.36$ [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of $d = 0.72$ [i.e., the effect size reported in @nalborczyk_orofacial_2017].
 As shown in Figure \@ref(fig:bf-dance), the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is d = 0).
-When the "true" effect size is of d = 0.36, `r round(100 - prop_d0.36 * 100, 2)`% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the "true" effect size is of d = 0.72, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the BF10 computed for the OOI by @moffatt_inner_2020 is "surprising" given or "compatible" with the sampling distribution of BFs under the hypothesis of an effect size of d = 0.36, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
+For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is $d = 0$).
+When the "true" effect size is of $d = 0.36$, `r round(100 - prop_d0.36 * 100, 2)`% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
+In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the $\text{BF}_{10}$ computed for the OOI by @moffatt_inner_2020 is "surprising" given or "compatible" with the hypothesis of an effect size of $d = 0.36$, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
 

### 2020-10-07 manuscript.tex
fixing some typos

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4536
+Wordcount (excluding abstract, references, tables, and figures): 4549
 
@@
 Their final sample of participants, after data exclusion, included 26 participants (data available at \url{https://osf.io/hj7tz/}).
-The EMG data is depicted in Figure \ref{fig:general} by condition (where \texttt{BAS}, \texttt{DIS}, and \texttt{RUM} refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, \texttt{FRO}; orbicularis oris inferior \texttt{OOI}; and oribicularis oris superior, \texttt{OOS}).
+The EMG data is depicted in Figure \ref{fig:general} by condition (where BAS, DIS, and RUM refer to the baseline, distraction, and rumination conditions, respectively) and by muscle (frontalis, FRO; orbicularis oris inferior, OOI; and orbicularis oris superior, OOS).
 This figure shows that the average natural logarithm of the EMG peak amplitude recorded over the FRO was at similar levels in the baseline and distraction conditions, but was much higher in the rumination condition.
@@
 If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), therefore the a priori power of the main statistical test from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.44\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the effect in the population was actually \(0.36\)).
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
 
@@
 
-First, we simulated 10.000 datasets (for N = 26) under the assumption of either no effect (i.e., the null hypothesis of d = 0), an effect size of d = 0.36 (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of d = 0.72 (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+First, we simulated 10.000 datasets (for \(N = 26\)) under the assumption of either no effect (i.e., the null hypothesis of \(d = 0\)), an effect size of \(d = 0.36\) (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of \(d = 0.72\) (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, 6.96\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is d = 0).
-When the ``true'' effect size is of d = 0.36, 71.83\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the ``true'' effect size is of d = 0.72, 25.58\% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the BF10 computed for the OOI by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is ``surprising'' given or ``compatible'' with the sampling distribution of BFs under the hypothesis of an effect size of d = 0.36, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
+For instance, under the null hypothesis, 6.96\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
+When the ``true'' effect size is of \(d = 0.36\), 71.83\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of \(d = 0.72\), 25.58\% of the BFs are still below 0.
+In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the \(\text{BF}_{10}\) computed for the OOI by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is ``surprising'' given or ``compatible'' with the hypothesis of an effect size of \(d = 0.36\), we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
 

### 2020-10-07 code/bf_simulation.R
minor updates in readme

@@ -3,7 +3,7 @@
 # Simulating the effect of sample size on BFs          #
 # ---------------------------------------------------- #
 # Ladislas Nalborczyk                                  #
-# Last updated on 05.10.2020                           #
+# Last updated on 08.10.2020                           #
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 
@@ -123,34 +123,3 @@ for (i in 1:nrow(overall_results) ) {
 
 # saving the results
 # save(overall_results, file = "results/overall_results.Rda")
-
-###############################
-# Speeding up the simulations #
-###############################
-
-# https://datashenanigan.wordpress.com/2016/01/15/speeding-bayesian-power-analysis-t-test-up-with-snowfall/
-# https://www4.stat.ncsu.edu/~post/isaac/parallel_programming_R.pdf
-
-# vectorisation using sapply (slightly faster, ~1.48mn for 1 sim, against 1.69mn for the for loop)
-# set.seed(123)
-# start_time <- proc.time()
-# sapply(sample_size, simulating_bfs)
-# print(proc.time() - start_time)
-
-# parallelisation using the parallel package
-# library(parallel)
-# num_cores <- detectCores() # / 2
-# my_cluster <- makeCluster(num_cores)
-# start_time <- proc.time()
-# results_parallel <- parSapply(my_cluster, sample_size, simulating_bfs)
-# print(proc.time() - start_time)
-# shut down the cluster
-# stopCluster(my_cluster)
-
-# parallelisation using the doParallel package (slightly faster, around 1.75mn for 1 simulation)
-# library(doParallel)
-# cl <- makeCluster(4)
-# registerDoParallel(cl)
-# start_time <- proc.time()
-# results_foreach <- foreach(n = sample_size, .packages = c("brms", "BayesFactor", "tidyverse") ) %dopar% simulating_bfs(n)
-# print(proc.time() - start_time)

### 2020-10-08 manuscript.Rmd
updating the dance plot

@@
 
-Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis:
+Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis (p.12):
 
@@
 ```{r bf-dance, fig.cap = "Illustrating the distribution of Bayes factors in favour of the alternative hypothesis for different population effect sizes (N = 26).
-In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017)."}
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017).
+The red vertical dashed line indicates the value of the BF computed for the OOI by Moffatt et al.
+(2020), on the log scale."}
 # inspired from http://daniellakens.blogspot.com/2016/07/dance-of-bayes-factors.html
@@
 
-# sample size
+# sample size in Mofatt et al. (2020)
 n <- 26
@@
   ggplot(aes(x = log(value), fill = type) ) +
-  geom_density(alpha = 0.5, show.legend = FALSE) +
   geom_vline(xintercept = 0, linetype = 2) +
+  geom_vline(xintercept = log(0.278), linetype = 2, colour = "orangered") +
+  geom_histogram(colour = "white", show.legend = FALSE, bins = 50) +
   theme_bw(base_size = 12) +
   facet_wrap(~ type, scales = "free_x") +
-  labs(x = "Natural logarithm of the BF10", y = "Density") +
+  labs(x = "Natural logarithm of the BF10", y = "Number of simulations") +
   scale_colour_brewer(palette = "Dark2", direction = 1) +
@@
 When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the $\text{BF}_{10}$ computed for the OOI by @moffatt_inner_2020 is "surprising" given or "compatible" with the hypothesis of an effect size of $d = 0.36$, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
+In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the BF computed for the OOI by @moffatt_inner_2020 (i.e., $\text{BF}_{10} = 0.278$) is "surprising" given or "compatible" with the hypothesis of an effect size of $d = 0.36$, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
 
@@
 Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
-We used a "medium" prior (i.e., $r = \sqrt{2}/2$) on the scale of the Cauchy prior for the alternative hypothesis.
+We used a "medium" prior (i.e., $r = \sqrt{2}/2$) on the scale parameter of the Cauchy prior for the alternative hypothesis.
 We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $1000$ simulations (i.e., 1000 simulated datasets) for each sample size.
@@
 
-> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order."
+> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order." (p.7)
 
@@
 
-To conclude, we wish to bring some nuance to the conclusion of @moffatt_inner_2020, who stated that "In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction".
+To conclude, we wish to bring some nuance to the conclusion of @moffatt_inner_2020, who stated that "In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction" (p.14).
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
@@
 
-We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for provding helpful comments on a previous version of this manuscript.
+We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for providing helpful comments on a previous version of this manuscript.
 

### 2020-10-08 manuscript.tex
updating the dance plot

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4549
+Wordcount (excluding abstract, references, tables, and figures): 4561
 
@@
 Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis:
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis (p.12):
 
@@
 \caption{Illustrating the distribution of Bayes factors in favour of the alternative hypothesis for different population effect sizes (N = 26).
-In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017).}\label{fig:bf-dance}
+In the left panel, the effect size is fixed to d = 0 (i.e., the null hypothesis), in the middle panel, it is fixed to d = 0.36 (i.e., the supposed target effect size in Moffatt et al., 2020), and in the right panel, the effect size is fixed to d = 0.72 (i.e., the effect size reported in Nalborczyk et al., 2017).
+The red vertical dashed line indicates the value of the BF computed for the OOI by Moffatt et al.
+(2020), on the log scale.}\label{fig:bf-dance}
 \end{figure}
@@
 When the ``true'' effect size is of \(d = 0.72\), 25.58\% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the \(\text{BF}_{10}\) computed for the OOI by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is ``surprising'' given or ``compatible'' with the hypothesis of an effect size of \(d = 0.36\), we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
+In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the BF computed for the OOI by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with the hypothesis of an effect size of \(d = 0.36\), we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
 
@@
 Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
-We used a ``medium'' prior (i.e., \(r = \sqrt{2}/2\)) on the scale of the Cauchy prior for the alternative hypothesis.
+We used a ``medium'' prior (i.e., \(r = \sqrt{2}/2\)) on the scale parameter of the Cauchy prior for the alternative hypothesis.
 We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(1000\) simulations (i.e., 1000 simulated datasets) for each sample size.
@@
 \begin{quote}
-``Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order.''
+``Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order.'' (p.7)
 \end{quote}
@@
 To conclude, we wish to bring some nuance to the conclusion of Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction''.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction'' (p.14).
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
@@
 
-We thank Antonio Schettino for suggesting to include the ``Dance of the Bayes factors'' simulation and for provding helpful comments on a previous version of this manuscript.
+We thank Antonio Schettino for suggesting to include the ``Dance of the Bayes factors'' simulation and for providing helpful comments on a previous version of this manuscript.
 

### 2020-10-08 manuscript.Rmd
minor updates in plotting the dance of the BFs

@@
 
+# computing the proportion of simulated BFs above 1
+prop_d0 <- mean(results$BF10_null > 1)
+prop_d0.36 <- mean(results$BF10 > 1)
+prop_d0.72 <- mean(results$BF10_double > 1)
+
 # plotting the results
@@
     ) %>%
-  ggplot(aes(x = log(value), fill = type) ) +
+  ggplot(aes(x = log(value), colour = type, fill = type) ) +
   geom_vline(xintercept = 0, linetype = 2) +
   geom_vline(xintercept = log(0.278), linetype = 2, colour = "orangered") +
-  geom_histogram(colour = "white", show.legend = FALSE, bins = 50) +
+  geom_histogram(colour = "white", show.legend = FALSE, bins = 40) +
   theme_bw(base_size = 12) +
@@
   scale_colour_brewer(palette = "Dark2", direction = 1) +
-  scale_fill_brewer(palette = "Dark2", direction = 1)
-
-# computing the proportion of simulated BFs above 1
-prop_d0 <- mean(results$BF10_null > 1)
-prop_d0.36 <- mean(results$BF10 > 1)
-prop_d0.72 <- mean(results$BF10_double > 1)
+  scale_fill_brewer(palette = "Dark2", direction = 1) +
+  scale_y_continuous(expand =  expansion(mult = c(0, 0.1) ) )
 ```

### 2020-10-08 code/bf_simulation.R

@@ -3,7 +3,7 @@
 # Simulating the effect of sample size on BFs          #
 # ---------------------------------------------------- #
 # Ladislas Nalborczyk                                  #
-# Last updated on 08.10.2020                           #
+# Last updated on 06.10.2020                           #
 # https://github.com/lnalborczyk/inner_experience_EMG  #
 ########################################################
 

### 2020-10-12 manuscript.Rmd
pushing a first final version of the ms

@@
 
-The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech".
+The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech" (p.1).
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference should be substantiated by adequately-powered statistical tests (given the target effect size) as well as reliable measures.
 This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
@@
 This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles (as assessed by the BFs).
-However, the BFs supported the null hypothesis (i.e., no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
+However, the BFs supported the null hypothesis (i.e., the hypothesis of no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
 
@@
 Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
-In Figure \@ref(fig:posterior) we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle.
-This figure reveals that the most probable value for this difference was $\beta = 0.228$ (95% CrI [0.098, 0.357]) for the FRO muscle, $\beta = 0.081$ (95% CrI [-0.155, 0.324]) for the FRO muscle, and $\beta = 0.047$ (95% CrI [-0.167, 0.27]) for the OOS muscle.
+In Figure \@ref(fig:posterior), we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction conditions for each muscle.
+This figure reveals that the most probable value for this difference was $\beta = 0.228$ (95% CrI [0.098, 0.357]) for the FRO muscle, $\beta = 0.081$ (95% CrI [-0.155, 0.324]) for the OOI muscle, and $\beta = 0.047$ (95% CrI [-0.167, 0.27]) for the OOS muscle.
 Moreover, comparing the posterior distribution to $\theta = 0$ reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition [given the model, the priors, and the data from @moffatt_inner_2020].
@@
 Therefore, the null hypothesis is false (or has low probability)".
-In short, this argument is fallacious because it fails to consider the alternative hypothesis.
+In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
 
@@
 We previously noted [e.g., @nalborczyk_orofacial_2017; @nalborczyk_dissociating_2020; @nalborczyk_understanding_2019; @nalborczyk_can_2020] that surface EMG measures of inner speech production were highly variable between individuals.
-This can be explained by the imagery ability of each individual, the reliability of the measurement, and the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
+This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
 The data collected by @moffatt_inner_2020 is no exception and presents an important degree of inter-individual variability.
@@
 Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of @moffatt_inner_2020.
-Because the tests conducted by @moffatt_inner_2020 were heavily under-powered, they provide only weak evidence for the absence of difference.
+Because the statistical tests conducted by @moffatt_inner_2020 were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
 Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
@@
 In @nalborczyk_dissociating_2020, we suggested that this observation was coherent with the mental-habit view of depressive rumination [@watkins_habit-goal_2014], which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
-We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
 Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system [e.g., @cohen_motor_1986; @sokolov_inner_1972].
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of theses ideas in the broader context of motor imagery, @guillot_imagining_2012].
+Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of theses ideas in the broader context of motor imagery, @guillot_imagining_2012].
 
-Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor systems [@nalborczyk_understanding_2019].
-In other words, the production of automatic or non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
-This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulations in speech perception and comprehension [@pickering_integrated_2013].
-The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more simulation of the motor action leading to the speech auditory percept.
-In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating/emulating the corresponding overt action [cf.
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system [@nalborczyk_understanding_2019].
+In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
+This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulation in speech perception and comprehension [@pickering_integrated_2013].
+The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more on the simulation of the motor action leading to the speech auditory percept.
+In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating or emulating the corresponding overt action [cf.
 also the motor simulation vs.
-direct simulation (memory retrieval) distinction in @tian_mental_2012].
-Whether the physiological correlates of automatic and non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
-We previously discussed these issues in more length and suggested ways forward from an experimental perspective [cf.
-the discussion in @nalborczyk_understanding_2019].
+direct simulation distinction in @tian_mental_2012].
+Whether the physiological correlates of automatic versus non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of @nalborczyk_understanding_2019.
 
@@
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
-Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence for the null hypothesis in this study.
+Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
 Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.

### 2020-10-12 manuscript.tex
pushing a first final version of the ms

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4561
+Wordcount (excluding abstract, references, tables, and figures): 4578
 
@@
 The main conclusion from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech''.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
-However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference has to be based on sufficiently powered sample size (given the target effect size) as well as on reliable measures.
+However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference should be substantiated by adequately-powered statistical tests (given the target effect size) as well as reliable measures.
 This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
@@
 Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
-In Figure \ref{fig:posterior} we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle.
-This figure reveals that the most probable value for this difference was \(\beta = 0.228\) (95\% CrI {[}0.098, 0.357{]}) for the FRO muscle, \(\beta = 0.081\) (95\% CrI {[}-0.155, 0.324{]}) for the FRO muscle, and \(\beta = 0.047\) (95\% CrI {[}-0.167, 0.27{]}) for the OOS muscle.
+In Figure \ref{fig:posterior}, we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction conditions for each muscle.
+This figure reveals that the most probable value for this difference was \(\beta = 0.228\) (95\% CrI {[}0.098, 0.357{]}) for the FRO muscle, \(\beta = 0.081\) (95\% CrI {[}-0.155, 0.324{]}) for the OOI muscle, and \(\beta = 0.047\) (95\% CrI {[}-0.167, 0.27{]}) for the OOS muscle.
 Moreover, comparing the posterior distribution to \(\theta = 0\) reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition (given the model, the priors, and the data from Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}).
@@
 Therefore, the null hypothesis is false (or has low probability)''.
-In short, this argument is fallacious because it fails to consider the alternative hypothesis.
+In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
 
@@
 As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, 6.96\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
-When the ``true'' effect size is of \(d = 0.36\), 71.83\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the ``true'' effect size is of \(d = 0.72\), 25.58\% of the BFs are still below 0.
+For instance, under the null hypothesis, 6.46\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
+When the ``true'' effect size is of \(d = 0.36\), 72.06\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of \(d = 0.72\), 24.46\% of the BFs are still below 0.
 In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the BF computed for the OOI by Moffatt et al.
@@
 We previously noted (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}; Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}) that surface EMG measures of inner speech production were highly variable between individuals.
-This can be explained by the imagery ability of each individual, the reliability of the measurement, and the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
+This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
 The data collected by Moffatt et al.
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-Because the tests conducted by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for the absence of difference.
+Because the statistical tests conducted by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
 Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
@@
 (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (Watkins \& Nolen-Hoeksema, \protect\hyperlink{ref-watkins_habit-goal_2014}{2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
-We know habitual behaviours are more automatic (they are not intentionally initiated) than non-habitual behaviours.
+We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
 Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972}).
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of theses ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
+Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of theses ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
 
-Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor systems (Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
-In other words, the production of automatic or non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
-This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulations in speech perception and comprehension (Pickering \& Garrod, \protect\hyperlink{ref-pickering_integrated_2013}{2013}).
-The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more simulation of the motor action leading to the speech auditory percept.
-In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating/emulating the corresponding overt action (cf.~also the motor simulation vs.~direct simulation (memory retrieval) distinction in Tian \& Poeppel, \protect\hyperlink{ref-tian_mental_2012}{2012}).
-Whether the physiological correlates of automatic and non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
-We previously discussed these issues in more length and suggested ways forward from an experimental perspective (cf.~the discussion in Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system (Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
+This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulation in speech perception and comprehension (Pickering \& Garrod, \protect\hyperlink{ref-pickering_integrated_2013}{2013}).
+The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more on the simulation of the motor action leading to the speech auditory percept.
+In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating or emulating the corresponding overt action (cf.~also the motor simulation vs.~direct simulation distinction in Tian \& Poeppel, \protect\hyperlink{ref-tian_mental_2012}{2012}).
+Whether the physiological correlates of automatic versus non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 

### 2020-10-13 manuscript.Rmd
minor updates in rmd

@@
 
-Which leads to the next point, what is the relation between self-reports and EMG?
-
 ## Relating the subjective inner experience to the psychophysiological correlates
 
-From page 10: "Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163).
+"Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163).
 The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumina- tion second (t(29) = 2.513, p = 0.018, d = 0.903).
-In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first"...
+In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first".
 

### 2020-10-19 manuscript.Rmd
fixing some typos in the ms

@@
 The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018].
-However, whereas the use inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
+However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
 For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse [for a review, see @Nolen-Hoeksema2008].
@@
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
 We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of @nalborczyk_dissociating_2020 and more extensively in @nalborczyk_understanding_2019.
-Although these discussions were ignored by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
+Although these points were not addressed by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 
@@
 However, this can not be done at the group level, at the risk of missing individual-level patterns.
-Therefore, we encourage @moffatt_inner_2020 to analyse further their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
+Therefore, we encourage @moffatt_inner_2020 to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
 
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of theses ideas in the broader context of motor imagery, @guillot_imagining_2012].
+Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of these ideas in the broader context of motor imagery, @guillot_imagining_2012].
 
@@
 Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
-We urge the authors to nuance their conclusions, to analyse further their data, and to plan adequately-powered studies in order to settle these issues.
+We urge the authors to nuance their conclusions, to further analyse their data, and to plan adequately-powered studies in order to settle these issues.
 

### 2020-10-19 manuscript.tex
fixing some typos in the ms

@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4578
+Wordcount (excluding abstract, references, tables, and figures): 4579
 
@@
 The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}).
-However, whereas the use inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
+However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
 For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (Martin \& Tesser, \protect\hyperlink{ref-Martin}{1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse (for a review, see Nolen-Hoeksema et al., \protect\hyperlink{ref-Nolen-Hoeksema2008}{2008}).
@@
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we have previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
 We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of Nalborczyk, Banjac, et al.
 (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
-Although these discussions were ignored by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and the (self-reported) subjective experience.
+Although these points were not addressed by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 
@@
 Therefore, we encourage Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to analyse further their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
 
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of theses ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
+Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of these ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
 

### 2020-12-16 manuscript.Rmd
updating the manuscript

@@
 ---
-title: |
-  | **Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.**
-  | 
-  | 
-  | Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy
+title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy"
 
@@
 These analyses were conducted using the `brms` package [@R-brms], an `R` implementation of Bayesian multilevel models that employs the probabilistic programming language `Stan` [@carpenter_stan_2017].
-We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations.
+We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations, using weakly informative priors on all parameters (for more details, see the [supplementary materials](#supp)).
 Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
@@
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
-More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being falsified, had the claim been false.
+More precisely, some claim (e.g., $\theta = 0$) is said to be *severely tested* if it had great chances of being corroborated/falsified, had the claim been true/false.
 When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
@@
 
-```{r power, echo = FALSE, eval = FALSE}
+```{r power, echo = FALSE, eval = TRUE, fig.cap = "Statistical power as a function of both sample size and effect size, for a one-sample t-test with a significance level of 0.05.
+The white dot indicates the minimal effect size that can be detected with a probability equal or superior to 0.9 with a sample size of N = 26."}
 # How many participants do we need for a target statistical power of 0.8?
-library(pwr)
-pwr.t.test(
-  d = 0.72, sig.level = 0.05, power = 0.8,
-  type = "one.sample", alternative = "two.sided"
+# library(pwr)
+
+# pwr.anova.test(
+#   k = 3,
+#   # n = 26,
+#   f = 0.36,
+#   power = 0.8,
+#   sig.level = 0.05
+#   )
+# 
+# pwr.t.test(
+#   power = 0.8, d = 0.72, sig.level = 0.05,
+#   type = "one.sample", alternative = "two.sided"
+#   )
+
+# pwr.t.test(
+#   n = 10, d = 0.72, sig.level = 0.05,
+#   type = "one.sample", alternative = "two.sided"
+#   )
+
+# creating a grid of possible sample and effect sizes
+parameter_grid <- expand.grid(
+  sample_size = seq.int(from = 10, to = 100, length.out = 1e2),
+  effect_size = seq.int(from = 0.1, to = 1, length.out = 1e3)
   )
+
+# computing power for all combinations of sample and effect sizes
+parameter_grid$power <- power.t.test(
+  n = parameter_grid$sample_size,
+  delta = parameter_grid$effect_size,
+  sd = 1,
+  type = "one.sample",
+  alternative = "two.sided")$power
+
+# computing the effect size for a power = 0.8 at sample size = 26
+target <- parameter_grid %>%
+  filter(round(sample_size) == 26, round(power, 2) == 0.9) %>%
+  pull(effect_size) %>%
+  mean
+
+# plotting the results
+parameter_grid %>%
+  mutate(power = as.numeric(power) ) %>%
+  ggplot(aes(x = sample_size, y = effect_size, colour = NULL) ) +
+  geom_contour_filled(aes(z = power), alpha = 0.8) +
+  # geom_raster(aes(fill = power), interpolate = TRUE) +
+  geom_line(
+    data = parameter_grid %>% filter(round(power, 3) == 0.9),
+    color = "black", lwd = 0.8
+    ) +
+  geom_segment(
+    x = 26, xend = 26, y = 0, yend = target,
+    lwd = 0.5, linetype = 3
+    ) +
+  geom_segment(
+    x = 0, xend = 26, y = target, yend = target,
+    lwd = 0.5, linetype = 3
+    ) +
+  geom_point(
+    x = 26, y = target,
+    pch = 21, size = 3, fill = "white"
+    ) +
+  theme_bw(base_size = 12) +
+  labs(x = "Number of participants (per group)", y = "Standardised mean difference") +
+  coord_cartesian(expand = FALSE) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank() ) +
+  # scale_fill_manual(values = ., labels = seq(0.304, 2.129, length.out = 10) %>% round(2) )+
+  # guides(fill = guide_colorbar() )
+  # https://stackoverflow.com/questions/62543112/how-to-make-discrete-gradient-color-bar-with-geom-contour-filled
+  # metR::scale_fill_discretised()
+  # scale_fill_distiller(super = metR::ScaleDiscretised, palette = "RdYlBu") +
+  guides(fill = guide_legend(title = "Power", reverse = TRUE) )
 ```
@@
 the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.42$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually $0.36$).
+Notice that whereas taking half the effect size of @nalborczyk_orofacial_2017 may seem arbitrary, Figure \@ref(fig:power) shows that a one-sample t-test with a sample size of $N = 26$ is under-powered for a vast range of effect sizes.
 
-```{r actual_power, echo = TRUE}
+```{r actual_power, echo = FALSE, eval = FALSE}
 # A priori power for n = 26 and d = 0.36
@@
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this point, we present below the results of two simulations.
+To illustrate this point, we simulated 10.000 datasets (for $N = 26$) under the assumption of either no effect (i.e., the null hypothesis of $d = 0$), an effect size of $d = 0.36$ [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of $d = 0.72$ [i.e., the effect size reported in @nalborczyk_orofacial_2017].
 
@@
 
-# sample size in Mofatt et al. (2020)
+# sample size in Moffatt et al. (2020)
 n <- 26
@@
 
-First, we simulated 10.000 datasets (for $N = 26$) under the assumption of either no effect (i.e., the null hypothesis of $d = 0$), an effect size of $d = 0.36$ [i.e., the supposed target effect size in @moffatt_inner_2020], or an effect size of $d = 0.72$ [i.e., the effect size reported in @nalborczyk_orofacial_2017].
 As shown in Figure \@ref(fig:bf-dance), the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
@@
 When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.^[To assess the extent to which the BF computed for the OOI by @moffatt_inner_2020 (i.e., $\text{BF}_{10} = 0.278$) is "surprising" given or "compatible" with the hypothesis of an effect size of $d = 0.36$, we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to `r round(1 - mean(results$BF10 > 0.278), 2)`.]
+In other words, for small sample and effect sizes, BFs have high error rates.
+To assess the extent to which the BF computed for the OOI by @moffatt_inner_2020 (i.e., $\text{BF}_{10} = 0.278$) is "surprising" given or "compatible" with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to `r round(1 - mean(results$BF10_null > 0.278), 2)`, `r round(1 - mean(results$BF10 > 0.278), 2)`, and `r round(1 - mean(results$BF10_double > 0.278), 2)`, for the hypothesis of $d = 0$, $d = 0.36$, and $d = 0.72$, respectively.
+In other words, observing a $\text{BF}_{10} = 0.278$ is more compatible with the hypothesis of $d = 0$ (i.e., the null hypothesis) than with the hypothesis of $d = 0.36$ or $d = 0.72$ (at this sample size).
+
+<!--
 
@@
 By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the results of the simulation.
+
+-->
 
@@
 "Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163).
-The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumina- tion second (t(29) = 2.513, p = 0.018, d = 0.903).
+The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumination second (t(29) = 2.513, p = 0.018, d = 0.903).
 In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first".

### 2020-12-16 manuscript.tex
updating the manuscript

@@
 \hypersetup{
+  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the absence of evidence fallacy},
+  pdfauthor={Ladislas Nalborczyk1},
   pdflang={en-EN},
@@
 \urlstyle{same} % disable monospaced font for URLs
-\usepackage{color}
-\usepackage{fancyvrb}
-\newcommand{\VerbBar}{|}
-\newcommand{\VERB}{\Verb[commandchars=\\\{\}]}
-\DefineVerbatimEnvironment{Highlighting}{Verbatim}{commandchars=\\\{\}}
-% Add ',fontsize=\small' for more characters per line
-\usepackage{framed}
-\definecolor{shadecolor}{RGB}{248,248,248}
-\newenvironment{Shaded}{\begin{snugshade}}{\end{snugshade}}
-\newcommand{\AlertTok}[1]{\textcolor[rgb]{0.94,0.16,0.16}{#1}}
-\newcommand{\AnnotationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\AttributeTok}[1]{\textcolor[rgb]{0.77,0.63,0.00}{#1}}
-\newcommand{\BaseNTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\BuiltInTok}[1]{#1}
-\newcommand{\CharTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\CommentTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\CommentVarTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ConstantTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ControlFlowTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\DataTypeTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{#1}}
-\newcommand{\DecValTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\DocumentationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\ErrorTok}[1]{\textcolor[rgb]{0.64,0.00,0.00}{\textbf{#1}}}
-\newcommand{\ExtensionTok}[1]{#1}
-\newcommand{\FloatTok}[1]{\textcolor[rgb]{0.00,0.00,0.81}{#1}}
-\newcommand{\FunctionTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\ImportTok}[1]{#1}
-\newcommand{\InformationTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
-\newcommand{\KeywordTok}[1]{\textcolor[rgb]{0.13,0.29,0.53}{\textbf{#1}}}
-\newcommand{\NormalTok}[1]{#1}
-\newcommand{\OperatorTok}[1]{\textcolor[rgb]{0.81,0.36,0.00}{\textbf{#1}}}
-\newcommand{\OtherTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{#1}}
-\newcommand{\PreprocessorTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textit{#1}}}
-\newcommand{\RegionMarkerTok}[1]{#1}
-\newcommand{\SpecialCharTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\SpecialStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\StringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\VariableTok}[1]{\textcolor[rgb]{0.00,0.00,0.00}{#1}}
-\newcommand{\VerbatimStringTok}[1]{\textcolor[rgb]{0.31,0.60,0.02}{#1}}
-\newcommand{\WarningTok}[1]{\textcolor[rgb]{0.56,0.35,0.01}{\textbf{\textit{#1}}}}
 \usepackage{graphicx}
@@
   {}{\typeout{Failed to patch abstract.}}
+\patchcmd{\HyOrg@maketitle}
+  {\section{\protect\normalfont{\@title}}}
+  {\section*{\protect\normalfont{\@title}}}
+  {}{\typeout{Failed to patch title.}}
 \makeatother
 \shorttitle{The absence of evidence fallacy}
-\author{Ladislas Nalborczyk\textsuperscript{1}}
-\affiliation{
-\vspace{0.5cm}
-\textsuperscript{1} Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France}
-\authornote{
-
-Correspondence concerning this article should be addressed to Ladislas Nalborczyk, GIPSA-lab, CNRS, Univ.
-Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France.
-E-mail: ladislas.nalborczyk@gipsa-lab.fr}
 \keywords{NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography}
@@
 
-\title{\textbf{Submitted to Meta-Psychology.
-Click here to follow the fully transparent editorial process of this submission.
-Participate in open peer review by commenting through hypothes.is directly on this preprint.}\\
-~\\
-~\\
-Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
+\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
+\author{Ladislas Nalborczyk\textsuperscript{1}}
+\date{}
 
-\date{}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France}
 
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4579
+Wordcount (excluding abstract, references, tables, and figures): 4182
 
@@
 These analyses were conducted using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (Carpenter et al., \protect\hyperlink{ref-carpenter_stan_2017}{2017}).
-We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations.
+We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations, using weakly informative priors on all parameters (for more details, see the \protect\hyperlink{supp}{supplementary materials}).
 Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
@@
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
-More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being falsified, had the claim been false.
+More precisely, some claim (e.g., \(\theta = 0\)) is said to be \emph{severely tested} if it had great chances of being corroborated/falsified, had the claim been true/false.
 When a statistical test is under-powered (for detecting a given effect size), the claim under scrutiny is not strongly (severely) tested, hence it not possible to obtain strong or reliable evidence for the claim (bad test, no evidence).
@@
 
+\begin{figure}[!htb]
+
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/power-1}
+
+}
+
+\caption{Statistical power as a function of both sample size and effect size, for a one-sample t-test with a significance level of 0.05.
+The white dot indicates the minimal effect size that can be detected with a probability equal or superior to 0.9 with a sample size of N = 26.}\label{fig:power}
+\end{figure}
+
 We suggest the (a priori) power of the study ran by Moffatt et al.
@@
 (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
-
-\begin{Shaded}
-\begin{Highlighting}[]
-\CommentTok{\# A priori power for n = 26 and d = 0.36}
-\KeywordTok{library}\NormalTok{(pwr)}
-\KeywordTok{pwr.t.test}\NormalTok{(}
-  \DataTypeTok{n =} \DecValTok{26}\NormalTok{, }\DataTypeTok{d =} \FloatTok{0.72} \OperatorTok{/}\StringTok{ }\DecValTok{2}\NormalTok{, }\DataTypeTok{sig.level =} \FloatTok{0.05}\NormalTok{,}
-  \DataTypeTok{type =} \StringTok{"one.sample"}\NormalTok{, }\DataTypeTok{alternative =} \StringTok{"two.sided"}
-\NormalTok{  )}
-\end{Highlighting}
-\end{Shaded}
-
-\begin{verbatim}
-## 
-##      One-sample t test power calculation 
-## 
-##               n = 26
-##               d = 0.36
-##       sig.level = 0.05
-##           power = 0.4228455
-##     alternative = two.sided
-\end{verbatim}
+Notice that whereas taking half the effect size of Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
 
@@
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this point, we present below the results of two simulations.
+To illustrate this point, we simulated 10.000 datasets (for \(N = 26\)) under the assumption of either no effect (i.e., the null hypothesis of \(d = 0\)), an effect size of \(d = 0.36\) (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of \(d = 0.72\) (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 
@@
 
-First, we simulated 10.000 datasets (for \(N = 26\)) under the assumption of either no effect (i.e., the null hypothesis of \(d = 0\)), an effect size of \(d = 0.36\) (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of \(d = 0.72\) (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
@@
 When the ``true'' effect size is of \(d = 0.72\), 24.46\% of the BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.\footnote{To assess the extent to which the BF computed for the OOI by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with the hypothesis of an effect size of \(d = 0.36\), we can compute the probability of obtaining this finding or a more extreme finding given the hypothesis, which is approximately equal to 0.29.}
-
-Second, we conducted another simulation with the aim of assessing the relation between the sample size and the value of the BF.
-In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis (\(\text{BF}_{10}\)) using the \texttt{BayesFactor} package (Morey \& Rouder, \protect\hyperlink{ref-R-BayesFactor}{2018}).
-We used a ``medium'' prior (i.e., \(r = \sqrt{2}/2\)) on the scale parameter of the Cauchy prior for the alternative hypothesis.
-We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with \(1000\) simulations (i.e., 1000 simulated datasets) for each sample size.
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/simulated-power-1}
-
-}
-
-\caption{Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
-(2020).
-A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative hypothesis) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null hypothesis).}\label{fig:simulated-power}
-\end{figure}
-
-As shown in Figure \ref{fig:simulated-power}, the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
-More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on larger samples support the alternative hypothesis for all three facial muscles.
-For instance, the average \(\text{BF}_{10}\) computed for the OOI muscle with a sample size of 160 participants is of \(\exp(2.18) \approx 8.85\), indicating that these data are approximately \(8.85\) times more likely under the alternative hypothesis than under the null hypothesis.
-To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis), this pattern may very well reverse for higher sample sizes.
-
-We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-This analysis resembles to the Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised (e.g., Lakens, \protect\hyperlink{ref-lakens_20_2014}{2014}).
-A crucial assumption of the present analysis is that the data from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is our best source of information regarding the main effect of interest.
-However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
-First, with the present analysis, we do not aim to assess the ability of our statistical test to pass some dichotomic threshold (e.g., accept/reject).
-Instead, we aim to assess how the \(\text{BF}_{10}\) (i.e., the evidence for the alternative hypothesis, relative to the null hypothesis) behaves with varying sample sizes.
-Second, the present analysis relies on the posterior predictive distribution of the model fitted on the data from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), which naturally incorporates uncertainty about the effect of interest.
-By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the results of the simulation.
+In other words, for small sample and effect sizes, BFs have high error rates.
+To assess the extent to which the BF computed for the OOI by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.29, and 0.03, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
+In other words, observing a \(\text{BF}_{10} = 0.278\) is more compatible with the hypothesis of \(d = 0\) (i.e., the null hypothesis) than with the hypothesis of \(d = 0.36\) or \(d = 0.72\) (at this sample size).
 
@@
 
-\leavevmode\hypertarget{ref-lakens_20_2014}{}%
-Lakens, D. (2014). The 20\% Statistician: Observed power, and what to do if your editor asks for post-hoc power analyses. In \emph{The 20\% Statistician}.
-
 \leavevmode\hypertarget{ref-loevenbruck_cognitive_2018}{}%
@@
 \url{https://doi.org/10.1371/journal.pone.0238920}
-
-\leavevmode\hypertarget{ref-R-BayesFactor}{}%
-Morey, R. D., \& Rouder, J. N. (2018). \emph{BayesFactor: Computation of bayes factors for common designs}. \url{https://CRAN.R-project.org/package=BayesFactor}
 

### 2020-12-16 code/bf_simulation.R

@@ -1,125 +1,0 @@
-########################################################
-# Re-analysing the data from Moffatt et al. (2020)     #
-# Simulating the effect of sample size on BFs          #
-# ---------------------------------------------------- #
-# Ladislas Nalborczyk                                  #
-# Last updated on 06.10.2020                           #
-# https://github.com/lnalborczyk/inner_experience_EMG  #
-########################################################
-
-# function for simulating BFs with varying sample size
-simulating_bfs <- function (n_obs) {
-    
-    # extracting posterior samples from varying-effects model
-    post <- posterior_samples(varying_effects)
-    
-    # number of simulated participants
-    n_ppts <- n_obs
-    
-    # what are the conditions?
-    nd <- crossing(
-        distinct(df2, condition),
-        data.frame(ID = as.numeric(201:(201 + n_ppts - 1) ) )
-        )
-    
-    # simulating data
-    bf_simulated_data <- posterior_predict(
-        varying_effects,
-        newdata = nd,
-        allow_new_levels = TRUE,
-        sample_new_levels = "gaussian",
-        summary = FALSE,
-        nsamples = 1
-        )[1, , ] %>%
-        data.frame() %>%
-        bind_cols(nd) %>%
-        mutate(condition = factor(condition, labels = unique(nd$condition) ) ) %>%
-        pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
-        mutate(muscle = factor(muscle) )
-    
-    # reshaping the simulated data
-    bf_simulated_data_wide <- bf_simulated_data %>%
-        pivot_wider(names_from = muscle, values_from = value) %>%
-        mutate(ID = as.numeric(ID), condition = as.character(condition) )
-    
-    # computing the BF10 for the FRO muscle
-    bf_fro <- ttestBF(
-        x = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "RUM"],
-        y = bf_simulated_data_wide$FRO[bf_simulated_data_wide$condition == "DIS"],
-        paired = TRUE, rscale = "medium"
-        ) %>% data.frame %>% pull(bf)
-    
-    # computing the BF10 for the OOI muscle
-    bf_ooi <- ttestBF(
-        x = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "RUM"],
-        y = bf_simulated_data_wide$OOI[bf_simulated_data_wide$condition == "DIS"],
[…]

### 2020-12-16 manuscript.Rmd
minor updates in github readme

@@
 parameter_grid <- expand.grid(
-  sample_size = seq.int(from = 10, to = 100, length.out = 1e2),
-  effect_size = seq.int(from = 0.1, to = 1, length.out = 1e3)
+  sample_size = seq.int(from = 10, to = 100, length.out = 100),
+  effect_size = seq.int(from = 0.1, to = 1, length.out = 300)
   )
@@
   geom_line(
-    data = parameter_grid %>% filter(round(power, 3) == 0.9),
+    data = parameter_grid %>%
+      filter(round(power, 2) == 0.9) %>%
+      group_by(sample_size) %>%
+      summarise(effect_size = mean(effect_size), power = mean(power) ) %>%
+      ungroup,
     color = "black", lwd = 0.8
@@
   theme_bw(base_size = 12) +
-  labs(x = "Number of participants (per group)", y = "Standardised mean difference") +
+  labs(x = "Number of participants", y = "Standardised mean difference") +
   coord_cartesian(expand = FALSE) +

### 2020-12-16 manuscript.Rmd
minor updates in manuscript pdf

@@
 
+# note: \textcolor{red}{This is an example of a note}
+
 author: 
-  - name: Ladislas Nalborczyk
+  - name: "Ladislas Nalborczyk"
     affiliation: 1
     corresponding: yes
-    address: GIPSA-lab, CNRS, Univ. Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France
-    email: ladislas.nalborczyk@gipsa-lab.fr
+    address: "GIPSA-lab, CNRS, Univ. Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France"
+    email: "ladislas.nalborczyk@univ-grenoble-alpes.fr"
 
@@
 nocite: | 
-  @R-base, @R-knitr, @R-rmarkdown, @R-tidyverse, @R-papaja, @R-wordcountaddin,
-  @R-here
+  @R-base, @R-knitr, @R-rmarkdown, @R-tidyverse, @R-papaja,
+  @R-wordcountaddin, @R-here
 
@@
     latex_engine: xelatex
-
-editor_options: 
-  chunk_output_type: console
 ---

### 2020-12-16 manuscript.tex
minor updates in manuscript pdf

@@
 
+% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
+% See https://github.com/crsh/papaja/issues/292
+\makeatletter
+\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-1em}%
+  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
+
+\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
+  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
+  {-\z@\relax}%
+  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
+\makeatother
+
 % \usepackage{etoolbox}
@@
 \date{}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Ladislas Nalborczyk, GIPSA-lab, CNRS, Univ.
+Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France.
+E-mail: \href{mailto:ladislas.nalborczyk@univ-grenoble-alpes.fr}{\nolinkurl{ladislas.nalborczyk@univ-grenoble-alpes.fr}}
+
+}
 

### 2021-04-11 manuscript.Rmd
minor updates to manuscript

@@
 However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
-For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse [for a review, see @Nolen-Hoeksema2008].
-
-Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse [for a review, see @Nolen-Hoeksema2008].
+
+Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period [@nalborczyk_orofacial_2017].
@@
 
-This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to *severe* tests [e.g., @mayo_severe_2006; @mayo_statistical_2018].
+This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to *severe* tests [e.g., @mayo_statistical_2018; @mayo_severe_2006].
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives *severe* tests.
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve the problem of low power.
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
@@
 
-As shown in Figure \@ref(fig:bf-dance), the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is $d = 0$).
-When the "true" effect size is of $d = 0.36$, `r round(100 - prop_d0.36 * 100, 2)`% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the BFs are still below 0.
+As shown in Figure \@ref(fig:bf-dance), the distribution of log-BFs computed under each hypothesis reveals important inter-simulation variability.
+For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is $d = 0$).
+When the "true" effect size is of $d = 0.36$, `r round(100 - prop_d0.36 * 100, 2)`% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the log-BFs are still below 0.
 In other words, for small sample and effect sizes, BFs have high error rates.
 To assess the extent to which the BF computed for the OOI by @moffatt_inner_2020 (i.e., $\text{BF}_{10} = 0.278$) is "surprising" given or "compatible" with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to `r round(1 - mean(results$BF10_null > 0.278), 2)`, `r round(1 - mean(results$BF10 > 0.278), 2)`, and `r round(1 - mean(results$BF10_double > 0.278), 2)`, for the hypothesis of $d = 0$, $d = 0.36$, and $d = 0.72$, respectively.
-In other words, observing a $\text{BF}_{10} = 0.278$ is more compatible with the hypothesis of $d = 0$ (i.e., the null hypothesis) than with the hypothesis of $d = 0.36$ or $d = 0.72$ (at this sample size).
+In other words, observing a $\text{BF}_{10} = 0.278$ is more compatible with the hypothesis of $d = 0$ (i.e., the null hypothesis) than with the hypothesis of $d = 0.36$ or $d = 0.72$, for this sample size.
 
@@
 In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
-This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulation in speech perception and comprehension [@pickering_integrated_2013].
+This distinction is similar to the distinction between the two routes of prediction-by-association and prediction-by-simulation in speech perception and comprehension [@pickering_integrated_2013].
 The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more on the simulation of the motor action leading to the speech auditory percept.
 In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating or emulating the corresponding overt action [cf.
-also the motor simulation vs.
-direct simulation distinction in @tian_mental_2012].
+also the distinction between *motor simulation* and *direct simulation* in @tian_mental_2012].
 Whether the physiological correlates of automatic versus non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
@@
 
-# Supplementary materials {#supp}
-
-Reproducible code and figures are available at https://osf.io/ba3gk/.
-
 # Acknowledgements {-}
@@
 We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for providing helpful comments on a previous version of this manuscript.
+
+# Funding information
+
+This project did not benefit from any specific funding.
+
+# Data accessibility {#supp}
+
+Reproducible code for the manuscript, analyses, and figures is available at [https://osf.io/ba3gk/](https://osf.io/ba3gk/).
+
+<!--
+
+# Authors contribution
+
+LN, MPB, CB, RG, EK, and HL contributed to conception and design of the study, LN collected the data, LN, MPB, CB, EK, and HL contributed to data analysis and interpretation, LN, MPB, CB, RG, ES, EK, and HL drafted and/or revised the article and all authors approved the submitted version for publication.
+
+-->
+
+# Competing Interests
+
+The author has no competing interests to declare.
 

### 2021-04-11 manuscript.tex
minor updates to manuscript

@@
 \usepackage{lmodern}
-\usepackage{amssymb,amsmath}
+\usepackage{amsmath}
 \usepackage{ifxetex,ifluatex}
@@
   \usepackage{textcomp} % provide euro and other symbols
+  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \fi
+\ifluatex
+  \usepackage{selnolig}  % disable illegal ligatures
+\fi
 \newlength{\cslhangindent}
 \setlength{\cslhangindent}{1.5em}
-\newenvironment{cslreferences}%
-  {\setlength{\parindent}{0pt}%
-  \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces}%
-  {\par}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
+  % set entry spacing
+  \ifnum #2 > 0
+  \setlength{\parskip}{#2\baselineskip}
+  \fi
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
+\title{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
 \author{Ladislas Nalborczyk\textsuperscript{1}}
@@
 \abstract{
-Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
-Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+\protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
 We suggest this conclusion is at best hasty.
@@
 Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group averages is inappropriate.
-Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and we suggest ways forward, both from a theoretical and from a methodological perspective.
+Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and we suggest ways forward, both from a theoretical and from a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ba3gk/}.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4182
+Wordcount (excluding abstract, references, tables, and figures): 4207
 
@@
 
-The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see Alderson-Day \& Fernyhough, \protect\hyperlink{ref-alderson-day_inner_2015}{2015}; Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Perrone-Bertolotti et al., \protect\hyperlink{ref-perrone-bertolotti_what_2014}{2014}).
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see \protect\hyperlink{ref-alderson-day_inner_2015}{Alderson-Day \& Fernyhough, 2015}; \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}; \protect\hyperlink{ref-perrone-bertolotti_what_2014}{Perrone-Bertolotti et al., 2014}).
 However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
-For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (Martin \& Tesser, \protect\hyperlink{ref-Martin}{1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders or substance abuse (for a review, see Nolen-Hoeksema et al., \protect\hyperlink{ref-Nolen-Hoeksema2008}{2008}).
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (\protect\hyperlink{ref-Martin}{Martin \& Tesser, 1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse (for a review, see \protect\hyperlink{ref-Nolen-Hoeksema2008}{Nolen-Hoeksema et al., 2008}).
 
-Given the predominantly verbal nature of rumination (e.g., Ehring \& Watkins, \protect\hyperlink{ref-ehring_repetitive_2008}{2008}; Goldwin et al., \protect\hyperlink{ref-goldwin_concreteness_2013}{2013}; Goldwin \& Behar, \protect\hyperlink{ref-goldwin_concreteness_2012}{2012}; McLaughlin et al., \protect\hyperlink{ref-mclaughlin_effects_2007}{2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Perrone-Bertolotti, et al., \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
-We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+Given the predominantly verbal nature of rumination (e.g., \protect\hyperlink{ref-ehring_repetitive_2008}{Ehring \& Watkins, 2008}; \protect\hyperlink{ref-goldwin_concreteness_2013}{Goldwin et al., 2013}; \protect\hyperlink{ref-goldwin_concreteness_2012}{Goldwin \& Behar, 2012}; \protect\hyperlink{ref-mclaughlin_effects_2007}{McLaughlin et al., 2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}; e.g., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}; \protect\hyperlink{ref-nalborczyk_articulatory_2020}{Nalborczyk, Perrone-Bertolotti, et al., 2020}).
+We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
-We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of Nalborczyk, Banjac, et al.
-(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
-Although these points were not addressed by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}).
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+Although these points were not addressed by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 
-The main conclusion from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
+The main conclusion from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
@@
 
-As typical in studies manipulating induced rumination, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
+As typical in studies manipulating induced rumination, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
 First, they aimed to induce a negative mood by asking participants to solve unsolvable or excessively difficult anagram and subtraction tasks.
@@
 Therefore, the intercept represents the estimated natural logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
-These analyses were conducted using the \texttt{brms} package (Bürkner, \protect\hyperlink{ref-R-brms}{2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (Carpenter et al., \protect\hyperlink{ref-carpenter_stan_2017}{2017}).
+These analyses were conducted using the \texttt{brms} package (\protect\hyperlink{ref-R-brms}{Bürkner, 2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (\protect\hyperlink{ref-carpenter_stan_2017}{Carpenter et al., 2017}).
 We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations, using weakly informative priors on all parameters (for more details, see the \protect\hyperlink{supp}{supplementary materials}).
@@
 Constant effects estimates were summarised via their posterior mean and 95\% credible interval.
-We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (Wagenmakers et al., \protect\hyperlink{ref-wagenmakers_bayesian_2010}{2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
+We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (\protect\hyperlink{ref-wagenmakers_bayesian_2010}{Wagenmakers et al., 2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
 A summary of the estimations from this model is presented in Table \ref{tab:summary}.
@@
 This figure reveals that the most probable value for this difference was \(\beta = 0.228\) (95\% CrI {[}0.098, 0.357{]}) for the FRO muscle, \(\beta = 0.081\) (95\% CrI {[}-0.155, 0.324{]}) for the OOI muscle, and \(\beta = 0.047\) (95\% CrI {[}-0.167, 0.27{]}) for the OOS muscle.
-Moreover, comparing the posterior distribution to \(\theta = 0\) reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition (given the model, the priors, and the data from Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+Moreover, comparing the posterior distribution to \(\theta = 0\) reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition (given the model, the priors, and the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al., 2020}).
 
@@
 
-Having nuanced some of the conclusions from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
+Having nuanced some of the conclusions from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
 
@@
 
-There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (e.g., Meehl, \protect\hyperlink{ref-harlow_problem_1997}{1997}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990}\protect\hyperlink{ref-meehl_why_1990}{a}, \protect\hyperlink{ref-meehl_appraising_1990-1}{1990}\protect\hyperlink{ref-meehl_appraising_1990-1}{b}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}).
-By ``uninformative'', we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
+There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (\protect\hyperlink{ref-meehl_appraising_1990-1}{Meehl, 1990a}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990b}, e.g., \protect\hyperlink{ref-harlow_problem_1997}{1997}).
+By ``uninformative,'' we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
-As highlighted by several authors (e.g., Cohen, \protect\hyperlink{ref-cohen_earth_1994}{1994}; Pollard \& Richardson, \protect\hyperlink{ref-pollard_probability_1987}{1987}; Rouder et al., \protect\hyperlink{ref-rouder_is_2016}{2016}), concluding that an effect is probably absent solely based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the modus tollens and is not a valid argument (i.e., the conclusion does not follow from the premises).
+As highlighted by several authors (e.g., \protect\hyperlink{ref-cohen_earth_1994}{J.
+Cohen, 1994}; \protect\hyperlink{ref-pollard_probability_1987}{Pollard \& Richardson, 1987}; \protect\hyperlink{ref-rouder_is_2016}{Rouder et al., 2016}), concluding that an effect is probably absent solely based on a non-significant \emph{p}-value is the continuous (i.e., probabilistic) extension of the modus tollens and is not a valid argument (i.e., the conclusion does not follow from the premises).
 This fallacious argument is also known as the \emph{fallacy of acceptance}, the \emph{absence of evidence fallacy} or \emph{the argument from ignorance}, and proceeds as follows: ``If the null hypothesis is true, then this observation should \emph{rarely} occur.
 This observation occurred.
-Therefore, the null hypothesis is false (or has low probability)''.
-In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
+Therefore, the null hypothesis is false (or has low probability).'' In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
 
-This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to \emph{severe} tests (e.g., Mayo \& Spanos, \protect\hyperlink{ref-mayo_severe_2006}{2006}; Mayo, \protect\hyperlink{ref-mayo_statistical_2018}{2018}).
+This problem is tackled in modern usages of null-hypothesis significance tests by ensuring that the claim under scrutiny is submitted to \emph{severe} tests (e.g., \protect\hyperlink{ref-mayo_statistical_2018}{Mayo, 2018}; \protect\hyperlink{ref-mayo_severe_2006}{Mayo \& Spanos, 2006}).
 In general terms, the strong severity principle states that we have evidence for a claim to the extent that it survives a stringent scrutiny, that is, to the extent that it survives \emph{severe} tests.
@@
 
-Anticipating the legitimate critiques on the power of their study, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
-This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+Anticipating the legitimate critiques on the power of their study, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
 
@@
 
-We suggest the (a priori) power of the study ran by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
+We suggest the (a priori) power of the study ran by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
 Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
-If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}), therefore the a priori power of the main statistical test from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
-Notice that whereas taking half the effect size of Nalborczyk et al.
-(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
+If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}), therefore the a priori power of the main statistical test from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
+Notice that whereas taking half the effect size of \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
 
-Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis (p.12):
+Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis (p.12):
 
@@
 While we appreciate the effort, the current approach poses new problems.
-First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve at all the problem of low power.
+First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve the problem of low power.
 More precisely, the sensitivity (i.e., the ability to attain a certain goal) of an experimental design to detect a given effect is an issue for both frequentist and Bayesian statistical tests.
-To illustrate this point, we simulated 10.000 datasets (for \(N = 26\)) under the assumption of either no effect (i.e., the null hypothesis of \(d = 0\)), an effect size of \(d = 0.36\) (i.e., the supposed target effect size in Moffatt et al., \protect\hyperlink{ref-moffatt_inner_2020}{2020}), or an effect size of \(d = 0.72\) (i.e., the effect size reported in Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+To illustrate this point, we simulated 10.000 datasets (for \(N = 26\)) under the assumption of either no effect (i.e., the null hypothesis of \(d = 0\)), an effect size of \(d = 0.36\) (i.e., the supposed target effect size in \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al., 2020}), or an effect size of \(d = 0.72\) (i.e., the effect size reported in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
 
@@
 
-As shown in Figure \ref{fig:bf-dance}, the distribution of BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, 6.46\% of the computed BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
-When the ``true'' effect size is of \(d = 0.36\), 72.06\% of the BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the ``true'' effect size is of \(d = 0.72\), 24.46\% of the BFs are still below 0.
+As shown in Figure \ref{fig:bf-dance}, the distribution of log-BFs computed under each hypothesis reveals important inter-simulation variability.
+For instance, under the null hypothesis, 6.46\% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
+When the ``true'' effect size is of \(d = 0.36\), 72.06\% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of \(d = 0.72\), 24.46\% of the log-BFs are still below 0.
 In other words, for small sample and effect sizes, BFs have high error rates.
-To assess the extent to which the BF computed for the OOI by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.29, and 0.03, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
-In other words, observing a \(\text{BF}_{10} = 0.278\) is more compatible with the hypothesis of \(d = 0\) (i.e., the null hypothesis) than with the hypothesis of \(d = 0.36\) or \(d = 0.72\) (at this sample size).
+To assess the extent to which the BF computed for the OOI by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.29, and 0.03, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
+In other words, observing a \(\text{BF}_{10} = 0.278\) is more compatible with the hypothesis of \(d = 0\) (i.e., the null hypothesis) than with the hypothesis of \(d = 0.36\) or \(d = 0.72\), for this sample size.
 
@@
 
-In Nalborczyk, Banjac, et al.
-(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+In \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
 More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
-In contrast to this approach, Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
+In contrast to this approach, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
 In Figure \ref{fig:order}, we depict again the EMG data, this time grouped by the order in which the participants went through the rumination and distraction conditions.
@@
 
-Anticipating again that the order of the within-subject conditions may be an issue, Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
+Anticipating again that the order of the within-subject conditions may be an issue, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
 
@@
 
-We previously noted (e.g., Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}; Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}; Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}) that surface EMG measures of inner speech production were highly variable between individuals.
+We previously noted (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}; \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}; e.g., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}) that surface EMG measures of inner speech production were highly variable between individuals.
 This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
-The data collected by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and presents an important degree of inter-individual variability.
+The data collected by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and presents an important degree of inter-individual variability.
 In Figure \ref{fig:everyone}, we represent again the EMG data for each participant (each line is a participant).
@@
 Moreover, this variability suggests that some important confounding factors were not taken into account (i.e., either not manipulated in the experiment or statistically controlled for).
-In line with Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
+In line with \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
 We agree that a lot could be learnt by relating this (self-reported) subjective experience to the peripheral muscular correlates of inner speech production.
 However, this can not be done at the group level, at the risk of missing individual-level patterns.
-Therefore, we encourage Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
+Therefore, we encourage \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
 
-It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by Haaf and Rouder (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in Nalborczyk, Grandchamp, et al., \protect\hyperlink{ref-nalborczyk_can_2020}{2020}).
+It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by \protect\hyperlink{ref-haaf_developing_2017}{Haaf \& Rouder} (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
+However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}).
 
@@
 
-With this paper we aimed to nuance the strong conclusion made by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
-First, we reanalysed the data from Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and provided some nuance to the conclusion that can be made from these data.
-Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-Because the statistical tests conducted by Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
+With this paper we aimed to nuance the strong conclusion made by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we reanalysed the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and provided some nuance to the conclusion that can be made from these data.
+Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+Because the statistical tests conducted by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
 Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
@@
 As discussed in the introduction section, we previously conducted several studies aiming to assess the role of the speech motor system in rumination.
-Following our initial study (Nalborczyk et al., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}), we ran an extension in which we compared verbal to non-verbal rumination.
-The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (Nalborczyk, Banjac, et al., \protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}).
-Given the ample evidence on the EMG correlates of inner speech production (for an overview, see Chapter 1 in Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}), we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
+Following our initial study (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}), we ran an extension in which we compared verbal to non-verbal rumination.
+The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}).
+Given the ample evidence on the EMG correlates of inner speech production (for an overview, see Chapter 1 in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}), we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
 
-In Nalborczyk, Banjac, et al.
-(\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (Watkins \& Nolen-Hoeksema, \protect\hyperlink{ref-watkins_habit-goal_2014}{2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+In \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (\protect\hyperlink{ref-watkins_habit-goal_2014}{Watkins \& Nolen-Hoeksema, 2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
 We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
-Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system (e.g., Cohen, \protect\hyperlink{ref-cohen_motor_1986}{1986}; Sokolov, \protect\hyperlink{ref-sokolov_inner_1972}{1972}).
-According to Cohen (\protect\hyperlink{ref-cohen_motor_1986}{1986}), the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
+Interestingly, it has been observed that the automaticity with which a verbal thought is evoked may influence the degree to which it is enacted, that is, the degree to which it recruits the speech motor system (e.g., \protect\hyperlink{ref-cohen_motor_1986}{B.
+H.
+Cohen, 1986}; \protect\hyperlink{ref-sokolov_inner_1972}{Sokolov, 1972}).
+According to \protect\hyperlink{ref-cohen_motor_1986}{B.
+H.
+Cohen} (\protect\hyperlink{ref-cohen_motor_1986}{1986}), the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed (e.g., Lœvenbruck et al., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{2018}; Grandchamp et al., \protect\hyperlink{ref-grandchamp_condialint_2019}{2019}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of these ideas in the broader context of motor imagery, Guillot et al., \protect\hyperlink{ref-guillot_imagining_2012}{2012}).
+Relating this idea to the motor control framework we previously proposed (\protect\hyperlink{ref-grandchamp_condialint_2019}{Grandchamp et al., 2019}; e.g., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of these ideas in the broader context of motor imagery, \protect\hyperlink{ref-guillot_imagining_2012}{Guillot et al., 2012}).
 
-Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system (Nalborczyk, \protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system (\protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
 In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
-This distinction is similar to the distinction between the two routes of predictions-by-association and prediction-by-simulation in speech perception and comprehension (Pickering \& Garrod, \protect\hyperlink{ref-pickering_integrated_2013}{2013}).
+This distinction is similar to the distinction between the two routes of prediction-by-association and prediction-by-simulation in speech perception and comprehension (\protect\hyperlink{ref-pickering_integrated_2013}{Pickering \& Garrod, 2013}).
 The prediction-by-association mechanism would rely more on perceptual sensory experiences and domain-general cognitive abilities whereas the prediction-by-simulation mechanism would rely more on the simulation of the motor action leading to the speech auditory percept.
-In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating or emulating the corresponding overt action (cf.~also the motor simulation vs.~direct simulation distinction in Tian \& Poeppel, \protect\hyperlink{ref-tian_mental_2012}{2012}).
+In the former case, no peripheral muscular activity is expected, whereas in the latter case, the speech motor system would be involved in simulating or emulating the corresponding overt action (cf.~also the distinction between \emph{motor simulation} and \emph{direct simulation} in \protect\hyperlink{ref-tian_mental_2012}{Tian \& Poeppel, 2012}).
 Whether the physiological correlates of automatic versus non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
-We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 
-To conclude, we wish to bring some nuance to the conclusion of Moffatt et al.
-(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction'' (p.14).
+To conclude, we wish to bring some nuance to the conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction'' (p.14).
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
@@
 We urge the authors to nuance their conclusions, to further analyse their data, and to plan adequately-powered studies in order to settle these issues.
-
-\hypertarget{supp}{%
-\section{Supplementary materials}\label{supp}}
-
-Reproducible code and figures are available at \url{https://osf.io/ba3gk/}.
 
@@
 
+\hypertarget{funding-information}{%
+\section{Funding information}\label{funding-information}}
+
+This project did not benefit from any specific funding.
+
+\hypertarget{supp}{%
+\section{Data accessibility}\label{supp}}
+
+Reproducible code for the manuscript, analyses, and figures is available at \url{https://osf.io/ba3gk/}.
+
+\hypertarget{competing-interests}{%
+\section{Competing Interests}\label{competing-interests}}
+
+The author has no competing interests to declare.
+
 \hypertarget{references}{%
@@
 \hypertarget{refs}{}
-\begin{cslreferences}
+\begin{CSLReferences}{1}{0}
 \leavevmode\hypertarget{ref-alderson-day_inner_2015}{}%
@@
 (2015).
-Inner speech: Development, cognitive functions, phenomenology, and neurobiology.
+Inner speech: {Development}, cognitive functions, phenomenology, and neurobiology.
 \emph{Psychological Bulletin}, \emph{141}(5), 931--965.
@@
 \leavevmode\hypertarget{ref-R-papaja}{}%
-Aust, F., \& Barth, M. (2017). \emph{papaja: Create APA manuscripts with R Markdown}. \url{https://github.com/crsh/papaja}
+Aust, F., \& Barth, M. (2017). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
 
 \leavevmode\hypertarget{ref-R-brms}{}%
-Bürkner, P.-C. (2017). brms: An R package for bayesian multilevel models using Stan. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
+Bürkner, P.-C. (2017). {brms}: An {R} package for bayesian multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
 
@@
 (2017).
-Stan: A probabilistic programming language.
+Stan: {A} probabilistic programming language.
 \emph{Journal of Statistical Software, Articles}, \emph{76}(1), 1--32.
@@
 \leavevmode\hypertarget{ref-cohen_motor_1986}{}%
-Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. Springer, Boston, MA.
+Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. {Springer, Boston, MA}.
 
 \leavevmode\hypertarget{ref-cohen_earth_1994}{}%
-Cohen, J. (1994). The earth is round (p \(<\) .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
+Cohen, J. (1994). The earth is round (p {\(<\)} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
 
@@
 (2019).
-The ConDialInt Model: Condensation, Dialogality, and Intentionality Dimensions of Inner Speech Within a Hierarchical Predictive Control Framework.
+The {ConDialInt Model}: {Condensation}, {Dialogality}, and {Intentionality Dimensions} of {Inner Speech Within} a {Hierarchical Predictive Control Framework}.
 \emph{Frontiers in Psychology}, \emph{10}.
@@
 (2012).
-Imagining is not doing but involves specific motor commands: A review of experimental data related to motor inhibition.
+Imagining is not doing but involves specific motor commands: {A} review of experimental data related to motor inhibition.
 \emph{Frontiers in Human Neuroscience}, \emph{6}.
@@
 \leavevmode\hypertarget{ref-haaf_developing_2017}{}%
-Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in Bayesian mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
+Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in {Bayesian} mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
 
@@
 Langland-Hassan \& A.
-Vicente (Eds.), \emph{Inner speech: New voices} (p.
+Vicente (Eds.), \emph{Inner speech: {New} voices} (p.
 37).
-Oxford University Press.
+{Oxford University Press}.
 
@@
 1--47).
-Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc.
+{Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc}.
 
@@
 \leavevmode\hypertarget{ref-mayo_statistical_2018}{}%
-Mayo, D. G. (2018). \emph{Statistical Inference as Severe Testing: How to Get Beyond the Statistics Wars}. Cambridge University Press. \url{https://doi.org/10.1017/9781107286184}
+Mayo, D. G. (2018). \emph{Statistical {Inference} as {Severe Testing}: {How} to {Get Beyond} the {Statistics Wars}}. {Cambridge University Press}. \url{https://doi.org/10.1017/9781107286184}
 
@@
 (2006).
-Severe Testing as a Basic Concept in a NeymanPearson Philosophy of Induction.
+Severe {Testing} as a {Basic Concept} in a {Neyman}{{Pearson Philosophy}} of {Induction}.
 \emph{The British Journal for the Philosophy of Science}, \emph{57}(2), 323--357.
@@
 
+\leavevmode\hypertarget{ref-meehl_appraising_1990-1}{}%
+Meehl, P.
+E.
+(1990a).
+Appraising and {Amending Theories}: {The Strategy} of {Lakatosian Defense} and {Two Principles} that {Warrant It}.
+\emph{Psychological Inquiry}, \emph{1}(2), 108--141.
+\url{https://doi.org/10.1207/s15327965pli0102_1}
+
+\leavevmode\hypertarget{ref-meehl_theory-testing_1967}{}%
+Meehl, P. E. (1967). Theory-testing in {Psychology} and {Physics}: {A} methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
+
 \leavevmode\hypertarget{ref-meehl_theoretical_1978}{}%
@@
 (1978).
-Theoretical risks and tabular asterisks: Sir Karl, Sir Ronald, and the slow progress of soft psychology.
+Theoretical risks and tabular asterisks: {Sir Karl}, {Sir Ronald}, and the slow progress of soft psychology.
 \emph{Journal of Consulting and Clinical Psychology}, \emph{46}(4), 806--834.
@@
 \leavevmode\hypertarget{ref-meehl_why_1990}{}%
-Meehl, P. E. (1990a). Why Summaries of Research on Psychological Theories are Often Uninterpretable. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
+Meehl, P. E. (1990b). Why {Summaries} of {Research} on {Psychological Theories} are {Often Uninterpretable}. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
 
@@
 (1997).
-The problem is epistemology, not statistics: Replace significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
+The problem is epistemology, not statistics: {Replace} significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
 \emph{What If There Were No Significance Tests?}, 393--425.
-
-\leavevmode\hypertarget{ref-meehl_appraising_1990-1}{}%
-Meehl, P.
-E.
-(1990b).
-Appraising and Amending Theories: The Strategy of Lakatosian Defense and Two Principles that Warrant It.
-\emph{Psychological Inquiry}, \emph{1}(2), 108--141.
-\url{https://doi.org/10.1207/s15327965pli0102_1}
-
-\leavevmode\hypertarget{ref-meehl_theory-testing_1967}{}%
-Meehl, P. E. (1967). Theory-testing in Psychology and Physics: A methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
 
@@
 What is that little voice inside my head?
-Inner speech phenomenology, its role in cognitive performance, and its relation to self-monitoring.
+{Inner} speech phenomenology, its role in cognitive performance, and its relation to self-monitoring.
 \emph{Behavioural Brain Research}, \emph{261}, 220--239.
@@
 \leavevmode\hypertarget{ref-pollard_probability_1987}{}%
-Pollard, P., \& Richardson, J. T. (1987). On the probability of making Type I errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
+Pollard, P., \& Richardson, J. T. (1987). On the probability of making {Type I} errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
 
@@
 (2016).
-Is There a Free Lunch in Inference?
+Is {There} a {Free Lunch} in {Inference}?
 \emph{Topics in Cognitive Science}, \emph{8}(3), 520--547.
@@
 \leavevmode\hypertarget{ref-sokolov_inner_1972}{}%
-Sokolov, A. (1972). \emph{Inner speech and thought}. Springer-Verlag.
+Sokolov, A. (1972). \emph{Inner speech and thought}. {Springer-Verlag}.
 
@@
 (2010).
-Bayesian hypothesis testing for psychologists: A tutorial on the SavageDickey method.
+Bayesian hypothesis testing for psychologists: {A} tutorial on the {Savage}{{Dickey}} method.
 \emph{Cognitive Psychology}, \emph{60}(3), 158--189.
@@
 \leavevmode\hypertarget{ref-R-knitr}{}%
-Xie, Y. (2015). \emph{Dynamic documents with R and knitr} (2nd ed.). Chapman; Hall/CRC. \url{https://yihui.org/knitr/}
+Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Chapman; Hall/CRC. \url{https://yihui.org/knitr/}
 
@@
 Xie, Y., Allaire, J. J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Chapman; Hall/CRC. \url{https://bookdown.org/yihui/rmarkdown}
-\end{cslreferences}
+
+\end{CSLReferences}
 

### 2021-11-03 manuscript.Rmd
uploading revisions for collabra

@@
 ---
-title: "Re-analysing the data from @moffatt_inner_2020: A textbook illustration of the absence of evidence fallacy"
-
+title: "Re-analysing the data from @moffatt_inner_2020: What can we learn from an under-powered absence of difference?"
 shorttitle: "The absence of evidence fallacy"
-
 # note: \textcolor{red}{This is an example of a note}
-
 author: 
   - name: "Ladislas Nalborczyk"
-    affiliation: 1
+    affiliation: "1, 2, 3"
     corresponding: yes
-    address: "GIPSA-lab, CNRS, Univ. Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France"
-    email: "ladislas.nalborczyk@univ-grenoble-alpes.fr"
-
+    address: "LPC, CNRS, Aix-Marseille University, 13 Boulevard Gustave Desplaces, 13003 Marseille, France"
+    email: "ladislas.nalborczyk@univ-amu.fr"
 affiliation:
@@
     institution: Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France
-
+  - id: 2
+    institution: Aix Marseille Univ, CNRS, LPC, Marseille, France
+  - id: 3
+    institution: Aix Marseille Univ, CNRS, LNC, Marseille, France
 abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
@@
 Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly uninformative.
-Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
-Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group averages is inappropriate.
-Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020 and we suggest ways forward, both from a theoretical and from a methodological perspective.
+In this short commentary, we show that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020.
+We suggest ways forward, both from a theoretical and methodological perspective.
 Complete source code, reproducible analyses, and figures are available at https://osf.io/ba3gk/."
-
-keywords: NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography
-
+keywords: NHST, Bayes factor, reanalysis, inner speech, rumination, electromyography
 csl: csl/apa7.csl
@@
 numbersections: false
-
+mask: yes # masking author names
 bibliography: [bib/library.bib, bib/r-references.bib]
-
 nocite: | 
@@
   @R-wordcountaddin, @R-here
-
 output:
@@
   warning = FALSE, message = FALSE,
-  fig.align = "center", dev = "pdf",
+  fig.align = "center", dev = "cairo_pdf",
   out.width = "100%", fig.width = 8,
@@
 
-The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018].
+The activity of silently talking to oneself or "inner speech" is a foundational ability, allowing oneself to remember, plan, self-motivate, or self-regulate [for reviews, see @alderson-day_inner_2015; @perrone-bertolotti_what_2014; @loevenbruck_cognitive_2018].
 However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
-For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse [for a review, see @Nolen-Hoeksema2008].
-
-Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols [e.g., @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_dissociating_2020; @nalborczyk_articulatory_2020].
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states [@Martin], is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse [for review, see @Nolen-Hoeksema2008].
+
+Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols [e.g., @nalborczyk_dissociating_2021; @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_articulatory_2020].
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period [@nalborczyk_orofacial_2017].
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2020].
-We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of @nalborczyk_dissociating_2020 and more extensively in @nalborczyk_understanding_2019.
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts [@nalborczyk_dissociating_2021].
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion of @nalborczyk_dissociating_2021 and more extensively in @nalborczyk_understanding_2019.
+
+<!--
+
 Although these points were not addressed by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 
-The main conclusion from @moffatt_inner_2020 is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech" (p.1).
+-->
+
+@moffatt_inner_2020 designed an experiment with the aim of refining our understanding of the involvement of the speech motor system in different varieties of inner speech and clarifying the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
+Their main conclusion is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech" (p.1).
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
@@
 This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
+
+<!--
+
 Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
@@
 This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
+In the following, we explore each of these limitations and suggests ways forward, both from a theoretical and from a methodological perspective.
+
 Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group averages.
-However, given the important inter-individual variability, this reasoning appears highly problematic.
-In the following, we explore each of these limitations and suggests ways forward, both from a theoretical and from a methodological perspective.
-
-# Exploring the data
+However, given the important inter-individual variability, this reasoning appears highly problematic
+
+-->
+
+# Re-analysing the data from @moffatt_inner_2020
+
+## Exploring the data
 
@@
 Second, they prompted participants to either ruminate on these (purportedly induced) negative feelings (by asking them to "think about the causes, consequences, and meaning of their current feelings") or to distract themselves (by asking them to "think about a village, city or town that you are particularly familiar with").
-Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
+Rumination and distraction were manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
 
@@
 However, the average natural logarithm of the EMG peak amplitude recorded over the OOI and OOS muscles was higher than baseline in both the rumination and distraction conditions, with a slight increase from distraction to rumination (both on the mean and median).
+Having described the data collected by @moffatt_inner_2020, we now turn to a discussion of some problems related to conclusions that can be made from under-powered non-significant results.
 
@@
         ) +
-    # plotting confidence intervals
+    # plotting 95% confidence intervals
     stat_summary(
@@
     labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
-    theme_bw(base_size = 10) +
+    theme_bw(base_size = 12, base_family = "Open Sans") +
     scale_colour_brewer(palette = "Dark2", direction = 1) +
@@
 ```
+
+<!--
 
@@
     data = df2,
-    chains = 4, cores = detectCores(),
+    chains = 4, cores = 4,
     warmup = 2000, iter = 10000,
@@
 hyp_fro <- hypothesis(
-    varying_effects,
-    "FRO_conditionDIS = FRO_conditionRUM"
+    x = varying_effects,
+    hypothesis = "FRO_conditionDIS = FRO_conditionRUM"
     )
@@
     geom_vline(xintercept = 0, linetype = 2) +
-    coord_cartesian(xlim = c(-5, 5) ) +
-    theme_bw(base_size = 10) +
+    coord_cartesian(xlim = c(-5, 5), ylim = c(0, 7.5) ) +
+    theme_bw(base_size = 12, base_family = "Open Sans") +
     theme(legend.title = element_blank() ) +
@@
       x = "Log EMG peak amplitude",
+      y = "Probability density",
       title = paste0(
@@
 
-Having nuanced some of the conclusions from @moffatt_inner_2020, we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
-
-## Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could possibly go wrong?
-
-There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology [e.g., @harlow_problem_1997; @meehl_appraising_1990-1; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
+-->
+
+## Conclusions from under-powered null-hypothesis significance tests
+
+There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology [e.g., @meehl_appraising_1990-1; @harlow_problem_1997; @meehl_theoretical_1978; @meehl_theory-testing_1967; @meehl_why_1990].
 By "uninformative", we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
@@
 
+## Enthusiastic prior specifications
+
 Anticipating the legitimate critiques on the power of their study, @moffatt_inner_2020 report the results of a power analysis using the effect size reported in @nalborczyk_orofacial_2017 of $d = 0.72$.
-This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude *between a rest and a rumination periods* [@nalborczyk_orofacial_2017].
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude *between a rest and a rumination periods* as estimated in @nalborczyk_orofacial_2017.
 
@@
     ) +
-  theme_bw(base_size = 12) +
+  theme_bw(base_size = 12, base_family = "Open Sans") +
   labs(x = "Number of participants", y = "Standardised mean difference") +
@@
 
+```{r power2, eval = FALSE, fig.cap = "Statistical power as a function of both sample size and effect size, for a one-sample t-test with a significance level of 0.05.
+The white dot indicates the minimal effect size that can be detected with a probability equal or superior to 0.9 with a sample size of N = 26."}
+# creating a grid of possible sample and effect sizes
+parameter_grid <- expand.grid(
+  alpha = seq.int(from = 0, to = 0.2, length.out = 100),
+  effect_size = seq.int(from = 0.1, to = 1, length.out = 300)
+  )
+
+# computing power for all combinations of sample and effect sizes
+parameter_grid$power <- power.t.test(
+  n = 26,
+  delta = parameter_grid$effect_size,
+  sd = 1,
+  type = "one.sample",
+  alternative = "two.sided",
+  sig.level = parameter_grid$alpha)$power
+
+# computing the effect size for a power = 0.8 at sample size = 26
+target <- parameter_grid %>%
+  filter(round(alpha, 2) == 0.05, round(power, 2) == 0.9) %>%
+  pull(effect_size) %>%
+  mean
+
+# plotting the results
+parameter_grid %>%
+  mutate(power = as.numeric(power) ) %>%
+  ggplot(aes(x = alpha, y = effect_size, colour = NULL) ) +
+  geom_contour_filled(aes(z = power), alpha = 0.8) +
+  geom_line(
+    data = parameter_grid %>%
+      filter(round(power, 2) == 0.9) %>%
+      group_by(alpha) %>%
+      summarise(effect_size = mean(effect_size), power = mean(power) ) %>%
+      ungroup,
+    color = "black", lwd = 0.8
+    ) +
+  geom_segment(
+    x = 0.05, xend = 0.05, y = 0, yend = target,
+    lwd = 0.5, linetype = 3
+    ) +
+  geom_segment(
+    x = 0, xend = 0.05, y = target, yend = target,
+    lwd = 0.5, linetype = 3
+    ) +
+  geom_point(
+    x = 0.05, y = target,
+    pch = 21, size = 3, fill = "white"
+    ) +
+  theme_bw(base_size = 12, base_family = "Open Sans") +
+  labs(x = "Alpha level", y = "Standardised mean difference") +
+  coord_cartesian(expand = FALSE) +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank() ) +
+  # scale_fill_manual(values = ., labels = seq(0.304, 2.129, length.out = 10) %>% round(2) )+
+  # guides(fill = guide_colorbar() )
+  # https://stackoverflow.com/questions/62543112/how-to-make-discrete-gradient-color-bar-with-geom-contour-filled
+  # metR::scale_fill_discretised()
+  # scale_fill_distiller(super = metR::ScaleDiscretised, palette = "RdYlBu") +
+  guides(fill = guide_legend(title = "Power", reverse = TRUE) )
+```
+
 We suggest the (a priori) power of the study ran by @moffatt_inner_2020 was much lower than suggested by the authors.
 Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
-If we assume that the former is half the size of the latter [which seems reasonable given the high inter-individual variability in such effects, cf.
-the next section but also @nalborczyk_can_2020], therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.42$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually $0.36$).
+If we assume that the former is half the size of the latter, therefore the a priori power of the main statistical test from @moffatt_inner_2020 was around $0.42$, meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually $0.36$).
 Notice that whereas taking half the effect size of @nalborczyk_orofacial_2017 may seem arbitrary, Figure \@ref(fig:power) shows that a one-sample t-test with a sample size of $N = 26$ is under-powered for a vast range of effect sizes.
@@
 
+## Frequentist properties of Bayes factors
+
 Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily "significant" evidence for the absence of an effect, @moffatt_inner_2020 reported the following Bayes factor (BF) analysis (p.12):
@@
 
-While we appreciate the effort, the current approach poses new problems.
+However, the current approach poses new problems.
 First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the *relative evidence* for the null, computing a BF (i.e., comparing two models) does not solve the problem of low power.
@@
   geom_histogram(colour = "white", show.legend = FALSE, bins = 40) +
-  theme_bw(base_size = 12) +
+  theme_bw(base_size = 12, base_family = "Open Sans") +
   facet_wrap(~ type, scales = "free_x") +
@@
 
-```{r simulated-power, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
+```{r simulated-power, eval = FALSE, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
 (2020).
@@
 
-We should keep in mind some limitations of this analysis, which uses simulated datasets form the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
+We should keep in mind some limitations of this analysis, which uses simulated datasets from the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
 This analysis resembles to the Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
@@
 
+The problems we discussed previously about the interpretation of under-powered non-significant results also apply to the test @moffatt_inner_2020 performed about the effect or the conditions' order.
+In @nalborczyk_dissociating_2021, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
+In contrast to this approach, @moffatt_inner_2020 asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
+Anticipating again that the order of the within-subject conditions may be an issue, @moffatt_inner_2020 say:
+
+> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order." (p.7)
+
+Unfortunately, obtaining a non-significant effect of the conditions' order is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed (the sample size in each group was of N = 12 and N = 14).
+
+## Robustness of Bayes factors to prior specifications
+
+Formulated in Bayesian terms, the problem of specifying credible effect sizes in a priori power analyses may be described as a problem of prior specification.
+However, defining sound prior distributions for the alternative hypothesis is notoriously difficult [for some guidance, see for instance @dienes_obtaining_2021; @dienes_how_2019].
+In Figure \@ref(fig:sensitivity), we report the result of *sensitivity analyses*, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
+
+```{r sensitivity, fig.pos = "!h", fig.width = 12, fig.height = 6, fig.cap = "Prior sensitivity analysis for the Bayes factor computed for each muscle (OOI, OOS, and FRO).
+The x-axis represents the width of the prior put on the standardised effect size (i.e., the prior for the alternative hypothesis).
+The y-axis represents the logarithm of the Bayes factor in favour of the alternative hypothesis.
+The horizontal black dashed line represents equal support (evidence) for each hypothesis.
+The vertical red dashed line depicts the prior width used in Moffatt et al.
+(2020).
+The gray shaded area represents the conventional (but questionable) interval in which BFs are usually considered as negligible (i.e., from 1/3 to 3)."}
+# code adapted from https://vasishth.github.io/bayescogsci/book/sec-N400BF.html
+# sensitivity analyses
+
+# original BF for FRO
+# ttestBF(
+#     x = df2 %>% filter(condition == "RUM") %>% pull(FRO),
+#     y = df2 %>% filter(condition == "DIS") %>% pull(FRO),
+#     paired = TRUE,
+#     rscale = "medium"
+#     ) # %>%
+#     data.frame %>%
+#     pull(bf)
+
+# original BF for OOS
+# ttestBF(
+#     x = df2 %>% filter(condition == "RUM") %>% pull(OOS),
+#     y = df2 %>% filter(condition == "DIS") %>% pull(OOS),
+#     paired = TRUE,
+#     rscale = "medium"
+#     ) # %>%
+#     data.frame %>%
+#     pull(bf)
+
+# original BF for OOI
+# ttestBF(
+#     x = df2 %>% filter(condition == "RUM") %>% pull(OOI),
+#     y = df2 %>% filter(condition == "DIS") %>% pull(OOI),
+#     paired = TRUE,
+#     rscale = "medium"
+#     ) %>%
+#     data.frame %>%
+#     pull(bf)
+
+# prior width
+prior_sd <- seq(from = 0.05, to = 1.5, by = 0.05)
+
+# muscle
+muscles <- c("OOI", "OOS", "FRO")
+
+# grid
+grid <- expand.grid(prior_sd = prior_sd, muscle = muscles)
+
+# initialises an empty array to store the results
+results <- grid %>% mutate(BF10 = numeric(nrow(.) ) )
+
+for (i in 1:nrow(results) ) { # for each combination of prior width and muscle
+
+  # computes the BF01 for this prior width
+  results$BF10[i] <- ttestBF(
+    x = df2 %>% filter(condition == "RUM") %>% pull(results$muscle[i]),
+    y = df2 %>% filter(condition == "DIS") %>% pull(results$muscle[i]),
+    paired = TRUE,
+    rscale = results$prior_sd[i]
+    ) %>%
+    data.frame %>%
+    pull(bf)
+
+}
+
+# creates grid for background gradient
+df <- expand.grid(x = seq(from = 0, to = 1.6, by = 0.01), y = seq(from = -log(15), to = log(35), by = 0.01) )
+
+# plotting the results
+results %>%
+    ggplot(aes(x = prior_sd, y = log(BF10) ) ) +
+    geom_rect(
+        data = data.frame(xmin = -Inf, xmax = Inf, ymin = log(1 / 3), ymax = log(3) ),
+        aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
+        color = NA,
+        alpha = 0.3,
+        inherit.aes = FALSE
+        ) +
+    geom_tile(
+        data = df,
+        aes(x = x, y = y, fill = y),
+        alpha = 0.5, inherit.aes = FALSE, show.legend = FALSE
+        ) +
+    scale_fill_gradient2(
+        low = "orangered", high = "darkgreen", mid = "white",
+        midpoint = 0
+        ) +
+    geom_vline(xintercept = sqrt(2) / 2, linetype = 2, size = 0.5, color = "orangered") +
+    geom_hline(yintercept = log(1), linetype = 2, size = 0.5) +
+    geom_point(size = 2) +
+    geom_line(size = 0.5) +
+    theme_bw(base_size = 12, base_family = "Open Sans") +
+    coord_cartesian(expand = FALSE) +
+    labs(x = "Prior scale (width) for the alternative hypothesis", y = "Logarithm of the BF10") +
+    scale_x_continuous(
+        limits = c(0, 1.6),
+        breaks = format(seq(from = 0.1, to = 1.5, by = 0.1), digits = 2) %>% as.numeric,
+        labels = format(seq(from = 0.1, to = 1.5, by = 0.1) )
+        ) +
+    scale_y_continuous(
+        limits = c(-log(15), log(35) ),
+        breaks = c(c(-log(c(10, 3) ), 0, log(c(3, 10, 30) ) ) ),
+        labels = c("-log(10)", "-log(3)", "log(1)", "log(3)", "log(10)", "log(30)")
+        ) +
+    annotate(
+        geom = "text",
+        x = 1.2, y = log(0.5),
+        label = "Evidence in\nfavour of H0",
+        size = 4, fontface = "bold"
+        ) +
+    annotate(
+        geom = "text",
+        x = 1.2, y = log(2),
+        label = "Evidence in\nfavour of H1",
+        size = 4, fontface = "bold"
+        ) +
+    facet_wrap(~muscle, ncol = 3)
+```
+
+This figure strikingly reveals large variability in the resulting BF with varying prior specification.
+More precisely, when the scale (width) of the prior put on the standardised effect size is changed (along the x-axis), the BF changes accordingly.
+For instance, varying the prior scale from 0.1 to 1.0 for the OOI results in BFs from 0.78 to 0.21, respectively.
+
+<!--
+
 ## Within-subject manipulation of rumination and distraction
 
-In @nalborczyk_dissociating_2020, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+In @nalborczyk_dissociating_2021, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
 More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
@@
 
-```{r order, fig.cap = "Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
+```{r order, eval = FALSE, fig.cap = "Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
 The green dots and intervals represent the by-group average and 95\\% confidence interval for the participants that first went through the rumination condition, then through the distraction condition.
@@
 
-We previously noted [e.g., @nalborczyk_orofacial_2017; @nalborczyk_dissociating_2020; @nalborczyk_understanding_2019; @nalborczyk_can_2020] that surface EMG measures of inner speech production were highly variable between individuals.
+We previously noted [e.g., @nalborczyk_orofacial_2017; @nalborczyk_dissociating_2021; @nalborczyk_understanding_2019; @nalborczyk_can_2020] that surface EMG measures of inner speech production were highly variable between individuals.
 This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
@@
 
-<!--
-
 ## Relating the subjective inner experience to the psychophysiological correlates
@@
 
-With this paper we aimed to nuance the strong conclusion made by @moffatt_inner_2020, who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
-First, we reanalysed the data from @moffatt_inner_2020 and provided some nuance to the conclusion that can be made from these data.
-Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of @moffatt_inner_2020.
+With this short paper, we aimed to nuance the strong conclusion made by @moffatt_inner_2020, who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of @moffatt_inner_2020.
 Because the statistical tests conducted by @moffatt_inner_2020 were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
-Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
-Finally, we showed that the group analyses masked important inter-individual variability that should be more carefully examined.
+Second, we highlighted that the frequentist properties of Bayesian tools (e.g., Bayes factors) provide an important piece of information that may help design more informative studies.
+Third, sensitivity analyses further suggested that various prior specifications may lead to different resulting Bayes factors.
 
@@
 Following our initial study [@nalborczyk_orofacial_2017], we ran an extension in which we compared verbal to non-verbal rumination.
-The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar [@nalborczyk_dissociating_2020].
+The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar [@nalborczyk_dissociating_2021].
 Given the ample evidence on the EMG correlates of inner speech production [for an overview, see Chapter 1 in @nalborczyk_understanding_2019], we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
 
-In @nalborczyk_dissociating_2020, we suggested that this observation was coherent with the mental-habit view of depressive rumination [@watkins_habit-goal_2014], which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+In @nalborczyk_dissociating_2021, we suggested that this observation was coherent with the mental-habit view of depressive rumination [@watkins_habit-goal_2014], which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
 We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed [e.g., @loevenbruck_cognitive_2018; @grandchamp_condialint_2019], it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity [see also a discussion of these ideas in the broader context of motor imagery, @guillot_imagining_2012].
-
-Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system [@nalborczyk_understanding_2019].
+Relating this idea to the motor control framework we previously proposed [e.g., @grandchamp_condialint_2019; @loevenbruck_cognitive_2018], it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production [@nalborczyk_role_2021], hence resulting in more or less visible peripheral muscular activity [for a discussion of these ideas in the broader context of motor imagery, see @guillot_imagining_2012].
+
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system [@nalborczyk_role_2021; @nalborczyk_understanding_2019].
 In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
@@
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
-Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
+Indeed, we provided theoretical (epistemological) and empirical (via simulation and sensitivity analyses) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
+This commentary stresses the importance of planning adequately-powered studies of induced rumination, and the need for more thoughtful statistical analyses and data interpretation, as recommended by @wasserstein_moving_2019.
+
+<!--
+
 Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.
 Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
-We urge the authors to nuance their conclusions, to further analyse their data, and to plan adequately-powered studies in order to settle these issues.
+
+-->
 
@@
 We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for providing helpful comments on a previous version of this manuscript.
+Thanks to Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
 

### 2021-11-03 manuscript.tex
uploading revisions for collabra

@@
   english,
-  man, donotrepeattitle,floatsintext]{apa6}
+  man, donotrepeattitle,mask,floatsintext]{apa6}
+\title{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): What can we learn from an under-powered absence of difference?}
+\author{Ladislas Nalborczyk\textsuperscript{1, 2, 3}}
+\date{}
+
+\usepackage{amsmath,amssymb}
 \usepackage{lmodern}
-\usepackage{amsmath}
-\usepackage{ifxetex,ifluatex}
-\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
+\usepackage{iftex}
+\ifPDFTeX
   \usepackage[T1]{fontenc}
@@
   \usepackage{textcomp} % provide euro and other symbols
-  \usepackage{amssymb}
 \else % if luatex or xetex
@@
 \hypersetup{
-  pdftitle={Re-analysing the data from Moffatt et al. (2020): A textbook illustration of the absence of evidence fallacy},
-  pdfauthor={Ladislas Nalborczyk1},
+  pdftitle={Re-analysing the data from Moffatt et al. (2020): What can we learn from an under-powered absence of difference?},
+  pdfauthor={Ladislas Nalborczyk1, 2, 3},
   pdflang={en-EN},
-  pdfkeywords={NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography},
+  pdfkeywords={NHST, Bayes factor, reanalysis, inner speech, rumination, electromyography},
   hidelinks,
@@
 \fi
+\newlength{\cslhangindent}
+\setlength{\cslhangindent}{1.5em}
+\newlength{\csllabelwidth}
+\setlength{\csllabelwidth}{3em}
+\newlength{\cslentryspacingunit} % times entry-spacing
+\setlength{\cslentryspacingunit}{\parskip}
+\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
+ {% don't indent paragraphs
+  \setlength{\parindent}{0pt}
+  % turn on hanging indent if param 1 is 1
+  \ifodd #1
+  \let\oldpar\par
+  \def\par{\hangindent=\cslhangindent\oldpar}
+  \fi
+  % set entry spacing
+  \setlength{\parskip}{#2\cslentryspacingunit}
+ }%
+ {}
+\usepackage{calc}
+\newcommand{\CSLBlock}[1]{#1\hfill\break}
+\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
+\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
+\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\begin{center}\begin{threeparttable}}
-%   {\end{threeparttable}\end{center}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
+%   {\begin{landscape}\centering\begin{threeparttable}}
+%   {\end{threeparttable}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
 
@@
 % \setlength{\parskip}{0pt plus 0pt minus 0pt}
-
-% Overwrite redefinition of paragraph and subparagraph by the default LaTeX template
-% See https://github.com/crsh/papaja/issues/292
-\makeatletter
-\renewcommand{\paragraph}{\@startsection{paragraph}{4}{\parindent}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-1em}%
-  {\normalfont\normalsize\bfseries\itshape\typesectitle}}
-
-\renewcommand{\subparagraph}[1]{\@startsection{subparagraph}{5}{1em}%
-  {0\baselineskip \@plus 0.2ex \@minus 0.2ex}%
-  {-\z@\relax}%
-  {\normalfont\normalsize\itshape\hspace{\parindent}{#1}\textit{\addperi}}{\relax}}
-\makeatother
 
@@
 \shorttitle{The absence of evidence fallacy}
-\keywords{NHST, Bayesian, logical fallacy, reanalysis, inner speech, rumination, electromyography}
+\keywords{NHST, Bayes factor, reanalysis, inner speech, rumination, electromyography}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
-\ifxetex
+\ifXeTeX
   % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
@@
 \else
-  \usepackage[shorthands=off,main=english]{babel}
+  \usepackage[main=english]{babel}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 \fi
-\ifluatex
+\ifLuaTeX
   \usepackage{selnolig}  % disable illegal ligatures
 \fi
-\newlength{\cslhangindent}
-\setlength{\cslhangindent}{1.5em}
-\newlength{\csllabelwidth}
-\setlength{\csllabelwidth}{3em}
-\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
- {% don't indent paragraphs
-  \setlength{\parindent}{0pt}
-  % turn on hanging indent if param 1 is 1
-  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
-  % set entry spacing
-  \ifnum #2 > 0
-  \setlength{\parskip}{#2\baselineskip}
-  \fi
- }%
- {}
-\usepackage{calc}
-\newcommand{\CSLBlock}[1]{#1\hfill\break}
-\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
-\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
-\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
 
-\title{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): A textbook illustration of the absence of evidence fallacy}
-\author{Ladislas Nalborczyk\textsuperscript{1}}
-\date{}
-
-\authornote{
-
-Correspondence concerning this article should be addressed to Ladislas Nalborczyk, GIPSA-lab, CNRS, Univ.
-Grenoble Alpes, 11 Rue des Mathématiques, 38400 Saint-Martin-d'Hères, France.
-E-mail: \href{mailto:ladislas.nalborczyk@univ-grenoble-alpes.fr}{\nolinkurl{ladislas.nalborczyk@univ-grenoble-alpes.fr}}
-
-}
-
-\affiliation{\vspace{0.5cm}\textsuperscript{1} Univ. Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France}
+\affiliation{\vspace{0.5cm}\textsuperscript{1} Univ.
+Grenoble Alpes, CNRS, Grenoble INP, GIPSA-lab, 38000 Grenoble, France\\\textsuperscript{2} Aix Marseille Univ, CNRS, LPC, Marseille, France\\\textsuperscript{3} Aix Marseille Univ, CNRS, LNC, Marseille, France}
 
@@
 Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly uninformative.
-Moreover, the relation between self-reports and physiological measures was not directly assessed, but only indirectly inferred from differences (or absence thereof) in group averages.
-Given the ample inter-individual variability in these measures (as suggested by our reanalysis), we think inferring the individual-level relation between self-reports and physiological measures from group averages is inappropriate.
-Given these limitations, we conclude that there is limited evidence for the main conclusion put forward by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and we suggest ways forward, both from a theoretical and from a methodological perspective.
+In this short commentary, we show that there is limited evidence for the main conclusion put forward by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+We suggest ways forward, both from a theoretical and methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ba3gk/}.
@@
 
-Wordcount (excluding abstract, references, tables, and figures): 4207
+Wordcount (excluding abstract, references, tables, and figures): 3168
 
@@
 
-The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate or self-regulate (for reviews, see \protect\hyperlink{ref-alderson-day_inner_2015}{Alderson-Day \& Fernyhough, 2015}; \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}; \protect\hyperlink{ref-perrone-bertolotti_what_2014}{Perrone-Bertolotti et al., 2014}).
+The activity of silently talking to oneself or ``inner speech'' is a foundational ability, allowing oneself to remember, plan, self-motivate, or self-regulate (for reviews, see \protect\hyperlink{ref-alderson-day_inner_2015}{Alderson-Day \& Fernyhough, 2015}; \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}; \protect\hyperlink{ref-perrone-bertolotti_what_2014}{Perrone-Bertolotti et al., 2014}).
 However, whereas the use of inner speech is associated with many adaptive functions in everyday life, inner speech dysfunctions can be identified in multiple psychological disorders.
-For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (\protect\hyperlink{ref-Martin}{Martin \& Tesser, 1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse (for a review, see \protect\hyperlink{ref-Nolen-Hoeksema2008}{Nolen-Hoeksema et al., 2008}).
+For instance, rumination, broadly defined as unconstructive repetitive thinking about past events and current mood states (\protect\hyperlink{ref-Martin}{Martin \& Tesser, 1996}), is involved in the onset and maintenance of serious mental disorders such as depression, anxiety, eating disorders, or substance abuse (for review, see \protect\hyperlink{ref-Nolen-Hoeksema2008}{Nolen-Hoeksema et al., 2008}).
 
-Given the predominantly verbal nature of rumination (e.g., \protect\hyperlink{ref-ehring_repetitive_2008}{Ehring \& Watkins, 2008}; \protect\hyperlink{ref-goldwin_concreteness_2013}{Goldwin et al., 2013}; \protect\hyperlink{ref-goldwin_concreteness_2012}{Goldwin \& Behar, 2012}; \protect\hyperlink{ref-mclaughlin_effects_2007}{McLaughlin et al., 2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography and motor interference protocols (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}; e.g., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}; \protect\hyperlink{ref-nalborczyk_articulatory_2020}{Nalborczyk, Perrone-Bertolotti, et al., 2020}).
+Given the predominantly verbal nature of rumination (e.g., \protect\hyperlink{ref-ehring_repetitive_2008}{Ehring \& Watkins, 2008}; \protect\hyperlink{ref-goldwin_concreteness_2013}{Goldwin et al., 2013}; \protect\hyperlink{ref-goldwin_concreteness_2012}{Goldwin \& Behar, 2012}; \protect\hyperlink{ref-mclaughlin_effects_2007}{McLaughlin et al., 2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols (e.g., \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}; \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}, \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
 However, because rumination was only compared to a rest period, it remained uncertain whether this perioral activity was specifically related to (inner) speech processes.
-Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}).
-We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion section of \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}) and more extensively in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
-Although these points were not addressed by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
+Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}).
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion of \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}) and more extensively in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 
-The main conclusion from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
+\protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed an experiment with the aim of refining our understanding of the involvement of the speech motor system in different varieties of inner speech and clarifying the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
+Their main conclusion is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
 In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
@@
 This is unlikely to be the case here, for reasons that we will present and discuss in the present article.
-Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
-That is, some participants had higher perioral muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
-This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
-Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group averages.
-However, given the important inter-individual variability, this reasoning appears highly problematic.
-In the following, we explore each of these limitations and suggests ways forward, both from a theoretical and from a methodological perspective.
+
+\hypertarget{re-analysing-the-data-from-moffatt_inner_2020}{%
+\section{\texorpdfstring{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020})}{Re-analysing the data from Moffatt et al.
+(2020)}}\label{re-analysing-the-data-from-moffatt_inner_2020}}
 
 \hypertarget{exploring-the-data}{%
-\section{Exploring the data}\label{exploring-the-data}}
+\subsection{Exploring the data}\label{exploring-the-data}}
 
@@
 Second, they prompted participants to either ruminate on these (purportedly induced) negative feelings (by asking them to ``think about the causes, consequences, and meaning of their current feelings'') or to distract themselves (by asking them to ``think about a village, city or town that you are particularly familiar with'').
-Rumination and distraction was manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
+Rumination and distraction were manipulated within-subject, with all subjects alternating between rumination and distraction, in a counter-balanced order.
 
@@
 However, the average natural logarithm of the EMG peak amplitude recorded over the OOI and OOS muscles was higher than baseline in both the rumination and distraction conditions, with a slight increase from distraction to rumination (both on the mean and median).
+Having described the data collected by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of some problems related to conclusions that can be made from under-powered non-significant results.
 
@@
 
-To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and \emph{Condition} (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated natural logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
-These analyses were conducted using the \texttt{brms} package (\protect\hyperlink{ref-R-brms}{Bürkner, 2017}), an \texttt{R} implementation of Bayesian multilevel models that employs the probabilistic programming language \texttt{Stan} (\protect\hyperlink{ref-carpenter_stan_2017}{Carpenter et al., 2017}).
-We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations, using weakly informative priors on all parameters (for more details, see the \protect\hyperlink{supp}{supplementary materials}).
-Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
-Constant effects estimates were summarised via their posterior mean and 95\% credible interval.
-We also report Bayes factors (BFs) computed using the Savage-Dickey method.\footnote{This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point (\protect\hyperlink{ref-wagenmakers_bayesian_2010}{Wagenmakers et al., 2010}).} These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
-A summary of the estimations from this model is presented in Table \ref{tab:summary}.
-This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles (as assessed by the BFs).
-However, the BFs supported the null hypothesis (i.e., the hypothesis of no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
+\hypertarget{conclusions-from-under-powered-null-hypothesis-significance-tests}{%
+\subsection{Conclusions from under-powered null-hypothesis significance tests}\label{conclusions-from-under-powered-null-hypothesis-significance-tests}}
 
-\begin{table}[H]
-
-\begin{center}
-\begin{threeparttable}
-
-\caption{\label{tab:summary}Estimated value of the natural logarithm of the EMG peak amplitude in each condition and for each muscle.}
-
-\small{
-
-\begin{tabular}{lcccccc}
-\toprule
-Term & \multicolumn{1}{c}{Estimate} & \multicolumn{1}{c}{SE} & \multicolumn{1}{c}{Lower} & \multicolumn{1}{c}{Upper} & \multicolumn{1}{c}{Rhat} & \multicolumn{1}{c}{BF10}\\
-\midrule
-FRO\_Intercept & -2.076 & 0.096 & -2.266 & -1.888 & 1.000 & 1.785*10\textasciicircum{}16\\
-FRO\_conditionDIS & -0.006 & 0.066 & -0.136 & 0.124 & 1.000 & 0.068\\
-FRO\_conditionRUM & 0.223 & 0.067 & 0.091 & 0.354 & 1.000 & 19.703\\
-OOS\_Intercept & -2.362 & 0.142 & -2.641 & -2.085 & 1.000 & 4.254*10\textasciicircum{}14\\
-OOS\_conditionDIS & 0.165 & 0.111 & -0.053 & 0.384 & 1.000 & 0.336\\
-OOS\_conditionRUM & 0.212 & 0.111 & -0.005 & 0.432 & 1.000 & 0.689\\
-OOI\_Intercept & -2.284 & 0.117 & -2.514 & -2.053 & 1.001 & 7.411*10\textasciicircum{}15\\
-OOI\_conditionDIS & 0.290 & 0.120 & 0.054 & 0.526 & 1.000 & 2.006\\
-OOI\_conditionRUM & 0.371 & 0.119 & 0.137 & 0.603 & 1.000 & 12.876\\
-\bottomrule
-\addlinespace
-\end{tabular}
-
-}
-
-\begin{tablenotes}[para]
-\normalsize{\textit{Note.} For each effect, the 'Estimate' reports the estimated average value of the natural logarithm of the EMG peak amplitude, followed by its standard error (SE).
-The 'Lower' and 'Upper' columns contain the lower and upper bounds of the 95\% CrI, whereas the 'Rhat' column reports the Gelman-Rubin statistic.
-The last column reports the BF in favour of the alternative hypothesis (relative to the null hypothesis).}
-\end{tablenotes}
-
-\end{threeparttable}
-\end{center}
-
-\end{table}
-
-Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
-In Figure \ref{fig:posterior}, we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction conditions for each muscle.
-This figure reveals that the most probable value for this difference was \(\beta = 0.228\) (95\% CrI {[}0.098, 0.357{]}) for the FRO muscle, \(\beta = 0.081\) (95\% CrI {[}-0.155, 0.324{]}) for the OOI muscle, and \(\beta = 0.047\) (95\% CrI {[}-0.167, 0.27{]}) for the OOS muscle.
-Moreover, comparing the posterior distribution to \(\theta = 0\) reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition (given the model, the priors, and the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al., 2020}).
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/posterior-1}
-
-}
-
-\caption{Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\% credible interval.}\label{fig:posterior}
-\end{figure}
-
-Having nuanced some of the conclusions from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of the problems related to conclusions that can be made from under-powered non-significant results.
-
-\hypertarget{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-possibly-go-wrong}{%
-\subsection{Concluding on the null hypothesis from under-powered null-hypothesis significance tests: what could possibly go wrong?}\label{concluding-on-the-null-hypothesis-from-under-powered-null-hypothesis-significance-tests-what-could-possibly-go-wrong}}
-
-There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (\protect\hyperlink{ref-meehl_appraising_1990-1}{Meehl, 1990a}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990b}, e.g., \protect\hyperlink{ref-harlow_problem_1997}{1997}).
+There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (e.g., \protect\hyperlink{ref-meehl_appraising_1990-1}{Meehl, 1990a}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990b}, \protect\hyperlink{ref-harlow_problem_1997}{1997}).
 By ``uninformative,'' we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
@@
 
+\hypertarget{enthusiastic-prior-specifications}{%
+\subsection{Enthusiastic prior specifications}\label{enthusiastic-prior-specifications}}
+
 Anticipating the legitimate critiques on the power of their study, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
-This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} as estimated in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 
@@
 Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
-If we assume that the former is half the size of the latter (which seems reasonable given the high inter-individual variability in such effects, cf.~the next section but also \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}), therefore the a priori power of the main statistical test from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
+If we assume that the former is half the size of the latter, therefore the a priori power of the main statistical test from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
 Notice that whereas taking half the effect size of \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
+
+\hypertarget{frequentist-properties-of-bayes-factors}{%
+\subsection{Frequentist properties of Bayes factors}\label{frequentist-properties-of-bayes-factors}}
 
@@
 
-While we appreciate the effort, the current approach poses new problems.
+However, the current approach poses new problems.
 First, contrary to what the authors suggest, whereas computing a BF indeed allows assessing the \emph{relative evidence} for the null, computing a BF (i.e., comparing two models) does not solve the problem of low power.
@@
 As shown in Figure \ref{fig:bf-dance}, the distribution of log-BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, 6.46\% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
-When the ``true'' effect size is of \(d = 0.36\), 72.06\% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the ``true'' effect size is of \(d = 0.72\), 24.46\% of the log-BFs are still below 0.
+For instance, under the null hypothesis, 7.18\% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
+When the ``true'' effect size is of \(d = 0.36\), 71.69\% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
+When the ``true'' effect size is of \(d = 0.72\), 25.26\% of the log-BFs are still below 0.
 In other words, for small sample and effect sizes, BFs have high error rates.
-To assess the extent to which the BF computed for the OOI by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.29, and 0.03, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
+To assess the extent to which the BF computed for the OOI by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.28, and 0.04, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
 In other words, observing a \(\text{BF}_{10} = 0.278\) is more compatible with the hypothesis of \(d = 0\) (i.e., the null hypothesis) than with the hypothesis of \(d = 0.36\) or \(d = 0.72\), for this sample size.
 
-\hypertarget{within-subject-manipulation-of-rumination-and-distraction}{%
-\subsection{Within-subject manipulation of rumination and distraction}\label{within-subject-manipulation-of-rumination-and-distraction}}
-
-In \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+The problems we discussed previously about the interpretation of under-powered non-significant results also apply to the test \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) performed about the effect or the conditions' order.
+In \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
 More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
 In contrast to this approach, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
-In Figure \ref{fig:order}, we depict again the EMG data, this time grouped by the order in which the participants went through the rumination and distraction conditions.
-This figure reveals some potentially interesting differences between the two groups of participants.
-For instance, the participants that first went through the rumination condition (in green) seem to show a higher increase in the average EMG peak amplitude recorded over the FRO muscle from baseline than the participants that first went through the distraction condition (in orange).
-
-\begin{figure}[!htb]
-
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/order-1}
-
-}
-
-\caption{Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
-The green dots and intervals represent the by-group average and 95\% confidence interval for the participants that first went through the rumination condition, then through the distraction condition.
-The orange dots and intervals represent the by-group average and 95\% confidence interval for the participants that first went through the distraction condition, then through the rumination condition.
-The light green and orange dots in the background represent the individual-level average natural logarithm of the EMG amplitude by muscle, condition, and group.}\label{fig:order}
-\end{figure}
-
 Anticipating again that the order of the within-subject conditions may be an issue, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
@@
 
-Unfortunately, the problems we discussed in the previous section about the interpretation of under-powered non-significant results also apply to this test.
-Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
-This statistical argument is supported by the visual exploration of the data presented in Figure \ref{fig:order}, which suggests possibly crucial differences between the two groups of participants.
-However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
+Unfortunately, obtaining a non-significant effect of the conditions' order is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed (the sample size in each group was of N = 12 and N = 14).
 
-\hypertarget{does-everyone-show-the-effect}{%
-\subsection{Does everyone show the effect?}\label{does-everyone-show-the-effect}}
+\hypertarget{robustness-of-bayes-factors-to-prior-specifications}{%
+\subsection{Robustness of Bayes factors to prior specifications}\label{robustness-of-bayes-factors-to-prior-specifications}}
 
-We previously noted (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}; \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}; e.g., \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}) that surface EMG measures of inner speech production were highly variable between individuals.
-This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
-The data collected by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) is no exception and presents an important degree of inter-individual variability.
-In Figure \ref{fig:everyone}, we represent again the EMG data for each participant (each line is a participant).
-We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
-As it can be seen from this figure, whereas some participants show ``intermediate'' or ``ambiguous'' (i.e., equivalent) patterns of muscular activity across conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) and some others in the distraction condition (in orange).
+Formulated in Bayesian terms, the problem of specifying credible effect sizes in a priori power analyses may be described as a problem of prior specification.
+However, defining sound prior distributions for the alternative hypothesis is notoriously difficult (for some guidance, see for instance \protect\hyperlink{ref-dienes_obtaining_2021}{Dienes, 2021}, \protect\hyperlink{ref-dienes_how_2019}{2019}).
+In Figure \ref{fig:sensitivity}, we report the result of \emph{sensitivity analyses}, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
 
-\begin{figure}[!htb]
+\begin{figure}[!h]
 
-{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/everyone-1}
+{\centering \includegraphics[width=1\linewidth]{manuscript_files/figure-latex/sensitivity-1}
 
@@
 
-\caption{Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
-Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition.}\label{fig:everyone}
+\caption{Prior sensitivity analysis for the Bayes factor computed for each muscle (OOI, OOS, and FRO).
+The x-axis represents the width of the prior put on the standardised effect size (i.e., the prior for the alternative hypothesis).
+The y-axis represents the logarithm of the Bayes factor in favour of the alternative hypothesis.
+The horizontal black dashed line represents equal support (evidence) for each hypothesis.
+The vertical red dashed line depicts the prior width used in Moffatt et al.
+(2020).
+The gray shaded area represents the conventional (but questionable) interval in which BFs are usually considered as negligible (i.e., from 1/3 to 3).}\label{fig:sensitivity}
 \end{figure}
 
-This important inter-individual variability calls into question the use of group averages to describe the nature of inner speech at an individual level.
-Moreover, this variability suggests that some important confounding factors were not taken into account (i.e., either not manipulated in the experiment or statistically controlled for).
-In line with \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
-We agree that a lot could be learnt by relating this (self-reported) subjective experience to the peripheral muscular correlates of inner speech production.
-However, this can not be done at the group level, at the risk of missing individual-level patterns.
-Therefore, we encourage \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, \emph{at an individual level}.
-
-It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by \protect\hyperlink{ref-haaf_developing_2017}{Haaf \& Rouder} (\protect\hyperlink{ref-haaf_developing_2017}{2017}).
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition (e.g., as in \protect\hyperlink{ref-nalborczyk_can_2020}{Nalborczyk, Grandchamp, et al., 2020}).
+This figure strikingly reveals large variability in the resulting BF with varying prior specification.
+More precisely, when the scale (width) of the prior put on the standardised effect size is changed (along the x-axis), the BF changes accordingly.
+For instance, varying the prior scale from 0.1 to 1.0 for the OOI results in BFs from 0.78 to 0.21, respectively.
 
@@
 
-With this paper we aimed to nuance the strong conclusion made by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
-First, we reanalysed the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) and provided some nuance to the conclusion that can be made from these data.
-Second, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+With this short paper, we aimed to nuance the strong conclusion made by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
 Because the statistical tests conducted by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
-Third, we highlighted that the order of the conditions participants went through may impact the effects of the rumination induction (although we can not decide on this issue with the present data).
-Finally, we showed that the group analyses masked important inter-individual variability that should be more carefully examined.
+Second, we highlighted that the frequentist properties of Bayesian tools (e.g., Bayes factors) provide an important piece of information that may help design more informative studies.
+Third, sensitivity analyses further suggested that various prior specifications may lead to different resulting Bayes factors.
 
@@
 Following our initial study (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}), we ran an extension in which we compared verbal to non-verbal rumination.
-The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al., 2020}).
+The results suggested that the facial EMG correlates of verbal and non-verbal rumination were similar (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}).
 Given the ample evidence on the EMG correlates of inner speech production (for an overview, see Chapter 1 in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}), we needed to explain why this particular form of inner speech (induced rumination) was not associated with speech-specific peripheral muscular activity.
 
-In \protect\hyperlink{ref-nalborczyk_dissociating_2020}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2020}{2020}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (\protect\hyperlink{ref-watkins_habit-goal_2014}{Watkins \& Nolen-Hoeksema, 2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+In \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (\protect\hyperlink{ref-watkins_habit-goal_2014}{Watkins \& Nolen-Hoeksema, 2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
 We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
@@
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
-Relating this idea to the motor control framework we previously proposed (\protect\hyperlink{ref-grandchamp_condialint_2019}{Grandchamp et al., 2019}; e.g., \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production, hence resulting in more or less visible peripheral muscular activity (see also a discussion of these ideas in the broader context of motor imagery, \protect\hyperlink{ref-guillot_imagining_2012}{Guillot et al., 2012}).
+Relating this idea to the motor control framework we previously proposed (e.g., \protect\hyperlink{ref-grandchamp_condialint_2019}{Grandchamp et al., 2019}; \protect\hyperlink{ref-loevenbruck_cognitive_2018}{Lœvenbruck et al., 2018}), it may be said that the characteristics of the task or situation (e.g., novelty, difficulty) may influence the amount of inhibition that is applied to motor commands during inner speech production (\protect\hyperlink{ref-nalborczyk_role_2021}{Nalborczyk, Debarnot, et al., 2021}), hence resulting in more or less visible peripheral muscular activity (for a discussion of these ideas in the broader context of motor imagery, see \protect\hyperlink{ref-guillot_imagining_2012}{Guillot et al., 2012}).
 
-Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system (\protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
+Another possible interpretation is that automatic forms of inner speech may rely more heavily on higher-level (e.g., memory-based) cognitive processes whereas less automatic (i.e., more intentional or deliberate) forms of inner speech may rely more on simulation mechanisms via the use of internal models of the speech motor system (\protect\hyperlink{ref-nalborczyk_role_2021}{Nalborczyk, Debarnot, et al., 2021}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
 In other words, the production of automatic versus non-automatic inner speech would be underpinned by different processes that would involve the speech motor system to a different extent.
@@
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
-Indeed, we provided theoretical (epistemological) and empirical (via simulation) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
-Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.
-Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
-We urge the authors to nuance their conclusions, to further analyse their data, and to plan adequately-powered studies in order to settle these issues.
+Indeed, we provided theoretical (epistemological) and empirical (via simulation and sensitivity analyses) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
+This commentary stresses the importance of planning adequately-powered studies of induced rumination, and the need for more thoughtful statistical analyses and data interpretation, as recommended by \protect\hyperlink{ref-wasserstein_moving_2019}{Wasserstein et al.} (\protect\hyperlink{ref-wasserstein_moving_2019}{2019}).
 
@@
 We thank Antonio Schettino for suggesting to include the ``Dance of the Bayes factors'' simulation and for providing helpful comments on a previous version of this manuscript.
+Thanks to Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
 
@@
 \begin{CSLReferences}{1}{0}
-\leavevmode\hypertarget{ref-alderson-day_inner_2015}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-alderson-day_inner_2015}{}}%
 Alderson-Day, B., \& Fernyhough, C.
 (2015).
-Inner speech: {Development}, cognitive functions, phenomenology, and neurobiology.
+Inner speech: Development, cognitive functions, phenomenology, and neurobiology.
 \emph{Psychological Bulletin}, \emph{141}(5), 931--965.
@@
 
-\leavevmode\hypertarget{ref-R-papaja}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-papaja}{}}%
 Aust, F., \& Barth, M. (2017). \emph{{papaja}: {Create} {APA} manuscripts with {R Markdown}}. \url{https://github.com/crsh/papaja}
 
-\leavevmode\hypertarget{ref-R-brms}{}%
-Bürkner, P.-C. (2017). {brms}: An {R} package for bayesian multilevel models using {Stan}. \emph{Journal of Statistical Software}, \emph{80}(1), 1--28. \url{https://doi.org/10.18637/jss.v080.i01}
-
-\leavevmode\hypertarget{ref-carpenter_stan_2017}{}%
-Carpenter, B., Gelman, A., Hoffman, M., Lee, D., Goodrich, B., Betancourt, M., Brubaker, M., Guo, J., Li, P., \& Riddell, A.
-(2017).
-Stan: {A} probabilistic programming language.
-\emph{Journal of Statistical Software, Articles}, \emph{76}(1), 1--32.
-\url{https://doi.org/10.18637/jss.v076.i01}
-
-\leavevmode\hypertarget{ref-cohen_motor_1986}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen_motor_1986}{}}%
 Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. {Springer, Boston, MA}.
 
-\leavevmode\hypertarget{ref-cohen_earth_1994}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-cohen_earth_1994}{}}%
 Cohen, J. (1994). The earth is round (p {\(<\)} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
 
-\leavevmode\hypertarget{ref-ehring_repetitive_2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-dienes_obtaining_2021}{}}%
+Dienes, Z. (2021). Obtaining {Evidence} for {No Effect}. \emph{Collabra: Psychology}, \emph{7}(1), 28202. \url{https://doi.org/10.1525/collabra.28202}
+
+\leavevmode\vadjust pre{\hypertarget{ref-dienes_how_2019}{}}%
+Dienes, Z. (2019). How {Do I Know What My Theory Predicts}? \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 364--377. \url{https://doi.org/10.1177/2515245919876960}
+
+\leavevmode\vadjust pre{\hypertarget{ref-ehring_repetitive_2008}{}}%
 Ehring, T., \& Watkins, E.
@@
 
-\leavevmode\hypertarget{ref-goldwin_concreteness_2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-goldwin_concreteness_2012}{}}%
 Goldwin, M., \& Behar, E.
@@
 
-\leavevmode\hypertarget{ref-goldwin_concreteness_2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-goldwin_concreteness_2013}{}}%
 Goldwin, M., Behar, E., \& Sibrava, N.
@@
 
-\leavevmode\hypertarget{ref-grandchamp_condialint_2019}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-grandchamp_condialint_2019}{}}%
 Grandchamp, R., Rapin, L., Perrone-Bertolotti, M., Pichat, C., Haldin, C., Cousin, E., Lachaux, J.-P., Dohen, M., Perrier, P., Garnier, M., Baciu, M., \& Lœvenbruck, H.
 (2019).
-The {ConDialInt Model}: {Condensation}, {Dialogality}, and {Intentionality Dimensions} of {Inner Speech Within} a {Hierarchical Predictive Control Framework}.
+The {ConDialInt Model}: Condensation, {Dialogality}, and {Intentionality Dimensions} of {Inner Speech Within} a {Hierarchical Predictive Control Framework}.
 \emph{Frontiers in Psychology}, \emph{10}.
@@
 
-\leavevmode\hypertarget{ref-guillot_imagining_2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-guillot_imagining_2012}{}}%
 Guillot, A., Di Rienzo, F., MacIntyre, T., Moran, A., \& Collet, C.
 (2012).
-Imagining is not doing but involves specific motor commands: {A} review of experimental data related to motor inhibition.
+Imagining is not doing but involves specific motor commands: A review of experimental data related to motor inhibition.
 \emph{Frontiers in Human Neuroscience}, \emph{6}.
@@
 
-\leavevmode\hypertarget{ref-haaf_developing_2017}{}%
-Haaf, J. M., \& Rouder, J. N. (2017). Developing constraint in {Bayesian} mixed models. \emph{Psychological Methods}, \emph{22}(4), 779--798. \url{https://doi.org/10.1037/met0000156}
-
-\leavevmode\hypertarget{ref-loevenbruck_cognitive_2018}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-loevenbruck_cognitive_2018}{}}%
 Lœvenbruck, H., Grandchamp, R., Rapin, L., Nalborczyk, L., Dohen, M., Perrier, P., Baciu, M., \& Perrone-Bertolotti, M.
@@
 Langland-Hassan \& A.
-Vicente (Eds.), \emph{Inner speech: {New} voices} (p.
+Vicente (Eds.), \emph{Inner speech: New voices} (p.
 37).
@@
 
-\leavevmode\hypertarget{ref-Martin}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Martin}{}}%
 Martin, L.
@@
 
-\leavevmode\hypertarget{ref-R-wordcountaddin}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-wordcountaddin}{}}%
 Marwick, B. (2019). \emph{Wordcountaddin: Word counts and readability statistics in r markdown documents}.
 
-\leavevmode\hypertarget{ref-mayo_statistical_2018}{}%
-Mayo, D. G. (2018). \emph{Statistical {Inference} as {Severe Testing}: {How} to {Get Beyond} the {Statistics Wars}}. {Cambridge University Press}. \url{https://doi.org/10.1017/9781107286184}
+\leavevmode\vadjust pre{\hypertarget{ref-mayo_statistical_2018}{}}%
+Mayo, D. G. (2018). \emph{Statistical {Inference} as {Severe Testing}: How to {Get Beyond} the {Statistics Wars}}. {Cambridge University Press}. \url{https://doi.org/10.1017/9781107286184}
 
-\leavevmode\hypertarget{ref-mayo_severe_2006}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mayo_severe_2006}{}}%
 Mayo, D.
@@
 (2006).
-Severe {Testing} as a {Basic Concept} in a {Neyman}{{Pearson Philosophy}} of {Induction}.
+Severe {Testing} as a {Basic Concept} in a {Neyman}--{Pearson Philosophy} of {Induction}.
 \emph{The British Journal for the Philosophy of Science}, \emph{57}(2), 323--357.
@@
 
-\leavevmode\hypertarget{ref-mclaughlin_effects_2007}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-mclaughlin_effects_2007}{}}%
 McLaughlin, K.
@@
 
-\leavevmode\hypertarget{ref-meehl_appraising_1990-1}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-meehl_appraising_1990-1}{}}%
 Meehl, P.
@@
 (1990a).
-Appraising and {Amending Theories}: {The Strategy} of {Lakatosian Defense} and {Two Principles} that {Warrant It}.
+Appraising and {Amending Theories}: The {Strategy} of {Lakatosian Defense} and {Two Principles} that {Warrant It}.
 \emph{Psychological Inquiry}, \emph{1}(2), 108--141.
@@
 
-\leavevmode\hypertarget{ref-meehl_theory-testing_1967}{}%
-Meehl, P. E. (1967). Theory-testing in {Psychology} and {Physics}: {A} methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
+\leavevmode\vadjust pre{\hypertarget{ref-meehl_theory-testing_1967}{}}%
+Meehl, P. E. (1967). Theory-testing in {Psychology} and {Physics}: A methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
 
-\leavevmode\hypertarget{ref-meehl_theoretical_1978}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-meehl_theoretical_1978}{}}%
 Meehl, P.
@@
 (1978).
-Theoretical risks and tabular asterisks: {Sir Karl}, {Sir Ronald}, and the slow progress of soft psychology.
+Theoretical risks and tabular asterisks: Sir {Karl}, {Sir Ronald}, and the slow progress of soft psychology.
 \emph{Journal of Consulting and Clinical Psychology}, \emph{46}(4), 806--834.
@@
 
-\leavevmode\hypertarget{ref-meehl_why_1990}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-meehl_why_1990}{}}%
 Meehl, P. E. (1990b). Why {Summaries} of {Research} on {Psychological Theories} are {Often Uninterpretable}. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
 
-\leavevmode\hypertarget{ref-harlow_problem_1997}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-harlow_problem_1997}{}}%
 Meehl, P.
@@
 (1997).
-The problem is epistemology, not statistics: {Replace} significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
+The problem is epistemology, not statistics: Replace significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
 \emph{What If There Were No Significance Tests?}, 393--425.
+\url{http://citeseerx.ist.psu.edu/viewdoc/citations;jsessionid=72FF987997EFB5F0602B02E1A2E04E40?doi=10.1.1.693.9583}
 
-\leavevmode\hypertarget{ref-moffatt_inner_2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-moffatt_inner_2020}{}}%
 Moffatt, J., Mitrenga, K.
@@
 
-\leavevmode\hypertarget{ref-R-here}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-here}{}}%
 Müller, K. (2017). \emph{Here: A simpler way to find your files}. \url{https://CRAN.R-project.org/package=here}
 
-\leavevmode\hypertarget{ref-nalborczyk_understanding_2019}{}%
-Nalborczyk, L. (2019). \emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}PhD Thesis{]}. Univ. Grenoble Alpes \& Ghent University.
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_understanding_2019}{}}%
+Nalborczyk, L.
+(2019).
+\emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}PhD thesis, {Univ.
+Grenoble Alpes \& Ghent University}{]}.
+\url{https://thesiscommons.org/p6dct/}
 
-\leavevmode\hypertarget{ref-nalborczyk_dissociating_2020}{}%
-Nalborczyk, L., Banjac, S., Celine, B., Grandchamp, R., Koster, E.
-H.
-W., Marcela, P.-B., \& Loevenbruck, H.
-(2020).
-\emph{Dissociating facial electromyographic correlates of visual and verbal induced rumination}.
-\url{https://doi.org/10.31234/osf.io/vfjn2}
-
-\leavevmode\hypertarget{ref-nalborczyk_can_2020}{}%
-Nalborczyk, L., Grandchamp, R., Koster, E.
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_dissociating_2021}{}}%
+Nalborczyk, L., Banjac, S., Baeyens, C., Grandchamp, R., Koster, E.
 H.
 W., Perrone-Bertolotti, M., \& Lœvenbruck, H.
-(2020).
-Can we decode phonetic features in inner speech using surface electromyography?
-\emph{PLOS ONE}, \emph{15}(5), e0233282.
-\url{https://doi.org/10.1371/journal.pone.0233282}
+(2021).
+Dissociating facial electromyographic correlates of visual and verbal induced rumination.
+\emph{International Journal of Psychophysiology}, \emph{159}, 23--36.
+\url{https://doi.org/10.1016/j.ijpsycho.2020.10.009}
 
-\leavevmode\hypertarget{ref-nalborczyk_orofacial_2017}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_role_2021}{}}%
+Nalborczyk, L., Debarnot, U., Longcamp, M., Guillot, A., \& Alario, F.-X.
+(2021).
+\emph{The role of motor inhibition during covert speech production} {[}Preprint{]}.
+{PsyArXiv}.
+\url{https://doi.org/10.31234/osf.io/3df57}
+
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_orofacial_2017}{}}%
 Nalborczyk, L., Perrone-Bertolotti, M., Baeyens, C., Grandchamp, R., Polosan, M., Spinelli, E., Koster, E.
@@
 
-\leavevmode\hypertarget{ref-nalborczyk_articulatory_2020}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_articulatory_2020}{}}%
 Nalborczyk, L., Perrone-Bertolotti, M., Baeyens, C., Grandchamp, R., Spinelli, E., Koster, E.
@@
 (2020).
-\emph{Articulatory suppression effects on induced rumination} {[}Under Review{]}.
+\emph{Articulatory suppression effects on induced rumination} {[}Under review{]}.
+Under review.
+\url{https://psyarxiv.com/5d6h7/}
 
-\leavevmode\hypertarget{ref-Nolen-Hoeksema2008}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-Nolen-Hoeksema2008}{}}%
 Nolen-Hoeksema, S., Wisco, B.
@@
 
-\leavevmode\hypertarget{ref-perrone-bertolotti_what_2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-perrone-bertolotti_what_2014}{}}%
 Perrone-Bertolotti, M., Rapin, L., Lachaux, J.
@@
 What is that little voice inside my head?
-{Inner} speech phenomenology, its role in cognitive performance, and its relation to self-monitoring.
+Inner speech phenomenology, its role in cognitive performance, and its relation to self-monitoring.
 \emph{Behavioural Brain Research}, \emph{261}, 220--239.
@@
 
-\leavevmode\hypertarget{ref-pickering_integrated_2013}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pickering_integrated_2013}{}}%
 Pickering, M.
@@
 
-\leavevmode\hypertarget{ref-pollard_probability_1987}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-pollard_probability_1987}{}}%
 Pollard, P., \& Richardson, J. T. (1987). On the probability of making {Type I} errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
 
-\leavevmode\hypertarget{ref-R-base}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-base}{}}%
 R Core Team. (2017). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
 
-\leavevmode\hypertarget{ref-rouder_is_2016}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-rouder_is_2016}{}}%
 Rouder, J.
@@
 
-\leavevmode\hypertarget{ref-sokolov_inner_1972}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-sokolov_inner_1972}{}}%
 Sokolov, A. (1972). \emph{Inner speech and thought}. {Springer-Verlag}.
 
-\leavevmode\hypertarget{ref-tian_mental_2012}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-tian_mental_2012}{}}%
 Tian, X., \& Poeppel, D.
@@
 
-\leavevmode\hypertarget{ref-wagenmakers_bayesian_2010}{}%
-Wagenmakers, E.-J., Lodewyckx, T., Kuriyal, H., \& Grasman, R.
-(2010).
-Bayesian hypothesis testing for psychologists: {A} tutorial on the {Savage}{{Dickey}} method.
-\emph{Cognitive Psychology}, \emph{60}(3), 158--189.
-\url{https://doi.org/10.1016/j.cogpsych.2009.12.001}
+\leavevmode\vadjust pre{\hypertarget{ref-wasserstein_moving_2019}{}}%
+Wasserstein, R.
+L., Schirm, A.
+L., \& Lazar, N.
+A.
+(2019).
+Moving to a world beyond {`` {\emph{p}} {\(<\)} 0.05.''} \emph{The American Statistician}, \emph{73}, 1--19.
+\url{https://doi.org/10.1080/00031305.2019.1583913}
 
-\leavevmode\hypertarget{ref-watkins_habit-goal_2014}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-watkins_habit-goal_2014}{}}%
 Watkins, E. R., \& Nolen-Hoeksema, S. (2014). A habit-goal framework of depressive rumination. \emph{Journal of Abnormal Psychology}, \emph{123}(1), 24--34. \url{https://doi.org/10.1037/a0035540}
 
-\leavevmode\hypertarget{ref-R-tidyverse}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-tidyverse}{}}%
 Wickham, H. (2017). \emph{Tidyverse: Easily install and load the 'tidyverse'}. \url{https://CRAN.R-project.org/package=tidyverse}
 
-\leavevmode\hypertarget{ref-R-knitr}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-knitr}{}}%
 Xie, Y. (2015). \emph{Dynamic documents with {R} and knitr} (2nd ed.). Chapman; Hall/CRC. \url{https://yihui.org/knitr/}
 
-\leavevmode\hypertarget{ref-R-rmarkdown}{}%
+\leavevmode\vadjust pre{\hypertarget{ref-R-rmarkdown}{}}%
 Xie, Y., Allaire, J. J., \& Grolemund, G. (2018). \emph{R markdown: The definitive guide}. Chapman; Hall/CRC. \url{https://bookdown.org/yihui/rmarkdown}

### 2022-02-11 manuscript.Rmd
manucript second revision

@@
 shorttitle: "The absence of evidence fallacy"
-# note: \textcolor{red}{This is an example of a note}
 author: 
@@
 abstract: "@moffatt_inner_2020 reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
-Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that *self-reported* inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
-We suggest this conclusion is at best hasty.
-Indeed, concluding on the absence of an effect based on an under-powered non-significant *p*-value is strongly uninformative.
-In this short commentary, we show that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020.
-We suggest ways forward, both from a theoretical and methodological perspective.
+Based on the absence of significant difference (and BFs between 3.6 and 4.3) in the perioral muscular activity between the rumination and distraction conditions, @moffatt_inner_2020 concluded that *self-reported* inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+In this short commlentary, we show that there is limited evidence for the main conclusion put forward by @moffatt_inner_2020, and we suggest ways forward, both from a theoretical and a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at https://osf.io/ba3gk/."
@@
 numbersections: false
-mask: yes # masking author names
+wordcount: "`r wordcountaddin::word_count(knitr::current_input() )` (excluding abstract, references, tables, and figures)"
+# mask: yes # masking author names
 bibliography: [bib/library.bib, bib/r-references.bib]
@@
 library(BayesFactor)
-library(ggbeeswarm)
+library(simhelpers)
 library(rmarkdown)
 library(tidyverse)
-library(patchwork)
 library(parallel)
@@
 library(readxl)
+library(future)
+library(furrr)
 library(knitr)
-library(BEST)
-library(brms)
 library(glue)
@@
 # counting words in the current .Rmd file
-wordcount <- word_count(knitr::current_input() )
+# wordcount <- word_count(knitr::current_input() )
 ```
-
-Wordcount (excluding abstract, references, tables, and figures): `r wordcount`
-
-\newpage
 
@@
 
-Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols [e.g., @nalborczyk_dissociating_2021; @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_articulatory_2020].
+Given the predominantly verbal nature of rumination [e.g., @ehring_repetitive_2008; @goldwin_concreteness_2012; @goldwin_concreteness_2013; @mclaughlin_effects_2007], we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols [e.g., @nalborczyk_dissociating_2021; @nalborczyk_orofacial_2017; @nalborczyk_understanding_2019; @nalborczyk_articulatory_2022].
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period [@nalborczyk_orofacial_2017].
@@
 
-<!--
-
-Although these points were not addressed by @moffatt_inner_2020, their experimental design nevertheless had the potential to inform our understanding of the involvement of the speech motor system in different varieties of inner speech as well as to clarify the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
-
--->
-
 @moffatt_inner_2020 designed an experiment with the aim of refining our understanding of the involvement of the speech motor system in different varieties of inner speech and clarifying the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 Their main conclusion is that inner experience between induced rumination and distraction differs "without a change in electromyographic correlates of inner speech" (p.1).
-In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference should be substantiated by adequately-powered statistical tests (given the target effect size) as well as reliable measures.
@@
 
-<!--
-
-Moreover, a simple visual exploration of the data reveals important variability between individuals in the main effect of interest.
-That is, some participants had higher perioral muscular activity in the rumination condition than in the distraction condition, and some other participants showed the reverse pattern.
-This suggests unexplored variation in the determinants of this effect (e.g., the content of the inner experience).
-In the following, we explore each of these limitations and suggests ways forward, both from a theoretical and from a methodological perspective.
-
-Indeed, the relation between the inner experience and the physiological correlates of inner speech production was only inferred from group averages.
-However, given the important inter-individual variability, this reasoning appears highly problematic
-
--->
-
-# Re-analysing the data from @moffatt_inner_2020
+# Reconsidering the data from @moffatt_inner_2020
 
@@
 
-<!--
-
-To model EMG peak amplitude variations in response to the rumination and distraction inductions, we fitted a Bayesian multivariate regression model with the natural logarithm of the EMG peak amplitude as an outcome and *Condition* (baseline, rumination, distraction) as a categorical predictor.
-Therefore, the intercept represents the estimated natural logarithm of the EMG peak amplitude in the baseline condition, and the slopes for the rumination and distraction conditions represent deviations from the baseline.
-These analyses were conducted using the `brms` package [@R-brms], an `R` implementation of Bayesian multilevel models that employs the probabilistic programming language `Stan` [@carpenter_stan_2017].
-We ran four chains including each 10.000 iterations and a warmup of 2.000 iterations, using weakly informative priors on all parameters (for more details, see the [supplementary materials](#supp)).
-Posterior convergence was assessed examining autocorrelation and trace plots, as well as the Gelman-Rubin statistic.
-Constant effects estimates were summarised via their posterior mean and 95% credible interval.
-We also report Bayes factors (BFs) computed using the Savage-Dickey method.^[This method consists in taking the ratio of the posterior density at the point of interest divided by the prior density at that point [@wagenmakers_bayesian_2010].] These BFs can be interpreted as updating factors, from prior knowledge (what we knew before seeing the data) to posterior knowledge (what we know after seeing the data).
-A summary of the estimations from this model is presented in Table \@ref(tab:summary).
-This analysis revealed strong evidence for the hypothesis of a higher average EMG peak amplitude in the rumination condition as compared to the baseline condition for both the FRO and OOI muscles (as assessed by the BFs).
-However, the BFs supported the null hypothesis (i.e., the hypothesis of no difference) between the baseline and distraction conditions for the FRO and were inconclusive for both the OOI and OOS muscles.
-
-```{r models, results = "hide"}
-##############################
-# Bayesian multilevel models #
-##############################
-
-# priors for the constant-effects model
-priors_constant <- c(
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "FRO"),
-    prior(normal(0, 1), class = b, resp = "FRO"),
-    prior(exponential(1), class = sigma, resp = "FRO"),
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOS"),
-    prior(normal(0, 1), class = b, resp = "OOS"),
-    prior(exponential(1), class = sigma, resp = "OOS"),
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOI"),
-    prior(normal(0, 1), class = b, resp = "OOI"),
-    prior(exponential(1), class = sigma, resp = "OOI")
-    )
-
-# fitting the model
-constant_effects <- brm(
-    mvbind(FRO, OOS, OOI) ~ 0 + Intercept + condition,
-    family = gaussian(),
-    prior = priors_constant,
-    data = df2,
-    chains = 4, cores = 4,
-    warmup = 2000, iter = 10000,
-    control = list(adapt_delta = 0.95),
-    sample_prior = TRUE,
-    file = here("models/constant_effects")
-    )
-
-# priors for the varying-effects model
-priors_varying <- c(
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "FRO"),
-    prior(normal(0, 1), class = b, resp = "FRO"),
-    prior(exponential(1), class = sigma, resp = "FRO"),
-    prior(exponential(1), class = sd, resp = "FRO"),
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOS"),
-    prior(normal(0, 1), class = b, resp = "OOS"),
-    prior(exponential(1), class = sigma, resp = "OOS"),
-    prior(exponential(1), class = sd, resp = "OOS"),
-    prior(normal(0, 5), class = b, coef = Intercept, resp = "OOI"),
-    prior(normal(0, 1), class = b, resp = "OOI"),
-    prior(exponential(1), class = sigma, resp = "OOI"),
-    prior(exponential(1), class = sd, resp = "OOI")
-    )
-
-# fitting the model
-varying_effects <- brm(
-    mvbind(FRO, OOS, OOI) ~ 0 + Intercept + condition + (0 + Intercept | ID),
-    family = gaussian(),
-    prior = priors_varying,
-    data = df2,
-    chains = 4, cores = 4,
-    warmup = 2000, iter = 10000,
-    control = list(adapt_delta = 0.95),
-    sample_prior = TRUE,
-    file = here("models/varying_effects")
-    )
-```
-
-```{r bf, eval = FALSE, fig.width = 10, fig.cap = "Savage-Dickey Bayes factor for the difference between the rumination and distraction conditions for each muscle.
-The BF is computed as the ratio of the posterior density to the prior density at $\\theta = 0$."}
-# BF testing
-hyp_fro <- hypothesis(
-    x = varying_effects,
-    hypothesis = "FRO_conditionDIS = FRO_conditionRUM"
-    )
-
-p1 <- plot(hyp_fro, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
-    geom_vline(xintercept = 0, linetype = 2) +
-    coord_cartesian(xlim = c(-5, 5), ylim = c(0, 7.5) ) +
-    theme_bw(base_size = 12, base_family = "Open Sans") +
-    theme(legend.title = element_blank() ) +
-    labs(
-      x = "Log EMG peak amplitude",
-      y = "Probability density",
-      title = paste0(
-        "BF10 = ", round(1 / hyp_fro$hypothesis$Evid.Ratio, 3),
-        " (BF01 = ", round(hyp_fro$hypothesis$Evid.Ratio, 3), ")"
-        )
-      )
-
-hyp_ooi <- hypothesis(
-    varying_effects,
-    "OOI_conditionDIS = OOI_conditionRUM"
-    )
-
-p2 <- plot(hyp_ooi, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
-    geom_vline(xintercept = 0, linetype = 2) +
-    coord_cartesian(xlim = c(-5, 5), ylim = c(0, 7.5) ) +
-    theme_bw(base_size = 12, base_family = "Open Sans") +
-    theme(legend.title = element_blank() ) +
-    labs(
-      x = "Log EMG peak amplitude",
-      title = paste0(
-        "BF10 = ", round(1 / hyp_ooi$hypothesis$Evid.Ratio, 3),
-        " (BF01 = ", round(hyp_ooi$hypothesis$Evid.Ratio, 3), ")"
-        )
-      )
-
-hyp_oos <- hypothesis(
-    varying_effects,
-    "OOS_conditionDIS = OOS_conditionRUM"
-    )
-
-p3 <- plot(hyp_oos, plot = FALSE, theme = theme_bw(base_size = 12) )[[1]] +
-    geom_vline(xintercept = 0, linetype = 2) +
-    coord_cartesian(xlim = c(-5, 5), ylim = c(0, 7.5) ) +
-    theme_bw(base_size = 12, base_family = "Open Sans") +
-    theme(legend.title = element_blank() ) +
-    labs(
-      x = "Log EMG peak amplitude",
-      title = paste0(
-        "BF10 = ", round(1 / hyp_oos$hypothesis$Evid.Ratio, 3),
-        " (BF01 = ", round(hyp_oos$hypothesis$Evid.Ratio, 3), ")"
-        )
-      )
-
-p1 + p2 + p3 + plot_layout(guides = "collect") & theme(legend.position = "bottom")
-```
-
-```{r summary, result = "asis"}
-changeSciNot <- function(n) {
-
-  output <- format(n, digits = 4, scientific = TRUE)
-  output <- sub("e", "*10^", output)
-  output <- sub("\\+0?", "", output)
-  output <- sub("-0?", "-", output)
-  output
-
-}
-
-summary_varying_effects <-
-    # retrieve estimations from bmod5
-    summary(varying_effects, prob = 0.95)$fixed %>%
-    # convert to dataframe
-    data.frame %>%
-    # sets rownames as the first column
-    rownames_to_column(var = "response") %>%
-    # removing ESS information
-    dplyr::select(-Bulk_ESS, -Tail_ESS) %>%
-    # rename columns
-    magrittr::set_colnames(
-        c("Term", "Estimate", "SE", "Lower", "Upper", "Rhat")
-        ) %>%
-    # compute BF for each effect
-    mutate(
-        BF10 = 1 / hypothesis(
-          varying_effects, glue("{Term} = 0")
-          )$hypothesis$Evid.Ratio
-        ) %>%
-    # round BFs
-    mutate(
-      BF10 = ifelse(
-        BF10 < 0.001 | BF10 > 1e3,
-        changeSciNot(abs(BF10) ),
-        round(BF10, 3)
-        )
-      ) %>%
-    # if numeric, round to 3 decimals
-    mutate_if(is.numeric, round, 3)
-
-apa_table(
-    summary_varying_effects,
-    placement = "H",
-    digits = 3,
-    align = c("l", rep("c", 6) ),
-    caption = "Estimated value of the natural logarithm of the EMG peak amplitude in each condition and for each muscle.",
-    note = "For each effect, the 'Estimate' reports the estimated average value of the natural logarithm of the EMG peak amplitude, followed by its standard error (SE).
-The 'Lower' and 'Upper' columns contain the lower and upper bounds of the 95% CrI, whereas the 'Rhat' column reports the Gelman-Rubin statistic.
-The last column reports the BF in favour of the alternative hypothesis (relative to the null hypothesis).",
-    small = TRUE,
-    escape = TRUE
-    )
-```
-
-Because the result of a Bayesian analysis is a joint posterior probability over all parameters of the model, we can compute the posterior distribution of the difference between any pair of conditions.
-In Figure \@ref(fig:posterior), we represent the posterior distribution of the difference in EMG peak amplitude between the rumination and distraction conditions for each muscle.
-This figure reveals that the most probable value for this difference was $\beta = 0.228$ (95% CrI [0.098, 0.357]) for the FRO muscle, $\beta = 0.081$ (95% CrI [-0.155, 0.324]) for the OOI muscle, and $\beta = 0.047$ (95% CrI [-0.167, 0.27]) for the OOS muscle.
-Moreover, comparing the posterior distribution to $\theta = 0$ reveals that there is a probability of 0.753 that the average peak EMG amplitude recorded over the OOI is higher in the rumination condition than in the distraction condition [given the model, the priors, and the data from @moffatt_inner_2020].
-
-```{r posterior, fig.width = 10, fig.height = 4, eval = TRUE, fig.cap = "Posterior distribution of the difference in EMG peak amplitude between the rumination and distraction condition for each muscle, along with its mean and 95\\% credible interval."}
-# extracts posterior samples
-post <- posterior_samples(varying_effects)
-
-# grid of plots
-par(mfrow = c(1, 3) )
-
-plotPost(
-    post$b_FRO_conditionRUM - post$b_FRO_conditionDIS,
-    compVal = 0, xlab = "Rumination - Distraction", main = "FRO"
-    )
-
-plotPost(
-    post$b_OOI_conditionRUM - post$b_OOI_conditionDIS,
-    compVal = 0, xlab = "Rumination - Distraction", main = "OOI"
-    )
-
-plotPost(
-    post$b_OOS_conditionRUM - post$b_OOS_conditionDIS,
-    compVal = 0, xlab = "Rumination - Distraction", main = "OOS"
-    )
-```
-
--->
-
 ## Conclusions from under-powered null-hypothesis significance tests
@@
 
-## Enthusiastic prior specifications
+## Optimistic a priori power analysis
 
@@
 The red vertical dashed line indicates the value of the BF computed for the OOI by Moffatt et al.
-(2020), on the log scale."}
+(2020), on the logarithmic scale.
+The grey shaded area represents the conventional (but questionable) interval in which BFs are usually considered as inconclusive."}
 # inspired from http://daniellakens.blogspot.com/2016/07/dance-of-bayes-factors.html
-# population effect size
-cohensd <- 0.36
 
@@
 
-# initialises an empty array to store the results
-results <- data.frame(
-  BF10 = numeric(nsims),
-  BF10_null = numeric(nsims),
-  BF10_double = numeric(nsims)
-  )
+# defining the combinations of parameters values to explore
+params <- crossing(cohensd = c(0, 0.36, 0.72), iterations = 1:nsims) %>%
+    mutate(seed = round(runif(n = 1, min = 0, max = 1) * 2^30) + 1:n() )
 
-for (i in 1:nsims) { # for each simulated experiment
+run_sim <- function(cohensd, iterations, seed = NULL) {
 
-  # produces N simulated participants
+    # setting the seed
+    if (!is.null(seed) ) set.seed(seed)
+
+    # produces N simulated participants in condition 1
     x <- rnorm(n = n, mean = 0, sd = 1)
 
-  # produces N simulated participants when d = 0.36
+    # produces N simulated participants in condition 2
     y <- rnorm(n = n, mean = 0 + cohensd, sd = 1)
 
-  # produces N simulated participants when d = 0
-  y_null <- rnorm(n = n, mean = 0, sd = 1)
-
-  # produces N simulated participants when d = 0.72
-  y_double <- rnorm(n = n, mean = 0 + cohensd * 2, sd = 1)
-
-  # computes the BF10 when d = 0.36
-  results$BF10[i] <- ttestBF(
-    x = x, y = y, paired = TRUE, rscale = "medium"
-    ) %>%
+    # computing the BF
+    results <- ttestBF(x = x, y = y, paired = TRUE, rscale = "medium") %>%
     data.frame %>%
@@
 
-  # computes the BF10 when d = 0
-  results$BF10_null[i] <- ttestBF(
-    x = x, y = y_null, paired = TRUE, rscale = "medium"
-    ) %>%
-    data.frame %>%
-    pull(bf)
-
-  # computes the BF10 when d = 0.72
-  results$BF10_double[i] <- ttestBF(
-    x = x, y = y_double, paired = TRUE, rscale = "medium"
-    ) %>%
-    data.frame %>%
-    pull(bf)
+    # returning the BF
+    return(results)
 
@@
 
-# computing the proportion of simulated BFs above 1
-prop_d0 <- mean(results$BF10_null > 1)
-prop_d0.36 <- mean(results$BF10 > 1)
-prop_d0.72 <- mean(results$BF10_double > 1)
+# choosing an appropriate plan from the future package
+plan(multisession(workers = detectCores() ) )
+
+# then, running the simulations
+simulation_results <- evaluate_by_row(
+    params = params, sim_function = run_sim,
+    .progress = FALSE, system_time = FALSE
+    )
+
+# computing the proportion of "erroneous" BFs
+prop_error_d0 <- simulation_results %>% filter(cohensd == 0) %>% pull(.results)
+prop_error_d0 <- mean(prop_error_d0 > 3)
+prop_error_d0.36 <- simulation_results %>% filter(cohensd == 0.36) %>% pull(.results)
+prop_error_d0.36 <- mean(prop_error_d0.36 < 1 / 3)
+prop_error_d0.72 <- simulation_results %>% filter(cohensd == 0.72) %>% pull(.results)
+prop_error_d0.72 <- mean(prop_error_d0.72 < 1 / 3)
+
+# computing the proportion of inconclusive BFs
+prop_inconclusive_d0 <- simulation_results %>% filter(cohensd == 0) %>% pull(.results)
+prop_inconclusive_d0 <- mean(prop_inconclusive_d0 > 1/3 & prop_inconclusive_d0 < 3)
+prop_inconclusive_d0.36 <- simulation_results %>% filter(cohensd == 0.36) %>% pull(.results)
+prop_inconclusive_d0.36 <- mean(prop_inconclusive_d0.36 > 1/3 & prop_inconclusive_d0.36 < 3)
+prop_inconclusive_d0.72 <- simulation_results %>% filter(cohensd == 0.72) %>% pull(.results)
+prop_inconclusive_d0.72 <- mean(prop_inconclusive_d0.72 > 1/3 & prop_inconclusive_d0.72 < 3)
 
 # plotting the results
-results %>%
-  pivot_longer(cols = BF10:BF10_double, names_to = "type") %>%
+simulation_results %>%
   mutate(
     type = factor(
-      type,
-      levels = c("BF10_null", "BF10", "BF10_double"),
+      x = cohensd,
       labels = c("Cohen's d = 0", "Cohen's d = 0.36", "Cohen's d = 0.72")
@@
     ) %>%
+  rename(value = .results) %>%
   ggplot(aes(x = log(value), colour = type, fill = type) ) +
+  geom_rect(
+    data = data.frame(xmin = log(1 / 3), xmax = log(3), ymin = -Inf, ymax = Inf),
+    aes(xmin = xmin, xmax = xmax, ymin = ymin, ymax = ymax),
+    color = NA,
+    alpha = 0.25,
+    inherit.aes = FALSE
+    ) +
   geom_vline(xintercept = 0, linetype = 2) +
-  geom_vline(xintercept = log(0.278), linetype = 2, colour = "orangered") +
-  geom_histogram(colour = "white", show.legend = FALSE, bins = 40) +
+  geom_histogram(alpha = 0.5, show.legend = FALSE, bins = 60) +
+  geom_vline(xintercept = log(0.278), linetype = 1, size = 0.5, colour = "orangered") +
+  annotate(geom = "point", x = log(0.278), y = 0, colour = "orangered", size = 2) +
   theme_bw(base_size = 12, base_family = "Open Sans") +
-  facet_wrap(~ type, scales = "free_x") +
+  facet_wrap(~ type) + # , scales = "free_x") +
+  coord_cartesian(xlim = c(NA, 8) ) +
   labs(x = "Natural logarithm of the BF10", y = "Number of simulations") +
@@
 As shown in Figure \@ref(fig:bf-dance), the distribution of log-BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, `r round(prop_d0 * 100, 2)`% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the "true" effect size is $d = 0$).
-When the "true" effect size is of $d = 0.36$, `r round(100 - prop_d0.36 * 100, 2)`% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the "true" effect size is of $d = 0.72$, `r round(100 - prop_d0.72 * 100, 2)`% of the log-BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.
-To assess the extent to which the BF computed for the OOI by @moffatt_inner_2020 (i.e., $\text{BF}_{10} = 0.278$) is "surprising" given or "compatible" with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to `r round(1 - mean(results$BF10_null > 0.278), 2)`, `r round(1 - mean(results$BF10 > 0.278), 2)`, and `r round(1 - mean(results$BF10_double > 0.278), 2)`, for the hypothesis of $d = 0$, $d = 0.36$, and $d = 0.72$, respectively.
-In other words, observing a $\text{BF}_{10} = 0.278$ is more compatible with the hypothesis of $d = 0$ (i.e., the null hypothesis) than with the hypothesis of $d = 0.36$ or $d = 0.72$, for this sample size.
+For instance, `r round(prop_inconclusive_d0 * 100, 2)`% of the computed log-BFs under the null hypothesis are "inconclusive" and `r round(prop_error_d0 * 100, 2)`% of the log-BFs support the alternative hypothesis (although the population effect size is $d = 0$).
+When the population effect size is of $d = 0.36$, `r round(prop_inconclusive_d0.36 * 100, 2)`% of the computed log-BFs are "inconclusive" and `r round(prop_error_d0.36 * 100, 2)`% of the log-BFs support the null hypothesis (although the population effect size is actually non-null).
+When the population effect size is of $d = 0.72$, `r round(prop_inconclusive_d0.72 * 100, 2)`% of the computed log-BFs are "inconclusive" and `r round(prop_error_d0.72 * 100, 2)`% of the log-BFs support the null hypothesis.
+In brief, this simulations shows that for small sample and effect sizes, BFs have non-negligible error rates [see also @schonbrodt_sequential_2017].^[It should be noted that, as stressed by @rouder_optional_2014, Bayes factors indicate the relative evidence for a hypothesis, conditional on some observed data.
+In other words, Bayesian updating is not conditional on some hypothetical truth.
+With this in mind, the present simulation aims at illustrating how the frequentist properties of BFs may be used to design more informative studies [see also @schonbrodt_bayes_2018], while acknowledging that proper long-term error rates *control* is not the realm of the Bayesian framework.]
 
-<!--
-
-Second, we conducted another simulation with the aim of assessing the relation between the sample size and the value of the BF.
-In the previous section, we fitted a multivariate Bayesian regression model with varying-intercepts by participant and weakly informative priors on the EMG data collected by @moffatt_inner_2020.
-Using this model, we i) generated new datasets from the posterior predictive distribution of this model and ii) we computed the BF in favour of the alternative hypothesis ($\text{BF}_{10}$) using the `BayesFactor` package [@R-BayesFactor].
-We used a "medium" prior (i.e., $r = \sqrt{2}/2$) on the scale parameter of the Cauchy prior for the alternative hypothesis.
-We repeated this procedure for varying sample sizes from 20 to 200 participants (by increments of 10 participants) with $1000$ simulations (i.e., 1000 simulated datasets) for each sample size.
-
-```{r simulated-power, eval = FALSE, fig.cap = "Average natural logarithm of the Bayes factor in favour of the alternative hypothesis, along with its standard error, computed over 1000 datasets of increasing size simulated from the posterior predictive distribution of the varying-intercept multivariate Bayesian regresion model, fitted on the data from Moffatt et al.
-(2020).
-A log-BF belows 0 represents evidence for the null hypothesis (relative to the alternative hypothesis) and a log-BF above 0 represents evidence for the alternative hypothesis (relative to the null hypothesis)."}
-# running the simulations
-# source("code/bf_simulation.R")
-
-# loading the results
-load(file = "results/overall_results.Rda")
-
-# simulations parameters
-nsims <- 1e3
-sample_size <- seq.int(from = 20, to = 200, by = 10)
-
-# plotting the results
-overall_results %>%
-    na.omit() %>%
-    filter_all(any_vars(. != 0) ) %>%
-    pivot_longer(cols = bf_fro:bf_oos, names_to = "bf_type") %>%
-    mutate(value = log(value) ) %>%
-    mutate(bf_type = factor(bf_type, labels = c("FRO", "OOI", "OOS") ) ) %>%
-    group_by(nobs, bf_type) %>%
-    summarise(
-        across(
-            .cols = value,
-            .fns = list(mean = mean, se = ~sd(.x) / sqrt(nsims) )
-            )
-        ) %>%
-    ungroup() %>% 
-    ggplot(aes(x = nobs, y = value_mean, colour = bf_type, fill = bf_type) ) +
-    geom_hline(yintercept = 0, lty = 3) +
-    geom_ribbon(
-        aes(
-          x = nobs, ymin = value_mean - 1.96 * value_se,
-          ymax = value_mean + 1.96 * value_se, colour = NULL
-          ),
-        alpha = 0.5, show.legend = FALSE
-        ) + 
-    geom_line(show.legend = FALSE) +
-    geom_point(show.legend = FALSE) +
-    facet_wrap(~bf_type, scales = "free") +
-    scale_x_continuous(breaks = unique(sample_size)[c(TRUE, FALSE)]) +
-    theme_bw(base_size = 10) +
-    labs(x = "Number of participants", y = "Natural logarithm of the Bayes factor") +
-    scale_colour_brewer(palette = "Dark2", direction = 1) +
-    scale_fill_brewer(palette = "Dark2", direction = 1)
-```
-
-As shown in Figure \@ref(fig:simulated-power), the natural logarithm of the BF in favour of the alternative hypothesis is growing proportionally with sample size.
-More precisely, whereas BFs computed on small samples (i.e., below 80 participants) support the null hypothesis, BFs computed on larger samples support the alternative hypothesis for all three facial muscles.
-For instance, the average $\text{BF}_{10}$ computed for the OOI muscle with a sample size of 160 participants is of $\exp(2.18) \approx 8.85$, indicating that these data are approximately $8.85$ times more likely under the alternative hypothesis than under the null hypothesis.
-To sum up, this reveals that although at low sample sizes, the BF may provide (weak) evidence for the null hypothesis (relative to the alternative hypothesis), this pattern may very well reverse for higher sample sizes.
-
-We should keep in mind some limitations of this analysis, which uses simulated datasets from the posterior predictive distribution estimated on the data collected by @moffatt_inner_2020.
-This analysis resembles to the Bayesian analogue of the frequentist post-hoc power analysis, which has been much criticised [e.g., @lakens_20_2014].
-A crucial assumption of the present analysis is that the data from @moffatt_inner_2020 is our best source of information regarding the main effect of interest.
-However, the present analysis also differs from the frequentist post-hoc power analysis on several grounds.
-First, with the present analysis, we do not aim to assess the ability of our statistical test to pass some dichotomic threshold (e.g., accept/reject).
-Instead, we aim to assess how the $\text{BF}_{10}$ (i.e., the evidence for the alternative hypothesis, relative to the null hypothesis) behaves with varying sample sizes.
-Second, the present analysis relies on the posterior predictive distribution of the model fitted on the data from @moffatt_inner_2020, which naturally incorporates uncertainty about the effect of interest.
-By simulating datasets of varying sample sizes from the posterior predictive distribution (and by relying on a large number of simulations), uncertainty about the effect size is naturally incorporated into the results of the simulation.
-
--->
-
-The problems we discussed previously about the interpretation of under-powered non-significant results also apply to the test @moffatt_inner_2020 performed about the effect or the conditions' order.
+The problems discussed above about the interpretation of under-powered non-significant results also apply to the test @moffatt_inner_2020 performed regarding the effect or the conditions' order.
 In @nalborczyk_dissociating_2021, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
@@
 However, defining sound prior distributions for the alternative hypothesis is notoriously difficult [for some guidance, see for instance @dienes_obtaining_2021; @dienes_how_2019].
-In Figure \@ref(fig:sensitivity), we report the result of *sensitivity analyses*, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
+In Figure \@ref(fig:sensitivity), we report the results of prior *sensitivity analyses*, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
 
@@
 (2020).
-The gray shaded area represents the conventional (but questionable) interval in which BFs are usually considered as negligible (i.e., from 1/3 to 3)."}
+The grey shaded area represents the conventional (but questionable) interval in which BFs are usually considered as inconclusive."}
 # code adapted from https://vasishth.github.io/bayescogsci/book/sec-N400BF.html
@@
     coord_cartesian(expand = FALSE) +
-    labs(x = "Prior scale (width) for the alternative hypothesis", y = "Logarithm of the BF10") +
+    labs(x = "Prior scale (width) for the alternative hypothesis", y = "Natural logarithm of the BF10") +
     scale_x_continuous(
@@
 
-This figure strikingly reveals large variability in the resulting BF with varying prior specification.
+This figure strikingly reveals large variability in the resulting BF with various prior specifications.
 More precisely, when the scale (width) of the prior put on the standardised effect size is changed (along the x-axis), the BF changes accordingly.
 For instance, varying the prior scale from 0.1 to 1.0 for the OOI results in BFs from 0.78 to 0.21, respectively.
-
-<!--
-
-## Within-subject manipulation of rumination and distraction
-
-In @nalborczyk_dissociating_2021, we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
-More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
-In contrast to this approach, @moffatt_inner_2020 asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
-In Figure \@ref(fig:order), we depict again the EMG data, this time grouped by the order in which the participants went through the rumination and distraction conditions.
-This figure reveals some potentially interesting differences between the two groups of participants.
-For instance, the participants that first went through the rumination condition (in green) seem to show a higher increase in the average EMG peak amplitude  recorded over the FRO muscle from baseline than the participants that first went through the distraction condition (in orange).
-
-```{r order, eval = FALSE, fig.cap = "Average natural logarithm of the EMG peak amplitude by muscle, condition, and group.
-The green dots and intervals represent the by-group average and 95\\% confidence interval for the participants that first went through the rumination condition, then through the distraction condition.
-The orange dots and intervals represent the by-group average and 95\\% confidence interval for the participants that first went through the distraction condition, then through the rumination condition.
-The light green and orange dots in the background represent the individual-level average natural logarithm of the EMG amplitude by muscle, condition, and group."}
-# position for groups
-pd <- position_dodge(0.8)
-
-# plotting the data
-df2 %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = FRO:OOI,
-        names_to = "muscle",
-        values_to = "value",
-        values_drop_na = TRUE
-        ) %>%
-    mutate(order = factor(order, labels = c("RUM -> DIS", "DIS -> RUM")) ) %>%
-    # plots the data
-    ggplot(aes(x = condition, y = value, colour = order, fill = order) ) +
-    # plotting individual data points
-    geom_quasirandom(alpha = 0.3) +
-    # plotting means
-    stat_summary(
-        fun.y = mean,
-        geom = "line", size = 1,
-        aes(group = interaction(muscle, order) ),
-        position = pd,
-        show.legend = FALSE
-        ) +
-    # plotting means
-    stat_summary(
-        fun.y = "mean",
-        geom = "point", shape = 16, size = 3,
-        position = pd,
-        show.legend = TRUE
-        ) +
-    # plotting confidence intervals
-    stat_summary(
-        fun.data = mean_cl_normal,
-        geom = "errorbar", size = 1, width = 0,
-        fun.args = list(mult = 1.96),
-        show.legend = FALSE,
-        position = pd
-        ) +
-    # facetting by muscle
-    facet_wrap(~muscle, ncol = 3) +
-    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
-    theme_bw(base_size = 10) +
-    scale_colour_brewer(palette = "Dark2", direction = 1) +
-    scale_fill_brewer(palette = "Dark2", direction = 1) +
-    theme(
-      legend.title = element_blank(),
-      legend.position = "top",
-      legend.background = element_rect(size = 0.5, linetype = "solid", colour = "black")
-    )
-```
-
-Anticipating again that the order of the within-subject conditions may be an issue, @moffatt_inner_2020 say:
-
-> "Unless otherwise reported, the inclusion of order in which the conditions were completed as a between-subjects variable as part of a mixed-design ANOVA produced no significant main effects or interactions involving order." (p.7)
-
-Unfortunately, the problems we discussed in the previous section about the interpretation of under-powered non-significant results also apply to this test.
-Namely, obtaining a non-significant effect of group is very weak evidence that order did not play a role in the results, given the low power of the tests that were performed.
-This statistical argument is supported by the visual exploration of the data presented in Figure \@ref(fig:order), which suggests possibly crucial differences between the two groups of participants.
-However, given the sample size in each group (N = 12 and N = 14), it is impossible to know for sure at this point.
-
-## Does everyone show the effect?
-
-We previously noted [e.g., @nalborczyk_orofacial_2017; @nalborczyk_dissociating_2021; @nalborczyk_understanding_2019; @nalborczyk_can_2020] that surface EMG measures of inner speech production were highly variable between individuals.
-This can be explained by the imagery ability of each individual, the reliability of the measurement, or the instructions that are given to the participants (and whether they are understood in a similar manner by all participants).
-The data collected by @moffatt_inner_2020 is no exception and presents an important degree of inter-individual variability.
-In Figure \@ref(fig:everyone), we represent again the EMG data for each participant (each line is a participant).
-We used two colours to represent the participants that showed a higher average EMG peak amplitude either in the rumination condition (in green) or in the distraction condition (in orange).
-As it can be seen from this figure, whereas some participants show "intermediate" or "ambiguous" (i.e., equivalent) patterns of muscular activity across conditions, some participants show a clear superior EMG peak amplitude in the rumination condition (in green) and some others in the distraction condition (in orange).
-
-```{r everyone, fig.cap = "Inter-individual variability in the main effect of interest (i.e., the difference between the rumination and distraction conditions).
-Green dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the rumination condition than in the distraction condition, whereas orange dots and lines represent the average natural logarithm of the EMG amplitude of participants that showed a higher EMG amplitude in the distraction condition than in the rumination condition."}
-# does everyone plot
-df2 %>%
-    pivot_longer(cols = FRO:OOI, names_to = "muscle") %>%
-    pivot_wider(names_from = condition, values_from = value) %>%
-    mutate(ruminator = ifelse(RUM > DIS, 1, 0) ) %>%
-    mutate(ruminator = as.factor(ruminator) ) %>%
-    mutate(rum_dis = RUM - DIS) %>%
-    pivot_longer(cols = RUM:BAS, names_to = "condition") %>%
-    ggplot(aes(x = condition, y = value, colour = ruminator) ) +
-    # violin plots
-    geom_violin(
-        scale = "count",
-        fill = "black",
-        alpha = 0.15,
-        colour = "white",
-        position = pd,
-        draw_quantiles = 0.5,
-        show.legend = FALSE
-        ) +
-    # plotting individual data points
-    geom_point(size = 2, alpha = 0.8, show.legend = FALSE) +
-    # plotting individual trajectories
-    geom_line(aes(group = ID), size = 0.5, alpha = 0.8, show.legend = FALSE) +
-    # facetting by muscle
-    facet_wrap(~muscle) +
-    # axis labels
-    labs(x = "Condition", y = "Natural logarithm of peak amplitude") +
-    theme_bw(base_size = 10) +
-    scale_colour_brewer(palette = "Dark2", direction = -1) +
-    scale_fill_brewer(palette = "Dark2", direction = -1)
-```
-
-This important inter-individual variability calls into question the use of group averages to describe the nature of inner speech at an individual level.
-Moreover, this variability suggests that some important confounding factors were not taken into account (i.e., either not manipulated in the experiment or statistically controlled for).
-In line with @moffatt_inner_2020, we suggest these discrepancies could be explained by differences in the subjective experience of inner speech.
-We agree that a lot could be learnt by relating this (self-reported) subjective experience to the peripheral muscular correlates of inner speech production.
-However, this can not be done at the group level, at the risk of missing individual-level patterns.
-Therefore, we encourage @moffatt_inner_2020 to further analyse their data in order to assess whether the perioral EMG correlates (e.g., the amplitude of the difference between the rumination and distraction conditions on the OOI) can be predicted by the self-reported subjective experience, *at an individual level*.
-
-It should be noted that the question of the qualitative differences in the EMG correlates of inner speech may also be assessed more formally using the model comparison approach developed by @haaf_developing_2017.
-However, this would require data coming from an experimental design in which inner speech and non-inner speech conditions would be manipulated within-subject and with multiple observations for each participants in each condition [e.g., as in @nalborczyk_can_2020].
-
-## Relating the subjective inner experience to the psychophysiological correlates
-
-"Independent t-tests revealed that inner speech in the rumination condition was rated as more Condensed if it was engaged in first, compared to if it was completed second (t(29) = 3.237, p = 0.003, d = 1.163).
-The rumination condition was rated as involving more Positive inner speech by those who engaged in rumination first, compared to those who completed rumination second (t(29) = 2.513, p = 0.018, d = 0.903).
-In summary, rumination tended to involve more Condensed and Positive inner speech if engaged in first".
-
-```{r reports, eval = FALSE}
-# reshaping from wide to long
-EMG <- df %>%
-    select(ID, order = Order, RUM_FRO_MAX_ln:BAS_OOI_MAX_ln) %>%
-    na.omit %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = starts_with(c("RUM", "DIS", "BAS") ),
-        names_to = "condition",
-        # names_prefix = "wk",
-        values_to = "EMG",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = condition,
-        into = c("condition", "muscle"),
-        sep = "_", extra = "merge"
-        ) %>%
-    # extracts muscle name
-    mutate(muscle = substr(muscle, 1, 3) )
-
-ESM <- df %>%
-    select(ID, order = Order, DIS_Future:RUM_Thoughts) %>%
-    na.omit %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = starts_with(c("RUM", "DIS") ),
-        names_to = "condition",
-        # names_prefix = "wk",
-        values_to = "ESM",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = condition,
-        into = c("condition", "esm_scale"),
-        sep = "_", extra = "merge"
-        )
-
-VISQ <- df %>%
-    select(ID, order = Order, starts_with("VISQ") ) %>%
-    na.omit %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = starts_with("VISQ"),
-        names_to = "visq_item",
-        # names_prefix = "wk",
-        values_to = "visq_value",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = visq_item,
-        into = c("visq_item", "condition"),
-        sep = "_(?=[^_]+$)"
-        # sep = "_", extra = "merge"
-        )
-
-# MOOD <- df %>%
-#     select(ID, order = Order, PANAS_T1:VAS_Sad_T2) %>%
-#     na.omit
-
-VAS <- df %>%
-    select(ID, order = Order, VAS_Feelings_RUM:VAS_Problems_DIS) %>%
-    na.omit %>%
-    # reshapes data from wide to long format
-    pivot_longer(
-        cols = starts_with("VAS"),
-        names_to = "vas_item",
-        # names_prefix = "wk",
-        values_to = "vas_value",
-        values_drop_na = TRUE
-        ) %>%
-    separate(
-        col = vas_item,
-        into = c("vas_item", "condition"),
-        sep = "_(?=[^_]+$)"
-        # sep = "_", extra = "merge"
-        )
-
-df3 <- bind_cols(c(EMG, ESM, VAS, VISQ) )
-```
-
--->
 
@@
 Second, we highlighted that the frequentist properties of Bayesian tools (e.g., Bayes factors) provide an important piece of information that may help design more informative studies.
-Third, sensitivity analyses further suggested that various prior specifications may lead to different resulting Bayes factors.
+Third, sensitivity analyses further suggested that various prior specifications may lead to widely different Bayes factors.
 
@@
 
-<!--
-
-Moreover, supplementary analyses showed that the order of the conditions participants went through may have influenced the effects of the rumination induction on the EMG correlates.
-Finally, important under-explored inter-individual variability suggests that important determinants of these correlates were not taken into account.
-
--->
-
 # Acknowledgements {-}
@@
 We thank Antonio Schettino for suggesting to include the "Dance of the Bayes factors" simulation and for providing helpful comments on a previous version of this manuscript.
-Thanks to Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
+We also thank Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
 
@@
 
-This project did not benefit from any specific funding.
+This work, partly carried out within the Institut Convergence ILCB (ANR-16-CONV-0002), has benefited from support from the French government, managed by the French National Agency for Research (ANR) and the Excellence Initiative of Aix-Marseille University (A*MIDEX).
 
@@
 
-Reproducible code for the manuscript, analyses, and figures is available at [https://osf.io/ba3gk/](https://osf.io/ba3gk/).
+The full code used to produce the manuscript, analyses, and figures, is available at [https://osf.io/ba3gk/](https://osf.io/ba3gk/).
 

### 2022-02-11 manuscript.tex
minor updates
manucript second revision

@@
 \documentclass[
-  english,
-  man, donotrepeattitle,mask,floatsintext]{apa6}
-\title{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): What can we learn from an under-powered absence of difference?}
-\author{Ladislas Nalborczyk\textsuperscript{1, 2, 3}}
-\date{}
-
+  man, donotrepeattitle,floatsintext]{apa6}
 \usepackage{amsmath,amssymb}
@@
 \newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
+\ifLuaTeX
+\usepackage[bidi=basic]{babel}
+\else
+\usepackage[bidi=default]{babel}
+\fi
+\babelprovide[main,import]{english}
+% get rid of language-specific shorthands (see #6817):
+\let\LanguageShortHands\languageshorthands
+\def\languageshorthands#1{}
 % Manuscript styling
@@
 % \newenvironment{ltable}
-%   {\begin{landscape}\centering\begin{threeparttable}}
-%   {\end{threeparttable}\end{landscape}}
-\newenvironment{lltable}{\begin{landscape}\centering\begin{ThreePartTable}}{\end{ThreePartTable}\end{landscape}}
+%   {\begin{landscape}\begin{center}\begin{threeparttable}}
+%   {\end{threeparttable}\end{center}\end{landscape}}
+\newenvironment{lltable}{\begin{landscape}\begin{center}\begin{ThreePartTable}}{\end{ThreePartTable}\end{center}\end{landscape}}
 
@@
 \makeatother
-\shorttitle{The absence of evidence fallacy}
-\keywords{NHST, Bayes factor, reanalysis, inner speech, rumination, electromyography}
+
+\usepackage{xpatch}
+\makeatletter
+\xapptocmd\appendix
+  {\xapptocmd\section
+    {\addcontentsline{toc}{section}{\appendixname\ifoneappendix\else~\theappendix\fi\\: #1}}
+    {}{\InnerPatchFailed}%
+  }
+{}{\PatchFailed}
+\keywords{NHST, Bayes factor, reanalysis, inner speech, rumination, electromyography\newline\indent Word count: 3152 (excluding abstract, references, tables, and figures)}
 \usepackage{lineno}
@@
 \usepackage{csquotes}
-\ifXeTeX
-  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
-  \usepackage{polyglossia}
-  \setmainlanguage[]{english}
-\else
-  \usepackage[main=english]{babel}
-% get rid of language-specific shorthands (see #6817):
-\let\LanguageShortHands\languageshorthands
-\def\languageshorthands#1{}
-\fi
 \ifLuaTeX
@@
 
+\title{Re-analysing the data from Moffatt et al. (\protect\hyperlink{ref-moffatt_inner_2020}{2020}): What can we learn from an under-powered absence of difference?}
+\author{Ladislas Nalborczyk\textsuperscript{1, 2, 3}}
+\date{}
+
+\shorttitle{The absence of evidence fallacy}
+
+\authornote{
+
+Correspondence concerning this article should be addressed to Ladislas Nalborczyk, LPC, CNRS, Aix-Marseille University, 13 Boulevard Gustave Desplaces, 13003 Marseille, France.
+E-mail: \href{mailto:ladislas.nalborczyk@univ-amu.fr}{\nolinkurl{ladislas.nalborczyk@univ-amu.fr}}
+
+}
+
 \affiliation{\vspace{0.5cm}\textsuperscript{1} Univ.
@@
 
-\abstract{
-\protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
-Based on the absence of significant difference in the perioral muscular activity between the rumination and distraction conditions, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
-We suggest this conclusion is at best hasty.
-Indeed, concluding on the absence of an effect based on an under-powered non-significant \emph{p}-value is strongly uninformative.
-In this short commentary, we show that there is limited evidence for the main conclusion put forward by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-We suggest ways forward, both from a theoretical and methodological perspective.
+\abstract{%
+Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the results of an experiment (N = 26 in the final sample) comparing the facial electromyographic correlates of mental rumination and distraction, following an experimentally induced stressor.
+Based on the absence of significant difference (and BFs between 3.6 and 4.3) in the perioral muscular activity between the rumination and distraction conditions, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) concluded that \emph{self-reported} inner experience was unrelated to peripheral muscular activity as assessed using surface electromyography.
+In this short commlentary, we show that there is limited evidence for the main conclusion put forward by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), and we suggest ways forward, both from a theoretical and a methodological perspective.
 Complete source code, reproducible analyses, and figures are available at \url{https://osf.io/ba3gk/}.
@@
 \maketitle
-
-Wordcount (excluding abstract, references, tables, and figures): 3168
-
-\newpage
 
@@
 
-Given the predominantly verbal nature of rumination (e.g., \protect\hyperlink{ref-ehring_repetitive_2008}{Ehring \& Watkins, 2008}; \protect\hyperlink{ref-goldwin_concreteness_2013}{Goldwin et al., 2013}; \protect\hyperlink{ref-goldwin_concreteness_2012}{Goldwin \& Behar, 2012}; \protect\hyperlink{ref-mclaughlin_effects_2007}{McLaughlin et al., 2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols (e.g., \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}; \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}, \protect\hyperlink{ref-nalborczyk_articulatory_2020}{2020}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
+Given the predominantly verbal nature of rumination (e.g., \protect\hyperlink{ref-ehring_repetitive_2008}{Ehring \& Watkins, 2008}; \protect\hyperlink{ref-goldwin_concreteness_2013}{Goldwin et al., 2013}; \protect\hyperlink{ref-goldwin_concreteness_2012}{Goldwin \& Behar, 2012}; \protect\hyperlink{ref-mclaughlin_effects_2007}{McLaughlin et al., 2007}), we previously proposed to consider rumination as a form of inner speech and to study it using the methods that have historically been used to study other forms of inner speech, namely, by using surface electromyography (EMG) and motor interference protocols (e.g., \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}; \protect\hyperlink{ref-nalborczyk_articulatory_2022}{Nalborczyk et al., 2022}, \protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}; \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk, 2019}).
 We first showed that induced rumination was accompanied by increased facial (both over a forehead and a perioral site) muscular activity in comparison to a rest period (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al., 2017}).
@@
 Therefore, we ran a follow-up study comparing verbal to non-verbal rumination, which suggested that the facial EMG correlates we had previously identified were not specifically related to the verbal content of the ruminative thoughts (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al., 2021}).
-We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion of \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}) and more extensively in \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+We discussed these findings in length and proposed several theoretical interpretations that can account for these results in the discussion of Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}) and more extensively in Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 
-\protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed an experiment with the aim of refining our understanding of the involvement of the speech motor system in different varieties of inner speech and clarifying the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
+Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed an experiment with the aim of refining our understanding of the involvement of the speech motor system in different varieties of inner speech and clarifying the relation between the peripheral correlates of inner speech and (self-reported) subjective experience.
 Their main conclusion is that inner experience between induced rumination and distraction differs ``without a change in electromyographic correlates of inner speech'' (p.1).
-In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented mostly by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
+In other words, they suggest that the subjective experience of inner speech is unrelated (or loosely related) to the electromyographic correlates of inner speech, which are thought to be represented by the EMG amplitude recorded over the orbicularis oris inferior and orbicularis oris superior muscles.
 However, for this in-sample observation to be of interest in an out-of-sample context (i.e., to be informative for other non-observed individuals, or said otherwise, to bring information about the population), this absence of difference should be substantiated by adequately-powered statistical tests (given the target effect size) as well as reliable measures.
@@
 
-\hypertarget{re-analysing-the-data-from-moffatt_inner_2020}{%
-\section{\texorpdfstring{Re-analysing the data from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020})}{Re-analysing the data from Moffatt et al.
-(2020)}}\label{re-analysing-the-data-from-moffatt_inner_2020}}
+\hypertarget{reconsidering-the-data-from-moffatt_inner_2020}{%
+\section{\texorpdfstring{Reconsidering the data from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020})}{Reconsidering the data from Moffatt et al.
+(2020)}}\label{reconsidering-the-data-from-moffatt_inner_2020}}
 
@@
 
-As typical in studies manipulating induced rumination, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
+As typical in studies manipulating induced rumination, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) designed a two-step protocol.
 First, they aimed to induce a negative mood by asking participants to solve unsolvable or excessively difficult anagram and subtraction tasks.
@@
 However, the average natural logarithm of the EMG peak amplitude recorded over the OOI and OOS muscles was higher than baseline in both the rumination and distraction conditions, with a slight increase from distraction to rumination (both on the mean and median).
-Having described the data collected by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of some problems related to conclusions that can be made from under-powered non-significant results.
+Having described the data collected by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), we now turn to a discussion of some problems related to conclusions that can be made from under-powered non-significant results.
 
@@
 There is an infamous tradition of conducting and interpreting uninformative null-hypothesis significance tests in Psychology (e.g., \protect\hyperlink{ref-meehl_appraising_1990-1}{Meehl, 1990a}, \protect\hyperlink{ref-meehl_theory-testing_1967}{1967}, \protect\hyperlink{ref-meehl_theoretical_1978}{1978}, \protect\hyperlink{ref-meehl_why_1990}{1990b}, \protect\hyperlink{ref-harlow_problem_1997}{1997}).
-By ``uninformative,'' we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
+By ``uninformative'', we mean that some null-hypothesis significance tests are simply not diagnostic with regards to the substantive effect of interest (e.g., whether there is a difference between conditions A and B).
 
@@
 This observation occurred.
-Therefore, the null hypothesis is false (or has low probability).'' In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
+Therefore, the null hypothesis is false (or has low probability)''.
+In short, this argument is fallacious because it fails to consider the (probability of the data under the) alternative hypothesis.
 
@@
 
-\hypertarget{enthusiastic-prior-specifications}{%
-\subsection{Enthusiastic prior specifications}\label{enthusiastic-prior-specifications}}
+\hypertarget{optimistic-a-priori-power-analysis}{%
+\subsection{Optimistic a priori power analysis}\label{optimistic-a-priori-power-analysis}}
 
-Anticipating the legitimate critiques on the power of their study, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
-This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} as estimated in \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
+Anticipating the legitimate critiques on the power of their study, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) report the results of a power analysis using the effect size reported in Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) of \(d = 0.72\).
+This represents a highly optimistic estimate of the substantive effect of interest (i.e., the difference in the natural logarithm of the EMG peak amplitude between the rumination and distraction conditions) as this effect represents the standardised mean difference in EMG amplitude \emph{between a rest and a rumination periods} as estimated in Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}).
 
@@
 
-We suggest the (a priori) power of the study ran by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
+We suggest the (a priori) power of the study ran by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was much lower than suggested by the authors.
 Indeed, we speculate that the standardised mean difference in EMG peak amplitude between the rumination and distraction conditions may be much weaker than the standardised mean difference in EMG amplitude between the rumination and rest conditions.
-If we assume that the former is half the size of the latter, therefore the a priori power of the main statistical test from \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
-Notice that whereas taking half the effect size of \protect\hyperlink{ref-nalborczyk_orofacial_2017}{Nalborczyk et al.} (\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
+If we assume that the former is half the size of the latter, therefore the a priori power of the main statistical test from Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) was around \(0.42\), meaning that they had less than 1 chance out of 2 to find a significant effect (given that the population effect size was actually \(0.36\)).
+Notice that whereas taking half the effect size of Nalborczyk et al.
+(\protect\hyperlink{ref-nalborczyk_orofacial_2017}{2017}) may seem arbitrary, Figure \ref{fig:power} shows that a one-sample t-test with a sample size of \(N = 26\) is under-powered for a vast range of effect sizes.
 
@@
 
-Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis (p.12):
+Once again, anticipating the legitimate critique that the absence of a significant difference is not necessarily ``significant'' evidence for the absence of an effect, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) reported the following Bayes factor (BF) analysis (p.12):
 
@@
 The red vertical dashed line indicates the value of the BF computed for the OOI by Moffatt et al.
-(2020), on the log scale.}\label{fig:bf-dance}
+(2020), on the logarithmic scale.
+The grey shaded area represents the conventional (but questionable) interval in which BFs are usually considered as inconclusive.}\label{fig:bf-dance}
 \end{figure}
@@
 As shown in Figure \ref{fig:bf-dance}, the distribution of log-BFs computed under each hypothesis reveals important inter-simulation variability.
-For instance, under the null hypothesis, 7.18\% of the computed log-BFs are above 0 and hence support the alternative hypothesis (although the ``true'' effect size is \(d = 0\)).
-When the ``true'' effect size is of \(d = 0.36\), 71.69\% of the log-BFs are below 0 and hence support the null hypothesis (although the true effect size is actually non-null).
-When the ``true'' effect size is of \(d = 0.72\), 25.26\% of the log-BFs are still below 0.
-In other words, for small sample and effect sizes, BFs have high error rates.
-To assess the extent to which the BF computed for the OOI by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) (i.e., \(\text{BF}_{10} = 0.278\)) is ``surprising'' given or ``compatible'' with some effect size, we can compute the proportion of simulated BFs that are equal or more extreme than the one reported by the authors for each hypothesis, which is approximately equal to 0.57, 0.28, and 0.04, for the hypothesis of \(d = 0\), \(d = 0.36\), and \(d = 0.72\), respectively.
-In other words, observing a \(\text{BF}_{10} = 0.278\) is more compatible with the hypothesis of \(d = 0\) (i.e., the null hypothesis) than with the hypothesis of \(d = 0.36\) or \(d = 0.72\), for this sample size.
+For instance, 29.60\% of the computed log-BFs under the null hypothesis are ``inconclusive'' and 1.88\% of the log-BFs support the alternative hypothesis (although the population effect size is \(d = 0\)).
+When the population effect size is of \(d = 0.36\), 49.97\% of the computed log-BFs are ``inconclusive'' and 37.50\% of the log-BFs support the null hypothesis (although the population effect size is actually non-null).
+When the population effect size is of \(d = 0.72\), 41.65\% of the computed log-BFs are ``inconclusive'' and 6.41\% of the log-BFs support the null hypothesis.
+In brief, this simulations shows that for small sample and effect sizes, BFs have non-negligible error rates (see also \protect\hyperlink{ref-schonbrodt_sequential_2017}{Schönbrodt et al., 2017}).\footnote{It should be noted that, as stressed by Rouder (\protect\hyperlink{ref-rouder_optional_2014}{2014}), Bayes factors indicate the relative evidence for a hypothesis, conditional on some observed data.
+In other words, Bayesian updating is not conditional on some hypothetical truth.
+With this in mind, the present simulation aims at illustrating how the frequentist properties of BFs may be used to design more informative studies (see also \protect\hyperlink{ref-schonbrodt_bayes_2018}{Schönbrodt \& Wagenmakers, 2018}), while acknowledging that proper long-term error rates \emph{control} is not the realm of the Bayesian framework.}
 
-The problems we discussed previously about the interpretation of under-powered non-significant results also apply to the test \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) performed about the effect or the conditions' order.
-In \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
+The problems discussed above about the interpretation of under-powered non-significant results also apply to the test Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) performed regarding the effect or the conditions' order.
+In Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we manipulated the modality of rumination (whether it is verbal or non-verbal) in a between-subject manner to avoid order effects and to avoid dissipating the effects of the negative mood induction.
 More precisely, we assumed that inducing rumination after a distraction condition in a within-subject manner would dissipate the effects of the mood induction and therefore reduce the impact of the rumination induction.
-In contrast to this approach, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
-Anticipating again that the order of the within-subject conditions may be an issue, \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
+In contrast to this approach, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) asked participants to ruminate and then distract themselves (or reciprocally), after an induced stressor (an induced failure).
+Anticipating again that the order of the within-subject conditions may be an issue, Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) say:
 
@@
 However, defining sound prior distributions for the alternative hypothesis is notoriously difficult (for some guidance, see for instance \protect\hyperlink{ref-dienes_obtaining_2021}{Dienes, 2021}, \protect\hyperlink{ref-dienes_how_2019}{2019}).
-In Figure \ref{fig:sensitivity}, we report the result of \emph{sensitivity analyses}, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
+In Figure \ref{fig:sensitivity}, we report the results of prior \emph{sensitivity analyses}, depicting the value of the BF in favour of the alternative hypothesis (relative to the null hypothesis) for the difference between the distraction and rumination conditions, under various prior specifications, for each muscle.
 
@@
 (2020).
-The gray shaded area represents the conventional (but questionable) interval in which BFs are usually considered as negligible (i.e., from 1/3 to 3).}\label{fig:sensitivity}
+The grey shaded area represents the conventional (but questionable) interval in which BFs are usually considered as inconclusive.}\label{fig:sensitivity}
 \end{figure}
 
-This figure strikingly reveals large variability in the resulting BF with varying prior specification.
+This figure strikingly reveals large variability in the resulting BF with various prior specifications.
 More precisely, when the scale (width) of the prior put on the standardised effect size is changed (along the x-axis), the BF changes accordingly.
@@
 
-With this short paper, we aimed to nuance the strong conclusion made by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
-First, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
-Because the statistical tests conducted by \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
+With this short paper, we aimed to nuance the strong conclusion made by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who asserted that the inner experience of rumination was not related to its peripheral muscular correlates.
+First, we discussed the statistical and epistemological reasons that cast doubt upon the main conclusion of Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}).
+Because the statistical tests conducted by Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}) were heavily under-powered, they provide only weak evidence for an absence of difference between conditions.
 Second, we highlighted that the frequentist properties of Bayesian tools (e.g., Bayes factors) provide an important piece of information that may help design more informative studies.
-Third, sensitivity analyses further suggested that various prior specifications may lead to different resulting Bayes factors.
+Third, sensitivity analyses further suggested that various prior specifications may lead to widely different Bayes factors.
 
@@
 
-In \protect\hyperlink{ref-nalborczyk_dissociating_2021}{Nalborczyk, Banjac, et al.} (\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (\protect\hyperlink{ref-watkins_habit-goal_2014}{Watkins \& Nolen-Hoeksema, 2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
+In Nalborczyk, Banjac, et al.
+(\protect\hyperlink{ref-nalborczyk_dissociating_2021}{2021}), we suggested that this observation was coherent with the mental-habit view of depressive rumination (\protect\hyperlink{ref-watkins_habit-goal_2014}{Watkins \& Nolen-Hoeksema, 2014}), which defines rumination as a habitual behaviour, automatically triggered by contextual cues such as negative mood.
 We know habitual behaviours are more automatic (i.e., they are not intentionally initiated) than non-habitual behaviours.
@@
 Cohen, 1986}; \protect\hyperlink{ref-sokolov_inner_1972}{Sokolov, 1972}).
-According to \protect\hyperlink{ref-cohen_motor_1986}{B.
+According to B.
 H.
-Cohen} (\protect\hyperlink{ref-cohen_motor_1986}{1986}), the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
+Cohen (\protect\hyperlink{ref-cohen_motor_1986}{1986}), the presence of peripheral motor activity during inner speech production may be interpreted in terms of attention sharing.
 For instance, in novel (hence non-automatic) or difficult situations, the vividness of inner speech may be strengthened by increasing the speech motor activity, resulting in more salient auditory percepts.
@@
 Whether the physiological correlates of automatic versus non-automatic (deliberate) forms of inner speech differ because of inhibitory constraints or because they rely on different processes (e.g., prediction-by-association or prediction-by-simulation) remains an open empirical question.
-We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of \protect\hyperlink{ref-nalborczyk_understanding_2019}{Nalborczyk} (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
+We previously discussed these issues in more length and suggested ways forward from an experimental perspective in the discussion of Nalborczyk (\protect\hyperlink{ref-nalborczyk_understanding_2019}{2019}).
 
-To conclude, we wish to bring some nuance to the conclusion of \protect\hyperlink{ref-moffatt_inner_2020}{Moffatt et al.} (\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction'' (p.14).
+To conclude, we wish to bring some nuance to the conclusion of Moffatt et al.
+(\protect\hyperlink{ref-moffatt_inner_2020}{2020}), who stated that ``In conclusion, induced rumination appeared to involve similar levels of inner speech-related muscle activity to a period of distraction'' (p.14).
 In consideration of the limitations discussed in the present article, this conclusion seems hasty.
 Indeed, we provided theoretical (epistemological) and empirical (via simulation and sensitivity analyses) reasons to doubt the strength of the evidence in favour of the null hypothesis in this study.
-This commentary stresses the importance of planning adequately-powered studies of induced rumination, and the need for more thoughtful statistical analyses and data interpretation, as recommended by \protect\hyperlink{ref-wasserstein_moving_2019}{Wasserstein et al.} (\protect\hyperlink{ref-wasserstein_moving_2019}{2019}).
+This commentary stresses the importance of planning adequately-powered studies of induced rumination, and the need for more thoughtful statistical analyses and data interpretation, as recommended by Wasserstein et al.
+(\protect\hyperlink{ref-wasserstein_moving_2019}{2019}).
 
@@
 We thank Antonio Schettino for suggesting to include the ``Dance of the Bayes factors'' simulation and for providing helpful comments on a previous version of this manuscript.
-Thanks to Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
+We also thank Daniel Lakens and two anonymous reviewers for valuable comments on previous versions of this manuscript.
 
@@
 
-Reproducible code for the manuscript, analyses, and figures is available at \url{https://osf.io/ba3gk/}.
+The full code used to produce the manuscript, analyses, and figures, is available at \url{https://osf.io/ba3gk/}.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-cohen_motor_1986}{}}%
-Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. {Springer, Boston, MA}.
+Cohen, B. H. (1986). The motor theory of voluntary thinking. In R. J. Davidson, G. E. Schartz, \& D. Shapiro (Eds.), \emph{Consciousness and self-regulation}. Springer, Boston, MA.
 
 \leavevmode\vadjust pre{\hypertarget{ref-cohen_earth_1994}{}}%
-Cohen, J. (1994). The earth is round (p {\(<\)} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
+Cohen, J. (1994). The earth is round (p {\textless{}} .05). \emph{American Psychologist}, \emph{49}(12), 997--1003. \url{https://doi.org/10.1037/0003-066X.49.12.997}
 
 \leavevmode\vadjust pre{\hypertarget{ref-dienes_obtaining_2021}{}}%
-Dienes, Z. (2021). Obtaining {Evidence} for {No Effect}. \emph{Collabra: Psychology}, \emph{7}(1), 28202. \url{https://doi.org/10.1525/collabra.28202}
+Dienes, Z. (2021). Obtaining {Evidence} for {No} {Effect}. \emph{Collabra: Psychology}, \emph{7}(1), 28202. \url{https://doi.org/10.1525/collabra.28202}
 
 \leavevmode\vadjust pre{\hypertarget{ref-dienes_how_2019}{}}%
-Dienes, Z. (2019). How {Do I Know What My Theory Predicts}? \emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 364--377. \url{https://doi.org/10.1177/2515245919876960}
+Dienes, Z.
+(2019).
+How {Do} {I} {Know} {What} {My} {Theory} {Predicts}?
+\emph{Advances in Methods and Practices in Psychological Science}, \emph{2}(4), 364--377.
+\url{https://doi.org/10.1177/2515245919876960}
 
@@
 (2019).
-The {ConDialInt Model}: Condensation, {Dialogality}, and {Intentionality Dimensions} of {Inner Speech Within} a {Hierarchical Predictive Control Framework}.
+The {ConDialInt} {Model}: {Condensation}, {Dialogality}, and {Intentionality} {Dimensions} of {Inner} {Speech} {Within} a {Hierarchical} {Predictive} {Control} {Framework}.
 \emph{Frontiers in Psychology}, \emph{10}.
@@
 Langland-Hassan \& A.
-Vicente (Eds.), \emph{Inner speech: New voices} (p.
+Vicente (Eds.), \emph{Inner speech: {New} voices} (p.
 37).
-{Oxford University Press}.
+Oxford University Press.
 
@@
 1--47).
-{Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc}.
+Hillsdale, NJ, US: Lawrence Erlbaum Associates, Inc.
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-mayo_statistical_2018}{}}%
-Mayo, D. G. (2018). \emph{Statistical {Inference} as {Severe Testing}: How to {Get Beyond} the {Statistics Wars}}. {Cambridge University Press}. \url{https://doi.org/10.1017/9781107286184}
+Mayo, D. G. (2018). \emph{Statistical {Inference} as {Severe} {Testing}: {How} to {Get} {Beyond} the {Statistics} {Wars}}. Cambridge University Press. \url{https://doi.org/10.1017/9781107286184}
 
@@
 (2006).
-Severe {Testing} as a {Basic Concept} in a {Neyman}--{Pearson Philosophy} of {Induction}.
+Severe {Testing} as a {Basic} {Concept} in a {Neyman}--{Pearson} {Philosophy} of {Induction}.
 \emph{The British Journal for the Philosophy of Science}, \emph{57}(2), 323--357.
@@
 (1990a).
-Appraising and {Amending Theories}: The {Strategy} of {Lakatosian Defense} and {Two Principles} that {Warrant It}.
+Appraising and {Amending} {Theories}: {The} {Strategy} of {Lakatosian} {Defense} and {Two} {Principles} that {Warrant} {It}.
 \emph{Psychological Inquiry}, \emph{1}(2), 108--141.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-meehl_theory-testing_1967}{}}%
-Meehl, P. E. (1967). Theory-testing in {Psychology} and {Physics}: A methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
+Meehl, P. E. (1967). Theory-testing in {Psychology} and {Physics}: {A} methodological paradox. \emph{Philosophy of Science}, \emph{34}(2), 103--115. \url{https://doi.org/10.1086/288135}
 
@@
 (1978).
-Theoretical risks and tabular asterisks: Sir {Karl}, {Sir Ronald}, and the slow progress of soft psychology.
+Theoretical risks and tabular asterisks: {Sir} {Karl}, {Sir} {Ronald}, and the slow progress of soft psychology.
 \emph{Journal of Consulting and Clinical Psychology}, \emph{46}(4), 806--834.
@@
 \leavevmode\vadjust pre{\hypertarget{ref-meehl_why_1990}{}}%
-Meehl, P. E. (1990b). Why {Summaries} of {Research} on {Psychological Theories} are {Often Uninterpretable}. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
+Meehl, P. E. (1990b). Why {Summaries} of {Research} on {Psychological} {Theories} are {Often} {Uninterpretable}. \emph{Psychological Reports}. \url{https://doi.org/10.2466/pr0.1990.66.1.195}
 
@@
 (1997).
-The problem is epistemology, not statistics: Replace significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
+The problem is epistemology, not statistics: {Replace} significance tests by confidence intervals and quantify accuracy of risky numerical predictions.
 \emph{What If There Were No Significance Tests?}, 393--425.
@@
 (2019).
-\emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}PhD thesis, {Univ.
-Grenoble Alpes \& Ghent University}{]}.
+\emph{Understanding rumination as a form of inner speech: Probing the role of motor processes} {[}\{PhD\} \{Thesis\}, Univ.
+Grenoble Alpes \& Ghent University{]}.
 \url{https://thesiscommons.org/p6dct/}
@@
 \emph{The role of motor inhibition during covert speech production} {[}Preprint{]}.
-{PsyArXiv}.
+PsyArXiv.
 \url{https://doi.org/10.31234/osf.io/3df57}
@@
 
-\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_articulatory_2020}{}}%
+\leavevmode\vadjust pre{\hypertarget{ref-nalborczyk_articulatory_2022}{}}%
 Nalborczyk, L., Perrone-Bertolotti, M., Baeyens, C., Grandchamp, R., Spinelli, E., Koster, E.
@@
 W., \& Lœvenbruck, H.
-(2020).
-\emph{Articulatory suppression effects on induced rumination} {[}Under review{]}.
-Under review.
-\url{https://psyarxiv.com/5d6h7/}
+(2022).
+Articulatory {Suppression} {Effects} on {Induced} {Rumination}.
+\emph{Collabra: Psychology}, \emph{8}(1), 31051.
+\url{https://doi.org/10.1525/collabra.31051}
 
@@
 \leavevmode\vadjust pre{\hypertarget{ref-pollard_probability_1987}{}}%
-Pollard, P., \& Richardson, J. T. (1987). On the probability of making {Type I} errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
+Pollard, P., \& Richardson, J. T. (1987). On the probability of making {Type} {I} errors. \emph{Psychological Bulletin}, \emph{102}(1), 159--163. \url{https://doi.org/10.1037/0033-2909.102.1.159}
 
@@
 R Core Team. (2017). \emph{R: A language and environment for statistical computing}. R Foundation for Statistical Computing. \url{https://www.R-project.org/}
+
+\leavevmode\vadjust pre{\hypertarget{ref-rouder_optional_2014}{}}%
+Rouder, J. N. (2014). Optional stopping: {No} problem for {Bayesians}. \emph{Psychonomic Bulletin \& Review}, \emph{21}(2), 301--308. \url{https://doi.org/10.3758/s13423-014-0595-4}
 
@@
 (2016).
-Is {There} a {Free Lunch} in {Inference}?
+Is {There} a {Free} {Lunch} in {Inference}?
 \emph{Topics in Cognitive Science}, \emph{8}(3), 520--547.
@@
 
+\leavevmode\vadjust pre{\hypertarget{ref-schonbrodt_bayes_2018}{}}%
+Schönbrodt, F.
+D., \& Wagenmakers, E.-J.
+(2018).
+Bayes factor design analysis: {Planning} for compelling evidence.
+\emph{Psychonomic Bulletin \& Review}, \emph{25}(1), 128--142.
+\url{https://doi.org/10.3758/s13423-017-1230-y}
+
+\leavevmode\vadjust pre{\hypertarget{ref-schonbrodt_sequential_2017}{}}%
+Schönbrodt, F.
+D., Wagenmakers, E.-J., Zehetleitner, M., \& Perugini, M.
+(2017).
+Sequential hypothesis testing with {Bayes} factors: {Efficiently} testing mean differences.
+\emph{Psychological Methods}, \emph{22}(2), 322--339.
+\url{https://doi.org/10.1037/met0000061}
+
 \leavevmode\vadjust pre{\hypertarget{ref-sokolov_inner_1972}{}}%
-Sokolov, A. (1972). \emph{Inner speech and thought}. {Springer-Verlag}.
+Sokolov, A. (1972). \emph{Inner speech and thought}. Springer-Verlag.
 
@@
 (2019).
-Moving to a world beyond {`` {\emph{p}} {\(<\)} 0.05.''} \emph{The American Statistician}, \emph{73}, 1--19.
+Moving to a world beyond {`` \emph{p} {\textless{}} 0.05.''} \emph{The American Statistician}, \emph{73}(sup1), 1--19.
 \url{https://doi.org/10.1080/00031305.2019.1583913}
